# Age mixing (#age_mixing)

```{r, include=FALSE}
####################################################################################
# Setup
####################################################################################
#-----------------------------------------------------------------------------------
# Load packages
#-----------------------------------------------------------------------------------

    library("tidyverse")
    library("knitr")
    library("kableExtra")
    library("data.table")
    library("survey")

#-----------------------------------------------------------------------------------
# Knitr options
#-----------------------------------------------------------------------------------
opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE)
options(knitr.table.format = "html") 

#-----------------------------------------------------------------------------------
# Load data
#-----------------------------------------------------------------------------------

    load(file="Data/InternetSurveySample.Rdata")
    load(file="Data/rate.inst.fullpop.Rdata")
    load(file="Data/degreedists.Rdata")
    load(file = "Data/whpp_artnet.Rdata")
    load(file="/homes/dpwhite/win/project/MMP_WADOH/mmp_reweighted.Rdata")
    load(file = "/homes/dpwhite/win/project/MMP_WADOH/whpp_mmp.Rdata")

# Determine which of the MMP alter age vars to use (low, mid, or high estimate)
  whpp_mmp$variables$mrp_ageinyrs[whpp_mmp$variables$hiv %in% 1] <- whpp_mmp$variables$mrp_age_mid[whpp_mmp$variables$hiv %in% 1]
    
#-----------------------------------------------------------------------------------
# Plot settings
#-----------------------------------------------------------------------------------
plot_background <- theme(panel.background = element_rect(fill="white", colour = "black")) +
            theme(panel.grid.major = element_line(colour = "grey90"))
theme_title <- theme(plot.title = element_text(hjust = 0.5, size=12)) 

## Function to prepare mixing matrix data for plots
mixplot_age <- function(mm){
    
    # make it long format
    mm$ego <- rownames(mm)
    
    mm.l <- melt(mm, id="ego")
    names(mm.l)[names(mm.l) == "variable"] <- "alter"
    mm.l$ego <- as.numeric(mm.l$ego)
    mm.l$alter <- as.numeric(as.character(mm.l$alter))
    
    ## Collapse to 5/10-year age groups
    mm.l <- within(mm.l, {
        ego.cat <- cut(ego, c(17, 24, 29, 34, 39, 49, 59), labels=c("18-24", "25-29", "30-34", "35-39", "40-49", "50-59"))
        alter.cat <- cut(alter, c(17, 24, 29, 34, 39, 49, 59), labels=c("18-24", "25-29", "30-34", "35-39", "40-49", "50-59"))
    })
    
    mm.agecat <- mm.l %>% group_by(ego.cat, alter.cat) %>% summarise(count = sum(value))
    
    # Cast back to wide format
    obs <- dcast(mm.agecat, ego.cat ~ alter.cat, value.var = "count")
    obs$ego.cat <- factor(obs$ego.cat, levels = c("18-24", "25-29", "30-34", "35-39", "40-49", "50-59"))
    obs <- arrange(obs, ego.cat)
    rownames(obs) <- obs$ego.cat
    obs <- obs[,-1]

    # Calculate alphaij terms (observed / expected cell counts)
        nXn <- dim(obs)
        alphaij <- matrix(rep(NA, nXn[1]*nXn[2]), nrow = nXn[1])
        for(i in 1:nXn[1]){
            for(j in 1:nXn[2]){
                alphaij[i,j] <- obs[i,j] / ((sum(obs[i,])*sum(obs[,j]))/sum(obs))
            }
        }
        alphaij <- as.data.frame(alphaij, row.names = rownames(obs))
        names(alphaij) <- names(obs)
        
        # Convert to long format
        alphaij <- cbind.data.frame("ego" = rownames(alphaij), alphaij)
        alphaij_l <- melt(alphaij, id="ego")
        alphaij_l$log_alphaij <- log(alphaij_l$value)
        colnames(alphaij_l)[colnames(alphaij_l)=="variable"] <- "alter"
        
    # Observed mixing matrix as conditional row probabilities
        probs <- data.frame(matrix(rep(NA, nXn[1]*nXn[2]), nrow = nXn[1]))
        for(i in 1:nXn[1]){
            probs[i,] <- obs[i,]/sum(obs[i,]) 
        }
        probs <- as.data.frame(probs, row.names = rownames(obs))
        names(probs) <- names(obs)
    
        # Convert to long format
        probs <- cbind.data.frame("ego" = rownames(probs), probs)
        probs_l <- melt(probs, id="ego")
        colnames(probs_l)[colnames(probs_l)=="variable"] <- "alter"
        
    # Combined object to plot
        mm_plot <- cbind.data.frame(probs_l, alphaij = alphaij_l$value, log_alphaij = alphaij_l$log_alphaij)
        
        # Add column with proportion as percent to plot
        mm_plot$label <- paste0(round(mm_plot$value*100, 1),"%")
    
        # Define variable outline to outline the on-diagonal points
        mm_plot$ondiag <- ifelse(as.character(mm_plot$ego)==as.character(mm_plot$alter), 
                                 mm_plot$value, NA)
    
    # Reorder levels of ego factor so on-diagonal goes from left to right
        mm_plot$ego <- factor(mm_plot$ego, levels = rev(levels(mm_plot$ego)))
    
    return(mm_plot)
}

```

We will capture age mixing using a term to specify the absolute difference in the square root of ego and alter ages. Data on patterns of age mixing are from the WHPP sample and MMP^[MMP measured alter age in 5-year increments. Using the lower bound of the range for alter age yielded estimates of the absolute difference in the square root of ego and alter ages of 0.5442927,  0.8398329, and 0.813158 for main, persistent, and instantaneous partnerships, respectively. Using the midpoint of the range yielded estimates of 0.5383779, 0.8252217, and 0.7940946, and using the upper bound yielded estimates of 0.5351637, 0.8124105, 0.8180763. We use the mid-point of the range for target statistics. For comparison, using data from ART-Net and WHPP for age mixing, estimates were 0.5518785, 0.8413099, and 0.7753907.] samples, reweighted to Washington demographics. Since we only have data from the WHPP survey on the age of the most recent partner, we will restrict the MMP sample to the most recent partner as well, and weight the reported age mixing matrix in single years of age by the mean degree from the combined WHPP and ART-Net dataset. We will then take the averages of the off-diagonal terms to obtain a balanced matrix, which we will use to calculate the mean absolute difference between the square root of ego and alter ages. This approach is summarized below
  1. obtain the row percentages for mixing in single years of age from the ego's perspective (from WHPP and MMP data), 
  2. multiply these row percentages by the mean degree (or the mean rate of instantaneous partnerships) for egos of a given age (from WHPP and ART-Net data), 
  3. multiply this product by the target population size of each age. This will produce a weighted mixing matrix. 
  4. Balance the matrix by taking the mean of the off-diagonal elements.
  5. Obtain the target statistic by taking the square root of ego and alter ages, calculating the absolute difference for each combination of ego and alter ages, weighting these differences by the edge count in the corresponding cell in the balanced matrix, and taking the mean of the non-zero elements.

This approach assumes that mixing with the unobserved ties follows the same pattern as mixing with the observed ties, and that men who did not report on their main/persistent/instantaneous partner have the same mixing propensities as those of the same age who did report on their main/persistnet/instantaneous partner. Since we did not observe age mixing to vary meaningfully by race/ethnicity or region (section \@ref(explore_heterogeneity)), there is not an indication that we need to account for heterogeneity on these characteristics, such that this approach seems reasonable. Additionally, in section \@ref(mrp_limitations), we did not observe any differences in main partnerships reported by those with 0 compared to those with 1+ persistent partnerships, suggesting that we can use data on the most recent partnership to represent all partnerships of that type.

```{r}
####################################################
# For those with missing degree, impute main/persistent mean degree from those of same race/eth, region, and 5-year age group
####################################################

# Define age_cat variable
 whpp_artnet$variables$age_cat <- cut(whpp_artnet$variables$age, c(17, 24, 29, 34, 39, 44, 49, 54, 59), labels=c("18-24", "25-29", "30-34", "35-39", "40-44", "45-49", "50-54", "55-59"))

# Make main degree numeric
whpp_artnet$variables$degmain <- ifelse(whpp_artnet$variables$degree_main %in% "No main", 0,
                                              ifelse(whpp_artnet$variables$degree_main %in% "Main", 1,
                                                     NA))

# Make persistent degree indicator numeric, and cap it at 2 for those with 2+ since the network model caps men at 2 ongoing pers partners
whpp_artnet$variables$degpers <- ifelse(whpp_artnet$variables$degreecat_cas %in% "None", 0,
                                              ifelse(whpp_artnet$variables$degreecat_cas %in% "One", 1,
                                              ifelse(whpp_artnet$variables$degreecat_cas %in% "Two or more", 2,
                                                     NA)))

# Define numeric indicator of combined race/ethnicity, region, and age_cat group to use in the `for` loops
whpp_artnet$variables$hbo.r <- factor(whpp_artnet$variables$hbo, levels = c("Hispanic", "Black", "Other"), labels = c("h", "b", "o"))
whpp_artnet$variables$region.r <- factor(whpp_artnet$variables$region, levels = c("King County", "Western WA", "Eastern WA", "US"), labels = c("KC", "OW", "EW", "US"))
whpp_artnet$variables$age_cat.r <- factor(whpp_artnet$variables$age_cat)

whpp_artnet$variables$group <- factor(paste0(whpp_artnet$variables$hbo.r, whpp_artnet$variables$region.r, whpp_artnet$variables$age_cat.r))
whpp_artnet$variables$group.num <- as.numeric(whpp_artnet$variables$group)

# Define vectors for the imputed variables with values equal to observed if nonmissing
whpp_artnet$variables$main <- whpp_artnet$variables$degmain
whpp_artnet$variables$numpers <- whpp_artnet$variables$degpers

# Set degree to mean of 2 age groups on either side for the group that has no reported degree (Blacks in OW age 30-34)
whpp_artnet$variables$degmain[whpp_artnet$variables$group %in% "bOW30-34"] <- svymean(~degmain, whpp_artnet[whpp_artnet$variables$group %in% c("bOW25-29", "bOW35-39")], na.rm=TRUE)
whpp_artnet$variables$degpers[whpp_artnet$variables$group %in% "bOW30-34"] <- svymean(~degpers, whpp_artnet[whpp_artnet$variables$group %in% c("bOW25-29", "bOW35-39")], na.rm=TRUE)

# Deterministic imputation - set to the mean value among men of the same race/ethnicity, region, and age group
for(n in 1:length(unique(whpp_artnet$variables$group.num))){
            whpp_artnet$variables$main[is.na(whpp_artnet$variables$main) & whpp_artnet$variables$group.num %in% n] <- svymean(~degmain, whpp_artnet[whpp_artnet$variables$group.num %in% n], na.rm=TRUE)[1]
            whpp_artnet$variables$numpers[is.na(whpp_artnet$variables$numpers) & whpp_artnet$variables$group.num %in% n] <- svymean(~degpers, whpp_artnet[whpp_artnet$variables$group.num %in% n], na.rm=TRUE)[1]        
        }


```

## Main partnerships
The table below shows part of the unbalanced mixing matrix for main partnerships by age from the raked WHPP and MMP surveys, weighted by mean degree from the WHPP and ART-Net samples and scaled back to the size of the original samples. Note these counts are not integers because they are from the raked samples. 
```{r}

#Conditional row probabilities
  agemix_main <- prop.table(svytable(~age + mrp_ageinyrs, whpp_mmp[whpp_mmp$variables$mrp_type_mix %in% "Main"], round=FALSE),1)

  #Mean degree by age 
  meandegXage_main <- svyby(~main, ~age, whpp_artnet, svymean, na.rm=TRUE)[2]
   
  #N by age in reweighted sample
   ## Scaling to the total N assumes that those with missing data on degree or who didn't provide the age of their most recent partner are missing at random
   ## Allocate the number in each 5-yr age group by dividing evenly within the age groups (b/c the model assumes a flat distribution within specified age groups and samples randomly)
      n <- (dim(sample)[1] + dim(mmp_rake$variables)[1])
      agestr <- as.vector(prop.table(svytable(~age_cat, whpp_artnet, round=FALSE)))
      nXage <- n*(c(rep(agestr[1]/7, 7), rep(agestr[2]/5, 5), rep(agestr[3]/5, 5), rep(agestr[4]/5, 5), rep(agestr[5]/5, 5), rep(agestr[6]/5, 5), rep(agestr[7]/5, 5), rep(agestr[8]/5, 5)))
    
  #Reweighted mixing matrix, accounting for mean degree
    # Check that agemix_main has the same number of rows as meandegXage_main and nXage (i.e. no ages had missing values for any of these)
    if (!(dim(agemix_main)[1] == dim(meandegXage_main)[1])) {
    stop("objects must each have a row for every age")
    }
    if (!(dim(agemix_main)[1] == length(nXage))) {
    stop("objects must each have a row for every age")
    }
    if (!(dim(agemix_main)[1] == 42)) {
    stop("objects must each have a row for every age")
    }
    
    # Construct an empty data frame
    agemix_main_rwt <- as.data.frame(matrix(rep(NA, dim(agemix_main)[1]*dim(agemix_main)[2]), byrow=TRUE, nrow=dim(agemix_main)[1]))
    
    # Multiply each row in agemix_main by the corresponding n and mean degree
    for(i in 1:dim(agemix_main)[1]){
      agemix_main_rwt[i, ] <- c(agemix_main[i,]*meandegXage_main[i,1]*nXage[i])
    }
    row.names(agemix_main_rwt)=c(row.names(agemix_main))
    names(agemix_main_rwt) <- c(as.character(sort(unique(whpp_mmp$variables$mrp_ageinyrs[whpp_mmp$variables$mrp_type_mix %in% "Main"]))))
  
# Make a kable
agemix_main_rwt.kbl <- agemix_main_rwt[1:10,1:10]
kable(agemix_main_rwt.kbl, align=c(rep("c", dim(agemix_main_rwt.kbl)[2])), digits=c(rep(2, dim(agemix_main_rwt.kbl)[2]))) %>% kable_styling(full_width=F, position="center") %>% column_spec(1, bold=T, color="black", width="2cm")

```

Taking the average of the off-diagonal elements to balance the matrix, we get the following:
```{r}
# Check whether any ages are missing from the vectors or ego or alter age (i.e. make sure the matrix is symmetric)
egoages <- as.numeric(row.names(agemix_main_rwt))
alterages <- as.numeric(names(agemix_main_rwt))
mismatch <- egoages[!(egoages %in% alterages)]

# Add a column to the reweighted mixing matrix for the missing alter ages (53 and 56) containing 0s to make the matrix symmetric
agemix_main_rwt$`53` <- rep(0, dim(agemix_main_rwt)[1])
agemix_main_rwt$`56` <- rep(0, dim(agemix_main_rwt)[1])

# Reorder columns so they are in numeric order
agemix_main_rwt <- agemix_main_rwt[c("18", "19", "20", "21", "22", "23", "24", "25", "26", "27", "28", "29", "30", "31", "32", "33", "34", "35", "36", "37", "38", "39", "40", "41", "42", "43", "44", "45", "46", "47", "48", "49", "50", "51", "52", "53", "54", "55", "56", "57", "58", "59")]

# Take average of off-diagonals to balance
agemix_main_bal <- as.data.frame(matrix(c(rep(NA, dim(agemix_main_rwt)[1]*dim(agemix_main_rwt)[2])), nrow=dim(agemix_main_rwt[1])))

for(i in 1:dim(agemix_main_rwt)[1]){
  for(j in 1:dim(agemix_main_rwt)[2]){
      agemix_main_bal[i,j] <- mean(c(agemix_main_rwt[i,j],agemix_main_rwt[j,i]))
      agemix_main_bal[j,i] <- mean(c(agemix_main_rwt[i,j],agemix_main_rwt[j,i]))
  }
}
  
row.names(agemix_main_bal)=c(row.names(agemix_main_rwt))
names(agemix_main_bal) <- names(agemix_main_rwt)

# Look at implied mean degree by age from balanced matrix to see if anything looks weird
# rowSums(agemix_main_bal)/nXage

# Make a kable
agemix_main_bal.kbl <- agemix_main_bal[1:10,1:10]
kable(agemix_main_bal.kbl, align=c(rep("c", dim(agemix_main_bal.kbl)[2])), digits=c(rep(2, dim(agemix_main_bal.kbl)[2]))) %>% kable_styling(full_width=F, position="center") %>% column_spec(1, bold=T, color="black", width="2cm")

```

The plot below shows the balanced age mixing matrix, with age collapsed into 5- to 10-year age bins.
```{r fig.align="center"}
# PLOT BALANCED MIXING MATRIX

main_bal_plot <- mixplot_age(agemix_main_bal)
# Plot
ggplot(main_bal_plot, aes(x=alter, y=ego)) + 
    geom_point(aes(size = value), colour="steelblue2") + 
    geom_point(aes(size = ondiag), colour = "black", shape = 1) + 
    geom_text(aes(label = label), hjust=0.6, size=4) +
    scale_size_continuous(range = c(1,30), guide = "none") + 
    labs(x="Alter", y="Ego", title="Age mixing row conditional probabilities: Main") + 
    plot_background + theme_title 

```

To calculate the target statistic, we take the absolute difference between the square root of each combination of ego and alter ages and weight it by the count in the corresponding cell in the balanced mixing matrix. We then take the mean of the non-zero weighted differences (because cells are zero if no partnerships of that age combination were reported, which should not be included), shown below.

```{r}
# Create vectors with the square root of ego and alter ages corresponding to the rows and columns in the balanced matrix
sqrt.ego <- sqrt(as.integer(row.names(agemix_main_bal)))
sqrt.alter <- sqrt(as.integer(names(agemix_main_bal)))

# Create a matrix with the absolute differences between sqrt.ego and sqrt.alter weighted by the count in the corresponding cell in the balanced matrix
absdiff_main <- matrix(c(rep(NA, dim(agemix_main_bal)[1]*dim(agemix_main_bal)[2])), nrow=dim(agemix_main_bal[1]))

for(i in 1:dim(agemix_main_bal)[1]){
  for(j in 1:dim(agemix_main_bal)[2]){
    absdiff_main[i,j] <- abs(sqrt.ego[i]-sqrt.alter[j])*agemix_main_bal[i,j]
  }
}

# Take the mean as the sum of the values in the matrix divided by the total number of main partnerships
(mean.absdiff_main <- round(sum(absdiff_main),5) / sum(agemix_main_bal))
```

## Persistent partnerships
The table below shows part of the unbalanced mixing matrix for persistent partnerships by age from the raked WHPP and MMP surveys, weighted by mean degree from WHPP and ART-Net and scaled back to the size of the original samples. Note these counts are not integers because they are from the raked samples. 

```{r}
#Conditional row probabilities
  agemix_pers <- prop.table(svytable(~age + mrp_ageinyrs, whpp_mmp[whpp_mmp$variables$mrp_type_mix %in% "Persistent"], round=FALSE),1)

  #Mean degree by age 
  meandegXage_pers <- svyby(~numpers, ~age, whpp_artnet, svymean, na.rm=TRUE)[2]

  #No men at age 42 reported on a most recent persistent partner, so age mix matrix is empty at this age. Remove the corresponding rows from meandegXage and nXage
  meandegXage_pers <- meandegXage_pers[-(25),]
  nXage_pers <- nXage[-25]

  #Reweighted mixing matrix, accounting for mean degree
    # Check that agemix_pers has the same number of rows as meandegXage_pers and nXage 
    if (!(dim(agemix_pers)[1] == length(meandegXage_pers))) {
    stop("objects must each have a row for every age")
    }
    if (!(dim(agemix_pers)[1] == length(nXage_pers))) {
    stop("objects must each have a row for every age")
    }
    if (!(dim(agemix_pers)[1] == 41)) {
    stop("objects must each have a row for every age")
    }
    
    # Construct an empty data frame
    agemix_pers_rwt <- as.data.frame(matrix(rep(NA, dim(agemix_pers)[1]*dim(agemix_pers)[2]), byrow=TRUE, nrow=dim(agemix_pers)[1]))
    
    # Multiply each row in agemix_pers by the corresponding n and mean degree
    for(i in 1:dim(agemix_pers)[1]){
      agemix_pers_rwt[i, ] <- c(agemix_pers[i,]*meandegXage_pers[i]*nXage_pers[i])
    }
    row.names(agemix_pers_rwt)=c(row.names(agemix_pers))
    names(agemix_pers_rwt) <- c(as.character(sort(unique(whpp_mmp$variables$mrp_ageinyrs[whpp_mmp$variables$mrp_type_mix %in% "Persistent"]))))

# Replace NA cells (which resulted for ego ages where no persistent partners were named and/or the age of partners was missing) with 0
  agemix_pers_rwt[is.na(agemix_pers_rwt)] <- 0
  
# Make a kable
agemix_pers_rwt.kbl <- agemix_pers_rwt[1:10,1:10]
kable(agemix_pers_rwt.kbl, align=c(rep("c", dim(agemix_pers_rwt.kbl)[2])), digits=c(rep(2, dim(agemix_pers_rwt.kbl)[2]))) %>% kable_styling(full_width=F, position="center") %>% column_spec(1, bold=T, color="black", width="2cm")

```

Taking the average of the off-diagonal elements to balance the matrix, we get the following:
```{r}
# Check whether any ages are missing from the vectors or ego or alter age (i.e. make sure the matrix is symmetric)
egoages <- as.numeric(row.names(agemix_pers_rwt))
alterages <- as.numeric(names(agemix_pers_rwt))
mismatch1 <- egoages[!(egoages %in% alterages)]
mismatch2 <- alterages[!(alterages %in% egoages)]


# Add columns to the reweighted mixing matrix for the missing alter ages (37,43,47,49,51,53,54,57,58) containing 0s to make the matrix symmetric
agemix_pers_rwt$`37` <- rep(0, dim(agemix_pers_rwt)[1])
agemix_pers_rwt$`43` <- rep(0, dim(agemix_pers_rwt)[1])
agemix_pers_rwt$`47` <- rep(0, dim(agemix_pers_rwt)[1])
agemix_pers_rwt$`49` <- rep(0, dim(agemix_pers_rwt)[1])
agemix_pers_rwt$`51` <- rep(0, dim(agemix_pers_rwt)[1])
agemix_pers_rwt$`53` <- rep(0, dim(agemix_pers_rwt)[1])
agemix_pers_rwt$`54` <- rep(0, dim(agemix_pers_rwt)[1])
agemix_pers_rwt$`57` <- rep(0, dim(agemix_pers_rwt)[1])
agemix_pers_rwt$`58` <- rep(0, dim(agemix_pers_rwt)[1])

# Add row to the reweighted mixing matrix for the missing ego age (42) containing 0s to make the matrix symmetric
agemix_pers_rwt <- rbind.data.frame(agemix_pers_rwt, "42" = rep(0, dim(agemix_pers_rwt)[2]))


# Reorder rows and columns so they are in numeric order
agemix_pers_rwt <- agemix_pers_rwt[c("18", "19", "20", "21", "22", "23", "24", "25", "26", "27", "28", "29", "30", "31", "32", "33", "34", "35", "36", "37", "38", "39", "40", "41", "42", "43", "44", "45", "46", "47", "48", "49", "50", "51", "52", "53", "54", "55", "56", "57", "58", "59"), c("18", "19", "20", "21", "22", "23", "24", "25", "26", "27", "28", "29", "30", "31", "32", "33", "34", "35", "36", "37", "38", "39", "40", "41", "42", "43", "44", "45", "46", "47", "48", "49", "50", "51", "52", "53", "54", "55", "56", "57", "58", "59")]

# Take average of off-diagonals to balance
agemix_pers_bal <- as.data.frame(matrix(c(rep(NA, dim(agemix_pers_rwt)[1]*dim(agemix_pers_rwt)[2])), nrow=dim(agemix_pers_rwt[1])))

for(i in 1:dim(agemix_pers_rwt)[1]){
  for(j in 1:dim(agemix_pers_rwt)[2]){
      agemix_pers_bal[i,j] <- mean(c(agemix_pers_rwt[i,j],agemix_pers_rwt[j,i]))
      agemix_pers_bal[j,i] <- mean(c(agemix_pers_rwt[i,j],agemix_pers_rwt[j,i]))
  }
}
  
row.names(agemix_pers_bal)=c(row.names(agemix_pers_rwt))
names(agemix_pers_bal) <- names(agemix_pers_rwt)
  
# Look at implied mean degree by age from balanced matrix to see if anything looks weird
# rowSums(agemix_pers_bal)/nXage

# Make a kable
agemix_pers_bal.kbl <- agemix_pers_bal[1:10,1:10]
kable(agemix_pers_bal.kbl, align=c(rep("c", dim(agemix_pers_bal.kbl)[2])), digits=c(rep(2, dim(agemix_pers_bal.kbl)[2]))) %>% kable_styling(full_width=F, position="center") %>% column_spec(1, bold=T, color="black", width="2cm")

```

The plot below shows the balanced age mixing matrix, with age collapsed into 5- to 10-year age bins.
```{r fig.align="center"}
# PLOT BALANCED MIXING MATRIX

pers_bal_plot <- mixplot_age(agemix_pers_bal)

# Plot
ggplot(pers_bal_plot, aes(x=alter, y=ego)) + 
    geom_point(aes(size = value), colour="steelblue2") + 
    geom_point(aes(size = ondiag), colour = "black", shape = 1) + 
    geom_text(aes(label = label), hjust=0.6, size=4) +
    scale_size_continuous(range = c(1,30), guide = "none") + 
    labs(x="Alter", y="Ego", title="Age mixing row conditional probabilities: Persistent") + 
    plot_background + theme_title 

```

To calculate the target statistic, we take the absolute difference between the square root of each combination of ego and alter ages and weight it by the count in the corresponding cell in the balanced mixing matrix. We then take the mean of the non-zero weighted differences (because cells are zero if no partnerships of that age combination were reported, which should not be included), shown below.

```{r}
# Create vectors with the square root of ego and alter ages corresponding to the rows and columns in the balanced matrix
sqrt.ego <- sqrt(as.integer(row.names(agemix_pers_bal)))
sqrt.alter <- sqrt(as.integer(names(agemix_pers_bal)))

# Create a matrix with the absolute differences between sqrt.ego and sqrt.alter weighted by the count in the corresponding cell in the balanced matrix
absdiff_pers <- matrix(c(rep(NA, dim(agemix_pers_bal)[1]*dim(agemix_pers_bal)[2])), nrow=dim(agemix_pers_bal[1]))

for(i in 1:dim(agemix_pers_bal)[1]){
  for(j in 1:dim(agemix_pers_bal)[2]){
    absdiff_pers[i,j] <- abs(sqrt.ego[i]-sqrt.alter[j])*agemix_pers_bal[i,j]
  }
}

# Take the mean as the sum of the values in the matrix divided by the total number of persistent partnerships
(mean.absdiff_pers <- round(sum(absdiff_pers),5) / sum(agemix_pers_bal))
```

## Instantaneous partnerships
The table below shows part of the the unbalanced mixing matrix for instantaneous partnerships by age from the raked WHPP and MMP surveys, weighted by the mean rate of one-time partnerships from WHPP and ART-Net and scaled back to the size of the original WHPP sample. Note these counts are not integers because they are from the re-weighted samples. 
```{r}
#Conditional row probabilities
  agemix_inst <- prop.table(svytable(~age + mrp_ageinyrs, whpp_mmp[whpp_mmp$variables$mrp_type_mix %in% "Instantaneous"], round=FALSE),1)

  #Mean rate of instantaneous partnerships by age 
  rateinstXage <- svyby(~rate_inst, ~age, inst.full, svymean, na.rm=TRUE)[2]

  #Reweighted mixing matrix, accounting for mean rate_inst
    # Check that agemix_inst has the same number of rows as rateinstXage and nXage (i.e. no ages had missing values for any of these)
    if (!(dim(agemix_inst)[1] == dim(rateinstXage)[1])) {
    stop("objects must each have a row for every age")
    }
    if (!(dim(agemix_inst)[1] == length(nXage))) {
    stop("objects must each have a row for every age")
    }
    if (!(dim(agemix_inst)[1] == 42)) {
    stop("objects must each have a row for every age")
    }
    
    # Construct an empty data frame
    agemix_inst_rwt <- as.data.frame(matrix(rep(NA, dim(agemix_inst)[1]*dim(agemix_inst)[2]), byrow=TRUE, nrow=dim(agemix_inst)[1]))
    
    # Multiply each row in agemix_inst by the corresponding n and mean degree
    for(i in 1:dim(agemix_inst)[1]){
      agemix_inst_rwt[i, ] <- c(agemix_inst[i,]*rateinstXage[i,1]*nXage[i])
    }
    row.names(agemix_inst_rwt)=c(row.names(agemix_inst))
    names(agemix_inst_rwt) <- c(as.character(sort(unique(whpp_mmp$variables$mrp_ageinyrs[whpp_mmp$variables$mrp_type_mix %in% "Instantaneous"]))))

# Replace NA cells (which resulted for ego ages where no instantaneous partners were named and/or the age of partners was missing) with 0
  agemix_inst_rwt[is.na(agemix_inst_rwt)] <- 0
  
# Make a kable
agemix_inst_rwt.kbl <- agemix_inst_rwt[1:10,1:10]
kable(agemix_inst_rwt.kbl, align=c(rep("c", dim(agemix_inst_rwt.kbl)[2])), digits=c(rep(2, dim(agemix_inst_rwt.kbl)[2]))) %>% kable_styling(full_width=F, position="center") %>% column_spec(1, bold=T, color="black", width="2cm")

```

Taking the average of the off-diagonal elements to balance the matrix, we get the following:
```{r}
# Check whether any ages are missing from the vectors or ego or alter age (i.e. make sure the matrix is symmetric)
egoages <- as.numeric(row.names(agemix_inst_rwt))
alterages <- as.numeric(names(agemix_inst_rwt))
mismatch <- egoages[!(egoages %in% alterages)]

# Add a columns to the reweighted mixing matrix for the missing alter ages (21, 44, 49, 51, 52, 53, 54, 55, 57, 58, 59) containing 0s to make the matrix symmetric
agemix_inst_rwt$`21` <- rep(0, dim(agemix_inst_rwt)[1])
agemix_inst_rwt$`44` <- rep(0, dim(agemix_inst_rwt)[1])
agemix_inst_rwt$`49` <- rep(0, dim(agemix_inst_rwt)[1])
agemix_inst_rwt$`51` <- rep(0, dim(agemix_inst_rwt)[1])
agemix_inst_rwt$`52` <- rep(0, dim(agemix_inst_rwt)[1])
agemix_inst_rwt$`53` <- rep(0, dim(agemix_inst_rwt)[1])
agemix_inst_rwt$`54` <- rep(0, dim(agemix_inst_rwt)[1])
agemix_inst_rwt$`55` <- rep(0, dim(agemix_inst_rwt)[1])
agemix_inst_rwt$`57` <- rep(0, dim(agemix_inst_rwt)[1])
agemix_inst_rwt$`58` <- rep(0, dim(agemix_inst_rwt)[1])
agemix_inst_rwt$`59` <- rep(0, dim(agemix_inst_rwt)[1])

# Reorder columns so they are in numeric order
agemix_inst_rwt <- agemix_inst_rwt[c("18", "19", "20", "21", "22", "23", "24", "25", "26", "27", "28", "29", "30", "31", "32", "33", "34", "35", "36", "37", "38", "39", "40", "41", "42", "43", "44", "45", "46", "47", "48", "49", "50", "51", "52", "53", "54", "55", "56", "57", "58", "59")]

# Take average of off-diagonals to balance
agemix_inst_bal <- as.data.frame(matrix(c(rep(NA, dim(agemix_inst_rwt)[1]*dim(agemix_inst_rwt)[2])), nrow=dim(agemix_inst_rwt[1])))

for(i in 1:dim(agemix_inst_rwt)[1]){
  for(j in 1:dim(agemix_inst_rwt)[2]){
      agemix_inst_bal[i,j] <- mean(c(agemix_inst_rwt[i,j],agemix_inst_rwt[j,i]))
      agemix_inst_bal[j,i] <- mean(c(agemix_inst_rwt[i,j],agemix_inst_rwt[j,i]))
  }
}
  
row.names(agemix_inst_bal)=c(row.names(agemix_inst_rwt))
names(agemix_inst_bal) <- names(agemix_inst_rwt)

# Look at implied mean degree by age from balanced matrix to see if anything looks weird
# rowSums(agemix_inst_bal)/nXage

# Make a kable
agemix_inst_bal.kbl <- agemix_inst_bal[1:10,1:10]
kable(agemix_inst_bal.kbl, align=c(rep("c", dim(agemix_inst_bal.kbl)[2])), digits=c(rep(2, dim(agemix_inst_bal.kbl)[2]))) %>% kable_styling(full_width=F, position="center") %>% column_spec(1, bold=T, color="black", width="2cm")

```

The plot below shows the balanced age mixing matrix, with age collapsed into 5- to 10-year age bins.
```{r fig.align="center"}
# PLOT BALANCED MIXING MATRIX

inst_bal_plot <- mixplot_age(agemix_inst_bal)

# Plot
ggplot(inst_bal_plot, aes(x=alter, y=ego)) + 
    geom_point(aes(size = value), colour="steelblue2") + 
    geom_point(aes(size = ondiag), colour = "black", shape = 1) + 
    geom_text(aes(label = label), hjust=0.6, size=4) +
    scale_size_continuous(range = c(1,30), guide = "none") + 
    labs(x="Alter", y="Ego", title="Age mixing row conditional probabilities: Instantaneous") + 
    plot_background + theme_title 

```


To calculate the target statistic, we take the absolute difference between the square root of each combination of ego and alter ages and weight it by the count in the corresponding cell in the balanced mixing matrix. We then take the mean of the non-zero weighted differences (because cells are zero if no partnerships of that age combination were reported, which should not be included), shown below.

```{r}
# Create vectors with the square root of ego and alter ages corresponding to the rows and columns in the balanced matrix
sqrt.ego <- sqrt(as.integer(row.names(agemix_inst_bal)))
sqrt.alter <- sqrt(as.integer(names(agemix_inst_bal)))

# Create a matrix with the absolute differences between sqrt.ego and sqrt.alter weighted by the count in the corresponding cell in the balanced matrix
absdiff_inst <- matrix(c(rep(NA, dim(agemix_inst_bal)[1]*dim(agemix_inst_bal)[2])), nrow=dim(agemix_inst_bal[1]))

for(i in 1:dim(agemix_inst_bal)[1]){
  for(j in 1:dim(agemix_inst_bal)[2]){
    absdiff_inst[i,j] <- abs(sqrt.ego[i]-sqrt.alter[j])*agemix_inst_bal[i,j]
  }
}

# Take the mean as the sum of the values in the matrix divided by the total number of instantaneous partnerships
(mean.absdiff_inst <- round(sum(absdiff_inst),5) / sum(agemix_inst_bal))

```

```{r}
#Save the means from the three networks
sqrtabsdiff_agemix <- c(mean.absdiff_main, mean.absdiff_pers, mean.absdiff_inst)
save(sqrtabsdiff_agemix, file="Data/sqrtabsdiff_agemix.Rdata")
```

```{r fig.align="center", include=FALSE}
# Plot with mixing matrices in one pane for presentations

## Combine long mixing matrix datasets
main_bal_plot$ptype <- "Main"
pers_bal_plot$ptype <- "Persistent"
inst_bal_plot$ptype <- "Instantaneous"

mixing_plot <- rbind.data.frame(main_bal_plot, pers_bal_plot, inst_bal_plot)

mixing_plot$ptype <- factor(mixing_plot$ptype, levels = c("Main", "Persistent", "Instantaneous"))

## Define indicator of on-diagnoal to have it be a different color
mixing_plot$ondiag <- ifelse(as.character(mixing_plot$ego)==as.character(mixing_plot$alter), "yes", "no")

## Define indicator of on-diagnoal to have it be outlined 
mixing_plot$outline <- ifelse(as.character(mixing_plot$ego)==as.character(mixing_plot$alter), 1, 0)

## Define threshold for label being white
mixing_plot$threshold <- ifelse(mixing_plot$value < 0.4, 1, 0)

## Plot
# # All the same color
# ggplot(mixing_plot, aes(x=alter.cat, y=ego.cat)) + 
#     geom_point(aes(size = prop), color = "steelblue2") + 
#     geom_text(aes(label = label), hjust=0.5, size=2.8) +
#     scale_size_continuous(range = c(1,18), guide = "none") + 
#     facet_grid(.~ptype) +
#     labs(x="Alter", y="Ego", title="Age mixing row conditional probabilities") +
#     theme(axis.text = element_text(size=10, color="black"), axis.title = element_text(size=12, color="black"),
#           strip.text = element_text(size=12, color="black"), plot.title = element_text(size=13, color="black")) +
#     plot_background + theme_title 

# Colored by log alphaij
ggplot(mixing_plot, aes(x=alter, y=ego)) + 
    geom_point(aes(size = value, color = log_alphaij)) + 
    geom_text(aes(label = label), hjust=0.5, size=2.8) +
    scale_size_continuous(range = c(1,18), guide = "none") + 
    scale_colour_gradient2(low = "steelblue", mid = "white", high = "red", midpoint = 0, guide = "none") +
    facet_grid(.~ptype) +
    labs(x="Alter", y="Ego", title="Age mixing row conditional probabilities") +
    theme(axis.text = element_text(size=10, color="black"), axis.title = element_text(size=12, color="black"),
          strip.text = element_text(size=12, color="black"), plot.title = element_text(size=13, color="black")) +
    plot_background + theme_title 

    
# # Alternate plot with color by value and all the same size
# 
# # rescale the proportions for the coloring so that the colors are more pronounced
# ggplot(mixing_plot, aes(x=alter.cat, y=ego.cat)) + 
#     geom_point(aes(color = prop), size = 18) + 
#     geom_text(aes(label = label, color = threshold), hjust=0.5, size=3.5) +
#     geom_point(aes(color = outline), shape = 1, size=18) + 
#     scale_colour_gradient(low="white", high="black") +
#     facet_grid(.~ptype) +
#     labs(x="Alter", y="Ego", title="Age mixing row conditional probabilities") +
#     theme(axis.text = element_text(size=12, color="black"), axis.title = element_text(size=13, color="black"),
#           strip.text = element_text(size=14, color="black"), plot.title = element_text(size=15, color="black")) +
#     plot_background + theme_title 

```