# Heterogeneity on nodal attributes {#explore_heterogeneity}
```{r, include=FALSE}
####################################################################################
# Setup
####################################################################################
#-----------------------------------------------------------------------------------
# Load packages
#-----------------------------------------------------------------------------------

    library("tidyverse")
    library("knitr")
    library("data.table")
    library("lmtest")
    library("kableExtra")
    library("logbin")

#-----------------------------------------------------------------------------------
# Knitr options
#-----------------------------------------------------------------------------------
opts_chunk$set(echo=FALSE, message=FALSE, warning=TRUE, error=TRUE, fig.align = "center")
options(knitr.table.format = "html") 

#-----------------------------------------------------------------------------------
# Plot settings
#-----------------------------------------------------------------------------------
#save plot settings for white background and light grey lines and darkening the colors a bit
plot_background <- theme(panel.background = element_rect(fill="white", colour = "black")) + theme(panel.grid.major = element_line(colour = "grey90"))
darken_color <- scale_colour_hue(l=50)
theme_title <- theme(plot.title = element_text(hjust = 0.5, size=12)) 
        
#-----------------------------------------------------------------------------------
# Load data
#-----------------------------------------------------------------------------------

load(file="Data/InternetSurveySample.Rdata")
load(file="Data/InternetSurveySample_allages.Rdata")

#-----------------------------------------------------------------------------------
# Define alternate age categorization
#-----------------------------------------------------------------------------------
   sample$age_chunks <-  cut(sample$age, c(17, 29, 39, 44, 59), labels=c("18-29", "30-39", "40-49", "50-59"))   
    sample$age_cat_alt <- cut(sample$age, c(17, 24, 29, 34, 39, 49, 59), labels=c("18-24", "25-29", "30-34", "35-39", "40-49", "50-59"))

#----------------------------------------------------------------------------------
# Define multiplot function
#_---------------------------------------------------------------------------------
        multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
            library(grid)
            
            # Make a list from the ... arguments and plotlist
            plots <- c(list(...), plotlist)
            
            numPlots = length(plots)
            
            # If layout is NULL, then use 'cols' to determine layout
            if (is.null(layout)) {
                # Make the panel
                # ncol: Number of columns of plots
                # nrow: Number of rows needed, calculated from # of cols
                layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                                 ncol = cols, nrow = ceiling(numPlots/cols))
            }
            
            if (numPlots==1) {
                print(plots[[1]])
                
            } else {
                # Set up the page
                grid.newpage()
                pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))
                
                # Make each plot, in the correct location
                for (i in 1:numPlots) {
                    # Get the i,j matrix positions of the regions that contain this subplot
                    matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))
                    
                    print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                                    layout.pos.col = matchidx$col))
                }
            }
        }

#-----------------------------------------------------------------------------------
# Write function to streamline analyses
#-----------------------------------------------------------------------------------
#Function to plot the coefficients for age
plot.age.coefs <- function(full) {
    agecoefs <- cbind.data.frame(age_cat = c("25-29", "30-34", "35-39", "40-44", "45-49", "50-54", "55-59"), coefs = as.vector(full$coefficients[2:8]), se = as.vector(coef(summary(full))[2:8,2]))
    plot <- ggplot(agecoefs, aes(x=age_cat, y=coefs)) + geom_pointrange(aes(ymin=coefs - 1.96*se, ymax=coefs + 1.96*se))
    return(plot)
}

#Function to get likelihood ratio tests
    #Outcomes for which we are looking at age, race, and region
    compare.models <- function(full, noreg, norace, noage, full_withint, noraceXreg, noageXreg, noraceXage) {
        lrt_region <- lrtest(full, noreg)
        lrt_race <- lrtest(full, norace)
        lrt_age <- lrtest(full, noage)
        lrt_summary_main <- cbind.data.frame("Variable" = c("Region", "Race", "Age"), "pvalue" = c(round(lrt_region$'Pr(>Chisq)'[2], 4), round(lrt_race$'Pr(>Chisq)'[2], 4), round(lrt_age$'Pr(>Chisq)'[2], 4)))
        lrt_summary_main$sig <- ifelse(lrt_summary_main$pvalue<0.001, "***", ifelse(lrt_summary_main$pvalue<0.01, "**", ifelse(lrt_summary_main$pvalue<0.05, "*", "")))
        
        lrt_raceXreg <- lrtest(full_withint, noraceXreg)
        lrt_ageXreg <- lrtest(full_withint, noageXreg)
        lrt_raceXage <- lrtest(full_withint, noraceXage)
        lrt_summary_int <- cbind.data.frame("Variable" = c("Race by region", "Age by region", "Race by age"), "pvalue" = c(round(lrt_raceXreg$'Pr(>Chisq)'[2], 4), round(lrt_ageXreg$'Pr(>Chisq)'[2], 4), round(lrt_raceXage$'Pr(>Chisq)'[2], 4)))
        lrt_summary_int$sig <-  ifelse(lrt_summary_int$pvalue<0.001, "***", ifelse(lrt_summary_int$pvalue<0.01, "**", ifelse(lrt_summary_int$pvalue<0.05, "*", "")))
    
        #results <- list(summary(full), lrt_summary_main, summary(full_withint), lrt_summary_int)
        results <- list(lrt_summary_main, lrt_summary_int)

        return(results)
    }

#Outcomes for which we are looking only at race and region
    compare.models.noage <- function(full, noreg, norace, full_withint, noraceXreg) {
        lrt_region <- lrtest(full, noreg)
        lrt_race <- lrtest(full, norace)
        lrt_summary_main <- cbind.data.frame("Variable" = c("Region", "Race"), "pvalue" = c(round(lrt_region$'Pr(>Chisq)'[2], 4), round(lrt_race$'Pr(>Chisq)'[2], 4)))
        lrt_summary_main$sig <- ifelse(lrt_summary_main$pvalue<0.001, "***", ifelse(lrt_summary_main$pvalue<0.01, "**", ifelse(lrt_summary_main$pvalue<0.05, "*", "")))
        
        lrt_raceXreg <- lrtest(full_withint, noraceXreg)
        lrt_summary_int <- cbind.data.frame("Variable" = c("Race by region"), "pvalue" = round(lrt_raceXreg$'Pr(>Chisq)'[2], 4))
        lrt_summary_int$sig <-  ifelse(lrt_summary_int$pvalue<0.001, "***", ifelse(lrt_summary_int$pvalue<0.01, "**", ifelse(lrt_summary_int$pvalue<0.05, "*", "")))
    
        #results <- list(summary(full), lrt_summary_main, summary(full_withint), lrt_summary_int)
        results <- list(lrt_summary_main, lrt_summary_int)
        
        return(results)
    }

```


This section documents the results of regression analyses aimed at identifying which variables vary by region, race, and/or age to determine the combination of attributes on which to stratify each parameter. The first step looks at associations by age after adjusting for race/ethnicty and region to determine whether the data show any age effects and, if so, how age should be parameterized. After fitting a model adjusted for the main effects of race/ethnicity, region, and age (categorized as a factor variable with categories 18-24, 25-34... 54-59), we plot the coefficients for age and examine the pattern. Error bars on these plots show the 95% confidence interval around the estimates (1.96 times the standard error of the estimate). If the plots suggest a meaningful trend or other pattern by age, we re-run the models including age in the form indicated by the plot. If not, we fit models excluding age to examine the associations with race and region. We first examine main effects and then test the significance of all two-way interactions. 

P-values are to be used as a guide but not as the sole criteria determining which differences may be worth modeling. The purpose of this analysis is to determine how to specify parameters in order to get the network to reproduce the data. It is not an analysis to determine from the data which parameters differ significantly by region, race, or age in the population (since the sample is not probability-based, this would be difficult to conclude even if it were our goal). As such, corrections for multiple comparisons are not necessary, as these adjust the false discovery rate in analyses attempting to make inference about the population. We use likelihood ratio tests (package `lmtest`) to compare models for joint significance testing.

For variables from which the models suggest meaningful heterogeneity by age, race/ethnicity, and/or region, we further explore this heterogeneity by plotting the data stratified by the indicated nodal attributes. These plots are used to inform how, or if at all, to represent the observed heterogeneity in the model.

## Degree distribution

To look for differences in the degree distribution, we will break it down to four binary indicators corresponding to: 1) whether men have any ongoing main partners, 2) whether they have any ongoing persistent partners, 3) whether they have two or more ongoing persistent partners, and 4) whether men who reported an ongoing main partner reported any concurrent persistent partners.

### Any ongoing main partner
We first look at the number of observations that are non-missing for this outcome and for model predictors
```{r}
  #Look at the number of observations that are non-missing for this outcome and for model predictors
  table(sample$hbo[!is.na(sample$race_eth_m) & !is.na(sample$hasmain)], sample$age_cat[!is.na(sample$race_eth_m) & !is.na(sample$hasmain)], sample$region[!is.na(sample$race_eth_m) & !is.na(sample$hasmain)])
```

Next we will look at how to parameterize age by plotting the ceofficients for age from the model adjusting for age, race, and region, with age input as a dummy variable. The error bars on these plots correspond to 1.96 times the standard error on either side of the point estimate.
```{r}
 #Figure out how to parameterize age
    hasmain_full_testage <- glm(hasmain ~ age_cat + race_eth_m.reg + region.bKC, family=binomial(link="logit"), data=sample)
    plot.age.coefs(hasmain_full_testage)
```

From this there does not appear to be any significant pattern by age, so we will not represent heterogeneity by age. The models below test the effects of race/ethnicity and region in models that do not adjust for age.
```{r hasmain, eval=TRUE, error=TRUE}
 #Main effects
  hasmain_full <- glm(hasmain ~ race_eth_m.reg + region.bKC, family=binomial(link="logit"), data=sample)
  hasmain_noregion <- glm(hasmain ~ race_eth_m.reg, family=binomial(link="logit"), data=sample)
  hasmain_norace <- glm(hasmain ~ region.bKC, family=binomial(link="logit"), data=sample)

 #Interactions
  hasmain_full_withint <- glm(hasmain ~ race_eth_m.reg + region.bKC + race_eth_m.reg*region.bKC, family=binomial(link="logit"), data=sample)
  hasmain_noraceXreg <- glm(hasmain ~ race_eth_m.reg + region.bKC, family=binomial(link="logit"), data=sample)
  
  results_hasmain <- compare.models.noage(hasmain_full, hasmain_noregion, hasmain_norace, hasmain_full_withint, hasmain_noraceXreg)
  
  results_hasmain
```


### Any ongoing persistent partners
We first look at the number of observations that re non-missing for this outcome and for model predictors
```{r}
  #Look at the number of observations that are non-missing for this outcome and for model predictors
  table(sample$hbo[!is.na(sample$race_eth_m) & !is.na(sample$anypers)], sample$age_cat[!is.na(sample$race_eth_m) & !is.na(sample$anypers)], sample$region[!is.na(sample$race_eth_m) & !is.na(sample$anypers)])
```

Next we will look at how to parameterize age by plotting the ceofficients for age from the model adjusting for age, race, and region, with age input as a dummy variable. The error bars on these plots correspond to 2 times the standard error on either side of the point estimate.
```{r}
 #Figure out how to parameterize age
    anypers_full_testage <- glm(anypers ~ age_cat + race_eth_m.reg + region.bKC, family=binomial(link="logit"), data=sample)
    plot.age.coefs(anypers_full_testage)
```

Although the likelihood of having any persistent partner is higher for men aged 40-44 and 45-49 relative to men aged 18-24, there is not a meaningful pattern by age, so we will not represent heterogeneity by age. The models below test the effects of race/ethnicity and region in models that do not adjust for age.
```{r anypers, eval=TRUE, error=TRUE}
 #Main effects
  anypers_full <- glm(anypers ~ race_eth_m.reg + region.bKC, family=binomial(link="logit"), data=sample)
  anypers_noregion <- glm(anypers ~ race_eth_m.reg, family=binomial(link="logit"), data=sample)
  anypers_norace <- glm(anypers ~ region.bKC, family=binomial(link="logit"), data=sample)

 #Interactions
  anypers_full_withint <- glm(anypers ~ race_eth_m.reg + region.bKC + race_eth_m.reg*region.bKC, family=binomial(link="logit"), data=sample)
  anypers_noraceXreg <- glm(anypers ~ race_eth_m.reg + region.bKC, family=binomial(link="logit"), data=sample)
  
  results_anypers <- compare.models.noage(anypers_full, anypers_noregion, anypers_norace, anypers_full_withint, anypers_noraceXreg)
  
  results_anypers
```

### Two or more ongoing persistent partners
We first look at the number of observations that re non-missing for this outcome and for model predictors
```{r}
  #Look at the number of observations that are non-missing for this outcome and for model predictors
  table(sample$hbo[!is.na(sample$race_eth_m) & !is.na(sample$concurrent_pers)], sample$age_cat[!is.na(sample$race_eth_m) & !is.na(sample$concurrent_pers)], sample$region[!is.na(sample$race_eth_m) & !is.na(sample$concurrent_pers)])
```

Next we will look at how to parameterize age by plotting the ceofficients for age from the model adjusting for age, race, and region, with age input as a dummy variable. The error bars on these plots correspond to 2 times the standard error on either side of the point estimate.
```{r}
 #Figure out how to parameterize age
    concurrent_pers_full_testage <- glm(concurrent_pers ~ age_cat + race_eth_m.reg + region.bKC, family=binomial(link="logit"), data=sample)
    plot.age.coefs(concurrent_pers_full_testage)
```

The pattern of concurrent persistent partnerships by age is similar to the pattern for having any persistent partnership. There is not a meaningful pattern by age, so we will not represent heterogeneity by age. The models below test the effects of race/ethnicity and region in models that do not adjust for age.
```{r concurrent_pers, eval=TRUE, error=TRUE}
 #Main effects
  concurrent_pers_full <- glm(concurrent_pers ~ race_eth_m.reg + region.bKC, family=binomial(link="logit"), data=sample)
  concurrent_pers_noregion <- glm(concurrent_pers ~ race_eth_m.reg, family=binomial(link="logit"), data=sample)
  concurrent_pers_norace <- glm(concurrent_pers ~ region.bKC, family=binomial(link="logit"), data=sample)

 #Interactions
  concurrent_pers_full_withint <- glm(concurrent_pers ~ race_eth_m.reg + region.bKC + race_eth_m.reg*region.bKC, family=binomial(link="logit"), data=sample)
  concurrent_pers_noraceXreg <- glm(concurrent_pers ~ race_eth_m.reg + region.bKC, family=binomial(link="logit"), data=sample)
  
  results_concurrent_pers <- compare.models.noage(concurrent_pers_full, concurrent_pers_noregion, concurrent_pers_norace, concurrent_pers_full_withint, concurrent_pers_noraceXreg)
  
  results_concurrent_pers
```

### Ongoing main partners with concurrent persistent partners
We first look at the number of observations that re non-missing for this outcome and for model predictors
```{r}
  #Look at the number of observations that are non-missing for this outcome and for model predictors
  table(sample$hbo[!is.na(sample$race_eth_m) & !is.na(sample$concurrent_mainpers)], sample$age_cat[!is.na(sample$race_eth_m) & !is.na(sample$concurrent_mainpers)], sample$region[!is.na(sample$race_eth_m) & !is.na(sample$concurrent_mainpers)])
```

Next we will look at how to parameterize age by plotting the ceofficients for age from the model adjusting for age, race, and region, with age input as a dummy variable. The error bars on these plots correspond to 2 times the standard error on either side of the point estimate.
```{r}
 #Figure out how to parameterize age
    concurrent_mainpers_full_testage <- glm(concurrent_mainpers ~ age_cat + race_eth_m.reg + region.bKC, family=binomial(link="logit"), data=sample)
    plot.age.coefs(concurrent_mainpers_full_testage)
```

It appears that the probability of having persistent partners concurrently with a main partner increases through age 49, but the only age group for which this is significant is 45-49. The overall lack of significance and incongruent observation for men aged 35-39 suggests that this parameter does not vary meaningfully by age. The models below test the effects of race/ethnicity and region in models that do not adjust for age.
```{r concurrent_mainpers, eval=TRUE, error=TRUE}
 #Main effects
  concurrent_mainpers_full <- glm(concurrent_mainpers ~ race_eth_m.reg + region.bKC, family=binomial(link="logit"), data=sample)
  concurrent_mainpers_noregion <- glm(concurrent_mainpers ~ race_eth_m.reg, family=binomial(link="logit"), data=sample)
  concurrent_mainpers_norace <- glm(concurrent_mainpers ~ region.bKC, family=binomial(link="logit"), data=sample)

 #Interactions
  concurrent_mainpers_full_withint <- glm(concurrent_mainpers ~ race_eth_m.reg + region.bKC + race_eth_m.reg*region.bKC, family=binomial(link="logit"), data=sample)
  concurrent_mainpers_noraceXreg <- glm(concurrent_mainpers ~ race_eth_m.reg + region.bKC, family=binomial(link="logit"), data=sample)
  
  results_concurrent_mainpers <- compare.models.noage(concurrent_mainpers_full, concurrent_mainpers_noregion, concurrent_mainpers_norace, concurrent_mainpers_full_withint, concurrent_mainpers_noraceXreg)
  
  results_concurrent_mainpers
```

## Rate of instantaneous partners
This analysis looks at heterogeneity in the rate of one-time partnerships separately for men who have 0 main, those who have 1 main, those who have 0 persistent, and those who have one or more persistent partnerships. <span style="color:red">Wouldn't I want to look at this by the joint distribution of main and persistent partnerships?</span>

### No main partners
We first look at the number of observations that re non-missing for this outcome and for model predictors
```{r}
    #Look at the number of observations that are non-missing for this outcome and for model predictors
  table(sample$hbo[!is.na(sample$race_eth_m) & !is.na(sample$rate_inst) & sample$degree_main %in% 0], sample$age_cat[!is.na(sample$race_eth_m) & !is.na(sample$rate_inst) & sample$degree_main %in% 0], sample$region[!is.na(sample$race_eth_m) & !is.na(sample$rate_inst) & sample$degree_main %in% 0])
```

Next we will look at how to parameterize age by plotting the ceofficients from the full model with age input as a dummy variable with 5-year age bins
```{r}
 #Figure out how to parameterize age
    rateinst_nomain_full_testage <- lm(rate_inst ~ age_cat + race_eth_m.reg + region.bKC, data=sample, subset = degree_main %in% 0)
    plot.age.coefs(rateinst_nomain_full_testage)
```

<span style="color:red">This plot suggests that the rate of instantaneous partners increases for men aged 35-39 and subsequently decreases with age. The point for ages 30-34 does not fit with a trend suggesting that the rate increases with age up through age 39, but it may be an outlier. To further explore the association with age, we will include age as a dummy variable, grouping together men in age groups 40-49 and 50-59 </span>.

The models and likelihood ratio tests are below.
```{r rateinst_nomain, eval=TRUE, error=TRUE}
 
 #Main effects
  rateinst_nomain_full <- lm(rate_inst ~ age_cat_alt + race_eth_m.reg + region.bKC, data=sample, subset = degree_main %in% 0)
  rateinst_nomain_noregion <- lm(rate_inst ~ age_cat_alt + race_eth_m.reg, data=sample, subset = degree_main %in% 0)
  rateinst_nomain_norace <- lm(rate_inst ~ age_cat_alt + region.bKC, data=sample, subset = degree_main %in% 0)
  rateinst_nomain_noage <- lm(rate_inst ~ race_eth_m.reg + region.bKC, data=sample, subset = degree_main %in% 0)

 #Interactions
  rateinst_nomain_full_withint <- lm(rate_inst ~ age_cat_alt + race_eth_m.reg + region.bKC + race_eth_m.reg*region.bKC + age_cat_alt*region.bKC + race_eth_m.reg*age_cat_alt, data=sample, subset = degree_main %in% 0)
  rateinst_nomain_noraceXreg <- lm(rate_inst ~ age_cat_alt + race_eth_m.reg + region.bKC + age_cat_alt*region.bKC + race_eth_m.reg*age_cat_alt, data=sample, subset = degree_main %in% 0)
  rateinst_nomain_noageXreg <- lm(rate_inst ~ age_cat_alt + race_eth_m.reg + region.bKC + race_eth_m.reg*region.bKC + race_eth_m.reg*age_cat_alt, data=sample, subset = degree_main %in% 0)
  rateinst_nomain_noraceXage <- lm(rate_inst ~ age_cat_alt + race_eth_m.reg + region.bKC + age_cat_alt*region.bKC + race_eth_m.reg*region.bKC, data=sample, subset = degree_main %in% 0)
  
  results_rateinst_nomain <- compare.models(rateinst_nomain_full, rateinst_nomain_noregion, rateinst_nomain_norace, rateinst_nomain_noage, rateinst_nomain_full_withint, rateinst_nomain_noraceXreg, rateinst_nomain_noageXreg, rateinst_nomain_noraceXage)
    results_rateinst_nomain
```

### Main partner
We first look at the number of observations that re non-missing for this outcome and for model predictors
```{r}
    #Look at the number of observations that are non-missing for this outcome and for model predictors
  table(sample$hbo[!is.na(sample$race_eth_m) & !is.na(sample$rate_inst) & sample$degree_main %in% 1], sample$age_cat[!is.na(sample$race_eth_m) & !is.na(sample$rate_inst) & sample$degree_main %in% 1], sample$region[!is.na(sample$race_eth_m) & !is.na(sample$rate_inst) & sample$degree_main %in% 1])
```

Next we will look at how to parameterize age by plotting the ceofficients from the full model with age input as a dummy variable with 5-year age bins
```{r}
 #Figure out how to parameterize age
    rateinst_main_full_testage <- lm(rate_inst ~ age_cat + race_eth_m.reg + region.bKC, data=sample, subset = degree_main %in% 1)
    plot.age.coefs(rateinst_main_full_testage)
```

<span style="color:red">As for men with no main partners, this plot suggests that the rate of instantaneous partners increases with age through age 39 and subsequently decreases. Consistent with the approach taken above, we will include age as a dummy variable, grouping together men in age groups 40-49 and 50-59 </span>.

The models and likelihood ratio tests are below.
```{r rateinst_main, eval=TRUE, error=TRUE}
 
 #Main effects
  rateinst_main_full <- lm(rate_inst ~ age_cat_alt + race_eth_m.reg + region.bKC, data=sample, subset = degree_main %in% 1)
  rateinst_main_noregion <- lm(rate_inst ~ age_cat_alt + race_eth_m.reg, data=sample, subset = degree_main %in% 1)
  rateinst_main_norace <- lm(rate_inst ~ age_cat_alt + region.bKC, data=sample, subset = degree_main %in% 1)
  rateinst_main_noage <- lm(rate_inst ~ race_eth_m.reg + region.bKC, data=sample, subset = degree_main %in% 1)

 #Interactions
  rateinst_main_full_withint <- lm(rate_inst ~ age_cat_alt + race_eth_m.reg + region.bKC + race_eth_m.reg*region.bKC + age_cat_alt*region.bKC + race_eth_m.reg*age_cat_alt, data=sample, subset = degree_main %in% 1)
  rateinst_main_noraceXreg <- lm(rate_inst ~ age_cat_alt + race_eth_m.reg + region.bKC + age_cat_alt*region.bKC + race_eth_m.reg*age_cat_alt, data=sample, subset = degree_main %in% 1)
  rateinst_main_noageXreg <- lm(rate_inst ~ age_cat_alt + race_eth_m.reg + region.bKC + race_eth_m.reg*region.bKC + race_eth_m.reg*age_cat_alt, data=sample, subset = degree_main %in% 1)
  rateinst_main_noraceXage <- lm(rate_inst ~ age_cat_alt + race_eth_m.reg + region.bKC + age_cat_alt*region.bKC + race_eth_m.reg*region.bKC, data=sample, subset = degree_main %in% 1)
  
  results_rateinst_main <- compare.models(rateinst_main_full, rateinst_main_noregion, rateinst_main_norace, rateinst_main_noage, rateinst_main_full_withint, rateinst_main_noraceXreg, rateinst_main_noageXreg, rateinst_main_noraceXage)
    results_rateinst_main
```

### No persistent partners
We first look at the number of observations that re non-missing for this outcome and for model predictors
```{r}
    #Look at the number of observations that are non-missing for this outcome and for model predictors
  table(sample$hbo[!is.na(sample$race_eth_m) & !is.na(sample$rate_inst) & sample$degreecat_cas %in% "None"], sample$age_cat[!is.na(sample$race_eth_m) & !is.na(sample$rate_inst) & sample$degreecat_cas %in% "None"], sample$region[!is.na(sample$race_eth_m) & !is.na(sample$rate_inst) & sample$degreecat_cas %in% "None"])
```

Next we will look at how to parameterize age by plotting the ceofficients from the full model with age input as a dummy variable with 5-year age bins
```{r}
 #Figure out how to parameterize age
    rateinst_nopers_full_testage <- lm(rate_inst ~ age_cat + race_eth_m.reg + region.bKC, data=sample, subset = degreecat_cas %in% "None")
    plot.age.coefs(rateinst_nopers_full_testage)
```

<span style="color:red">The pattern here is a bit less clear than above, but it suggests that the rate of instantaneous partners increases through age 39 and subsequently decreases with age. Although only the coefficient for ages 35-39 is significant, we will further explore the association with age, including age as a dummy variable, grouping together men in age groups 40-49 and 50-59 </span>.

The models and likelihood ratio tests are below.
```{r rateinst_nopers, eval=TRUE, error=TRUE}
 
 #Main effects
  rateinst_nopers_full <- lm(rate_inst ~ age_cat_alt + race_eth_m.reg + region.bKC, data=sample, subset = degreecat_cas %in% "None")
  rateinst_nopers_noregion <- lm(rate_inst ~ age_cat_alt + race_eth_m.reg, data=sample, subset = degreecat_cas %in% "None")
  rateinst_nopers_norace <- lm(rate_inst ~ age_cat_alt + region.bKC, data=sample, subset = degreecat_cas %in% "None")
  rateinst_nopers_noage <- lm(rate_inst ~ race_eth_m.reg + region.bKC, data=sample, subset = degreecat_cas %in% "None")

 #Interactions
  rateinst_nopers_full_withint <- lm(rate_inst ~ age_cat_alt + race_eth_m.reg + region.bKC + race_eth_m.reg*region.bKC + age_cat_alt*region.bKC + race_eth_m.reg*age_cat_alt, data=sample, subset = degreecat_cas %in% "None")
  rateinst_nopers_noraceXreg <- lm(rate_inst ~ age_cat_alt + race_eth_m.reg + region.bKC + age_cat_alt*region.bKC + race_eth_m.reg*age_cat_alt, data=sample, subset = degreecat_cas %in% "None")
  rateinst_nopers_noageXreg <- lm(rate_inst ~ age_cat_alt + race_eth_m.reg + region.bKC + race_eth_m.reg*region.bKC + race_eth_m.reg*age_cat_alt, data=sample, subset = degreecat_cas %in% "None")
  rateinst_nopers_noraceXage <- lm(rate_inst ~ age_cat_alt + race_eth_m.reg + region.bKC + age_cat_alt*region.bKC + race_eth_m.reg*region.bKC, data=sample, subset = degreecat_cas %in% "None")
  
  results_rateinst_nopers <- compare.models(rateinst_nopers_full, rateinst_nopers_noregion, rateinst_nopers_norace, rateinst_nopers_noage, rateinst_nopers_full_withint, rateinst_nopers_noraceXreg, rateinst_nopers_noageXreg, rateinst_nopers_noraceXage)
    results_rateinst_nopers
```

### Any persistent partners
We first look at the number of observations that re non-missing for this outcome and for model predictors
```{r}
    #Look at the number of observations that are non-missing for this outcome and for model predictors
  table(sample$hbo[!is.na(sample$race_eth_m) & !is.na(sample$rate_inst) & sample$degreecat_cas %in% c("One", "Two or more")], sample$age_cat[!is.na(sample$race_eth_m) & !is.na(sample$rate_inst) & sample$degreecat_cas %in% c("One", "Two or more")], sample$region[!is.na(sample$race_eth_m) & !is.na(sample$rate_inst) & sample$degreecat_cas %in% c("One", "Two or more")])
```

Next we will look at how to parameterize age by plotting the ceofficients from the full model with age input as a dummy variable with 5-year age bins
```{r}
 #Figure out how to parameterize age
    rateinst_anypers_full_testage <- lm(rate_inst ~ age_cat + race_eth_m.reg + region.bKC, data=sample, subset = degreecat_cas %in% c("One", "Two or more"))
    plot.age.coefs(rateinst_anypers_full_testage)
```

<span style="color:red">The pattern here is even less clear than stratified by main partner status, but it suggests that the rate of instantaneous partners increases through age 39 and subsequently decreases with age. Although only the coefficient for ages 35-39 is significant, we will further explore the association with age, including age as a dummy variable, grouping together men in age groups 40-49 and 50-59 to be consistent with the approach taken above</span>.

The models and likelihood ratio tests are below.
```{r rateinst_anypers, eval=TRUE, error=TRUE}
 
 #Main effects
  rateinst_anypers_full <- lm(rate_inst ~ age_cat_alt + race_eth_m.reg + region.bKC, data=sample, subset = degreecat_cas %in% c("One", "Two or more"))
  rateinst_anypers_noregion <- lm(rate_inst ~ age_cat_alt + race_eth_m.reg, data=sample, subset = degreecat_cas %in% c("One", "Two or more"))
  rateinst_anypers_norace <- lm(rate_inst ~ age_cat_alt + region.bKC, data=sample, subset = degreecat_cas %in% c("One", "Two or more"))
  rateinst_anypers_noage <- lm(rate_inst ~ race_eth_m.reg + region.bKC, data=sample, subset = degreecat_cas %in% c("One", "Two or more"))

 #Interactions
  rateinst_anypers_full_withint <- lm(rate_inst ~ age_cat_alt + race_eth_m.reg + region.bKC + race_eth_m.reg*region.bKC + age_cat_alt*region.bKC + race_eth_m.reg*age_cat_alt, data=sample, subset = degreecat_cas %in% c("One", "Two or more"))
  rateinst_anypers_noraceXreg <- lm(rate_inst ~ age_cat_alt + race_eth_m.reg + region.bKC + age_cat_alt*region.bKC + race_eth_m.reg*age_cat_alt, data=sample, subset = degreecat_cas %in% c("One", "Two or more"))
  rateinst_anypers_noageXreg <- lm(rate_inst ~ age_cat_alt + race_eth_m.reg + region.bKC + race_eth_m.reg*region.bKC + race_eth_m.reg*age_cat_alt, data=sample, subset = degreecat_cas %in% c("One", "Two or more"))
  rateinst_anypers_noraceXage <- lm(rate_inst ~ age_cat_alt + race_eth_m.reg + region.bKC + age_cat_alt*region.bKC + race_eth_m.reg*region.bKC, data=sample, subset = degreecat_cas %in% c("One", "Two or more"))
  
  results_rateinst_anypers <- compare.models(rateinst_anypers_full, rateinst_anypers_noregion, rateinst_anypers_norace, rateinst_anypers_noage, rateinst_anypers_full_withint, rateinst_anypers_noraceXreg, rateinst_anypers_noageXreg, rateinst_anypers_noraceXage)
    results_rateinst_anypers
```

## Race/ethnicity mixing
To examine differences in mixing by race/ethnicity, we will look at the proportion of men reporting that their most recent partner was in the same racial/ethnic group (Hispanic, black, or other) as themselves. For main and persistent partner types, this analysis is restricted to most recent partners who are _ongoing_. __Note__: The outcome is based on ego reports of their partners race and, at this point, does not adjust for imbalances in reported partnering patterns.

```{r samerace_define}

  #Set to missing if the respondent did not know his partner's race/ethnicity
  sample$mrp_race_eth_m_removedk <- sample$mrp_race_eth_m[!(sample$mrp_race_eth_m %in% "Dont know")]
  sample$mrp_race_eth_m_removedk <- factor(sample$mrp_race_eth_m_removedk)
  
  #Define indicator of respondent and partner being of the same race/ethnicity
  sample$samerace <- ifelse(sample$race_eth_m==sample$mrp_race_eth_m_removedk, 1,
                                   ifelse(!is.na(sample$race_eth_m) & !is.na(sample$mrp_race_eth_m_removedk), 0,
                                          NA))
```

### Main partners
We first look at the number of observations that re non-missing for this outcome and for model predictors
```{r}
     #Look at the number of observations that are non-missing for this outcome and for model predictors
  table(sample$hbo[!is.na(sample$race_eth_m) & !is.na(sample$samerace) & sample$mrp_type_ongoing %in% "Main"], sample$age_cat[!is.na(sample$race_eth_m) & !is.na(sample$samerace) & sample$mrp_type_ongoing %in% "Main"], sample$region[!is.na(sample$race_eth_m) & !is.na(sample$samerace) & sample$mrp_type_ongoing %in% "Main"])
```

Next we will look at how to parameterize age by plotting the ceofficients from the full model with age input as a dummy variable with 5-year age bins. All men in age group 55-59 reported a partner of the same race/ethnicity, making this estimate unstable. Because this estimate and it's confidence interval are much larger than the estimates and intervals for other age groups, the plot including this point masks variability. As such, the second plot excludes estimates for the 55-59 year-old group.
```{r}
 #Figure out how to parameterize age
    samerace_main_full_testage <- glm(samerace ~ age_cat + race_eth_m.reg + region.bKC, family=binomial(link="logit"), data=sample, subset = mrp_type_ongoing %in% "Main")
    p1 <- plot.age.coefs(samerace_main_full_testage)
    
    #Dropping age_cat 55-59
     agecoefs_dropcat <- cbind.data.frame(age_cat = c("25-29", "30-34", "35-39", "40-44", "45-49", "50-54"), coefs = as.vector(samerace_main_full_testage$coefficients[2:7]), se = as.vector(coef(summary(samerace_main_full_testage))[2:7,2]))
    p2 <- ggplot(agecoefs_dropcat, aes(x=age_cat, y=coefs)) + geom_pointrange(aes(ymin=coefs - 1.96*se, ymax=coefs + 1.96*se))
    
    multiplot(p1, p2, cols=1)
```

These coefficients suggest that racial/ethnic homophily is lower among those aged 30-34 and 50-54 and higher among those aged 40-44 and 55-59, though these latter two estimates are not statistically significant. This does not suggest any meaningful trend, so we will not include age in the models below.

The models and likelihood ratio tests are below.
```{r samerace_main, eval=TRUE}
 #Main effects
  samerace_main_full <- glm(samerace ~ race_eth_m.reg + region.bKC, family=binomial(link="logit"), data=sample[sample$mrp_type_ongoing %in% "Main", ])
  samerace_main_noregion <- glm(samerace ~ race_eth_m.reg, family=binomial(link="logit"), data=sample[sample$mrp_type_ongoing %in% "Main", ])
  samerace_main_norace <- glm(samerace ~ region.bKC, family=binomial(link="logit"), data=sample[sample$mrp_type_ongoing %in% "Main", ])

 #Interactions
  samerace_main_full_withint <- glm(samerace ~ race_eth_m.reg + region.bKC + race_eth_m.reg*region.bKC, family=binomial(link="logit"), data=sample[sample$mrp_type_ongoing %in% "Main", ])
  samerace_main_noraceXreg <- glm(samerace ~ race_eth_m.reg + region.bKC, family=binomial(link="logit"), data=sample[sample$mrp_type_ongoing %in% "Main", ])
 
  results_samerace_main <- compare.models.noage(samerace_main_full, samerace_main_noregion, samerace_main_norace, samerace_main_full_withint, samerace_main_noraceXreg)
  results_samerace_main

```


### Persistent partners
We first look at the number of observations that re non-missing for this outcome and for model predictors
```{r}
    
 #Look at the number of observations that are non-missing for this outcome and for model predictors
  table(sample$hbo[!is.na(sample$race_eth_m) & !is.na(sample$samerace) & sample$mrp_type_ongoing %in% "Persistent"], sample$age_cat[!is.na(sample$race_eth_m) & !is.na(sample$samerace) & sample$mrp_type_ongoing %in% "Persistent"], sample$region[!is.na(sample$race_eth_m) & !is.na(sample$samerace) & sample$mrp_type_ongoing %in% "Persistent"])

```

Next we will look at how to parameterize age by plotting the ceofficients from the full model with age input as a dummy variable with 5-year age bins. As with main partnerships, all men in age group 55-59 reported a persistent partner of the same race/ethnicity, making this estimate unstable. Because this estimate and it's confidence interval are much larger than the estimates and intervals for other age groups, the plot including this point masks variability. As such, the second plot excludes estimates for the 55-59 year-old group.
```{r}
 #Figure out how to parameterize age
    samerace_pers_full_testage <- glm(samerace ~ age_cat + race_eth_m.reg + region.bKC, family=binomial(link="logit"), data=sample, subset = mrp_type_ongoing %in% "Persistent")
    p1 <- plot.age.coefs(samerace_pers_full_testage)
    
    #Dropping age_cat 55-59
     agecoefs_dropcat <- cbind.data.frame(age_cat = c("25-29", "30-34", "35-39", "40-44", "45-49", "50-54"), coefs = as.vector(samerace_pers_full_testage$coefficients[2:7]), se = as.vector(coef(summary(samerace_pers_full_testage))[2:7,2]))
    p2 <- ggplot(agecoefs_dropcat, aes(x=age_cat, y=coefs)) + geom_pointrange(aes(ymin=coefs - 1.96*se, ymax=coefs + 1.96*se))
    
    multiplot(p1, p2, cols=1)
```

As with main partnerships, there does not appear to be a meaningful pattern by age. As such, the models below do not adjust for age.

The models and likelihood ratio tests are below.
```{r samerace_pers, eval=TRUE}
 
 #Main effects
  samerace_pers_full <- glm(samerace ~ race_eth_m.reg + region.bKC, family=binomial(link="logit"), data=sample[sample$mrp_type_ongoing %in% "Persistent", ])
  samerace_pers_noregion <- glm(samerace ~ race_eth_m.reg, family=binomial(link="logit"), data=sample[sample$mrp_type_ongoing %in% "Persistent", ])
  samerace_pers_norace <- glm(samerace ~ region.bKC, family=binomial(link="logit"), data=sample[sample$mrp_type_ongoing %in% "Persistent", ])

 #Interactions
  samerace_pers_full_withint <- glm(samerace ~ race_eth_m.reg + region.bKC + race_eth_m.reg*region.bKC, family=binomial(link="logit"), data=sample[sample$mrp_type_ongoing %in% "Persistent", ])
  samerace_pers_noraceXreg <- glm(samerace ~ race_eth_m.reg + region.bKC, family=binomial(link="logit"), data=sample[sample$mrp_type_ongoing %in% "Persistent", ])
  
  results_samerace_pers <- compare.models.noage(samerace_pers_full, samerace_pers_noregion, samerace_pers_norace, samerace_pers_full_withint, samerace_pers_noraceXreg)
  results_samerace_pers

```

### Instantaneous partners
We first look at the number of observations that re non-missing for this outcome and for model predictors
```{r}
  
 #Look at the number of observations that are non-missing for this outcome and for model predictors
  table(sample$hbo[!is.na(sample$race_eth_m) & !is.na(sample$samerace) & sample$mrp_type_r %in% "One time"], sample$age_cat_alt[!is.na(sample$race_eth_m) & !is.na(sample$samerace) & sample$mrp_type_r %in% "One time"], sample$region[!is.na(sample$race_eth_m) & !is.na(sample$samerace) & sample$mrp_type_r %in% "One time"])

```

Next we will look at how to parameterize age by plotting the ceofficients from the full model with age input as a dummy variable with 5-year age bins
```{r}
 #Figure out how to parameterize age
    samerace_inst_full_testage <- glm(samerace ~ age_cat + race_eth_m.reg + region.bKC, family=binomial(link="logit"), data=sample[sample$mrp_type_r %in% "One time", ])
    plot.age.coefs(samerace_inst_full_testage)
```

This plot does not show any clear pattern of racial/ethnic mixing by age. As such, we will exclude age from the models below in examining associations with region adjusting for race/ethnicity.

The models and likelihood ratio tests are below.
```{r samerace_inst, eval=TRUE}

 #Main effects
  samerace_inst_full <- glm(samerace ~ race_eth_m.reg + region.bKC, family=binomial(link="logit"), data=sample[sample$mrp_type_r %in% "One time", ])
  samerace_inst_noregion <- glm(samerace ~ race_eth_m.reg, family=binomial(link="logit"), data=sample[sample$mrp_type_r %in% "One time", ])
  samerace_inst_norace <- glm(samerace ~ region.bKC, family=binomial(link="logit"), data=sample[sample$mrp_type_r %in% "One time", ])

 #Interactions
  samerace_inst_full_withint <- glm(samerace ~ race_eth_m.reg + region.bKC + race_eth_m.reg*region.bKC, family=binomial(link="logit"), data=sample[sample$mrp_type_r %in% "One time", ])
  samerace_inst_noraceXreg <- glm(samerace ~ race_eth_m.reg + region.bKC, family=binomial(link="logit"), data=sample[sample$mrp_type_r %in% "One time", ])

  results_samerace_inst <- compare.models.noage(samerace_inst_full, samerace_inst_noregion, samerace_inst_norace, samerace_inst_full_withint, samerace_inst_noraceXreg)
  results_samerace_inst
```


## Age mixing
As with race/ethnicity, examination of age differences with main and persistent partners is restricted to most recent partners who are _ongoing_. For this analysis, we model age mixing using a linear model with the outcome being the absolute difference between the square root of the ego and alter's ages.

### Main partners
We first look at the number of observations that re non-missing for this outcome and for model predictors
```{r}
 #Look at the number of observations that are non-missing for this outcome and for model predictors
  table(sample$hbo[!is.na(sample$race_eth_m) & !is.na(sample$sqrt_agediff) & sample$mrp_type_ongoing %in% "Main"], sample$age_cat[!is.na(sample$race_eth_m) & !is.na(sample$sqrt_agediff) & sample$mrp_type_ongoing %in% "Main"], sample$region[!is.na(sample$race_eth_m) & !is.na(sample$sqrt_agediff) & sample$mrp_type_ongoing %in% "Main"])

```

Next we will look at how to parameterize age by plotting the ceofficients from the full model with age input as a dummy variable with 5-year age bins
```{r}
 #Figure out how to parameterize age
    sqrtagediff_main_full_testage <- lm(sqrt_agediff ~ age_cat + race_eth_m.reg + region.bKC, data=sample[sample$mrp_type_ongoing %in% "Main", ])
    plot.age.coefs(sqrtagediff_main_full_testage)
```

With the exception of the coefficients for ages 50-54 and 55-59, these appear close to linear. The coefficients for these older groups suggest that a linear parameterization may not be appropriate, however. Although ages 50-54 and 55-59 appear quite different, there are only 19 and 17 respectively in each bin, so we will model age as a categorical variable, collapsing ages 40-59 into 10-year bins. 

The models and likelihood ratio tests are below.
```{r agemix_main, eval=TRUE}

 #Main effects
  sqrtagediff_main_full <- lm(sqrt_agediff ~ age_cat_alt + race_eth_m.reg + region.bKC, data=sample[sample$mrp_type_ongoing %in% "Main", ])
  sqrtagediff_main_noregion <- lm(sqrt_agediff ~ age_cat_alt + race_eth_m.reg, data=sample[sample$mrp_type_ongoing %in% "Main", ])
  sqrtagediff_main_norace <- lm(sqrt_agediff ~ age_cat_alt + region.bKC, data=sample[sample$mrp_type_ongoing %in% "Main", ])
  sqrtagediff_main_noage <- lm(sqrt_agediff ~ race_eth_m.reg + region.bKC, data=sample[sample$mrp_type_ongoing %in% "Main", ])

 #Interactions
  sqrtagediff_main_full_withint <- lm(sqrt_agediff ~ age_cat_alt + race_eth_m.reg + region.bKC + race_eth_m.reg*region.bKC + age*region.bKC + race_eth_m.reg*age, data=sample[sample$mrp_type_ongoing %in% "Main", ])
  sqrtagediff_main_noraceXreg <- lm(sqrt_agediff ~ age_cat_alt + race_eth_m.reg + region.bKC + age*region.bKC + race_eth_m.reg*age, data=sample[sample$mrp_type_ongoing %in% "Main", ])
  sqrtagediff_main_noageXreg <- lm(sqrt_agediff ~ age_cat_alt + race_eth_m.reg + region.bKC + race_eth_m.reg*region.bKC + race_eth_m.reg*age, data=sample[sample$mrp_type_ongoing %in% "Main", ])
  sqrtagediff_main_noraceXage <- lm(sqrt_agediff ~ age_cat_alt + race_eth_m.reg + region.bKC + age*region.bKC + race_eth_m.reg*region.bKC, data=sample[sample$mrp_type_ongoing %in% "Main", ])
  
  results_adiff_main <- compare.models(sqrtagediff_main_full, sqrtagediff_main_noregion, sqrtagediff_main_norace, sqrtagediff_main_noage, sqrtagediff_main_full_withint, sqrtagediff_main_noraceXreg, sqrtagediff_main_noageXreg, sqrtagediff_main_noraceXage)  
  results_adiff_main

```

### Persistent partners
We first look at the number of observations that re non-missing for this outcome and for model predictors
```{r}
#Look at the number of observations that are non-missing for this outcome and for model predictors
  table(sample$hbo[!is.na(sample$race_eth_m) & !is.na(sample$sqrt_agediff) & sample$mrp_type_ongoing %in% "Persistent"], sample$age_cat[!is.na(sample$race_eth_m) & !is.na(sample$sqrt_agediff)  & sample$mrp_type_ongoing %in% "Persistent"], sample$region[!is.na(sample$race_eth_m) & !is.na(sample$sqrt_agediff)  & sample$mrp_type_ongoing %in% "Persistent"])

```

Next we will look at how to parameterize age by plotting the ceofficients from the full model with age input as a dummy variable with 5-year age bins
```{r}
 #Figure out how to parameterize age
    sqrtagediff_pers_full_testage <- lm(sqrt_agediff ~ age_cat + race_eth_m.reg + region.bKC, data=sample[sample$mrp_type_ongoing %in% "Persistent", ])
    plot.age.coefs(sqrtagediff_pers_full_testage)
```

With the exception of the estimate for ages 50-54, there does not appear to be a meaningful trend by age. However, to be consistent with the approach taken for main partners, we will model age as a categorical variable, collapsing ages 40-59 into 10-year bins. Although this groups together ages 50-54 and 55-59, for which the estimates appear different, there are only 6 and 4 men in each age group.

The models and likelihood ratio tests are below.
```{r agemix_pers, eval=TRUE}

 #Main effects
  sqrtagediff_pers_full <- lm(sqrt_agediff ~ age_cat_alt + race_eth_m.reg + region.bKC, data=sample[sample$mrp_type_ongoing %in% "Persistent", ])
  sqrtagediff_pers_noregion <- lm(sqrt_agediff ~ age_cat_alt + race_eth_m.reg, data=sample[sample$mrp_type_ongoing %in% "Persistent", ])
  sqrtagediff_pers_norace <- lm(sqrt_agediff ~ age_cat_alt + region.bKC, data=sample[sample$mrp_type_ongoing %in% "Persistent", ])
  sqrtagediff_pers_noage <- lm(sqrt_agediff ~ race_eth_m.reg + region.bKC, data=sample[sample$mrp_type_ongoing %in% "Persistent", ])

 #Interactions
  sqrtagediff_pers_full_withint <- lm(sqrt_agediff ~ age_cat_alt + race_eth_m.reg + region.bKC + race_eth_m.reg*region.bKC + age_cat_alt*region.bKC + race_eth_m.reg*age_cat_alt, data=sample[sample$mrp_type_ongoing %in% "Persistent", ])
  sqrtagediff_pers_noraceXreg <- lm(sqrt_agediff ~ age_cat_alt + race_eth_m.reg + region.bKC + age_cat_alt*region.bKC + race_eth_m.reg*age_cat_alt, data=sample[sample$mrp_type_ongoing %in% "Persistent", ])
  sqrtagediff_pers_noageXreg <- lm(sqrt_agediff ~ age_cat_alt + race_eth_m.reg + region.bKC + race_eth_m.reg*region.bKC + race_eth_m.reg*age_cat_alt, data=sample[sample$mrp_type_ongoing %in% "Persistent", ])
  sqrtagediff_pers_noraceXage <- lm(sqrt_agediff ~ age_cat_alt + race_eth_m.reg + region.bKC + age_cat_alt*region.bKC + race_eth_m.reg*region.bKC, data=sample[sample$mrp_type_ongoing %in% "Persistent", ])
  
  results_adiff_pers <- compare.models(sqrtagediff_pers_full, sqrtagediff_pers_noregion, sqrtagediff_pers_norace, sqrtagediff_pers_noage, sqrtagediff_pers_full_withint, sqrtagediff_pers_noraceXreg, sqrtagediff_pers_noageXreg, sqrtagediff_pers_noraceXage)  
  results_adiff_pers
```

### Instantaneous partners
We first look at the number of observations that re non-missing for this outcome and for model predictors
```{r}
#Look at the number of observations that are non-missing for this outcome and for model predictors
  table(sample$hbo[!is.na(sample$race_eth_m) & !is.na(sample$sqrt_agediff) & mrp_type_r %in% "One time"], sample$age_cat[!is.na(sample$race_eth_m) & !is.na(sample$sqrt_agediff) & mrp_type_r %in% "One time"], sample$region[!is.na(sample$race_eth_m) & !is.na(sample$sqrt_agediff) & mrp_type_r %in% "One time"])

```

Next we will look at how to parameterize age by plotting the ceofficients from the full model with age input as a dummy variable with 5-year age bins
```{r}
 #Figure out how to parameterize age
    sqrtagediff_inst_full_testage <- lm(sqrt_agediff ~ age_cat + race_eth_m.reg + region.bKC, data=sample[sample$mrp_type_r %in% "One time", ])
    plot.age.coefs(sqrtagediff_inst_full_testage)
```

This plot suggests that the difference between the square root of ego and alter ages increases with age. To be consistent with the approach for main and persistent partnerships, and becuase the estimate for 30-34 does not fit in a linear pattern, we will model age as a categorical variables with ages 40-59 in 10-year bins.

The models and likelihood ratio tests are below.
```{r agemix_inst, eval=TRUE}
 
 #Main effects
  sqrtagediff_inst_full <- lm(sqrt_agediff ~ age_cat_alt + race_eth_m.reg + region.bKC, data=sample[sample$mrp_type_r %in% "One time", ])
  sqrtagediff_inst_noregion <- lm(sqrt_agediff ~ age_cat_alt + race_eth_m.reg, data=sample[sample$mrp_type_r %in% "One time", ])
  sqrtagediff_inst_norace <- lm(sqrt_agediff ~ age_cat_alt + region.bKC, data=sample[sample$mrp_type_r %in% "One time", ])
  sqrtagediff_inst_noage <- lm(sqrt_agediff ~ race_eth_m.reg + region.bKC, data=sample[sample$mrp_type_r %in% "One time", ])

 #Interactions
  sqrtagediff_inst_full_withint <- lm(sqrt_agediff ~ age_cat_alt + race_eth_m.reg + region.bKC + race_eth_m.reg*region.bKC + age_cat_alt*region.bKC + race_eth_m.reg*age_cat_alt, data=sample[sample$mrp_type_r %in% "One time", ])
  sqrtagediff_inst_noraceXreg <- lm(sqrt_agediff ~ age_cat_alt + race_eth_m.reg + region.bKC + age_cat_alt*region.bKC + race_eth_m.reg*age_cat_alt, data=sample[sample$mrp_type_r %in% "One time", ])
  sqrtagediff_inst_noageXreg <- lm(sqrt_agediff ~ age_cat_alt + race_eth_m.reg + region.bKC + race_eth_m.reg*region.bKC + race_eth_m.reg*age_cat_alt, data=sample[sample$mrp_type_r %in% "One time", ])
  sqrtagediff_inst_noraceXage <- lm(sqrt_agediff ~ age_cat_alt + race_eth_m.reg + region.bKC + age_cat_alt*region.bKC + race_eth_m.reg*region.bKC, data=sample[sample$mrp_type_r %in% "One time", ])
  
  results_adiff_inst <- compare.models(sqrtagediff_inst_full, sqrtagediff_inst_noregion, sqrtagediff_inst_norace, sqrtagediff_inst_noage, sqrtagediff_inst_full_withint, sqrtagediff_inst_noraceXreg, sqrtagediff_inst_noageXreg, sqrtagediff_inst_noraceXage) 
  results_adiff_inst
```

## Partnership age
Partnership age was modeled as a linear outcome.

### Main partners
We first look at the number of observations that re non-missing for this outcome and for model predictors
```{r}
 #Look at the number of observations that are non-missing for this outcome and for model predictors
  table(sample$hbo[!is.na(sample$race_eth_m) & !is.na(sample$pship_age_main)], sample$age_cat[!is.na(sample$race_eth_m) & !is.na(sample$pship_age_main)], sample$region[!is.na(sample$race_eth_m) & !is.na(sample$pship_age_main)])

```

Next we will look at how to parameterize age by plotting the ceofficients from the full model with age input as a dummy variable with 5-year age bins
```{r}
 #Figure out how to parameterize age
    pshipage_main_full_testage <- lm(pship_age_main ~ age_cat + race_eth_m.reg + region.bKC, data=sample)
    plot.age.coefs(pshipage_main_full_testage)
```

The coefficients appear to follow a mostly linear trend with age, <span style="color:red"> so we will model age as a linear covariate.</span>

The models and likelihood ratio tests are below.
```{r pshipage_main, eval=TRUE}

 #Main effects
  pshipage_main_full <- lm(pship_age_main ~ age + race_eth_m.reg + region.bKC, data=sample)
  pshipage_main_noregion <- lm(pship_age_main ~ age + race_eth_m.reg, data=sample)
  pshipage_main_norace <- lm(pship_age_main ~ age + region.bKC, data=sample)
  pshipage_main_noage <- lm(pship_age_main ~ race_eth_m.reg + region.bKC, data=sample)

 #Interactions
  pshipage_main_full_withint <- lm(pship_age_main ~ age + race_eth_m.reg + region.bKC + race_eth_m.reg*region.bKC + age*region.bKC + race_eth_m.reg*age, data=sample)
  pshipage_main_noraceXreg <- lm(pship_age_main ~ age + race_eth_m.reg + region.bKC + age*region.bKC + race_eth_m.reg*age, data=sample)
  pshipage_main_noageXreg <- lm(pship_age_main ~ age + race_eth_m.reg + region.bKC + race_eth_m.reg*region.bKC + race_eth_m.reg*age, data=sample)
  pshipage_main_noraceXage <- lm(pship_age_main ~ age + race_eth_m.reg + region.bKC + age*region.bKC + race_eth_m.reg*region.bKC, data=sample)
  
  results_pshipage_main <- compare.models(pshipage_main_full, pshipage_main_noregion, pshipage_main_norace, pshipage_main_noage, pshipage_main_full_withint, pshipage_main_noraceXreg, pshipage_main_noageXreg, pshipage_main_noraceXage)  
  results_pshipage_main

```

                
### Persistent partners
We first look at the number of observations that re non-missing for this outcome and for model predictors
```{r}
  #Look at the number of observations that are non-missing for this outcome and for model predictors
  table(sample$hbo[!is.na(sample$race_eth_m) & !is.na(sample$pship_age_pers)], sample$age_cat[!is.na(sample$race_eth_m) & !is.na(sample$pship_age_pers)], sample$region[!is.na(sample$race_eth_m) & !is.na(sample$pship_age_pers)])

```

Next we will look at how to parameterize age by plotting the ceofficients from the full model with age input as a dummy variable with 5-year age bins
```{r}
 #Figure out how to parameterize age
    pshipage_pers_full_testage <- lm(pship_age_pers ~ age_cat + race_eth_m.reg + region.bKC, data=sample)
    plot.age.coefs(pshipage_pers_full_testage)
```

The coefficients do not follow a linear pattern, and do not seem to indicate any meaningful pattern by age. As such, we will exclude age from the models below. <span style="color:red"> Is it okay to do this if I include it for main partnerships?</span>

The models and likelihood ratio tests are below.
```{r pshipage_pers, eval=TRUE}

 #Main effects
  pshipage_pers_full <- lm(pship_age_pers ~ race_eth_m.reg + region.bKC, data=sample)
  pshipage_pers_noregion <- lm(pship_age_pers ~ race_eth_m.reg, data=sample)
  pshipage_pers_norace <- lm(pship_age_pers ~ region.bKC, data=sample)

 #Interactions
  pshipage_pers_full_withint <- lm(pship_age_pers ~ race_eth_m.reg + region.bKC + race_eth_m.reg*region.bKC, data=sample)
  pshipage_pers_noraceXreg <- lm(pship_age_pers ~ race_eth_m.reg + region.bKC, data=sample)

  results_pshipage_pers <- compare.models.noage(pshipage_pers_full, pshipage_pers_noregion, pshipage_pers_norace, pshipage_pers_full_withint, pshipage_pers_noraceXreg)  
  results_pshipage_pers
```

## Proportion never tested
The parameter indicating the proportion of men who never test is meant to indicate the proportion of men who will not be screened for HIV. In previous network models, this was defined as the proportion who never tested by age 40, since the model was capped at age 39. For this model, that may not be appropriate. For the current analysis, I simply modeled the probability that men had ever tested at their current age. This analysis excludes men currently taking PrEP, as they will all have tested and their testing patterns will be represented differently in the model.

We first look at the number of observations that re non-missing for this outcome and for model predictors
```{r}
   #Look at the number of observations that are non-missing for this outcome and for model predictors
  table(sample$hbo[!is.na(sample$race_eth_m) & !is.na(sample$evertest_r) & !(sample$prep_use_r %in% "Currently taking PrEP")], sample$age_cat[!is.na(sample$race_eth_m) & !is.na(sample$evertest_r) & !(sample$prep_use_r %in% "Currently taking PrEP")], sample$region[!is.na(sample$race_eth_m) & !is.na(sample$evertest_r) & !(sample$prep_use_r %in% "Currently taking PrEP")])

```

Next we will look at how to parameterize age by plotting the ceofficients from the full model with age input as a dummy variable with 5-year age bins
```{r}
 #Figure out how to parameterize age
    evertest_full_testage <- glm(evertest_r ~ age_cat + race_eth_m.reg + region.bKC, family=binomial(link="logit"), data=sample, subset = !(prep_use_r %in% "Currently taking PrEP"))
    plot.age.coefs(evertest_full_testage)
```
<span style="color:red">Should I just define the outcome now how I will represent it in the model? It looks like the proportion ever tested increases through ~ age 40 (code: agetest <- sample %>% filter(!is.na(evertest_r)) %>% group_by(age) %>% summarise(prop = mean(evertest_r)) then ggplot(agetest, aes(x=age, y=prop)) + geom_point() + geom_smooth(method="loess")), so could I just define the outcome as the proportion never tested by this age? Would I then only include data from men aged 40 (n=16) or include men aged 40-44 (n=72), 40-49 (n=145), 40+ (n=271)?</span>

The coefficients do not follow a linear pattern, but they do seem to suggest a pattern by age.  Especially because this outcome will most likely be conditional on age (e.g. proportion never tested by age X) in the model, we will adjust for age in the analyses below to test for heterogeneity by race/ethnicity and region. The number of respondents in older age groups seems sufficient to allow for categorizing age in 5-year bins.

The models and likelihood ratio tests are below.
```{r nevertest}
  
 #Main effects
  evertest_full <- glm(evertest_r ~ age_cat + race_eth_m.reg + region.bKC, family=binomial(link="logit"), data=sample, subset = !(prep_use_r %in% "Currently taking PrEP"))
  evertest_noregion <- glm(evertest_r ~ age_cat + race_eth_m.reg, family=binomial(link="logit"), data=sample, subset = !(prep_use_r %in% "Currently taking PrEP"))
  evertest_norace <- glm(evertest_r ~ age_cat + region.bKC, family=binomial(link="logit"), data=sample, subset = !(prep_use_r %in% "Currently taking PrEP"))
  evertest_noage <- glm(evertest_r ~ race_eth_m.reg + region.bKC, family=binomial(link="logit"), data=sample, subset = !(prep_use_r %in% "Currently taking PrEP"))

 #Interactions
  evertest_full_withint <- glm(evertest_r ~ age_cat + race_eth_m.reg + region.bKC + race_eth_m.reg*region.bKC + age_cat*region.bKC + race_eth_m.reg*age_cat, family=binomial(link="logit"), data=sample, subset = !(prep_use_r %in% "Currently taking PrEP"))
  evertest_noraceXreg <- glm(evertest_r ~ age_cat + race_eth_m.reg + region.bKC + age_cat*region.bKC + race_eth_m.reg*age_cat, family=binomial(link="logit"), data=sample, subset = !(prep_use_r %in% "Currently taking PrEP"))
  evertest_noageXreg <- glm(evertest_r ~ age_cat + race_eth_m.reg + region.bKC + race_eth_m.reg*region.bKC + race_eth_m.reg*age_cat, family=binomial(link="logit"), data=sample, subset = !(prep_use_r %in% "Currently taking PrEP"))
  evertest_noraceXage <- glm(evertest_r ~ age_cat + race_eth_m.reg + region.bKC + age_cat*region.bKC + race_eth_m.reg*region.bKC, family=binomial(link="logit"), data=sample, subset = !(prep_use_r %in% "Currently taking PrEP"))
  
  results_evertest <- compare.models(evertest_full, evertest_noregion, evertest_norace, evertest_noage, evertest_full_withint, evertest_noraceXreg, evertest_noageXreg, evertest_noraceXage)
  results_evertest
 
```


## Intertest interval
The last test interval is estimated as the days since men reported their last HIV test, assuming men test as an interval process (see Section \@ref(iti). This analysis is restricted to men who reported having ever tested, and excludes men who reported current use of PrEP, as their testing patterns will be different and will be represented with a separate parameter in the model.

We first look at the number of observations that re non-missing for this outcome and for model predictors
```{r}
  #Look at the number of observations that are non-missing for this outcome and for model predictors
  table(sample$hbo[!is.na(sample$race_eth_m) & !is.na(sample$iti) & !(sample$prep_use_r %in% "Currently taking PrEP")], sample$age_cat[!is.na(sample$race_eth_m) & !is.na(sample$iti) & !(sample$prep_use_r %in% "Currently taking PrEP")], sample$region[!is.na(sample$race_eth_m) & !is.na(sample$iti) & !(sample$prep_use_r %in% "Currently taking PrEP")])

```

Next we will look at how to parameterize age by plotting the ceofficients from the full model with age input as a dummy variable with 5-year age bins
```{r}
 #Figure out how to parameterize age
    iti_full_testage <- lm(iti ~ age_cat + race_eth_m.reg + region.bKC, data=sample, subset = !(prep_use_r %in% "Currently taking PrEP"))
    plot.age.coefs(iti_full_testage)
```

The coefficients suggest that the intertest interval increases with age, though the estimates do not follow a clear pattern. <span style="color:red"> ??? It may be appropriate to group age into the following bins: 18-24, 25-34, 35+. </span>

The models and likelihood ratio tests are below.
```{r iti, eval=TRUE}

 #Main effects
  iti_full <- lm(iti ~ age_cat + race_eth_m.reg + region.bKC, data=sample, subset = !(prep_use_r %in% "Currently taking PrEP"))
  iti_noregion <- lm(iti ~ age_cat + race_eth_m.reg, data=sample, subset = !(prep_use_r %in% "Currently taking PrEP"))
  iti_norace <- lm(iti ~ age_cat + region.bKC, data=sample, subset = !(prep_use_r %in% "Currently taking PrEP"))
  iti_noage <- lm(iti ~ race_eth_m.reg + region.bKC, data=sample, subset = !(prep_use_r %in% "Currently taking PrEP"))

 #Interactions
  iti_full_withint <- lm(iti ~ age_cat + race_eth_m.reg + region.bKC + race_eth_m.reg*region.bKC + age_cat*region.bKC + race_eth_m.reg*age_cat, data=sample, subset = !(prep_use_r %in% "Currently taking PrEP"))
  iti_noraceXreg <- lm(iti ~ age_cat + race_eth_m.reg + region.bKC + age_cat*region.bKC + race_eth_m.reg*age_cat, data=sample, subset = !(prep_use_r %in% "Currently taking PrEP"))
  iti_noageXreg <- lm(iti ~ age_cat + race_eth_m.reg + region.bKC + race_eth_m.reg*region.bKC + race_eth_m.reg*age_cat, data=sample, subset = !(prep_use_r %in% "Currently taking PrEP"))
  iti_noraceXage <- lm(iti ~ age_cat + race_eth_m.reg + region.bKC + age_cat*region.bKC + race_eth_m.reg*region.bKC, data=sample, subset = !(prep_use_r %in% "Currently taking PrEP"))
  
  results_iti <- compare.models(iti_full, iti_noregion, iti_norace, iti_noage, iti_full_withint, iti_noraceXreg, iti_noageXreg, iti_noraceXage)  
  results_iti
```

## Coital frequency
Data on coital frequency are from all most recent partnerships, not just those that are ongoing. 

### Main partners
We first look at the number of observations that re non-missing for this outcome and for model predictors
```{r}
 #Look at the number of observations that are non-missing for this outcome and for model predictors
  table(sample$hbo[!is.na(sample$race_eth_m) & !is.na(sample$airate_main)], sample$age_cat[!is.na(sample$race_eth_m) & !is.na(sample$airate_main)], sample$region[!is.na(sample$race_eth_m) & !is.na(sample$airate_main)])
```

Next we will look at how to parameterize age by plotting the ceofficients from the full model with age input as a dummy variable with 5-year age bins
```{r}
 #Figure out how to parameterize age
    airate_main_full_testage <- lm(airate_main ~ age_cat + race_eth_m.reg + region.bKC, data=sample)
    plot.age.coefs(airate_main_full_testage)
```

From these coefficients, coital frequency does not appear to follow a meaningful trend by age. The estimate for men aged 30-34 appears higher, but no other estiamtes are statistically significant. We will exclude age from subsequent analyses.

The models and likelihood ratio tests are below.
```{r coitalfreq_main}
 #Main effects
  airate_main_full <- lm(airate_main ~ race_eth_m.reg + region.bKC, data=sample)
  airate_main_noregion <- lm(airate_main ~ race_eth_m.reg, data=sample)
  airate_main_norace <- lm(airate_main ~ region.bKC, data=sample)

 #Interactions
  airate_main_full_withint <- lm(airate_main ~ race_eth_m.reg + region.bKC + race_eth_m.reg*region.bKC, data=sample)
  airate_main_noraceXreg <- lm(airate_main ~ race_eth_m.reg + region.bKC, data=sample)
  
  results_coitalfreq_main <- compare.models.noage(airate_main_full, airate_main_noregion, airate_main_norace, airate_main_full_withint, airate_main_noraceXreg)
  results_coitalfreq_main
  
```


### Persistent partners
We first look at the number of observations that re non-missing for this outcome and for model predictors
```{r}
 #Look at the number of observations that are non-missing for this outcome and for model predictors
  table(sample$hbo[!is.na(sample$race_eth_m) & !is.na(sample$airate_pers)], sample$age_cat[!is.na(sample$race_eth_m) & !is.na(sample$airate_pers)], sample$region[!is.na(sample$race_eth_m) & !is.na(sample$airate_pers)])

```

Next we will look at how to parameterize age by plotting the ceofficients from the full model with age input as a dummy variable with 5-year age bins
```{r}
 #Figure out how to parameterize age
    airate_pers_full_testage <- lm(airate_pers ~ age_cat + race_eth_m.reg + region.bKC, data=sample)
    plot.age.coefs(airate_pers_full_testage)
```

As above for coital frequency in main partnerships, there does not appear to be a meaningful trend by age, so we will exclude age.

The models and likelihood ratio tests are below.
```{r coitalfreq_pers}

 #Main effects
  airate_pers_full <- lm(airate_pers ~ race_eth_m.reg + region.bKC, data=sample)
  airate_pers_noregion <- lm(airate_pers ~ race_eth_m.reg, data=sample)
  airate_pers_norace <- lm(airate_pers ~ region.bKC, data=sample)

 #Interactions
  airate_pers_full_withint <- lm(airate_pers ~ race_eth_m.reg + region.bKC + race_eth_m.reg*region.bKC, data=sample)
  airate_pers_noraceXreg <- lm(airate_pers ~ race_eth_m.reg + region.bKC, data=sample)
  
  results_coitalfreq_pers <- compare.models.noage(airate_pers_full, airate_pers_noregion, airate_pers_norace, airate_pers_full_withint, airate_pers_noraceXreg)
  results_coitalfreq_pers
```

## Sex role
Sex role is categorized as exclusively bottom, exclusively top, or versatile, based on men's reported role in anal sex over the past 12 months. Responses of "mostly a bottom", "mostly a top", and "equally a bottom and a top" were categorized as versatile. For this analysis, a dichotomous indicator was constructed to measure whether men report any bottoming (bottoms and versatile men) or report exclusively topping.

We first look at the number of observations that are non-missing for this outcome and for model predictors
```{r}
 sample$position_top <- ifelse(sample$position_cat=="Exclusively top", 1, 
                                      ifelse(!is.na(sample$position_cat), 0, NA))
  sample$position_bottom <- ifelse(sample$position_cat=="Exclusively bottom", 1, 
                                      ifelse(!is.na(sample$position_cat), 0, NA))
  
  #Look at the number of observations that are non-missing for this outcome and for model predictors
  table(sample$hbo[!is.na(sample$race_eth_m) & !is.na(sample$position_top)], sample$age_cat[!is.na(sample$race_eth_m) & !is.na(sample$position_top)], sample$region[!is.na(sample$race_eth_m) & !is.na(sample$position_top)])

```

Next we will look at how to parameterize age by plotting the ceofficients from the full model with age input as a dummy variable with 5-year age bins
```{r}
 #Figure out how to parameterize age
    top_full_testage <-  glm(position_top ~ age_cat + race_eth_m.reg + region.bKC, family=binomial(link="logit"), data=sample)
    plot.age.coefs(top_full_testage)
```

Although the proportion of men reporting that they are exclusive tops seems to increase through age 44, it then fluctuates for older age groups. This suggests that there is not a clear pattern by age, so we will not explore age heterogeneity further. 

The models and likelihood ratio tests for race/ethnicity and region are below.
```{r sexrole}
  
 #Main effects
  top_full <- glm(position_top ~ race_eth_m.reg + region.bKC, family=binomial(link="logit"), data=sample)
  top_noregion <- glm(position_top ~ race_eth_m.reg, family=binomial(link="logit"), data=sample)
  top_norace <- glm(position_top ~ region.bKC, family=binomial(link="logit"), data=sample)

 #Interactions
  top_full_withint <- glm(position_top ~ race_eth_m.reg + region.bKC + race_eth_m.reg*region.bKC, family=binomial(link="logit"), data=sample)
  top_noraceXreg <- glm(position_top ~ race_eth_m.reg + region.bKC, family=binomial(link="logit"), data=sample)
  
  results_sexrole <- compare.models.noage(top_full, top_noregion, top_norace, top_full_withint, top_noraceXreg)
  results_sexrole
  
```

## Condom use
Data on condom use are restricted to dyads in which both the respondent and his partner were HIV-negative or of unknown status. This analysis includes data from all such partnerships, not just those that were ongoing. 

### Main partners
We first look at the number of observations that are non-missing for this outcome and for model predictors
```{r}
 
 #Look at the number of observations that are non-missing for this outcome and for model predictors
  table(sample$hbo[!is.na(sample$race_eth_m) & !is.na(sample$condoms_main)], sample$age_cat[!is.na(sample$race_eth_m) & !is.na(sample$condoms_main)], sample$region[!is.na(sample$race_eth_m) & !is.na(sample$condoms_main)])

```

Next we will look at how to parameterize age by plotting the ceofficients from the full model with age input as a dummy variable with 5-year age bins
```{r}
 #Figure out how to parameterize age
    condoms_main_full_testage <- lm(condoms_main ~ age_cat + race_eth_m.reg + region.bKC, data=sample)
    plot.age.coefs(condoms_main_full_testage)
```

The plot of these coefficients suggests that condom use in main partnerships decreases with age through age 49 and then increases slightly. The number of respondents aged 40 and higher is somewhat small, so we will group ages 40-59 in 10-year bins. 

```{r condoms_main}

 #Main effects
  condoms_main_full <- lm(condoms_main ~ age_cat_alt + race_eth_m.reg + region.bKC, data=sample)
  condoms_main_noregion <- lm(condoms_main ~ age_cat_alt + race_eth_m.reg, data=sample)
  condoms_main_norace <- lm(condoms_main ~ age_cat_alt + region.bKC, data=sample)
  condoms_main_noage <- lm(condoms_main ~ race_eth_m.reg + region.bKC, data=sample)

 #Interactions
  condoms_main_full_withint <- lm(condoms_main ~ age_cat_alt + race_eth_m.reg + region.bKC + race_eth_m.reg*region.bKC + age_cat_alt*region.bKC + race_eth_m.reg*age_cat_alt, data=sample)
  condoms_main_noraceXreg <- lm(condoms_main ~ age_cat_alt + race_eth_m.reg + region.bKC + age_cat_alt*region.bKC + race_eth_m.reg*age_cat_alt, data=sample)
  condoms_main_noageXreg <- lm(condoms_main ~ age_cat_alt + race_eth_m.reg + region.bKC + race_eth_m.reg*region.bKC + race_eth_m.reg*age_cat_alt, data=sample)
  condoms_main_noraceXage <- lm(condoms_main ~ age_cat_alt + race_eth_m.reg + region.bKC + age_cat_alt*region.bKC + race_eth_m.reg*region.bKC, data=sample)
  
 results_condoms_main <- compare.models(condoms_main_full, condoms_main_noregion, condoms_main_norace, condoms_main_noage, condoms_main_full_withint, condoms_main_noraceXreg, condoms_main_noageXreg, condoms_main_noraceXage)
  results_condoms_main
```


### Persistent partners
We first look at the number of observations that are non-missing for this outcome and for model predictors
```{r}
 
 #Look at the number of observations that are non-missing for this outcome and for model predictors
  table(sample$hbo[!is.na(sample$race_eth_m) & !is.na(sample$condoms_pers)], sample$age_cat[!is.na(sample$race_eth_m) & !is.na(sample$condoms_pers)], sample$region[!is.na(sample$race_eth_m) & !is.na(sample$condoms_pers)])

```

Next we will look at how to parameterize age by plotting the ceofficients from the full model with age input as a dummy variable with 5-year age bins
```{r}
 #Figure out how to parameterize age
    condoms_pers_full_testage <- lm(condoms_pers ~ age_cat + race_eth_m.reg + region.bKC, data=sample)
    plot.age.coefs(condoms_pers_full_testage)
```

The pattern by age is less clear for this condom use with persistent partners than with main partners. <span style="color:red"> We will not include age in models testing associations by race/ethnicity and region </span>

```{r condoms_pers}

 #Main effects
  condoms_pers_full <- lm(condoms_pers ~ race_eth_m.reg + region.bKC, data=sample)
  condoms_pers_noregion <- lm(condoms_pers ~ race_eth_m.reg, data=sample)
  condoms_pers_norace <- lm(condoms_pers ~ region.bKC, data=sample)

 #Interactions
  condoms_pers_full_withint <- lm(condoms_pers ~ race_eth_m.reg + region.bKC + race_eth_m.reg*region.bKC, data=sample)
  condoms_pers_noraceXreg <- lm(condoms_pers ~ race_eth_m.reg + region.bKC, data=sample)
  
  results_condoms_pers <- compare.models.noage(condoms_pers_full, condoms_pers_noregion, condoms_pers_norace, condoms_pers_full_withint, condoms_pers_noraceXreg)
  results_condoms_pers
  
```

### Instantaneous partners
We first look at the number of observations that are non-missing for this outcome and for model predictors
```{r}

 #Look at the number of observations that are non-missing for this outcome and for model predictors
  table(sample$hbo[!is.na(sample$race_eth_m) & !is.na(sample$condoms_inst)], sample$age_cat[!is.na(sample$race_eth_m) & !is.na(sample$condoms_inst)], sample$region[!is.na(sample$race_eth_m) & !is.na(sample$condoms_inst)])

```

Next we will look at how to parameterize age by plotting the ceofficients from the full model with age input as a dummy variable with 5-year age bins
```{r}
 #Figure out how to parameterize age
    condoms_inst_full_testage <- glm(condoms_inst ~ age_cat + race_eth_m.reg + region.bKC, family=binomial(link="logit"), data=sample)
    plot.age.coefs(condoms_inst_full_testage)
```

The plot of these coefficients suggests that there is not meaningful trend by age for the probability of condom use with instantaneous partners.

```{r condoms_inst}

 #Main effects
  condoms_inst_full <- glm(condoms_inst ~ race_eth_m.reg + region.bKC, family=binomial(link="logit"), data=sample)
  condoms_inst_noregion <- glm(condoms_inst ~ race_eth_m.reg, family=binomial(link="logit"), data=sample)
  condoms_inst_norace <- glm(condoms_inst ~ region.bKC, family=binomial(link="logit"), data=sample)

 #Interactions
  condoms_inst_full_withint <- glm(condoms_inst ~ race_eth_m.reg + region.bKC + race_eth_m.reg*region.bKC, family=binomial(link="logit"), data=sample)
  condoms_inst_noraceXreg <- glm(condoms_inst ~ race_eth_m.reg + region.bKC, family=binomial(link="logit"), data=sample)
  
  results_condoms_inst <- compare.models(condoms_inst_full, condoms_inst_noregion, condoms_inst_norace, condoms_inst_full_withint, condoms_inst_noraceXreg)
  results_condoms_inst
  
```


## PrEP use
To look at differences in PrEP use, the outcome is reported current use of PrEP _among those for whom PrEP is recommended_.

We first look at the number of observations that are non-missing for this outcome and for model predictors
```{r}
 
#Look at the number of observations that are non-missing for this outcome and for model predictors
  table(sample$hbo[!is.na(sample$race_eth_m) & !is.na(sample$prep_use_curr) & sample$prepelig_r %in% "Recommend"], sample$age_cat[!is.na(sample$race_eth_m) & !is.na(sample$prep_use_curr) & sample$prepelig_r %in% "Recommend"], sample$region[!is.na(sample$race_eth_m) & !is.na(sample$prep_use_curr) & sample$prepelig_r %in% "Recommend"])

```

Next we will look at how to parameterize age by plotting the ceofficients from the full model with age input as a dummy variable with 5-year age bins
```{r}
 #Figure out how to parameterize age
    prep_full_testage <- glm(prep_use_curr ~ age_cat + race_eth_m.reg + region.bKC, family=binomial(link="logit"), data=sample, subset=prepelig_r %in% "Recommend")
    plot.age.coefs(prep_full_testage)
```

The plot of these coefficients suggests that the probability of PrEP use is significantly higher for those aged 25-49 (and non-significantly higher for those aged 50-59) relative to those aged 18-24. Due to the small number of observations among men aged 40 and older, we will group ages 40-59 into 10-year age groups and include age as a factor variable. 

The models and likelihood ratio tests are below.
```{r prep}

 #Main effects
  prep_full <- glm(prep_use_curr ~ age_cat_alt + race_eth_m.reg + region.bKC, family=binomial(link="logit"), data=sample, subset=prepelig_r %in% "Recommend")
  prep_noregion <- glm(prep_use_curr ~ age_cat_alt + race_eth_m.reg, family=binomial(link="logit"), data=sample, subset=prepelig_r %in% "Recommend")
  prep_norace <- glm(prep_use_curr ~ age_cat_alt + region.bKC, family=binomial(link="logit"), data=sample, subset=prepelig_r %in% "Recommend")
  prep_noage <- glm(prep_use_curr ~ race_eth_m.reg + region.bKC, family=binomial(link="logit"), data=sample, subset=prepelig_r %in% "Recommend")

 #Interactions
  prep_full_withint <- glm(prep_use_curr ~ age_cat_alt + race_eth_m.reg + region.bKC + race_eth_m.reg*region.bKC + age_cat_alt*region.bKC + race_eth_m.reg*age_cat_alt, family=binomial(link="logit"), data=sample, subset=prepelig_r %in% "Recommend")
  prep_noraceXreg <- glm(prep_use_curr ~ age_cat_alt + race_eth_m.reg + region.bKC + age_cat_alt*region.bKC + race_eth_m.reg*age_cat_alt, family=binomial(link="logit"), data=sample, subset=prepelig_r %in% "Recommend")
  prep_noageXreg <- glm(prep_use_curr ~ age_cat_alt + race_eth_m.reg + region.bKC + race_eth_m.reg*region.bKC + race_eth_m.reg*age_cat_alt, family=binomial(link="logit"), data=sample, subset=prepelig_r %in% "Recommend")
  prep_noraceXage <- glm(prep_use_curr ~ age_cat_alt + race_eth_m.reg + region.bKC + age_cat_alt*region.bKC + race_eth_m.reg*region.bKC, family=binomial(link="logit"), data=sample, subset=prepelig_r %in% "Recommend")
  
  results_prep <- compare.models(prep_full, prep_noregion, prep_norace, prep_noage, prep_full_withint, prep_noraceXreg, prep_noageXreg, prep_noraceXage)
  results_prep

```


## Summary tables
<span style="color:red"> UPDATE - will ned to change the indexing for results as the result objects no longer contain the summary of the models as the first adn third list items (now only the p-values from the LR tests) and age is not tested for some covariates - put as NA for those.</span>

```{r summaries}
# 
#     summary_network <- cbind.data.frame("Parameter" = c("One or more partners", "Any concurrent partners", "Rate of instantaneous partners", "Main partnerships", "Persistent partnerships", "Instantaneous partnerships", "Main partnerships", "Persistent partnerships", "Instantaneous partnerships", "Main partnerships", "Persistent partnerships"), "Region" = c(results_hasmain[[2]][1,3], results_concurrent[[2]][1,3], results_rate_inst[[2]][1,3], results_samerace_main[[2]][1,3], results_samerace_pers[[2]][1,3], results_samerace_inst[[2]][1,3], results_adiff_main[[2]][1,3], results_adiff_pers[[2]][1,3], results_adiff_inst[[2]][1,3], results_pshipage_main[[2]][1,3], results_pshipage_pers[[2]][1,3]), "Race" = c(results_hasmain[[2]][2,3], results_concurrent[[2]][2,3], results_rate_inst[[2]][2,3], results_samerace_main[[2]][2,3], results_samerace_pers[[2]][2,3], results_samerace_inst[[2]][2,3], results_adiff_main[[2]][2,3], results_adiff_pers[[2]][2,3], results_adiff_inst[[2]][2,3], results_pshipage_main[[2]][2,3], results_pshipage_pers[[2]][2,3]), "Age" = c(results_hasmain[[2]][3,3], results_concurrent[[2]][3,3], results_rate_inst[[2]][3,3], results_samerace_main[[2]][3,3], results_samerace_pers[[2]][3,3], results_samerace_inst[[2]][3,3], results_adiff_main[[2]][3,3], results_adiff_pers[[2]][3,3], results_adiff_inst[[2]][3,3], results_pshipage_main[[2]][3,3], results_pshipage_pers[[2]][3,3]), "Race_by_region" = c(results_hasmain[[4]][1,3], results_concurrent[[4]][1,3], results_rate_inst[[4]][1,3], results_samerace_main[[4]][1,3], results_samerace_pers[[4]][1,3], results_samerace_inst[[4]][1,3], results_adiff_main[[4]][1,3], results_adiff_pers[[4]][1,3], results_adiff_inst[[4]][1,3], results_pshipage_main[[4]][1,3], results_pshipage_pers[[4]][1,3]), "Age_by_region" = c(results_hasmain[[4]][2,3], results_concurrent[[4]][2,3], results_rate_inst[[4]][2,3], results_samerace_main[[4]][2,3], results_samerace_pers[[4]][2,3], results_samerace_inst[[4]][2,3], results_adiff_main[[4]][2,3], results_adiff_pers[[4]][2,3], results_adiff_inst[[4]][2,3], results_pshipage_main[[4]][2,3], results_pshipage_pers[[4]][2,3]), "Race_by_age" = c(results_hasmain[[4]][3,3], results_concurrent[[4]][3,3], results_rate_inst[[4]][3,3], results_samerace_main[[4]][3,3], results_samerace_pers[[4]][3,3], results_samerace_inst[[4]][3,3], results_adiff_main[[4]][3,3], results_adiff_pers[[4]][3,3], results_adiff_inst[[4]][3,3], results_pshipage_main[[4]][3,3], results_pshipage_pers[[4]][3,3]))
# 
#     kable(summary_network, col.names=c("Parameter", "Region", "Race", "Age", "Race by region", "Age by region", "Race by age"), caption="Summary of regression model findings for associations with network model parameters") %>% kable_styling(full_width=F, position="center") %>% group_rows("Degree distribution", 1, 2) %>% group_rows("Proportion of partnerships same race", 4, 6) %>% group_rows("Age mixing (sqrt of age difference", 7, 9) %>% group_rows("Partnership age", 10, 11) %>% add_header_above(c(" " = 1, "Main effects" = 3, "Interactions" = 3)) %>% add_footnote(c("*p-value<0.05", "**p-value<0.01", "***p-value<0.001"), notation="number") %>% row_spec(3, bold=TRUE)
#     
#     summary_epidemic <- cbind.data.frame("Parameter" = c("Proportion ever tested", "Intertest interval", "Main partnerships", "Persistent partnerships", "Anal sex as top only", "Main partnerships", "Persistent partnerships", "Instantaneous partnerships", "PrEP use among those recommended"), "Region" = c(results_evertest[[2]][1,3], results_iti[[2]][1,3], results_coitalfreq_main[[2]][1,3], results_coitalfreq_pers[[2]][1,3], results_sexrole[[2]][1,3], results_condoms_main[[2]][1,3], results_condoms_pers[[2]][1,3], results_condoms_inst[[2]][1,3], results_prep[[2]][1,3]), "Race" = c(results_evertest[[2]][2,3], results_iti[[2]][2,3], results_coitalfreq_main[[2]][2,3], results_coitalfreq_pers[[2]][2,3], results_sexrole[[2]][2,3], results_condoms_main[[2]][2,3], results_condoms_pers[[2]][2,3], results_condoms_inst[[2]][2,3], results_prep[[2]][2,3]), "Age" = c(results_evertest[[2]][3,3], results_iti[[2]][3,3], results_coitalfreq_main[[2]][3,3], results_coitalfreq_pers[[2]][3,3], results_sexrole[[2]][3,3], results_condoms_main[[2]][3,3], results_condoms_pers[[2]][3,3], results_condoms_inst[[2]][3,3], results_prep[[2]][3,3]), "Race_by_region" = c(results_evertest[[4]][1,3], results_iti[[4]][1,3], results_coitalfreq_main[[4]][1,3], results_coitalfreq_pers[[4]][1,3], results_sexrole[[4]][1,3], results_condoms_main[[4]][1,3], results_condoms_pers[[4]][1,3], results_condoms_inst[[4]][1,3], results_prep[[4]][1,3]), "Age_by_region" = c(results_evertest[[4]][2,3], results_iti[[4]][2,3], results_coitalfreq_main[[4]][2,3], results_coitalfreq_pers[[4]][2,3], results_sexrole[[4]][2,3], results_condoms_main[[4]][2,3], results_condoms_pers[[4]][2,3], results_condoms_inst[[4]][2,3], results_prep[[4]][2,3]), "Race_by_age" = c(results_evertest[[4]][3,3], results_iti[[4]][3,3], results_coitalfreq_main[[4]][3,3], results_coitalfreq_pers[[4]][3,3], results_sexrole[[4]][3,3], results_condoms_main[[4]][3,3], results_condoms_pers[[4]][3,3], results_condoms_inst[[4]][3,3], results_prep[[4]][3,3]))
# 
#     kable(summary_epidemic, col.names=c("Parameter", "Region", "Race", "Age", "Race by region", "Age by region", "Race by age"), caption="Summary of regression model findings for associations with epidemic model parameters") %>% kable_styling(full_width=F, position="center") %>% group_rows("Coital frequency", 3, 4) %>% group_rows("Condom use", 6, 8) %>% add_header_above(c(" " = 1, "Main effects" = 3, "Interactions" = 3)) %>% add_footnote(c("*p-value<0.05", "**p-value<0.01", "***p-value<0.001"), notation="number") %>% row_spec(c(1,2,5,9), bold=TRUE)
    
    ```

These analyses were intended as a guide to suggest which nodal attributes appear to shape patterns of partnership formation/persistence and behaviors related to transmission and diagnosis. For network model parameters, there appear to be **racial/ethnic differences in race and age mixing** and **age differences in the <span style="color:red">degree distribution</span>, rate of instantaneous partnerships, race mixing, age mixing, and dissolution (partnership age)**. While there are some significant interactions, they do not suggest a clear pattern, so we will focus on the main effects. For epidemic model parameters, we will explore **age effects on HIV testing behavior and condom use**, and **the effects of all three nodal attributes on PrEP use**.

## Plots {#plots}
The plots below further explore the associations highlighted in the above section.

### Race mixing by race and age 

We would expect the proportion of partnerships that are same race to vary by race merely by chance due to the composition of the population, so the fact that this varies by race is not surprising. The first plot (\@ref(fig:plotsexplore_racemixing_1)) below shows the same race partnerships in blue and additionally examines the distribution of off-diagonal partnerships. Dyad race/ethnicity is listed along the x-axis as reported by the respondent, such that partnerships reported by black men with Hispanics are listed separately from partnerships reported by Hispanic men with blacks. The numbers are small for most of the dyad race categories, making this hard to interpret. The second plot (\@ref(fig:plotsexplore_racemixing_2)) looks at race mixing by age group. Plot \@ref(fig:plotsexplore_racemixing_3) shows race mixing by ego race and age group.
```{r plots_explore_racemixing_1}

#Race mixing by race
    # #Look at race mixing distribution expected by chance based on population distribution if everyone had equal contact rates
    #     total.hbo <- (pop.raceregion %>% group_by(hbo) %>% summarise(Freq=sum(Freq)))
    #     racemixing_expected_num <- c("H-H" = ((total.hbo$Freq[total.hbo$hbo %in% "Hispanic"]*total.hbo$Freq[total.hbo$hbo %in% "Hispanic"])/sum(total.hbo$Freq)), "H-B" = ((total.hbo$Freq[total.hbo$hbo %in% "Hispanic"]*total.hbo$Freq[total.hbo$hbo %in% "Black"])/sum(total.hbo$Freq)), "H-O" = ((total.hbo$Freq[total.hbo$hbo %in% "Hispanic"]*total.hbo$Freq[total.hbo$hbo %in% "Other"])/sum(total.hbo$Freq)), "B-H" = ((total.hbo$Freq[total.hbo$hbo %in% "Black"]*total.hbo$Freq[total.hbo$hbo %in% "Hispanic"])/sum(total.hbo$Freq)), "B-B" = ((total.hbo$Freq[total.hbo$hbo %in% "Black"]*total.hbo$Freq[total.hbo$hbo %in% "Black"])/sum(total.hbo$Freq)), "B-O" = ((total.hbo$Freq[total.hbo$hbo %in% "Black"]*total.hbo$Freq[total.hbo$hbo %in% "Other"])/sum(total.hbo$Freq)), "O-H" = ((total.hbo$Freq[total.hbo$hbo %in% "Other"]*total.hbo$Freq[total.hbo$hbo %in% "Hispanic"])/sum(total.hbo$Freq)), "O-B" = ((total.hbo$Freq[total.hbo$hbo %in% "Other"]*total.hbo$Freq[total.hbo$hbo %in% "Black"])/sum(total.hbo$Freq)), "O-O" = ((total.hbo$Freq[total.hbo$hbo %in% "Other"]*total.hbo$Freq[total.hbo$hbo %in% "Other"])/sum(total.hbo$Freq)))
    #     racemixing_expected_rowprob <- c(racemixing_expected_num[1]/sum(racemixing_expected_num[1:3]), racemixing_expected_num[2]/sum(racemixing_expected_num[1:3]), racemixing_expected_num[3]/sum(racemixing_expected_num[1:3]), racemixing_expected_num[4]/sum(racemixing_expected_num[4:6]), racemixing_expected_num[5]/sum(racemixing_expected_num[4:6]), racemixing_expected_num[6]/sum(racemixing_expected_num[4:6]), racemixing_expected_num[7]/sum(racemixing_expected_num[7:9]), racemixing_expected_num[8]/sum(racemixing_expected_num[7:9]), racemixing_expected_num[9]/sum(racemixing_expected_num[7:9]))
    #     racemixing_expected <- cbind.data.frame("hbo" = c("H-H", "H-B", "H-O", "B-H", "B-B", "B-O", "O-H", "O-B", "O-O"), "prob" = racemixing_expected_rowprob)

    racemixingXrace <- sample %>% filter(!is.na(mrp_race_eth_m) & !is.na(mrp_type_ongoing)) %>% group_by(mrp_type_ongoing, race_eth_m, mrp_race_eth_m) %>% summarise(Freq=n()) %>% mutate(Percent = Freq/sum(Freq))
    racemixingXrace$dyadrace <- (c("H-H", "H-B", "H-O", "B-H", "B-B", "B-O", "O-H", "O-B", "O-O", "H-H", "H-B", "H-O", "B-O", "O-H", "O-B", "O-O"))
    racemixingXrace$samerace <- c("Yes", "No", "No", "No", "Yes", "No", "No", "No", "Yes", "Yes", "No", "No", "No", "No", "No", "Yes")
    racemixingXrace$dyadrace <- factor(racemixingXrace$dyadrace, levels = c("H-H", "H-B", "H-O", "B-H", "B-B", "B-O", "O-H", "O-B", "O-O"))
    
    ggplot(racemixingXrace) + geom_point(aes(x=dyadrace, y=Percent, colour=samerace, size=Freq), shape=16) + facet_grid(mrp_type_ongoing ~.) + plot_background + labs(x="Dyad race/ethnicity (ego-alter)", y="Percent", title="Race mixing as reported by ego") + theme_title + ylim(0, 1)

```

```{r plots_explore_racemixing_2}
#Race mixing by age
    racemixingXage <- sample %>% filter(!is.na(mrp_race_eth_m) & !is.na(mrp_type_ongoing)) %>% mutate(samerace = ifelse(race_eth_m==mrp_race_eth_m, 1, 0)) %>% group_by(mrp_type_ongoing, age_chunks) %>% summarise(freq = n(), percent_samerace = mean(samerace))
    
    ggplot(racemixingXage) + geom_point(aes(x=age_chunks, y=percent_samerace, size=freq), shape=16) + facet_grid(mrp_type_ongoing ~.) + plot_background + labs(x="Age group", y="Percent", title="Racial/ethnic homophily by age as reported by ego") + theme_title + ylim(0, 1)
```

```{r plots_explore_racemixing_3}
#Race mixing by age and ego race
    racemixingXageandrace <- sample %>% filter(!is.na(mrp_race_eth_m) & !is.na(mrp_type_ongoing)) %>% group_by(mrp_type_ongoing, age_chunks, race_eth_m, mrp_race_eth_m) %>% summarise(Freq=n()) %>% mutate(Percent = Freq/sum(Freq))
    racemixingXageandrace$samerace <- factor(ifelse(racemixingXageandrace$race_eth_m==racemixingXageandrace$mrp_race_eth_m, "Yes", "No"))
    racemixingXageandrace <-  racemixingXageandrace %>% filter(samerace %in% "Yes")
    
    ggplot(racemixingXageandrace) + geom_point(aes(x=age_chunks, y=Percent, size=Freq, colour=race_eth_m), shape=16) + facet_grid(mrp_type_ongoing ~.) + plot_background + labs(x="Age group", y="Percent", title="Racial/ethnic homophily by age **and ego race** as reported by ego") + theme_title + ylim(0, 1)

```

__Decision__: While it does appear that 40-49 year-olds are slightly more likely to report a partner of the same racial/ethnic group, the data do not suggest a clear or meaningful pattern of race mixing by age. As such, we will not stratify race mixing by age.


### Age mixing by age and race

The left panel of figure \@ref(fig:plots_explore_agemixing_1) shows a scatter plot of respondents ages against the ages reported for their partners in single years. In partnerships below the diagonal line, the ego is older than his partner; in partnerships above the line, the partner is older than the ego. The right panel plots the absolute value of the difference between ego and alter ages, with a superimposed loess smooth curve. Plot \@ref(fig:plots_explore_agemixing_2) shows age mixing by age group and race in terms of the mean absolute difference in age between the ego and his partner in each age group. To inform how to parameterize age differences, plot \@ref(fig:plots_explore_agemixing_3) shows the absolute difference between the square root of ego and alter ages by ego ego, and plot \@ref(fig:plots_explore_agemixing_4) shows the absolute difference between the cube root of ego and alter ages by ego ego.

```{r plots_explore_agemixing_1}

#Age mixing
    sample$agediff <- abs(sample$age - sample$mrp_ageinyears_approx)

    age_scatter <- ggplot(sample[!is.na(sample$mrp_ageinyears_approx) & !is.na(sample$mrp_type_ongoing),]) + geom_point(aes(x=age, y=mrp_ageinyears_approx)) + geom_abline(slope=1, intercept= 0) + facet_grid(mrp_type_ongoing ~.) + labs(x="Ego age", y="Most recent partner age", title="Age differences by single year age")
    
    age_diff <- ggplot(sample[!is.na(sample$agediff) & !is.na(sample$mrp_type_ongoing),], aes(x=age, y=agediff)) + geom_point() + geom_smooth(method="loess") + facet_grid(mrp_type_ongoing ~.) + labs(x="Ego age", y="Absolute value of the difference between ego and alter ages", title = "Age mixing as the difference between ego and alter ages") + theme_title
    
    multiplot(age_scatter, age_diff, cols=2)
    
```

```{r plots_explore_agemixing_2}

#Age mixing by age and race 

    agemixingXrace <- sample %>% filter(!is.na(agediff) & !is.na(mrp_type_ongoing)) %>% group_by(mrp_type_ongoing, age_cat, race_eth_m) %>% summarise(freq= n(), mean = mean(agediff))
    ggplot(agemixingXrace) + geom_point(aes(x=age_cat, y=mean, size=freq, colour=race_eth_m)) + facet_grid(mrp_type_ongoing ~.) + geom_hline(yintercept=0) + labs(x="Ego age group", y="Mean difference between ego and partner age (absolute value)", title="Age differences by race and age category") + theme_title

```

```{r plots_explore_agemixing_3}

#Age mixing represented as square root of age differences
    ggplot(sample[!is.na(sample$sqrt_agediff) & !is.na(sample$mrp_type_ongoing),], aes(x=age, y=sqrt_agediff)) + geom_point() + geom_smooth(method="loess") + facet_grid(mrp_type_ongoing ~.) + labs(x="Ego age", y="Absolute value of the difference between the sqrt of ego and the sqrt of alter ages", title = "Age mixing as the difference between the square root of ego and alter ages") + theme_title

```

```{r plots_explore_agemixing_4}
    sample$cbrt_agediff <- abs(sample$age^(1/3) - sample$mrp_ageinyears_approx^(1/3))

    ggplot(sample[!is.na(sample$cbrt_agediff) & !is.na(sample$mrp_type_ongoing),], aes(x=age, y=cbrt_agediff)) + geom_point() + geom_smooth(method="loess") + facet_grid(mrp_type_ongoing ~.) + labs(x="Ego age", y="Absolute value of the difference between the cube root of ego and the cube root of alter ages", title = "Age mixing as the difference between the cube root of ego and alter ages") + theme_title
   
```

__Decision__: The patterns for non-Hispanic other and Hispanic respondents appear similar. Black men ages 18-24 report partners who are, on average, further in age from themselves than the other racial/ethnic groups. But the numbers are small: `r sum(!is.na(sample$mrp_ageinyears_approx) & sample$race_eth_m %in% "Black" & sample$mrp_type_ongoing %in% "Main" & sample$age_cat %in% "18-24")` black respondents provided data on the age of main partners and only `r sum(!is.na(sample$mrp_ageinyears_approx) & sample$race_eth_m %in% "Black" & sample$mrp_type_ongoing %in% "Persistent" & sample$age_cat %in% "18-24")` provided data on the age of persistent partners. As such, these patterns should be interpreted with caution. To capture potential racial ethnic differences, we will represent heterogeneity in age mixing by race, but we will not attempt to represent an interaction between race and age on patterns of age mixing.

To capture the age heterogeneity in age mixing, we need to decide how to parameterize the age difference. From plots \@ref(fig:plots_explore_agemixing_3) and \@ref(fig:plots_explore_agemixing_4), taking the difference between the square root of ego and alter ages reduces the heterogeneity by age, but does not fully account for differences by ego age in the age difference with persistent partnerships. Taking the cube root does not lead to a noticeable improvement.

### Degree distribution by age
The first plot (\@ref(fig:plots_explore_hasmain)) shows the proportion of men reporting at least one ongoing partner by age. Plot \@ref(fig:plots_explore_concurrent) shows the proportion of men reporting two or more concurrent partners by age.

```{r plots_explore_hasmain}
#One or more ongoing partners by age
    hasmainXage <- sample %>% filter(!is.na(hasmain)) %>% group_by(age_cat) %>% summarise(prop = mean(hasmain, na.rm=TRUE), freq=n())
    
    ggplot(hasmainXage) + geom_point(aes(x=age_cat, y=prop, size=freq), shape=16) + plot_background + labs(x="Age", y="Percent", title="Proportion reporting one or more ongoing partners by age") + theme_title + ylim(0, 1)

```

```{r plots_explore_concurrent}
#One or more ongoing partners by age
    concurrentXage <- sample %>% filter(!is.na(concurrent)) %>% group_by(age_cat) %>% summarise(prop = mean(concurrent, na.rm=TRUE), freq=n())
    
    ggplot(concurrentXage) + geom_point(aes(x=age_cat, y=prop, size=freq), shape=16) + plot_background + labs(x="Age", y="Percent", title="Proportion reporting two or more concurrent partners by age") + theme_title + ylim(0, 1)

```
__Decision__: <span style="color:red"> Fill me in </span>

### Rate of instantaneous partnerships by age

The left panel of figure \@ref(fig:plots_explore_rate_inst_1) shows the reported rate of instantaneous partnerships by respondent age in single years with a superimposed loess smooth curve. From this we see that there are some outliers - 4 respondents who reported >0.25 instantaneous partnerships per day. The right panel shows the same plot but with these 4 outliers removed. Figure \@ref(fig:plots_explore_rate_inst_2) groups ages into smaller bins for those aged 18-34 to get insight as to where the inflection point might be. The high point for ages 35-39 is largely driven by the outliers - removal of these outliers drops the point down in line with the others. 

```{r plots_explore_rateinst_1}
#Rate of instantaneous partnerships by age
    p_rateinstXage <- ggplot(sample[!is.na(sample$rate_inst),], aes(x=age, y=rate_inst)) + geom_point() + geom_smooth(method="loess") + labs(x="Ego age", y="Rate of instantaneous partnerships", title="Rate of instantaneous partnerships by ego age")
    p_rateinstXage_rmoutliers <- ggplot(sample[!is.na(sample$rate_inst) & sample$rate_inst <0.25,], aes(x=age, y=rate_inst)) + geom_point() + geom_smooth(method="loess") + labs(x="Ego age", y="Rate of instantaneous partnerships", title="Rate of instantaneous partnerships by ego age without outliers")
    multiplot(p_rateinstXage, p_rateinstXage_rmoutliers, cols=2)

```

```{r plots_explore_rateinst_2}
    sample$age_cat_explore <- cut(sample$age, c(17, 20, 22, 24, 26, 28, 30, 32, 34, 39, 44, 49, 54, 59), labels=c("18-20", "21-22", "23-24", "25-26", "27-28", "29-30", "31-32", "33-34", "35-39", "40-44", "45-49", "50-54", "55-59"))     
    rateinstXage <- sample %>% filter(!is.na(rate_inst)) %>% group_by(age_cat_explore) %>% summarise(mean = mean(rate_inst), median=median(rate_inst), freq = n()) 
    ggplot(rateinstXage) + geom_point(aes(x=age_cat_explore, y=mean, size=freq)) + labs(x="Ego age", y="Mean rate of instantaneous partnerships", title="Mean rate of instantaneous partnerships by ego age group")

```

To explore this further, we look at the proportion of men in each age group that fall in each of the quartiles of the distribution of instantaneous partnerships identified in section \@ref(rateinst_explore).
```{r plots_explore_rateinst_3}

    quartiles <- quantile(sample$rate_inst, c(0.025, 0.5, 0.75, 1), na.rm=TRUE)
sample$rate_inst_quart <- cut(sample$rate_inst, c(-0.01, quartiles), labels=c("0", "(0, 0.00274]", "(0.00274, 0.00821]", "(0.00821, 0.931]"))
table(sample$rate_inst_quart)

    ageXquartile_explore <- sample %>% filter(!is.na(rate_inst)) %>% group_by(age_cat_explore) %>% summarise(freq=n(), zero = sum(rate_inst_quart %in% "0")/freq, low = sum(rate_inst_quart %in% "(0, 0.00274]")/freq, med = sum(rate_inst_quart %in% "(0.00274, 0.00821]")/freq, high = sum(rate_inst_quart %in% "(0.00821, 0.931]")/freq)
    ggplot(ageXquartile) + geom_point(aes(x=age_cat_explore, y=zero, colour="a"), size=3) +  geom_point(aes(x=age_cat_explore, y=low, color="b"), size=3) + geom_point(aes(x=age_cat_explore, y=med, color="c"), size=3) + geom_point(aes(x=age_cat_explore, y=high, colour="d"), size=3) + scale_colour_manual(name = "Rate of partners", values=c("a"="red", "b"="orange", "c"="yellow", "d"="darkgreen"), labels=c("Zero", "Low", "Medium", "High")) + labs(x="Age group", y="Percent", title="Quantile distribution of the rate of instantaneous partners by detailed age groups") + theme_title + plot_background 
    

    ageXquartile <- sample %>% filter(!is.na(rate_inst)) %>% group_by(age_cat) %>% summarise(freq=n(), zero = sum(rate_inst_quart %in% "0")/freq, low = sum(rate_inst_quart %in% "(0, 0.00274]")/freq, med = sum(rate_inst_quart %in% "(0.00274, 0.00821]")/freq, high = sum(rate_inst_quart %in% "(0.00821, 0.931]")/freq)
    ggplot(ageXquartile) + geom_point(aes(x=age_cat, y=zero, colour="a"), size=3) +  geom_point(aes(x=age_cat, y=low, color="b"), size=3) + geom_point(aes(x=age_cat, y=med, color="c"), size=3) + geom_point(aes(x=age_cat, y=high, colour="d"), size=3) + scale_colour_manual(name = "Rate of partners", values=c("a"="red", "b"="orange", "c"="yellow", "d"="darkgreen"), labels=c("Zero", "Low", "Medium", "High")) + labs(x="Age group", y="Percent", title="Quantile distribution of the rate of instantaneous partners by age group") + theme_title + plot_background 

```

__Decision__: <span style="colour:red"> Fill me in</span>


### Partnership age by respondent age

These plots show the mean partnership age in main and persistent partnerships, respectively, by respondent age.

```{r plotsexplore_pshipage}
#Partnership age by ego age
    pshipage_mainXage <- sample %>% filter(!is.na(pship_age_main)) %>% group_by(age) %>% summarise(freq=n(), mean=mean(pship_age_main))
    ggplot(pshipage_mainXage, aes(x=age, y=mean, size=freq)) + geom_point() + labs(x="Ego age", y="Mean partnership age in days", title = "Mean age of main partnerships by respondent age") 
    
    pshipage_persXage <- sample %>% filter(!is.na(pship_age_pers)) %>% group_by(age) %>% summarise(freq=n(), mean=mean(pship_age_pers))
    ggplot(pshipage_persXage, aes(x=age, y=mean, size=freq)) + geom_point() + labs(x="Ego age", y="Mean partnership age in days", title = "Mean age of persistent partnerships by respondent age") 
    ```
    
### HIV testing by age
The first graph below looks at the proportion of men who report having ever tested by age group. The graph is a bit tricky to interpret because the figure represents both age and cohort effects, and because the number of respondents for some ages is small. It seems that if men don't test by age 40-45, they are unlikely to get tested. The pattern is similar if age is binned in 5 year groups.

The second figure looks at the mean and median intertest intervals by age group.

```{r plotsexplore_testing}
# Ever tested by age
    evertestedXage <- sample_allages %>%
              filter(!is.na(evertest_r) & !is.na(race_eth_m) & !(prep_use_r %in% "Currently taking PrEP")) %>%
              group_by(age) %>%
              summarise(prop = mean(evertest_r, na.rm=TRUE), freq=n())
    ggplot(evertestedXage) + geom_point(aes(x=age, y=prop, size=freq)) + geom_smooth(aes(x=age, y=prop), method="loess") + plot_background + theme_title + labs(x="Ego Age", y="Percent ever tested", title="Percent ever tested by age")        


#Intertest interval by age 
    itiXage <- sample %>% filter(!is.na(iti) & prep_use_r !="Currently taking PrEP") %>% group_by(age) %>% summarise(freq=n(), median=median(iti, na.rm=TRUE), mean=mean(iti, na.rm=TRUE))
    
   ggplot(iti_intervalXage) + geom_point(aes(x=age, y=median, size=freq, colour="Median")) + geom_point(aes(x=age, y=mean, size=freq, colour="Mean")) + geom_smooth(aes(x=age, y=median), method="loess") + geom_smooth(aes(x=age, y=mean), method="loess") + scale_colour_manual(name="Measure", values=c("Median" = "blue", "Mean"="red")) + labs(x="Ego age", y="Days since last test", title="Mean and median intertest intervals by age, assuming testing is an interval process")
        
```

### Condom use by age
The plots below show the probability of condom use by respondent age in main partnerships.
```{r plotsexplore_condoms_main}
#Condom use in main partnerships by ego age
   p_condoms_main <- ggplot(sample[!is.na(sample$condoms_main),], aes(x=age, y=condoms_main)) + geom_point() + labs(x="Ego age", y="Probability of condom use", title = "Probability of condom use in main partnerships by respondent age") + plot_background + theme_title
   condoms_mainXage <- sample %>% filter(!is.na(condoms_main)) %>% group_by(age_cat) %>% summarise(freq=n(), mean=mean(condoms_main))
    p_condoms_main_mean <- ggplot(condoms_mainXage, aes(x=age_cat, y=mean, size=freq)) + geom_point() + labs(x="Ego age", y="Mean probability of condom use", title = "Mean probability of condom use in main partnerships by respondent age") + ylim(0, 1)  + plot_background + theme_title
    multiplot(p_condoms_main_mean, p_condoms_main, cols=1)
```
Probability of condom use by respondent age in persistent partnerships:
```{r plotsexplore_condoms_pers}
#Condom use in persistent partnerships by ego age
 p_condoms_pers <- ggplot(sample[!is.na(sample$condoms_pers),], aes(x=age, y=condoms_pers)) + geom_point() + labs(x="Ego age", y="Probability of condom use", title = "Probability of condom use in persistent partnerships by respondent age") + plot_background + theme_title
   condoms_persXage <- sample %>% filter(!is.na(condoms_pers)) %>% group_by(age_cat) %>% summarise(freq=n(), mean=mean(condoms_pers))
    p_condoms_pers_mean <- ggplot(condoms_persXage, aes(x=age_cat, y=mean, size=freq)) + geom_point() + labs(x="Ego age", y="Mean probability of condom use", title = "Mean probability of condom use in persistent partnerships by respondent age") + ylim(0, 1) + plot_background + theme_title
    multiplot(p_condoms_pers_mean, p_condoms_pers, cols=1)
    ```
Probability of condom use in instantaneous partnerships
```{r plotsexplore_condoms_inst}
#Condom use in instantaneous partnerships by ego age
   condoms_instXage <- sample %>% filter(!is.na(condoms_inst)) %>% group_by(age_cat) %>% summarise(freq=n(), mean=mean(condoms_inst))
    ggplot(condoms_instXage, aes(x=age_cat, y=mean, size=freq)) + geom_point() + labs(x="Ego age", y="Mean probability of condom use", title = "Mean probability of condom use in instantaneous partnerships by respondent age") + ylim(0, 1) + plot_background + theme_title
    ```

### PrEP use by age, race, and region
The plots below illustrate the proportion of men for whom local guidelines recommend PrEP who report current use by age, race, and region
```{r plotsexplore_prep_age}
#PrEP use by age
   prepXage <- sample %>% filter(!is.na(prep_use_curr) & prepelig_r %in% "Recommend") %>% group_by(age_cat) %>% summarise(freq=n(), mean=mean(prep_use_curr))
    ggplot(prepXage, aes(x=age_cat, y=mean, size=freq)) + geom_point() + labs(x="Ego age", y="Mean probability of PrEP use", title = "Mean probability of PrEP use among men recommended to initiate PrEP by age") + ylim(0, 1) + plot_background + theme_title
```
    
```{r plotsexplore_prep_race}
#PrEP use by age
   prepXrace <- sample %>% filter(!is.na(prep_use_curr) & prepelig_r %in% "Recommend") %>% group_by(race_eth_m) %>% summarise(freq=n(), mean=mean(prep_use_curr))
    ggplot(prepXrace, aes(x=race_eth_m, y=mean, size=freq)) + geom_point() + labs(x="Ego race/ethnicity", y="Mean probability of PrEP use", title = "Mean probability of PrEP use among men recommended to initiate PrEP by race/ethnicity") + ylim(0, 1) + plot_background + theme_title
```

```{r plotsexplore_prep_region}
#PrEP use by age
   prepXregion <- sample %>% filter(!is.na(prep_use_curr) & prepelig_r %in% "Recommend") %>% group_by(region) %>% summarise(freq=n(), mean=mean(prep_use_curr))
    ggplot(prepXregion, aes(x=region, y=mean, size=freq)) + geom_point() + labs(x="Region", y="Mean probability of PrEP use", title = "Mean probability of PrEP use among men recommended to initiate PrEP by region") + ylim(0, 1) + plot_background + theme_title
```