# Condom use {#condoms}

```{r, include=FALSE}

####################################################################################
# Setup
####################################################################################
#-----------------------------------------------------------------------------------
# Load packages
#-----------------------------------------------------------------------------------

    library("tidyverse")
    library("knitr")
    library("data.table")
    library("survey")
    library("kableExtra")

#-----------------------------------------------------------------------------------
# Knitr options
#-----------------------------------------------------------------------------------
opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE)
options(knitr.table.format = "html") 

#-----------------------------------------------------------------------------------
# Load data
#-----------------------------------------------------------------------------------
  load(file="Data/InternetSurvey_reweighted_neg.Rdata")
  # load(file="Data/artnet_reweighted_all_w.Rdata")
  # load(file="Data/artnet_reweighted_all_l.Rdata")

#-----------------------------------------------------------------------------------
# set plot settings 
#-----------------------------------------------------------------------------------
    
    #White background and light grey lines
    plot_background_nogrid <- theme(panel.background = element_rect(fill="white", colour = "black")) 
    #Darken colors
    darken_color <- scale_colour_hue(l=50)
    #Title size to 12 and center it 
    theme_title <- theme(plot.title = element_text(hjust = 0.5, size=12)) 
    
#-----------------------------------------------------------------------------------
# Data manipulation
#-----------------------------------------------------------------------------------

 # Define indicator to use in subsetting of dyads in which the ego had not taken PrEP in the past 12 months and the alter was not taking PrEP
    sample_rake_neg$variables$p12noprep_dyad <- ifelse(sample_rake_neg$variables$prep_use_r %in% c("Took PrEP in the past", "Never taken PrEP") & !(sample_rake_neg$variables$monthsago_lastprep %in% c(0:12)) & !(sample_rake_neg$variables$mrp_prep_r %in% 1), "No PrEP", 
                                                  ifelse((sample_rake_neg$variables$prep_use_r %in% c("Currently taking PrEP")) | (sample_rake_neg$variables$prep_use_r %in% c("Took PrEP in the past") & (sample_rake_neg$variables$monthsago_lastprep %in% c(0:12))) | (sample_rake_neg$variables$mrp_prep_r %in% 1), "PrEP",
                                                         NA))
 
 # Define binary indicator of YY vs all other dyads
    sample_rake_neg$variables$dyad_age_bin <- ifelse(sample_rake_neg$variables$dyad_age %in% "YY", "Young-Young", ifelse(!is.na(sample_rake_neg$variables$dyad_age), "Other ages", NA))
    
 # Define indicators of reporting 2+ one-time and 2+ persistent partners
    sample_rake_neg$variables$mt1onetime <- ifelse(sample_rake_neg$variables$numonetime_r %in% c(2: max(sample_rake_neg$variables$numonetime_r, na.rm=TRUE)), 1, NA)
    
    sample_rake_neg$variables$mt1pers <- ifelse(sample_rake_neg$variables$numcasual_r %in% c(2: max(sample_rake_neg$variables$numcasual_r, na.rm=TRUE)), 1, NA)

  # Define variables to indicate those who always use condoms with inst and pers partners, of those with 2+ inst or pers partners, respectively. Denom for each is the total number who reported at least one inst or one pers partner.
    sample_rake_neg$variables$always_condoms_inst_p12 <- ifelse(sample_rake_neg$variables$always_condoms_p12 %in% 1 & sample_rake_neg$variables$mt1onetime %in% 1, 1, 
                                        ifelse(sample_rake_neg$variables$cai_nonmain_r %in% 0 & sample_rake_neg$variables$mt1onetime %in% 1, 1, 
                                        ifelse(sample_rake_neg$variables$numonetime_r %in% c(1:max(sample_rake_neg$variables$numonetime_r, na.rm=TRUE)), 0, NA)))
    
    sample_rake_neg$variables$always_condoms_pers_p12 <- ifelse(sample_rake_neg$variables$always_condoms_p12 %in% 1 & sample_rake_neg$variables$mt1pers %in% 1, 1, 
                                        ifelse(sample_rake_neg$variables$cai_nonmain_r %in% 0 & sample_rake_neg$variables$mt1pers %in% 1, 1, 
                                        ifelse(sample_rake_neg$variables$numcasual_r %in% c(1:max(sample_rake_neg$variables$numcasual_r, na.rm=TRUE)), 0, NA)))
       
    
```

In the model, condom use is specified with base probabilities specific to dyads in which both members are negative or undiagnosed, and coefficients to indicate the change in condom use with diagnosis and disclosure. We use data from the WHPP sample, reweighted to the population totals of negative/undiagnosed men, to estimate these baseline probabilities. <span style="color:red">Because the WHPP sample includes men on PrEP and we will separtely represent changes in condom use with PrEP, we restrict this analysis to men who have not used PrEP in the past 12 months and whose partners are not using PrEP.</span>.

Because we do not have Washington-specific data to estimate the change in condom use with diagnosis and disclosure, we will use data from Atlanta-area studies.

## Main partnerships
Exploratory analyses (\@ref(explore_heterogeneity)) suggest that the probability of condom use in main partnerships varies by the age of both partners, with dyads in which both partners are "young" (ages 18-34) having a higher probability of condom use than all other dyads. As such, we define separate estimates for "Young-Young" dyads and for all other dyads.
```{r}
# Condom use in main partnerships in which neither partner has used PrEP
condoms_main_prob <- svyby(~condoms_main, by=~dyad_age_bin, subset(sample_rake_neg, p12noprep_dyad %in% "No PrEP"), FUN=svymean, na.rm=TRUE)
row.names(condoms_main_prob) <- NULL
condoms_main_prob$dyad_age_bin <- factor(condoms_main_prob$dyad_age_bin, levels = c("Young-Young", "Other ages"))
condoms_main_prob <- arrange(condoms_main_prob, dyad_age_bin)

condoms_main_prob <- cbind.data.frame("Age" = condoms_main_prob[,1], "origN" = c(sum(!is.na(sample_rake_neg$variables$condoms_main) & sample_rake_neg$variables$p12noprep_dyad %in% "No PrEP" & sample_rake_neg$variables$dyad_age_bin %in% "Young-Young"), sum(!is.na(sample_rake_neg$variables$condoms_main) & sample_rake_neg$variables$p12noprep_dyad %in% "No PrEP" & sample_rake_neg$variables$dyad_age_bin %in% "Other ages")), "Mean" = condoms_main_prob[,2], "SE" = condoms_main_prob[,3])

kable(condoms_main_prob, col.names=c("Age", "Unweighted N", "Mean", "SE"), caption="Mean probability of condom use in main partnerships by age of both partners", digits = c(0,0,4,4)) %>% kable_styling(full_width=F, position="center") %>% column_spec(1, width = "3cm") %>% column_spec(2:4, width="3cm")
```

## Persistent partnerships
The EpiModelHIV code is currently set up to identify men who always use condoms in persistent and instantaneous partnerships, and to define the probability of condom use in those who do not always use condoms in these partnerships. Because the WHPP data only ask detailed questions about the most recent partnership, they do not allow for estimation of condom use in the same way as has been done for previous models. However, the WHPP survey does measure whether men reported any condomless anal sex with partners who were not main/primary. We will use this variable to define indicators of the proportion of men who always use condoms with persistent and instantaneous partnerships.  
  - We define the proportion of men who always use condoms with persistent partners as the number of men who reported two or more persistent partners in the past 12 months and reported not having had condomless anal sex with any non-main partners over the total number of men who reported at least one persistent partner. We restrict the numerator to men who reported two or more persitent partners becuase there is not enough information from men who reported only one partner to determine if they always use condoms with persistent partners. This will likely underestimate consistent condom use, however the objective of including these consistent condom use parameters is to better describe how patterns of condom use are distributed in the population. This approach is closer to the truth than if we simulated condom use as a draw from a probability distribution for all men.
  - We then calculate the probability of condom use with persistent partners among men who do not always use condoms, using data from the most recent partnership. Exploratory analyses did not indicate differences in condom use with persistent partnerships by age, race/ethnicity, or region, so these estimates are not stratified.

Note, after restricting to dyads without PrEP use, the estimate of the proportion that always use condoms with persistent partners is based on data from `r sum(sample_rake_neg$variables$p12noprep_dyad %in% "No PrEP" & !is.na(sample_rake_neg$variables$always_condoms_pers_p12))` respondents. The estimated probability of condom use with persistent partners is based on data from `r sum(sample_rake_neg$variables$p12noprep_dyad %in% "No PrEP" & !(sample_rake_neg$variables$always_condoms_pers_p12 %in% 1) & !is.na(sample_rake_neg$variables$condoms_pers))` respondents who reported not always using condoms and reported on a most recent persistent partner.

```{r}
# proportion of men who reported 2+ pers partners and no CAI with non-main partners, of those with 1+ pers partner
condoms_always_pers <- svymean(~always_condoms_pers_p12, subset(sample_rake_neg, p12noprep_dyad %in% "No PrEP"), na.rm=TRUE)

# probability of condom use among those not flagged as consistent condom users
condoms_pers_prob <- svymean(~condoms_pers, subset(sample_rake_neg, p12noprep_dyad %in% "No PrEP" & !(always_condoms_pers_p12 %in% 1)), na.rm=TRUE)

pers_condoms <- cbind.data.frame(Indicator = c("Consistent condom use with persistent partners", "Probability of condom use if not a consistent condom user"), N = c(sum(sample_rake_neg$variables$p12noprep_dyad %in% "No PrEP" & !is.na(sample_rake_neg$variables$always_condoms_pers_p12)), sum(sample_rake_neg$variables$p12noprep_dyad %in% "No PrEP" & !(sample_rake_neg$variables$always_condoms_pers_p12 %in% 1) & !is.na(sample_rake_neg$variables$condoms_pers))), Percent = c(condoms_always_pers[1], condoms_pers_prob[1]), SE = c(round(SE(condoms_always_pers),4), round(SE(condoms_pers_prob),4)))
row.names(pers_condoms) <- NULL

kable(pers_condoms, col.names=c("", "Unweighted N", "Proportion", "SE"), caption="Condom use in persistent partnerships", digits = c(0,0,4,4)) %>% kable_styling(full_width=F, position="center") %>% column_spec(1, width = "10cm") %>% column_spec(2:4, width="2cm")
```

## Instantaneous partnrships
As with persistent partnerships, we calculate the proportion of men who always use condoms with instantaneous partnerships as the the number of men who reported two or more instantaneous partners in the past 12 months and reported not having had condomless anal sex with any non-main partners over the total number of men who reported at least one instantaneous partner. We then calculate the probability of condom use with instantaneous partnerships among men who do not always use condoms with these partners, using data from the most recent partnership. Exploratory analyses did not indicate differences in condom use with instantaneous partnerships by age, race/ethnicity, or region, so these estimates are not stratified.

Note, after restricting to dyads without PrEP use, the estimate of the proportion that always use condoms with instantaneous partners is based on data from `r sum(sample_rake_neg$variables$p12noprep_dyad %in% "No PrEP" & !is.na(sample_rake_neg$variables$always_condoms_inst_p12))` respondents. The estimated probability of condom use with instantaneous partners is based on data from `r sum(sample_rake_neg$variables$p12noprep_dyad %in% "No PrEP" & !(sample_rake_neg$variables$always_condoms_inst_p12 %in% 1) & !is.na(sample_rake_neg$variables$condoms_inst))` respondents who reported not always using condoms and reported on a most recent instantaneous partner.

```{r}
# proportion of men who reported 2+ inst partners and no CAI with non-main partners, of those with 1+ inst partner
condoms_always_inst <- svymean(~always_condoms_inst_p12, subset(sample_rake_neg, p12noprep_dyad %in% "No PrEP"), na.rm=TRUE)

# probability of condom use among those not flagged as consistent condom users
condoms_inst_prob <- svymean(~condoms_inst, subset(sample_rake_neg, p12noprep_dyad %in% "No PrEP" & !(always_condoms_inst_p12 %in% 1)), na.rm=TRUE)

inst_condoms <- cbind.data.frame(Indicator = c("Consistent condom use with instantaneous partners", "Probability of condom use if not a consistent condom user"), N = c(sum(sample_rake_neg$variables$p12noprep_dyad %in% "No PrEP" & !is.na(sample_rake_neg$variables$always_condoms_inst_p12)), sum(sample_rake_neg$variables$p12noprep_dyad %in% "No PrEP" & !(sample_rake_neg$variables$always_condoms_inst_p12 %in% 1) & !is.na(sample_rake_neg$variables$condoms_inst))), Percent = c(condoms_always_inst[1], condoms_inst_prob[1]), SE = c(round(SE(condoms_always_inst),4), round(SE(condoms_inst_prob),4)))
row.names(inst_condoms) <- NULL

kable(inst_condoms, col.names=c("", "Unweighted N", "Proportion", "SE"), caption="Condom use in instantaneous partnerships", digits = c(0,0,4,4)) %>% kable_styling(full_width=F, position="center") %>% column_spec(1, width = "10cm") %>% column_spec(2:4, width="2cm")

```
## Correlation between consistent condom use with persistent and instantaneous partnerships

Using the indicators of consistent condom use with persistent and instantaneous partnerships defined above, we calculate the [Phi coefficient](https://en.wikipedia.org/wiki/Phi_coefficient) between consistent condom use with persistent and instantaneous partners. For this, we use data only from men who report both persistent and instantaneous partners in the past 12 months.

```{r}
always_condoms_persXinst <- svytable(~always_condoms_pers_p12 + always_condoms_inst_p12, subset(sample_rake_neg, p12noprep_dyad %in% "No PrEP"))
always_condoms_persXinst <- addmargins(always_condoms_persXinst, margin=c(1,2), sum, quiet = TRUE)

(cond.always.prob.corr <- ((always_condoms_persXinst[1,1]*always_condoms_persXinst[2,2])-(always_condoms_persXinst[1,2]*always_condoms_persXinst[2,1]))/sqrt(always_condoms_persXinst[1,3]*always_condoms_persXinst[2,3]*always_condoms_persXinst[3,1]*always_condoms_persXinst[3,2]))

```


```{r}
#Save
condoms_prob <- list(condoms_main_prob = condoms_main_prob, condoms_always_pers = condoms_always_pers[1], condoms_pers_prob = condoms_pers_prob[1], condoms_always_inst = condoms_always_inst[1], condoms_inst_prob = condoms_inst_prob[1], condoms_always_corr = cond.always.prob.corr)

save(condoms_prob, file = "Data/condoms.prob.Rdata")
```