# Decisions {#decisions}
```{r, echo=FALSE, include=FALSE}
#-----------------------------------------------------------------------------------
# Load packages
#-----------------------------------------------------------------------------------
    library("tidyverse")
    library("knitr")
    library("kableExtra")
    options(knitr.table.format = "html") 
```

This file summarizes the decisions made about parameter estimation and model structure.

##Racial/ethnic groups
- We decided to represent racial/ethnic heterogeneity by defining three groups: Hispanic, non-Hispanic black (including men who reported black race alone or in combination with another race), and non-Hispanic other (including men who listed any other non-Hispanic race). See section \@ref(composition) for more details on this decision.

## Age range
- Although the age range for the WHPP sample spanned ages 16-82, other sources from which we might want to estimate parameters (e.g. the Medical Monitoring Project) have a minimum age of 18. As such, we defined the minimum age for the modeled population to be 18. We set the maximum age for the network model to be 59 based on data showing that 1/3 of PrEP users are above the age of 40, such that expanding th emodel into older ages would be important (see section \@ref(composition)).
- We also decided to restrict alter ages to 18-59. Data on most recent partners who were under age 18 (n=18) or over age 59 (n=13) were excluded from calculation of partner-specific parameters (e.g. age and race mixing, coital frequency, condom use, partnership age). Egos who reported partners out of the age range were retained in the network for estimation of other parameters, and the out-of-range partnerships were still counted in calculation of mean degree. We found that men who reported partners outside of the age range differed in several ways from men who reported partners in the age range (section \@ref(alter_age_boundary). Future modeling work may want to explore different ways to represent these out-of-network partnerships, such as with a heat bath.

## Age structure
- Previous MSM network models have defined a relatively flat age structure for the tarting network, and allowed it to be modified by mortality without taking any steps to preserve a target age distribution. For this model, because we have a wider age range and we are weighting the sample to match the population distribution by age for Washington males, we would want to try to specify and preserve that age distribution in the absence of disease so that we know how to interpret changes due to disease processes. Although we don't know the "true" age distribution for MSM, we could start by specifying the age distriubtion for males in Washington. Then we specify entry and migration rates to balance mortality and preserve the distribution. <span style="color:red">Proposed approach:  </span>
  - <span style="color:red">For all men who age out of the network, have the same number come back in at age 18. Assume all who enter this way are not on PrEP and are disease-free.</span>
  - <span style="color:red">For those who die from background _or HIV-related_ mortality, have the same number of men enter the model with an age, racial/ethnic, and regional distribution that corresponds to the target population distribution. Assign a probability that those who enter are HIV-positive _based on the starting prevalence_. For those who enter as negaitve, assign a proability that they enter already using PrEP _(but how would this work for baseline "no PrEP" scnearios?)_.</span>

## Region
- To represent heterogeneity by region, we categorized men into three regions based on their reported zip codes: King County, other western Washington, eastern Washington (see \@ref(composition)). 
- We do not have data on patterns of sexual mixing by region, so we will specify different patterns in sensitivity analyses (i.e. entirely homophilous and allowing for some crosss-regional mixing).

## Data from HIV-positive men
- Because the WHPP sample excluded men who had ever tested positive for HIV, we would ideally obtain corresponding data from HIV-positive men. However, existing data sources on HIV-positive MSM in Washington are limited: the Medical Monitoring Project does collect data on some variables, but it will really only inform estimates of mixing patterns by race/ethnicity and age, sex role, and disclosure at the outset of relationships; the NHBS also has some relevant variables, but the sample of HIV-positive men is small, limited to Seattle-area MSM, and it does not not measure anything on HIV-positive men that we cannot get from MMP. As such, we will use data from MMP on HIV-positive men where we can, use data from Atlanta-area studies where appropriate (e.g. for estimates of changes in condom use with diagnosis or disclosure), but we will otherwise assume estimates are the same for HIV-positive as HIV-negative/uknown status men who completed the WHPP survey. <span style="color:red">Eli conducted an analysis that showed that the main thing that differed between HIV-positive and HIV-negative men was condom use, so this approach is supported by his analysis.</span>

## Reweighting
- We decided to re-weight the WHPP sample to the joint population distribution of race and region and the marginal distribution of age (see section \@ref(reweight)). 
- For parameters that will be estimated specifically for HIV-negative men (i.e. we have data from another source to inform parameter values for HIV-positive men), reweight the sample to the population totals for HIV-negative men. But if we will estiamte parameters from the WHPP survey or other sources that will apply to all men (i.e. we don't have data from another source for HIV-positives so we will assume that the estimates do not differ by HIV status), reweight to the population totals for all men.
- For some variables we have missing data, such that the sample reporting on those variables may not reflect the population distribution after reweighting the overall WHPP sample to the population totals. For now, we will assume that data are missing completely at random, such that this approach is appropriate.

## Using data from ongoing vs all partnerships
- We decided to use data only from ongoing partnerships to inform parameters relating to race and age mixing. This is because the formation model, to which these parameters are relevant, aims to recreate the network we observe at the cross-section. An issue is that the NHBS and MMP, datasets I will also be using to inform parameters, do not ask whether partnerships are ongoing. But we will just work with what we have.
- For parameters relating to condom use and coital frequency, we decided to use data from all partnerships. The analysis in section \@ref(coitfreq_condoms) revealed that, for all comparisons but coital frequency in persistent partnerships among Hispanic men, the estimates were comparable when using data from all vs. only ongoing partnerships. Because the sample sizes are considerably smaller when restricting to ongoing partnerships and there is not a good reason to do so, we decided to use data from all partnerships.

## Using data on most recent partners
- In analyses comparing the characteristics of most recent partners by momentary degree (i.e. comparing main most recent partners described by men with 0 vs. 1+ ongoing persistent partner and comparing persistent most recent partners described by men with 0 vs. 1 ongoing main partners) (\@ref(mrp_limitations)), no significant differences were observed. This suggests that it is appropriate to use data reported on all ongoing partners of a given type to impute the characteristics (implicitly or explicitly) of other ongoing partners who were not reported on as the most recent partner.

## Momentary degree (partnership formation)
- Main partnership status: The probability of having an ongoing main partner appears to differ by race/ethnicity and region (\@ref(explore_heterogeneity)), so we will include main effect terms for race/ethnicity and region in model code relating to main partner degree.
- Persistent partnership status: The probabilities of having any persistent partners, concurrent persistent partners, and having a persistent partner concurrent with a main partner were all higher for men aged 40-49. As such, we will code the model to define separate probabilities for men aged 40-49 of forming a persistent partnership, having concurrent persistent partnerships, and having a persistent partnership concurrent with a main partnership. However, because this pattern by age doesn’t align with our understanding of MSM’s sexual behavior, in the base model we will set this probability to be the same as for men of other ages. We will run sensitivity analyses in which we define a higher probability for men aged 40 to 49.  

## Rate of instantaneous partners
- We will code the model to represent heterogeneity in the rate of instantantous partnerships by assigning men into one of four categories based on the quartile distribution of the rate of instantaneous partnerships. By age, there appears to be an increased probability of having zero instantaneous partnerships after age 50 (\@ref(plots_explore_rateinst_3)). As such, men assigned to have >0 instantaneous partnerships at entry will be reassigned a quantile at age 50, with some of these men transitioning into the zero instantaneous partnerships category. This assumes that men who were assigned zero instantaneous partnerships at entry stay in that category for the entire duration of the simulation.
- In addition to age heterogeneity, the rate of instantaneous partnerships appears to differ by momentary degree (\@ref(fig:plotsexplore_rateinst_5)).We will define separate rates of instantaneous partnerships by the joint distribution of main and persistent (0 vs. 1+) partnership status. 

## Age mixing
- We will stratify age mixing by partner type.
- Age mixing appears to differ by ego age (see \@ref(explore_heterogeneity)), even after parameterizing it as the absolute difference in the square root of ego and later ages. However, this parameterization seems good enough, so we will not represent additional heterogeneity in age mixing by age.
- Age mixing did not appear to differ meaningfully by race/ethnicity (\@ref(fig:plots_explore_agemixing_4)) or region (\@ref(fig:plots_explore_agemixing_5)).

## Race mixing
- Exploratory analyses did not indicate differences in race mixing by age or region (see \@ref(explore_heterogeneity)). 
- Due to the small number of black men reporting ongoing partnerships of any type, we will collapse the off-diagonal elements and represent race mixing using a nodematch term. We will also collapse the persistent and instantaneous networks in calculation of sufficient statistics for race mixing. While neither of these approaches is ideal, they avoid putting too much weight on data from a very small number of respondents (in particular, 0 black men reported ongoing persistent partnerships with other black men). See section \@ref(mixing) for more detail and supporting tables.

## Partnership age
- Exploratory analyses (section \@ref(explore_heterogeneity) suggest that the age of main partnerships varies by age, but this is a complex phenomenon. For instance, the data are subject to censoring by age, in that the partnerships of younger men can only have persisted a relatively short time simply due to how long it has been since their presumed debut. We will not model heterogeneity in partnership duration by age at this point. 

## Network model formulas
- From the exploratory analyses, we will specify the following models for formation of main, persistent, and instantaneous partnerships (with acknowledgement that these models may need to be modified if we face convergence issues).
```{r formation_models, echo=FALSE}
formation.models <- cbind.data.frame("Partner type" = c("Main", "Persistent", "Instantaneous"), "Main effects" = c("edges; race/ethnicity; region", "edges; age 40-49 (in sensitivity analyses)", "edges; risk group"), "Mixing effects" = c("race/ethnicity (nodematch); absdiff sqrt of ego and alter ages", "race/ethnicity (nodematch); region (nodemix); absdiff sqrt of ego and alter ages", "nodematch race/ethnicity; nodemix region; absdiff square root of ego and alter ages"), "Dyad-dependent terms" = c("persistent degree (nodefactor)", "main degree (nodefactor); concurrent", "main/persistent degree (nodefactor)"), "Offsets" = c("role class (nodematch);  condom use categories (nodematch)", "role class (nodematch);  condom use categories (nodematch)", "role class (nodematch)"), "Constraints" = c("maximum degree of 1", "maximum degree of 2", ""))

kable(formation.models, col.names=c("Model", "Main effects", "Mixing effects", "Dyad-dependent terms", "Offsets", "Constraints")) %>% kable_styling(full_width= F, position="center") %>% column_spec(2:6, width = "26cm") 
```

## Proportion never tested for HIV
- To represent the proportion of men who do not test for HIV, we will use data on the proportion of men aged 40 and above who indicate that they've never tested. This was informed by examination of plots of the proportion of men who reported ever testing by age (section \@ref(hivtesting)). These plots indicate that the probability of having tested peaks around age 40, suggesting that if men don't test by this age they are unlikely to. Of course the data reflect a mix of age and cohort effects, but this provides a rough indication of the testing pattern in the population.
- The proportion of men who have not tested for HIV by age 40 appears to differ by region (section \@ref(explore_heterogeneity)). As such, we will stratify this parameter by region.

## Intertest interval
- We will model the intertest interval as an interval process, as this yields summary statistics that more closely match what we've seen in other sources (section \@ref(hivtesting)). With this assumption, the intertest interval is estimated as twice the time since the last test since the survey was not administered in connection with any testing event. The assumption is that the date of survey is randomly distributed throughout men's time between tests, such that on average it will come halfway through their intertest interval. We will use the median as the summary statistic, because for interval data that can be easily skewed by outliers, the median may be more stable. Additionally, using the median we get results that match what we've seen in other studies (see section \@ref(hivtesting)).
- For estimation of this parameter, we use data from men who did not report use of PrEP in the past 12 months, as we expect PrEP to change testing frequency and the model will represent the change in testing frequency with PrEP. While it is possible that men who are on PrEP tested more frequently before going on PrEP, for now we will just use data from men who had not used PrEP, though we will consider exploring ways to account for the pre-PrEP testing patterns of PrEP users in the future (see section \@ref(future_explore)).
- The intertest interval appears to vary by age (section \@ref(explore_heterogeneity)). To capture this heterogeneity, we will represent the intertest interval as a function of centered age and centered age squared.

## Anal sex role
- Although there is some indication that anal sex role differs by age and race/ethnicity, these patterns do not appear meaningful (see section \@ref(explore_heterogeneity)). Additionally, representing heterogeneity in anal sex role by these attributes introduces complexity into the model because it will affect balance in mixing. We have flagged this as something to explore in the future (section \@ref(future_explore)), but we will not stratify sex role by race/ethnicity or age in the current model.

## Coital frequency
- For data on coital frequency, we decided to drop data points from 4 men (3 of whom were in the age range 18-59) who reported having sex >=2 times per day and take the mean values as the summary statistics. 
- Exploratory analyses indicate that coital frequency differs significantly by region in main partnerships (section \@ref(explore_heterogeneity)). Since this is not an expected finding and doesn't make much intuitive sense, we will run the base model without stratifying by region. However, we will explore the impact of adding this regional heterogeneity in sensitivity analyses. 

## Condom use
- Condom use in main partnerships appears to differ by age. In the model, we will stratify condom use with main partners by dyad age, using one degree of freedom to specify the higher rate in young-young (18-34) dyads relative to all other dyads.
- Condom use in persistent and instantaneous partnerships does not appear to differ meaningfully by age, or by any other attribute.
- A challenge with specifying condom use probabilities is that the data measure condom use in a specific dyad. If we use this to infer condom use propensities at the individual level, we a) need to figure out what to do if two people with differnt individual propensities mix, and b) need to make sure that the resulting mean condom use probabilities match what we observed from the data. Proposal:
  - <span style="color:red">For instantaneous partnerships, just calculate the mean probability of condom use with one-time partners for the population and apply the same probability to everyone. Or assume some proportion of men never, some proportion sometimes, and some proportion always uses condoms with inst partners and tweak it to match observed mean?</span>
  - For main and persistent partnerships, assign people to one of three condom use categories: always, sometimes, or never. 
  - Define constraints in the formation models to prevent a never condom user from partnering with an always condom user. Then define rules to determine the probability of condom use if a never-user or an always-user mixes with a sometimes user. Could say that the preferences of the never- or always-users trump those of the somtimes user. If two sometimes users mix, need to determine what the probability of condom use will be.
  - Make sure the specified distribution of men in these categories and the resulting probabilities of condom use within dyads preserve the observed mean probability of condom use with the most recent partner, by partner type.

## PrEP use
- PrEP use among men for whom Washington guidelines recommend initiation or indicate discussion of PrEP with a provider differs in the sample by age and region. There is some suggestion of variabiltiy by race/ethnicity, but it is not very clear. However, we will code the model to represent the main effects of all three nodal attributes given the interest in disparities by race/ethnicity. We could explore the impact of graeter disparities in sensitivity analyses.

## Risk compensation with PrEP use
- There is evidence in the literature that PrEP use is associated with changes in condom use^[Oldenburg CE, Nunn AS, Montgomery M, Almonte A, Mena L, Patel RR, et al. Behavioral Changes Following Uptake of HIV Pre-exposure Prophylaxis Among Men Who Have Sex with Men in a Clinical Setting. AIDS and behavior. 2017; Lal L, Audsley J, Murphy DA, Fairley CK, Stoove M, Roth N, et al. Medication adherence, condom use and sexually transmitted infections in Australian preexposure prophylaxis users. AIDS (London, England). 2017;31(12):1709-14.; Newcomb ME, Moran K, Feinstein BA, Forscher E, Mustanski B. Pre-Exposure Prophylaxis (PrEP) Use and Condomless Anal Sex: Evidence of Risk Compensation in a Cohort of Young Men Who Have Sex with Men. JAIDS Journal of Acquired Immune Deficiency Syndromes. 2017;Publish Ahead of Print.], and some studies have reported changes in seroadaptive strategies such as positioning, the number of partners, and possibly coital frequency.^[Hughes AJ, Chen YH, Scheer S. Condomless Anal Sex Among HIV-Positive Men Who Have Sex with Men: Biomedical Context Matters. AIDS and behavior. 2017;21(10):2886-94; Lal L, Audsley J, Murphy DA, Fairley CK, Stoove M, Roth N, et al. Medication adherence, condom use and sexually transmitted infections in Australian preexposure prophylaxis users. AIDS (London, England). 2017;31(12):1709-14.; Newcomb ME, Moran K, Feinstein BA, Forscher E, Mustanski B. Pre-Exposure Prophylaxis (PrEP) Use and Condomless Anal Sex: Evidence of Risk Compensation in a Cohort of Young Men Who Have Sex with Men. JAIDS Journal of Acquired Immune Deficiency Syndromes. 2017;Publish Ahead of Print.]. We will start by assuming that condom use is the only thing to change with PrEP use, but consider building in other types of risk compensation as well. This would require re-estimating the parameters related to any behavior thought to change with PrEP to impute what the behaviors of PrEP users would be in the absence of PrEP. It might also be interesting to explore the possible impact of community-level risk compensation due to prevention optimism^[Holt M, Murphy DA. Individual Versus Community-Level Risk Compensation Following Preexposure Prophylaxis of HIV. American journal of public health. 2017:e1-e4.], but this could be tricky b/c the data from WHPP may already reflect some of this effect, so getting the counterfactual right would require some adjustments.

# Things to check against simulated data
- Make sure that the distribution of the age of partnerships by ego age produced by the model corresponds to the observed distributions (see \@ref(fig:plotsexplore_pshipage)).