# Notes on HIV testing {#hivtesting}

```{r, include=FALSE}
####################################################################################
# Setup
####################################################################################
#-----------------------------------------------------------------------------------
# Load packages
#-----------------------------------------------------------------------------------

    library("tidyverse")
    library("knitr")
    library("data.table")
    library("kableExtra")
    library("survey")

#-----------------------------------------------------------------------------------
# Knitr options
#-----------------------------------------------------------------------------------
opts_chunk$set(echo=FALSE, message=FALSE, warning=TRUE, error=TRUE, fig.align = "center")
options(knitr.table.format = "html") 

#-----------------------------------------------------------------------------------
# Plot settings
#-----------------------------------------------------------------------------------
#save plot settings for white background and light grey lines and darkening the colors a bit
plot_background <- theme(panel.background = element_rect(fill="white", colour = "black")) + theme(panel.grid.major = element_line(colour = "grey90"))
darken_color <- scale_colour_hue(l=50)
theme_title <- theme(plot.title = element_text(hjust = 0.5, size=12)) 
        
#-----------------------------------------------------------------------------------
# Load data
#-----------------------------------------------------------------------------------

load(file="Data/InternetSurveySample.Rdata")
load(file="Data/InternetSurveySample_allages.Rdata")
load(file="Data/InternetSurvey_reweighted.Rdata")

#-----------------------------------------------------------------------------------
#set plot settings 
#-----------------------------------------------------------------------------------
    
    #White background and light grey lines
    plot_background_nogrid <- theme(panel.background = element_rect(fill="white", colour = "black")) 
    #Darken colors
    darken_color <- scale_colour_hue(l=50)
    #Title size to 12 and center it 
    theme_title <- theme(plot.title = element_text(hjust = 0.5, size=12)) 
    
#----------------------------------------------------------------------------------
# Define multiplot function
#_---------------------------------------------------------------------------------
        multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
            library(grid)
            
            # Make a list from the ... arguments and plotlist
            plots <- c(list(...), plotlist)
            
            numPlots = length(plots)
            
            # If layout is NULL, then use 'cols' to determine layout
            if (is.null(layout)) {
                # Make the panel
                # ncol: Number of columns of plots
                # nrow: Number of rows needed, calculated from # of cols
                layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                                 ncol = cols, nrow = ceiling(numPlots/cols))
            }
            
            if (numPlots==1) {
                print(plots[[1]])
                
            } else {
                # Set up the page
                grid.newpage()
                pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))
                
                # Make each plot, in the correct location
                for (i in 1:numPlots) {
                    # Get the i,j matrix positions of the regions that contain this subplot
                    matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))
                    
                    print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                                    layout.pos.col = matchidx$col))
                }
            }
        }


```

This section explores how to parameterize HIV testing patterns. We first examine how to represent the proportion of men who will never test, then we look at how to represent patterns of testing among men who do test.

## Proportion that never tests
In previous MSM network models, never testers were defined as the proportion of men who never tested by age 40, since the models were capped at age 39. For this model, that may not be appropriate. In the plots below, we look at the proportion of men who report ever having tested by age. The first plot shows the proportion ever tested by single year, and the second plot groups age into 5-year bins. This analysis includes men who have taken PrEP, because many men who go on PrEP are likely to have come in for testing as the precipitating event to initiating PrEP. Excluding them would overestimate the proportion never tested. 

```{r evertest_byage}
  agetest <- sample %>% filter(!is.na(evertest_r)) %>% group_by(age) %>% summarise(prop = mean(evertest_r))
  ggplot(agetest, aes(x=age, y=prop)) + geom_point() + geom_smooth(method="loess") + labs(x="Age", y="Proprotion ever tested", title="Proportion of men ever tested for HIV by age") + theme_title + plot_background
  
   age_cat_test <- sample %>% filter(!is.na(evertest_r)) %>% group_by(age_cat) %>% summarise(prop = mean(evertest_r))
  ggplot(age_cat_test, aes(x=age_cat, y=prop)) + geom_point() + labs(x="Age group", y="Proprotion ever tested", title="Proportion of men ever testeed for HIV by age group") + theme_title + plot_background

```
Interpretation of these plots is challenging due to the fact that they show both age and cohort effects, but it appears that the probabilty of having ever tested is maximized around age 40. In the model, we will use data on the proportion of men aged 40 and higher who haven't tested to define a parameter for the proportion of men who will never test.


## Intertest interval
In this section, we examine the data from WHPP to inform the decision of whether to model HIV testing as an interval process or a memoryless process. If as an __interval process__, we assume that men test at regular intervals. Since the survey was not associated wtih any testing event, we assume the survey date is randomly distributed within men's intervals, such that on average it will fall halfway between their testing events. As such, the intertest interval is calculated as twice the reported days since the last test. If we model testing as a __memoryless process__, men are assumed to have a constant hazard of testing, such that the data follow an exponential distribution. Under this assumption, the expected time between tests is the average time from the last test.

In looking at the testing intervals, we exclude men who reported use of PrEP in the past 12 months, as these men will have different testing patterns that will be represented using separate parameters in the model. If we assume testing is an interval process, the median intertest interval is `r round(svyquantile(~iti_int, sample_rake[!(sample_rake$variables$prep_use_r %in% "Currently taking PrEP") & !(sample_rake$variables$monthsago_lastprep %in% c(0:12))], .5, na.rm=TRUE), 0)` and the mean is `r round(svymean(~iti_int, sample_rake[!(sample_rake$variables$prep_use_r %in% "Currently taking PrEP") & !(sample_rake$variables$monthsago_lastprep %in% c(0:12))], na.rm=TRUE)[1], 0)`. If we assume testing is a memoryless process, the median intertest interval is `r round(svyquantile(~iti_mem, sample_rake[!(sample_rake$variables$prep_use_r %in% "Currently taking PrEP") & !(sample_rake$variables$monthsago_lastprep %in% c(0:12))], .5, na.rm=TRUE),0)` and the mean is `r round(svymean(~iti_mem, sample_rake[!(sample_rake$variables$prep_use_r %in% "Currently taking PrEP") & !(sample_rake$variables$monthsago_lastprep %in% c(0:12))], na.rm=TRUE)[1], 0)`. These statistics and the plots below use data from the reweighted survey object.

Plot \@ref(fig:plots_iti_interval) shows the median and mean intertest intervals calculated as an interval process by respondent age. 
```{r plots_iti_interval}

#Intertest interval by age 
    itiXage_med <- as.vector(svyby(~iti_int, ~age, sample_rake[!(sample_rake$variables$prep_use_r %in% "Currently taking PrEP") & !(sample_rake$variables$monthsago_lastprep %in% c(0:12))], svyquantile, quantiles=0.5, na.rm=TRUE, keep.var = FALSE)[2])
    itiXage_mean <- as.vector(svyby(~iti_int, ~age, sample_rake[!(sample_rake$variables$prep_use_r %in% "Currently taking PrEP") & !(sample_rake$variables$monthsago_lastprep %in% c(0:12))], svymean, na.rm=TRUE, keep.var = FALSE)[2])
    itiXage_freq <- as.vector(svytable(~age, sample_rake[!(sample_rake$variables$prep_use_r %in% "Currently taking PrEP") & !(sample_rake$variables$monthsago_lastprep %in% c(0:12)) & !is.na(sample_rake$variables$iti_int)]))
    itiXage <- cbind.data.frame(age = 18:59, median = itiXage_med, mean = itiXage_mean, freq = itiXage_freq)
    names(itiXage)[2] <- "median"
    names(itiXage)[3] <- "mean"
    
    ggplot(itiXage) + geom_point(aes(x=age, y=median, size=freq, colour="Median")) + geom_point(aes(x=age, y=mean, size=freq, colour="Mean")) + geom_smooth(aes(x=age, y=median), method="loess") + geom_smooth(aes(x=age, y=mean), method="loess") + scale_colour_manual(name="Measure", values=c("Median" = "blue", "Mean"="red")) + labs(x="Ego age", y="Days since last test", title="Mean and median intertest intervals by age, \n assuming testing is an interval process") + plot_background_nogrid + theme_title
  
```

From these statistics and graphs, the median intertest interval based on testing as an interval process looks like a better summary statistic. For the model, we get to pick one summary statistic. For interval data that can be skewed easily by outliers, the median may be more stable. Additionally, the median based on testing as an interval process gets us results that more closely match Atlanta data (from Sam's PrEP paper appendix, the estimated mean ITI for HIV negative MSM was 301 days for blacks and 315 days for whites) and what STD clinic data show: David Katz' [analysis](https://www-ncbi-nlm-nih-gov.offcampus.lib.washington.edu/pmc/articles/PMC3465512/) of data from the PHSKC STD clinic and Gay City Health Project indicates that the median ITIs are 215-257 days. These are probably slightly lower than for all men, as the STD clinic in particular caters to higher risk men, and testing intervals in King County are likely shorter. Among [men diagnosed with HIV in 2015 King County](http://www.kingcounty.gov/depts/health/communicable-diseases/hiv-std/patients/epidemiology/~/media/depts/health/communicable-diseases/documents/hivstd/2016-hiv-aids-epidemiology-annual-report.ashx), the median time between the last negative test and first positive diagnosis was 12 months (ranging form 8-12 months between 2009 and 2015).