# HIV testing {#hivtesting}

```{r, include=FALSE}

####################################################################################
# Setup
####################################################################################
#-----------------------------------------------------------------------------------
# Load packages
#-----------------------------------------------------------------------------------

    library("tidyverse")
    library("knitr")
    library("data.table")
    library("survey")
    library("kableExtra")

#-----------------------------------------------------------------------------------
# Knitr options
#-----------------------------------------------------------------------------------
opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE)
options(knitr.table.format = "html") 

#-----------------------------------------------------------------------------------
# set plot settings 
#-----------------------------------------------------------------------------------
    
    #White background and light grey lines
    plot_background <- theme(panel.background = element_rect(fill="white", colour = "black")) + theme(panel.grid.major = element_line(colour = "grey90"))
    #Title size to 12 and center it 
    theme_title <- theme(plot.title = element_text(hjust = 0.5, size=12)) 
    
#-----------------------------------------------------------------------------------
# Load data
#-----------------------------------------------------------------------------------
  load(file="Data/InternetSurvey_reweighted_neg.Rdata")

#-----------------------------------------------------------------------------------
# Data manipulation
#-----------------------------------------------------------------------------------

  #Define indicator to use in subsetting of dyads in which the ego had not taken PrEP in the past 12 months
    sample_rake_neg$variables$p12noprep_ego <- ifelse(sample_rake_neg$variables$prep_use_r %in% c("Took PrEP in the past", "Never taken PrEP") & !(sample_rake_neg$variables$monthsago_lastprep %in% c(0:12)), "No PrEP", 
                                                  ifelse((sample_rake_neg$variables$prep_use_r %in% c("Currently taking PrEP")) | (sample_rake_neg$variables$prep_use_r %in% c("Took PrEP in the past") & (sample_rake_neg$variables$monthsago_lastprep %in% c(0:12))), "PrEP",
                                                         NA))

```
## Intertest interval
As documented in section \@ref(decisions), We will model the intertest interval as an __interval process__, estimated as twice the reported time since the last HIV test. We will use the median as the summary statistic (see section \@ref(hivtesting)).

We use data from the WHPP reweighted to the demographics of HIV-negative/undiagnosed men in Washington to estimate this paratmer. Additionally, because patterns of testing are different with PrEP use, which the model will reflect, <span style="color:red">we use data from men who did not report use of PrEP in the past 12 months to estimate testing among men not on PrEP. While it is possible that men who were on PrEP at the time of the survey were more frequent testers than the average MSM before going on PrEP, for now we will assume that the testing patterns of men not on PrEP represents testing in the absence of PrEP for all men, though we will consider exploring ways to account for the pre-PrEP testing patterns of PrEP users in the future (see section \@ref(future_explore)).</span>

Exploratory analyses indicate that the intertest interval varies by age (section \@ref(explore_heterogeneity)). To capture this, we will fit a regression model to estimate the intertest interval as a function of centered age and centered age squared, and we will use this in the epidemic model to predict the intertest interval as a function of age.^[Note that, by fitting to centered age squared, the predicted interval will start to come down at higher ages. This does not appear to be very strong by the maximum modeled age of 59, but models with wider age ranges or different data might lead to shorter intervals for older men, which may not reflect reality.] In the plot below, the blue line is the loess smooth on the observed data, and the red line is the prediction from the generalized linear model. 


```{r}
#Define centered age and centered age squared variables, centered on mean among those not on PrEP

sample_rake_neg$variables$age_centered <- NA
sample_rake_neg$variables$age_centered[sample_rake_neg$variables$p12noprep_ego %in% "No PrEP"] <- sample_rake_neg$variables$age[sample_rake_neg$variables$p12noprep_ego %in% "No PrEP"] - svymean(~age, subset(sample_rake_neg, p12noprep_ego %in% "No PrEP"), FUN=svymean, na.rm=TRUE)[1]

sample_rake_neg$variables$age_cent_sq <- sample_rake_neg$variables$age_centered^2

# Define a new column with the median ITI for each age
sample_rake_neg$variables$median_iti <- NA
for(age in min(sample_rake_neg$variables$age, na.rm=TRUE):max(sample_rake_neg$variables$age, na.rm=TRUE)){
  sample_rake_neg$variables$median_iti[sample_rake_neg$variables$age %in% age & sample_rake_neg$variables$p12noprep_ego %in% "No PrEP"] <- svyquantile(~iti_int, sample_rake_neg[sample_rake_neg$variables$p12noprep_ego %in% "No PrEP" & sample_rake_neg$variables$age %in% age], quantile=0.5, na.rm=TRUE)
}

#Fit linear model to the median ITI
lm_itiXage <- svyglm(median_iti ~ age_centered + age_cent_sq, design=subset(sample_rake_neg, p12noprep_ego %in% "No PrEP"))
summary(lm_itiXage)

#Create a data frame with prediction from the model and age
iti_pred <- cbind.data.frame(prediction = predict(lm_itiXage, list(age_centered = sample_rake_neg$variables$age_centered, age_cent_sq = sample_rake_neg$variables$age_cent_sq)), age = sample_rake_neg$variables$age[sample_rake_neg$variables$p12noprep_ego %in% "No PrEP"])

#Plot
 ggplot(sample_rake_neg$variables) + geom_point(aes(x=age, y=median_iti)) + geom_smooth(aes(x=age, y=median_iti), method="loess") + geom_line(data=iti_pred, aes(x=age, y=prediction.link), colour="red") + labs(x="Ego age", y="Days since last test", title="Median intertest interval by age, assuming testing is an interval process") + theme_title + plot_background

# Save model coefficients. In the simulation code, predicted value = lm_itiXage_coefs[1] + lm_itiXage_coefs[2]*age_centered + lm_itiXage_coefs[3]*age_centered_squared
 lm_itiXage_coefs <- lm_itiXage$coefficients
 save(lm_itiXage_coefs, file="Data/iti_coefs.Rdata")
```
