# Mixing by age, race, and region (#mixing)

```{r, include=FALSE}
####################################################################################
# Setup
####################################################################################
#-----------------------------------------------------------------------------------
# Load packages
#-----------------------------------------------------------------------------------

    library("tidyverse")
    library("knitr")
    library("kableExtra")
    library("data.table")
    library("survey")

#-----------------------------------------------------------------------------------
# Knitr options
#-----------------------------------------------------------------------------------
opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE)
options(knitr.table.format = "html") 

#-----------------------------------------------------------------------------------
# Load data
#-----------------------------------------------------------------------------------
    load(file="Data/InternetSurveySample.Rdata")
    load(file="Data/InternetSurveySample_allages.Rdata")
    load(file="Data/InternetSurvey_reweighted.Rdata")
   # load(file="Parameter estimation/Data/census_agebyregion.Rdata")
    # load(file="Parameter estimation/Data/census_racebyregion.Rdata")
    # load(file="Parameter estimation/Data/census_totalbyregion.Rdata")

#-----------------------------------------------------------------------------------
# Scale re-weighted dataset back to match sample size from the survey
#-----------------------------------------------------------------------------------
  # There are 81934 responses in the dataframe weighted to the population total, and 1,005 in the sample object
  # To get a re-weighted dataframe with the same number of observations as the sample, we will divide the raked
  # weights to scale it down (i.e. multiply the probabilities by the scaling factor since weights = 1/prob)
    ratio <- sum(weights(sample_rake))/dim(sample)[1]
    sample_rake_rescaled <- sample_rake
    sample_rake_rescaled$prob <- sample_rake_rescaled$prob * ratio
        
#-----------------------------------------------------------------------------------
# Plot settings
#-----------------------------------------------------------------------------------
plot_background <- theme(panel.background = element_rect(fill="white", colour = "black")) +
            theme(panel.grid.major = element_line(colour = "grey90"))
theme_title <- theme(plot.title = element_text(hjust = 0.5, size=12)) 

#Define multiplot function
    multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
        library(grid)
        
        # Make a list from the ... arguments and plotlist
        plots <- c(list(...), plotlist)
        
        numPlots = length(plots)
        
        # If layout is NULL, then use 'cols' to determine layout
        if (is.null(layout)) {
            # Make the panel
            # ncol: Number of columns of plots
            # nrow: Number of rows needed, calculated from # of cols
            layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                             ncol = cols, nrow = ceiling(numPlots/cols))
        }
        
        if (numPlots==1) {
            print(plots[[1]])
            
        } else {
            # Set up the page
            grid.newpage()
            pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))
            
            # Make each plot, in the correct location
            for (i in 1:numPlots) {
                # Get the i,j matrix positions of the regions that contain this subplot
                matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))
                
                print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                                layout.pos.col = matchidx$col))
            }
        }
    }
    
        
```
This file examines balance in sexual mixing by race and age in data from participants in the WHPP survey. For this analysis, the data are re-weighted to match the population distributions for race by region and age (see section \@ref(reweight)), but scaled back to the survey sample size.

## Observed race mixing
In the internet survey, we observed the following partnership counts for main, persistent, and one-off partnerships by dyad race. 
```{r racemixing}
 racemix_main <- svytable(~hbo + mrp_hbo, sample_rake_rescaled[sample_rake_rescaled$variables$mrp_type_ongoing %in% "Main"], round=FALSE)
 racemix_pers <- svytable(~hbo + mrp_hbo, sample_rake_rescaled[sample_rake_rescaled$variables$mrp_type_ongoing %in% "Persistent"], round=FALSE)
 racemix_inst <- svytable(~hbo + mrp_hbo, sample_rake_rescaled[sample_rake_rescaled$variables$mrp_type_r %in% "One time"], round=FALSE)

    kable(racemix_main, caption="Race mixing in main partnerships", digits=c(0, 0, 0)) %>% kable_styling(full_width=F, position="center") %>% add_header_above(c("Ego race/ethnicity", "Partner race/ethnicity" = 3))
    kable(racemix_pers, caption="Race mixing in persistent partnerships", digits=c(0, 0, 0)) %>% kable_styling(full_width=F, position="center") %>% add_header_above(c("Ego race/ethnicity", "Partner race/ethnicity" = 3))
    kable(racemix_inst, caption="Race mixing in instantaneous partnerships", digits=c(0, 0, 0)) %>% kable_styling(full_width=F, position="center") %>% add_header_above(c("Ego race/ethnicity", "Partner race/ethnicity" = 3))

```
Table \@ref(tab:racemixing) shows that there are some imbalances in the observed mixing patterns. We will address these imbalances by taking the mean of the of-diagonal elements, potentially conducting sensitivity analyses in which the off-diagonal elements are set to the low or high reported value.

If we take the averages of the off-diagonal elements, the mixing matrices are as follows. Due to the small cell count for black men, we will compare the averages based on data from ongoing partnerships only (for main and persistent partnerships) to the averages based on data from all partnerships reported as the most recent partner.

```{r}
# Define observed mixing matrices based on data from all partnerships
racemix_main_all <- svytable(~hbo + mrp_hbo, sample_rake_rescaled[sample_rake_rescaled$variables$mrp_type_r %in% "Main"], round=FALSE)
 racemix_pers_all <- svytable(~hbo + mrp_hbo, sample_rake_rescaled[sample_rake_rescaled$variables$mrp_type_r %in% "Casual"], round=FALSE)
 
 # Define tables with averages
 balance_avg_race <- function(x){
     balanced <- as.data.frame(matrix(c("HH"=x[1,1], "HB" = mean(c(x[1,2], x[2,1])), "HO" = mean(c(x[1,3], x[3,1])), "BH" = mean(c(x[1,2], x[2,1])), "BB" = x[2,2], "BO" = mean(c(x[2,3], x[3,2])), "OH" = mean(c(x[1,3], x[3,1])), "OB" = mean(c(x[2,3], x[3,2])), "OO" = x[3,3]), nrow=3, ncol=3, byrow=TRUE, dimnames=list(c("Hispanic", "Black", "Other"), c("Hispanic", "Black", "Other"))))
     return(balanced)
 }
 racemix_main_avg <- balance_avg_race(racemix_main)
 racemix_main_all_avg <- balance_avg_race(racemix_main_all)
 racemix_pers_avg <- balance_avg_race(racemix_pers)
 racemix_pers_all_avg <- balance_avg_race(racemix_pers_all)
 racemix_inst_avg <- balance_avg_race(racemix_inst)
 
 #Combine for kable
 balanced_racemix_main <- cbind.data.frame(racemix_main_avg, racemix_main_all_avg)
 balanced_racemix_pers <- cbind.data.frame(racemix_pers_avg, racemix_pers_all_avg)
 balanced_racemix_inst <- cbind.data.frame(racemix_inst_avg, data.frame(matrix(rep(NA, 9), nrow=3, dimnames=list(c("Hispanic", "Black", "Other"), c("Hispanic", "Black", "Other")))))
  
   #B/c it won't let me combine these with non-unique row names, rename rows for pers and inst to have extra spaces
    rownames(balanced_racemix_pers) <- c("Hispanic ", "Black ", "Other ")
    rownames(balanced_racemix_inst) <- c("Hispanic  ", "Black  ", "Other  ")

 balanced_racemix <- rbind.data.frame(balanced_racemix_main, balanced_racemix_pers, balanced_racemix_inst)
 
 #Make kable
 kable(balanced_racemix, caption="Race mixing: average of off-diagonal elements", digits=c(1, 1, 1, 1, 1, 1)) %>% kable_styling(full_width=T, position="center") %>% add_header_above(c("Ego race/ethnicity", "Ongoing partner race/ethnicity" = 3, "All partner race/ethnicity" = 3)) %>% group_rows("Main partnerships", 1, 3) %>% group_rows("Persistent partnerships", 4, 6) %>% group_rows("Instantaneous partnerships", 7, 9) %>% column_spec(5:7, background="#CACFD2") %>% column_spec(1, bold=T)

```

To facilitate comparison of the matrices using data from all vs. ongoing partnerships, below we look at the row percentages in the balanced mixing matrices, rather than the cell counts.
```{r}
 racemix_main_avg.p <- prop.table(balance_avg_race(racemix_main))
 racemix_main_all_avg.p <- prop.table(balance_avg_race(racemix_main_all))
 racemix_pers_avg.p <- prop.table(balance_avg_race(racemix_pers))
 racemix_pers_all_avg.p <- prop.table(balance_avg_race(racemix_pers_all))
 racemix_inst_avg.p <- prop.table(balance_avg_race(racemix_inst))
 
 #Combine for kable
 balanced_racemix_main.p <- cbind.data.frame(racemix_main_avg.p, racemix_main_all_avg.p)
 balanced_racemix_pers.p <- cbind.data.frame(racemix_pers_avg.p, racemix_pers_all_avg.p)
 balanced_racemix_inst.p <- cbind.data.frame(racemix_inst_avg.p, data.frame(matrix(rep(NA, 9), nrow=3, dimnames=list(c("Hispanic", "Black", "Other"), c("Hispanic", "Black", "Other")))))
  
   #B/c it won't let me combine these with non-unique row names, rename rows for pers and inst to have extra spaces
    rownames(balanced_racemix_pers.p) <- c("Hispanic ", "Black ", "Other ")
    rownames(balanced_racemix_inst.p) <- c("Hispanic  ", "Black  ", "Other  ")

 balanced_racemix.p <- rbind.data.frame(balanced_racemix_main.p, balanced_racemix_pers.p, balanced_racemix_inst.p)
 
 #Make kable
 kable(balanced_racemix.p, caption="Race mixing: average of off-diagonal elements", digits=c(3, 3, 3, 3, 3, 3)) %>% kable_styling(full_width=T, position="center") %>% add_header_above(c("Ego race/ethnicity", "Ongoing partner race/ethnicity" = 3, "All partner race/ethnicity" = 3)) %>% group_rows("Main partnerships", 1, 3) %>% group_rows("Persistent partnerships", 4, 6) %>% group_rows("Instantaneous partnerships", 7, 9) %>% column_spec(5:7, background="#CACFD2") %>% column_spec(1, bold=T)

```

<span style="color:red">Conclusions?</span>

Below, we calculate the $\alpha_{ij}$ terms (observed (averaged) cell count / expected cell count), where expected is the $N_i*N_j/N$. <span style="color:red>We will use data from ongoing partnerships for this comparison.</span>
```{r}
#write function
alphaij_race <- function(x){
    alphaij <- as.data.frame(matrix(c("HH"=x[1,1] / ((sum(x[1,])*sum(x[,1]))/sum(x)), "HB" = x[1,2] / ((sum(x[1,])*sum(x[,2]))/sum(x)), "HO" = x[1,3] / ((sum(x[1,])*sum(x[,3]))/sum(x)), "BH" = x[2,1] / ((sum(x[2,])*sum(x[,1]))/sum(x)), "BB" = x[2,2] / ((sum(x[2,])*sum(x[,2]))/sum(x)), "BO" = x[2,3] / ((sum(x[2,])*sum(x[,3]))/sum(x)), "OH" = x[3,1] / ((sum(x[3,])*sum(x[,1]))/sum(x)), "OB" = x[3,2] / ((sum(x[3,])*sum(x[,2]))/sum(x)), "OO" = x[3,3] / ((sum(x[3,])*sum(x[,3]))/sum(x))), nrow=3, ncol=3, byrow=TRUE, dimnames=list(c("Hispanic", "Black", "Other"), c("Hispanic", "Black", "Other"))))
    return(alphaij)
}

alphaij_race_main <- alphaij_race(racemix_main_avg)
alphaij_race_pers <- alphaij_race(racemix_pers_avg)
alphaij_race_inst <- alphaij_race(racemix_inst_avg)

#Combine to make kable
 #B/c it won't let me combine these with non-unique row names, rename rows for pers and inst to have extra spaces
    rownames(alphaij_race_pers) <- c("Hispanic ", "Black ", "Other ")
    rownames(alphaij_race_inst) <- c("Hispanic  ", "Black  ", "Other  ")

 alphaij_race <- rbind.data.frame(alphaij_race_main, alphaij_race_pers, alphaij_race_inst)
 
#Make kable
 kable(alphaij_race, caption="Race mixing: $alpha_{ij}$ terms", digits=c(2, 2, 2)) %>% kable_styling(full_width=F, position="center") %>% add_header_above(c("Ego race/ethnicity", "Partner race/ethnicity" = 3)) %>% group_rows("Main partnerships", 1, 3) %>% group_rows("Persistent partnerships", 4, 6) %>% group_rows("Instantaneous partnerships", 7, 9) 


```

<span style="color:red"> Because the $\alpha_{ij}$ terms for the off-diagonal elements differ, this suggests that we will need to specify nodemix instead of nodematch for mixing.</span>

## Observed age mixing
In the WHPP survey (re-weighted), we observed the following partnership counts for main, persistent, and one-off partnerships by ego and alter age group.

```{r agemixing}
    sample_rake_rescaled$variables$age_cat_crude <- cut(sample_rake_rescaled$variables$age, c(17, 24, 34, 44, 59), labels=c("18-24", "25-34", "35-44", "45-59"))
    sample_rake_rescaled$variables$mrp_age_cat_crude <- cut(sample_rake_rescaled$variables$mrp_ageinyears_approx, c(17, 24, 34, 44, 59), labels=c("18-24", "25-34", "35-44", "45-59"))    

    agemix_main <- svytable(~age_cat_crude + mrp_age_cat_crude, sample_rake_rescaled[sample_rake_rescaled$variables$mrp_type_ongoing %in% "Main"], round=FALSE)
    agemix_pers <- svytable(~age_cat_crude + mrp_age_cat_crude, sample_rake_rescaled[sample_rake_rescaled$variables$mrp_type_ongoing %in% "Persistent"], round=FALSE)
    agemix_inst <- svytable(~age_cat_crude + mrp_age_cat_crude, sample_rake_rescaled[sample_rake_rescaled$variables$mrp_type_r %in% "One time"], round=FALSE)

    kable(agemix_main, caption="Age mixing in main partnerships", digits=c(0, 0, 0, 0)) %>% kable_styling(full_width=F, position="center") %>% add_header_above(c("Ego age", "Partner age" = 4))
    kable(agemix_pers, caption="Age mixing in persistent partnerships", digits=c(0, 0, 0, 0)) %>% kable_styling(full_width=F, position="center") %>% add_header_above(c("Ego age", "Partner age" = 4))
    kable(agemix_inst, caption="Age mixing in instantaneous partnerships", digits=c(0, 0, 0, 0)) %>% kable_styling(full_width=F, position="center") %>% add_header_above(c("Ego age", "Partner age" = 4))

```
As with race, these data show imbalances in the observed mixing patterns. <span style="color:red">Parameterizing age mixing as the absolute difference in the square root of ego and alter ages will make these balance. </span>

Although we won't parameterize age mixing this way, we will further explore the patterns of mixing by taking the averages of the off-diagonal elements. Due to the small cell counts for some ages, the table below compares the averages based on data from ongoing partnerships only (for main and persistent partnerships) to the averages based on data from all partnerships reported as the most recent partner.

```{r}
# Define observed mixing matrices based on data from all partnerships
 agemix_main_all <- svytable(~age_cat_crude + mrp_age_cat_crude, sample_rake_rescaled[sample_rake_rescaled$variables$mrp_type_r %in% "Main"], round=FALSE)
 agemix_pers_all <- svytable(~age_cat_crude + mrp_age_cat_crude, sample_rake_rescaled[sample_rake_rescaled$variables$mrp_type_r %in% "Casual"], round=FALSE)
 
 # Define tables with averages
  balance_avg_age <- function(x){
     balanced <- as.data.frame(matrix(c("YY"=x[1,1], "YM1" = mean(c(x[1,2], x[2,1])), "YM2" = mean(c(x[1,3], x[3,1])), "YO" = mean(c(x[1,4], x[4,1])), "M1Y" = mean(c(x[1,2], x[2,1])), "M1M1" = x[2,2], "M1M2" = mean(c(x[2,3], x[3,2])), "M1O" = mean(c(x[2,4], x[4,2])), "M2Y"= mean(c(x[3,1], x[1,3])), "M2M1" = mean(c(x[3,2], x[2,3])), "M2M2" = x[3,3], "M2O" = mean(c(x[3,4], x[4,3])), "OY" = mean(c(x[4,1], x[1,4])), "OM1" = mean(c(x[4,2], x[2,4])), "OM2" = mean(c(x[4,3], x[3,4])), "OO" = x[4,4]), nrow=4, ncol=4, byrow=TRUE, dimnames=list(c("18-24", "25-34", "35-44", "45-59"), c("18-24", "25-34", "35-44", "45-59"))))
     return(balanced)
 }
 
 agemix_main_avg <- balance_avg_age(agemix_main)
 agemix_main_all_avg <- balance_avg_age(agemix_main_all)
 agemix_pers_avg <- balance_avg_age(agemix_pers)
 agemix_pers_all_avg <- balance_avg_age(agemix_pers_all)
 agemix_inst_avg <- balance_avg_age(agemix_inst)
 
 #Combine for kable
 balanced_agemix_main <- cbind.data.frame(agemix_main_avg, agemix_main_all_avg)
 balanced_agemix_pers <- cbind.data.frame(agemix_pers_avg, agemix_pers_all_avg)
 balanced_agemix_inst <- cbind.data.frame(agemix_inst_avg, matrix(rep(NA, 16), nrow=4, dimnames=list(c("18-24", "25-34", "35-44", "45-59"), c("18-24", "25-34", "35-44", "45-59"))))
  
   #B/c it won't let me combine these with non-unique row names, rename rows for pers and inst to have extra spaces
    rownames(balanced_agemix_pers) <- c("18-24 ", "25-34 ", "35-44 ", "45-59 ")
    rownames(balanced_agemix_inst) <- c("18-24  ", "25-34  ", "35-44  ", "45-59  ")

 balanced_agemix <- rbind.data.frame(balanced_agemix_main, balanced_agemix_pers, balanced_agemix_inst)
 
 #Make kable
 kable(balanced_agemix, caption="Age mixing: average of off-diagonal elements", digits=c(1, 1, 1, 1, 1, 1, 1, 1)) %>% kable_styling(full_width=T, position="center") %>% add_header_above(c("Ego age", "Ongoing partner age" = 4, "All partner age" = 4)) %>% group_rows("Main partnerships", 1, 4) %>% group_rows("Persistent partnerships", 5, 8) %>% group_rows("Instantaneous partnerships", 9, 12) %>% column_spec(6:9, background="#CACFD2") %>% column_spec(1, bold=T)

```

To facilitate comparison of the matrices using data from all vs. ongoing partnerships, below we look at the row percentages in the balanced mixing matrices, rather than the cell counts.
```{r}
 agemix_main_avg.p <- prop.table(balance_avg_age(agemix_main))
 agemix_main_all_avg.p <- prop.table(balance_avg_age(agemix_main_all))
 agemix_pers_avg.p <- prop.table(balance_avg_age(agemix_pers))
 agemix_pers_all_avg.p <- prop.table(balance_avg_age(agemix_pers_all))
 agemix_inst_avg.p <- prop.table(balance_avg_age(agemix_inst))
 
 #Combine for kable
 balanced_agemix_main.p <- cbind.data.frame(agemix_main_avg.p, agemix_main_all_avg.p)
 balanced_agemix_pers.p <- cbind.data.frame(agemix_pers_avg.p, agemix_pers_all_avg.p)
 balanced_agemix_inst.p <- cbind.data.frame(agemix_inst_avg.p, matrix(rep(NA, 16), nrow=4, dimnames=list(c("18-24", "25-34", "35-44", "45-59"), c("18-24", "25-34", "35-44", "45-59"))))
  
   #B/c it won't let me combine these with non-unique row names, rename rows for pers and inst to have extra spaces
    rownames(balanced_agemix_pers.p) <- c("18-24 ", "25-34 ", "35-44 ", "45-59 ")
    rownames(balanced_agemix_inst.p) <- c("18-24  ", "25-34  ", "35-44  ", "45-59  ")

 balanced_agemix.p <- rbind.data.frame(balanced_agemix_main.p, balanced_agemix_pers.p, balanced_agemix_inst.p)
 
 #Make kable
 kable(balanced_agemix.p, caption="Age mixing: average of off-diagonal elements", digits=c(3, 3, 3, 3, 3, 3, 3, 3)) %>% kable_styling(full_width=T, position="center") %>% add_header_above(c("Ego age", "Ongoing partner age" = 4, "All partner age" = 4)) %>% group_rows("Main partnerships", 1, 4) %>% group_rows("Persistent partnerships", 5, 8) %>% group_rows("Instantaneous partnerships", 9, 12) %>% column_spec(6:9, background="#CACFD2") %>% column_spec(1, bold=T)

```
<span style="color:red">Conclusions?</span>

Below, we calculate the $\alpha_{ij}$ terms (observed (averaged) cell count / expected cell count), where expected is the $N_i*N_j/N$. <span style="color:red>We will use data from ongoing partnerships for this comparison.</span>
```{r}
#write function
alphaij_age <- function(x){
    alphaij <- as.data.frame(matrix(c("YY"=x[1,1] / ((sum(x[1,])*sum(x[,1]))/sum(x)), "YM1" = x[1,2] / ((sum(x[1,])*sum(x[,2]))/sum(x)), "YM2" = x[1,3] / ((sum(x[1,])*sum(x[,3]))/sum(x)), "YO" = x[1,4] / ((sum(x[1,])*sum(x[,4]))/sum(x)), "M1Y" = x[2,1] / ((sum(x[2,])*sum(x[,1]))/sum(x)), "M1M1" = x[2,2] / ((sum(x[2,])*sum(x[,2]))/sum(x)), "M1M2" = x[2,3] / ((sum(x[2,])*sum(x[,3]))/sum(x)), "M1O" = x[2,4] / ((sum(x[2,])*sum(x[,4]))/sum(x)), "M2Y" = x[3,1] / ((sum(x[3,])*sum(x[,1]))/sum(x)), "M2M1" = x[3,2] / ((sum(x[3,])*sum(x[,2]))/sum(x)), "M2M2" = x[3,3] / ((sum(x[3,])*sum(x[,3]))/sum(x)), "M2O" = x[3,4] / ((sum(x[3,])*sum(x[,4]))/sum(x)), "OY" = x[4,1] / ((sum(x[4,])*sum(x[,1]))/sum(x)), "OM1" = x[4,2] / ((sum(x[4,])*sum(x[,2]))/sum(x)), "OM2" = x[4,3] / ((sum(x[4,])*sum(x[,3]))/sum(x)), "OO" = x[4,4] / ((sum(x[4,])*sum(x[,4]))/sum(x))), nrow=4, ncol=4, byrow=TRUE, dimnames=list(c("18-24", "25-34", "35-44", "45-59"), c("18-24", "25-34", "35-44", "45-59"))))
    return(alphaij)
}

alphaij_age_main <- alphaij_age(agemix_main_avg)
alphaij_age_pers <- alphaij_age(agemix_pers_avg)
alphaij_age_inst <- alphaij_age(agemix_inst_avg)

#Combine to make kable
 #B/c it won't let me combine these with non-unique row names, rename rows for pers and inst to have extra spaces
    rownames(alphaij_age_pers) <- c("18-24 ", "25-34 ", "35-44 ", "45-59 ")
    rownames(alphaij_age_inst) <- c("18-24  ", "25-34  ", "35-44  ", "45-59  ")

 alphaij_age <- rbind.data.frame(alphaij_age_main, alphaij_age_pers, alphaij_age_inst)
 
#Make kable
 kable(alphaij_age, caption="Age mixing: $alpha_{ij}$ terms", digits=c(2, 2, 2, 2)) %>% kable_styling(full_width=T, position="center") %>% add_header_above(c("Ego age", "Partner age" = 4)) %>% group_rows("Main partnerships", 1, 4) %>% group_rows("Persistent partnerships", 5, 8) %>% group_rows("Instantaneous partnerships", 9, 12) 


```

<span style="color:red"> The $\alpha_{ij}$ terms for the off-diagonal elements differ. This pattern will be captured by specifying age mixing using a term for the absolute difference in the square root of ego and alter ages.</span>