# Notes on rate of instantaneous partnerships (#rateinst_explore)
```{r}
####################################################################################
# Setup
####################################################################################
#-----------------------------------------------------------------------------------
# Load packages
#-----------------------------------------------------------------------------------

    library("tidyverse")
    library("knitr")
    library("kableExtra")

#-----------------------------------------------------------------------------------
# Knitr options
#-----------------------------------------------------------------------------------
opts_chunk$set(echo=FALSE, message=FALSE, warning=TRUE, error=TRUE, fig.align = "center")
options(knitr.table.format = "html") 

#-----------------------------------------------------------------------------------
# Plot settings
#-----------------------------------------------------------------------------------
#save plot settings for white background and light grey lines and darkening the colors a bit
plot_background <- theme(panel.background = element_rect(fill="white", colour = "black")) + theme(panel.grid.major = element_line(colour = "grey90"))
darken_color <- scale_colour_hue(l=50)
theme_title <- theme(plot.title = element_text(hjust = 0.5, size=12)) 
        
#-----------------------------------------------------------------------------------
# Load data
#-----------------------------------------------------------------------------------

load(file="Data/InternetSurveySample.Rdata")
```

This section explores the heterogeneity in the rate of instantaneous partnerships to inform decisions about how many quantiles of heterogeneity to represent and how to stratify it by momentary degree. 

## Quantiles of the rate of instantaneous partnerships
The statistics and plots below show the distribution of the reported rate of instantaneous partnerships (partnerships per day).

```{r rateinst_quants}
summary(sample$rate_inst)
ggplot(sample[!is.na(sample$rate_inst),], aes(rate_inst)) + geom_histogram(binwidth = 0.005) + labs(x="Rate of instantaneous partners", title="Distribution of the rate of instantaneous partners") + plot_background + theme_title
ggplot(sample[sample$rate_inst <0.25 & !is.na(sample$rate_inst),], aes(rate_inst)) + geom_histogram(binwidth = 0.005) + labs(x="Rate of instantaneous partners", title="Distribution of the rate of instantaneous partners, capped at 0.25") + plot_background + theme_title

```

From examining these data, we might group the data into quartiles, with the following distribution.
```{r rate_inst_quarts}
quartiles <- quantile(sample$rate_inst, c(0.025, 0.5, 0.75, 1), na.rm=TRUE)
sample$rate_inst_quart <- cut(sample$rate_inst, c(-0.01, quartiles), labels=c("0", "(0, 0.00274]", "(0.00274, 0.00821]", "(0.00821, 0.931]"))
table(sample$rate_inst_quart)
```

If we look at the mean within each quartile, we get the following:
```{r rate_inst_means}
    meanbyqrt <- function(x, y) {
        means <- as.vector(c((mean(x[x>=0 & x<=y[1]], na.rm=TRUE)),
                  (ifelse(y[1]<y[2], mean(x[x>y[1] & x<=y[2]], na.rm=TRUE), ifelse(y[1]==y[2], y[2], NA))),
                  (ifelse(y[2]<y[3], mean(x[x>y[2] & x<=y[3]], na.rm=TRUE), ifelse(y[2]==y[3], y[3], NA))),
                  (ifelse(y[3]<y[4], mean(x[x>y[3] & x<=y[4]], na.rm=TRUE), ifelse(y[3]==y[4], y[4], NA)))))
        return(means)
    }

   meanbyqrt(sample$rate_inst, quartiles)
```
  
## Heterogeneity in the rate of instantaneous partnerships by momentary degree
The statistics and plots below explore heterogeneity in the rate of instantaneous partners by momentary degree. In the plots, the rate of instantaneous partnerships is capped at 0.25, excluding 4 outliers.

```{r rate_inst_degree}
    sample %>% filter(!is.na(rate_inst) & !is.na(deg_matrix)) %>% group_by(deg_matrix) %>% summarise(freq = n(), Min = min(rate_inst), Q1 = quantile(rate_inst, 0.25), Median=median(rate_inst), Q3 = quantile(rate_inst, 0.75), Max = max(rate_inst))

    ggplot(sample[!is.na(sample$rate_inst) & !is.na(sample$deg_matrix) & sample$rate_inst<0.25,], aes(rate_inst)) + geom_histogram(binwidth = 0.005) + facet_grid(deg_matrix~.) + labs(x="Rate of instantaneous partnerships", title="Rate of instantaneous partnerships by momentary degree, capped at 0.25") + plot_background + theme_title
```