# Washington HIV Prevention Project demographic composition {#demog_compare}

```{r, echo=FALSE, include=FALSE}
####################################################################################
# 
####################################################################################

#-----------------------------------------------------------------------------------
# Load packages
#-----------------------------------------------------------------------------------

    library("tidyverse")
    library("psych") #To use "describe" function for continuous vars
    #library("nnet") #For multinomial logistic regression
    library("lmtest") #For likelihood ratio test
    library("ggplot2")
    library("survey")
    library("knitr")
    library("kableExtra")
    library("reshape2")

#-----------------------------------------------------------------------------------
# Load data
#-----------------------------------------------------------------------------------
    load(file="Data/InternetSurveySample.Rdata")
    load(file="Data/InternetSurveySample_allages.Rdata")
    load(file="Data/census_agebyregion.Rdata")
    load(file="Data/census_racebyregion.Rdata")
    load(file="Data/census_totalbyregion.Rdata")
    load(file="Data/wa_msm_est2013.Rdata")
    load(file="Data/msmbyregion.Rdata")
    load(file="Data/prop_msmbyregion.Rdata")
    load(file="Data/plwha_hboXregion.Rdata")
    load(file="Data/InternetSurvey_reweighted_neg.Rdata")
    
# Set options
    opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE)
    options(knitr.table.format = "html") 
    
```

This section compares the demographic composition of the 2017 Washington HIV Prevention Project (WHPP) sample to the demographic composition of Washington males. To examine the regional distribution, we compare the sample to the expected distribution of MSM by region, calculated by multiplying estimates of the proportion of males that are MSM at the county-level from [Grey et al.](http://www.emorycamp.org/item.php?i=48) [@Grey2016] by the size of the male population aged 18-59 in each county from the 2011-2015 American Community Survey (ACS)[@WA-census], and aggregating to the regional level. From these totals, we subtracted the number of MSM living with diagnosed HIV/AIDS^[2016 data on the number of persons living with diagnosed HIV/AIDS by age, race/ethnicity, and region were obtained from Jason Carr at the Washington State Department of Health in an email on 12/5/2017. These estimates were restricted to males whose infection was attributed to male-male sex (including those who also reported injection drug use). For this analysis, persons with no identified risk, such as male-male sex (approximately 10% of cases) were categorized using multiple imputation (procedure implemented by Jason Carr using a CDC-supplied MI program). Because there is differential missingness on exposure risk by county, using numbers for MSM that include imputed cases is recommended.] to better correspond to the sampled population, which excluded men who had ever tested HIV-positive. For age and race/ethnicity, because we lack population-based data on the demographic characteristics of Washington MSM, we compare the sample to 2011-2015 ACS data on all males aged 18-59. This comparison assumes that the demographic composition of the MSM population is similar to the demographic composition of all males. In these comparisons, persons living with HIV are not subtracted from the population totals, as this is unlikely to substantially alter the distribution at this level. In re-weighting the sample to better match the estimated number of MSM by age, race/ethnicity, and region, persons living with HIV are subtracted from the population totals (section \@ref(reweight)).

## Region {#region_compare}
Table \@ref(tab:region_compare), below, compares the regional composition of the WHPP sample, the regional distribution of males in Washington based on the 2011-2015 ACS, and the distribution calculated by applying the estimates of the size of the MSM population from @Grey2016 to the size of the male population ages 18-59 from the American Community Survey. The sample distribution appears to be a pretty close match to the distribution of MSM by region implied by application of @Grey2016's estimates to the American Community Survey population data.

```{r region_compare}

#Population distribution of WA males (calculated from ACS data and data on the distribution of PLWHA)
    #HIV-positive MSM regional distribution
    plwhaXregion <- plwha_hboXregion %>% group_by(region) %>% summarise(freq = sum(Freq))
        #Specify order of factors
        plwhaXregion$region <- factor(plwhaXregion$region, levels = c("King County", "Western WA", "Eastern WA"))
        plwhaXregion <- plwhaXregion %>% arrange(region)
    
    #Regional distribution of all males    
    wa_acs_totalbyregion$region <- factor(wa_acs_totalbyregion$region, levels = c("King County", "Other Western", "Eastern"))
        wa_acs_totalbyregion <- wa_acs_totalbyregion %>% arrange(region)
     
    #Calculated regional distribution for HIV-negative MSM 
    census_region_neg <- cbind.data.frame(region = c("King County", "Western WA", "Eastern WA"), freq = wa_acs_totalbyregion$total - plwhaXregion$freq)
    census_region_neg$percent <- census_region_neg$freq / sum(census_region_neg$freq)
        #Specify order of factors
        census_region_neg$region <- factor(census_region_neg$region, levels = c("King County", "Western WA", "Eastern WA"))
        census_region_neg <- census_region_neg %>% arrange(region)
    
#Sample distribution
    sample_region <- as.vector(prop.table(table(sample$region)))
    sample_region <- cbind.data.frame(region=c("King County", "Western WA", "Eastern WA"), percent=sample_region)
        #Specify order of factors
        sample_region$region <- factor(sample_region$region, levels = c("King County", "Western WA", "Eastern WA"))
        sample_region <- sample_region %>% arrange(region)

#Distribution by region from Grey et al. 
    propMSMbyregion$region <- factor(propMSMbyregion$region, levels = c("King County", "Other Western WA", "Eastern WA"))
    propMSMbyregion <- propMSMbyregion %>% arrange(region)
        
    MSMbyregion_neg <- cbind.data.frame(region = c("King County", "Western WA", "Eastern WA"), freq = census_region_neg$freq*propMSMbyregion$propmsm)
    MSMbyregion_neg$percent <- MSMbyregion_neg$freq / sum(MSMbyregion_neg$freq) 
        #Specify order of factors
        MSMbyregion_neg$region <- factor(MSMbyregion_neg$region, levels = c("King County", "Western WA", "Eastern WA"))
        MSMbyregion_neg <- MSMbyregion_neg %>% arrange(region)

#Combine columns
    region <- cbind.data.frame("Region" = sample_region$region,  "Census" = (census_region_neg$percent), "Sample" = (sample_region$percent), "Grey et al." = c(MSMbyregion_neg$percent))
    
#make table
    kable(region, col.names=c("Region", "Census (all males)", "WHPP (MSM)", "Grey et al. (MSM)"), digits=c(0, 3, 3, 3), caption="Regional distribution of HIV-negative/unknown status males: Census, WHPP sample, and Grey et al. 2016") %>% kable_styling(full_width=F, position="center")
```

## Age {#age_compare}
A limitation to using data from all males to approximate the true age composition of MSM is that there may be differences in the age profile of MSM due to migration patterns, particularly at the regional level, but we lack reliable data to inform this. Table \@ref(tab:agebyregion_compare) presents the age distribution of WHPP survey respondents by region alongside the age distribution of all Washington males, based on the 2011-2015 ACS 5-year estimates. We can see that the survey sample is proportionately younger and will need to be re-weighted (section \@ref(reweight)).

```{r agebyregion_compare}
#Define age distribution by region and combine columns
    #Census
    census_ageKC <- wa_acs_agebyregion %>% select(Age_group, Percent, region) %>% filter(region %in% "King County")
    census_ageOW <- wa_acs_agebyregion %>% select(Age_group, Percent, region) %>% filter(region %in% "Other Western")
    census_ageE <- wa_acs_agebyregion %>% select(Age_group, Percent, region) %>% filter(region %in% "Eastern")
    
    #Sample data
    sample_ageXregion <- sample %>% group_by(region, age_cat) %>% summarise(count = n()) %>% group_by(region) %>% mutate(percent = count / sum(count))
    sample_ageKC <- sample_ageXregion %>% select(region, age_cat, percent) %>% filter(region %in% "King County")
    sample_ageOW <- sample_ageXregion %>% select(region, age_cat, percent) %>% filter(region %in% "Western WA")
    sample_ageE <- sample_ageXregion %>% select(region, age_cat, percent) %>% filter(region %in% "Eastern WA")
    
    #Combine columns
    ageXregion <- cbind.data.frame("Age group" = sample_ageKC$age_cat,  "KC Census" = (census_ageKC$Percent), "KC Sample" = (sample_ageKC$percent), "OW Census" = (census_ageOW$Percent), "OW Sample" = (sample_ageOW$percent), "E Census" = (census_ageE$Percent), "E Sample" = (sample_ageE$percent))
    
#make table
    kable(ageXregion, col.names=c("Age Group", "Census", "WHPP", "Census", "WHPP", "Census", "WHPP"), digits=c(0, 3, 3, 3, 3, 3, 3), caption="Age distribution by region: Census and WHPP sample") %>% kable_styling(full_width=F, position="center") %>% add_header_above(c("", "King County" = 2, "Other Western WA" = 2, "Eastern WA" = 2)) 
```

## Race/ethnicity {#race_compare}
Table \@ref(tab:racebyregion_compare) presents the racial/ethnic distribution of WHPP survey respondents by region alongside the racial/ethnic distribution by region for males based on the 2011-2015 ACS data.^[The Hispanic group was defined as men of Hispanic/Latino ethnicity of any race, and the black group includes Non-Hispanic men who reported black race alone or in combination with one or more other races. Likely due to imprecision in the estimation algorithm for small areas, the sum of men across all race groups is slightly less than the total. As such, to define the 'other' race group, we subtracted the number of Hispanic and black men from the total in each region.] To better match the estimated population distribution by race/ethnicity in each region, we will reweight the sample (section \@ref(reweight)).

```{r racebyregion_compare}
#Define race/ethnic distribution by region and combine columns
    #Census
    wa_acs_racebyregion_melt <- melt(wa_acs_racebyregion, id="region")
    wa_acs_racebyregion_melt$hbo <- ifelse(wa_acs_racebyregion_melt$variable %in% "Percent_Hispanic", "Hispanic",
                                           ifelse(wa_acs_racebyregion_melt$variable %in% "Percent_black", "black",
                                                  "other"))
    names(wa_acs_racebyregion_melt)[names(wa_acs_racebyregion_melt)=="value"] <- "percent"
    
    census_raceKC <- wa_acs_racebyregion_melt %>% select(region, hbo, percent) %>% filter(region %in% "King County")
    census_raceOW <- wa_acs_racebyregion_melt %>% select(region, hbo, percent) %>% filter(region %in% "Other Western")
    census_raceE <- wa_acs_racebyregion_melt %>% select(region, hbo, percent) %>% filter(region %in% "Eastern")
    
    #Sample data
    sample_raceXregion <- sample %>% filter(!is.na(hbo)) %>% group_by(region, hbo) %>% summarise(count = n()) %>% group_by(region) %>% mutate(percent = count / sum(count))
    sample_raceKC <- sample_raceXregion %>% select(region, hbo, percent) %>% filter(region %in% "King County")
    sample_raceOW <- sample_raceXregion %>% select(region, hbo, percent) %>% filter(region %in% "Western WA")
    sample_raceE <- sample_raceXregion %>% select(region, hbo, percent) %>% filter(region %in% "Eastern WA")
    
    #Combine columns
    raceXregion <- cbind.data.frame("Race/ethnicity" = sample_raceKC$hbo,  "KC Census" = (census_raceKC$percent), "KC Sample" = (sample_raceKC$percent), "OW Census" = (census_raceOW$percent), "OW Sample" = (sample_raceOW$percent), "E Census" = (census_raceE$percent), "E Sample" = (sample_raceE$percent))
    
#make table
    kable(raceXregion, col.names=c("Race/ethnicity", "Census", "WHPP", "Census", "WHPP", "Census", "WHPP"), digits=c(0, 3, 3, 3, 3, 3, 3), caption="Racial/ethnic distribution by region: Census and WHPP sample") %>% kable_styling(full_width=F, position="center") %>% add_header_above(c("", "King County" = 2, "Other Western WA" = 2, "Eastern WA" = 2))

```