# Instantaneous partnerships {#rate_inst}
```{r, echo=FALSE, include=FALSE}
####################################################################################
# Setup
####################################################################################
#-----------------------------------------------------------------------------------
# Load packages
#-----------------------------------------------------------------------------------

    library("tidyverse")
    library("ggplot2")
    library("survey")
    library("knitr")
    library("xtable")
    library("kableExtra")
    library("data.table")

#-----------------------------------------------------------------------------------
# Load data
#-----------------------------------------------------------------------------------
    load(file="Data/InternetSurveySample.Rdata")
    load(file="Data/ARTNet_pos_wide.Rdata")
    load(file="Data/artnet_reweighted_pos_w.Rdata")
    load(file="Data/census_agebyregion.Rdata")
    load(file="Data/census_racebyregion.Rdata")
    load(file="Data/census_totalbyregion.Rdata")
    load(file="Data/wa_msm_est2013.Rdata")
    load(file="Data/msmbyregion.Rdata")
    load(file="Data/prop_msmbyregion.Rdata")
    load(file="Data/plwha_age.Rdata")
    load(file="Data/plwha_hboXregion.Rdata")
    

# Set options
    opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE)
    options(knitr.table.format = "html") 
 

```
The statistics in this file are based on the total number of reported instantaneous partnerships in the past 12 months. Data from HIV-negative/unknown status men are from the WHPP survey, and data from HIV-positive men are from the national ART-Net survey, both re-weighted to Washington demographics. 

To account for differential missingness in data on the number of one-time partners in the past 12 months in the WHPP survey (the ART-Net sample was defined to include only complete entries), we impute values for respondents with missing data using data from respondents of the same race/ethnicity, region, and age group. We do this by defining a restricted sample of people who had complete data on the number of one-time partners and main and persistent momentary degree.^[Because we define the rate of one-time partners stratified by main/persistent degree, we need to define the sample as those with non-missing data on all three variables. Only `r sum(!is.na(sample$deg_matrix) & is.na(sample$rate_inst))` people had missing data on the rate of one-time partners who did not have missing data on main/persistent degree, and `r sum(is.na(sample$deg_matrix) & !is.na(sample$rate_inst))` had missing data on main/pers degree who did not have missing data on the number of one-time partners.] We then rake this restricted sample to the joint distribution of race/ethnicity and region and simultaneously to the marginal distribution by age among Washington males without diagnosed HIV (see section \@ref(reweight) for details on this approach). This approach assumes that there is non-differential missingness. It ensures that the rate of instantaneous partnerships defined by main/persistent degree and age are consistent and imply the same total number of partnerships (see [issue 39](https://github.com/statnet/WHAMP/issues/39)). 

We will define the rate of instantaneous partnerships by main/persistent degree and age. We also define stratified rates by race/ethnicity and region for use in calculating mixing (`nodematch`) target statistics and for `nodefactor` target statistics (which are needed for interpretation of the mixing terms).

```{r, impute}
#-----------------------------------------------------------------------------------
# Define WHPP sample restricted to those with non-missing data on num one-time and degree
#-----------------------------------------------------------------------------------
 sample_nonmiss <- sample %>% filter(!is.na(rate_inst) & !is.na(degree_main) & !is.na(degreecat_cas))

#-----------------------------------------------------------------------------------
# Define survey object - set it up as though SRS
#-----------------------------------------------------------------------------------
    samplesvy_r <- svydesign(id=~1, data=sample_nonmiss)

#-----------------------------------------------------------------------------------
# Define "population" totals from census data and Jeremy Grey's analysis
#-----------------------------------------------------------------------------------

#Region
    pop.region.all <- MSMbyregion %>% select(region, numMSM) %>% mutate(total = round(numMSM)) %>% select(-numMSM)
    levels(pop.region.all$region)[levels(pop.region.all$region)=="Other Western WA"] <- "Western WA"
    
    #HIV-positive only
    pop.region.pos <- plwha_hboXregion %>% group_by(region) %>% summarise("total" = sum(Freq))
    pop.region.pos$region <- factor(pop.region.pos$region, levels = c("King County", "Western WA", "Eastern WA"))
    pop.region.pos <- pop.region.pos %>% arrange(region)

    #HIV-negative only
    pop.region.neg <- cbind.data.frame(region = c("King County", "Western WA", "Eastern WA"), total = c(round(pop.region.all$total[pop.region.all$region %in% "King County"] - pop.region.pos$total[pop.region.pos$region %in% "King County"]), round(pop.region.all$total[pop.region.all$region %in% "Western WA"] - pop.region.pos$total[pop.region.pos$region %in% "Western WA"]), round(pop.region.all$total[pop.region.all$region %in% "Eastern WA"] - pop.region.pos$total[pop.region.pos$region %in% "Eastern WA"])))
    pop.region.neg$region <- factor(pop.region.neg$region, levels = c("King County", "Western WA", "Eastern WA"))
    pop.region.neg <- pop.region.neg %>% arrange(region)
    
#Race and region
    pop.raceregion.all <- cbind.data.frame(region=c(rep("King County", 3), rep("Western WA", 3), rep("Eastern WA", 3)), hbo=c(rep(c("Hispanic", "Black", "Other"), 3)), Freq=c(wa_acs_racebyregion$Percent_Hispanic[wa_acs_racebyregion$region %in% "King County"]*pop.region.all$total[pop.region.all$region %in% "King County"], wa_acs_racebyregion$Percent_black[wa_acs_racebyregion$region %in% "King County"]*pop.region.all$total[pop.region.all$region %in% "King County"], wa_acs_racebyregion$Percent_other[wa_acs_racebyregion$region %in% "King County"]*pop.region.all$total[pop.region.all$region %in% "King County"], wa_acs_racebyregion$Percent_Hispanic[wa_acs_racebyregion$region %in% "Other Western"]*pop.region.all$total[pop.region.all$region %in% "Western WA"], wa_acs_racebyregion$Percent_black[wa_acs_racebyregion$region %in% "Other Western"]*pop.region.all$total[pop.region.all$region %in% "Western WA"], wa_acs_racebyregion$Percent_other[wa_acs_racebyregion$region %in% "Other Western"]*pop.region.all$total[pop.region.all$region %in% "Western WA"], wa_acs_racebyregion$Percent_Hispanic[wa_acs_racebyregion$region %in% "Eastern"]*pop.region.all$total[pop.region.all$region %in% "Eastern WA"], wa_acs_racebyregion$Percent_black[wa_acs_racebyregion$region %in% "Eastern"]*pop.region.all$total[pop.region.all$region %in% "Eastern WA"], wa_acs_racebyregion$Percent_other[wa_acs_racebyregion$region %in% "Eastern"]*pop.region.all$total[pop.region.all$region %in% "Eastern WA"]))
    #Specify order of factors
    pop.raceregion.all$hbo <- factor(pop.raceregion.all$hbo, levels = c("Hispanic", "Black", "Other"))
    pop.raceregion.all$region <- factor(pop.raceregion.all$region, levels = c("King County", "Western WA", "Eastern WA"))
    pop.raceregion.all <- pop.raceregion.all %>% arrange(region, hbo)

    #HIV-positive only
    pop.raceregion.pos <- plwha_hboXregion
        #Specify order of factors
        pop.raceregion.pos$hbo <- factor(pop.raceregion.pos$hbo, levels = c("Hispanic", "Black", "Other"))
        pop.raceregion.pos$region <- factor(pop.raceregion.pos$region, levels = c("King County", "Western WA", "Eastern WA"))
        pop.raceregion.pos <- pop.raceregion.pos %>% arrange(region, hbo)

    #HIV-negative only
    pop.raceregion.neg <- cbind.data.frame(region=c(rep("King County", 3), rep("Western WA", 3), rep("Eastern WA", 3)), hbo=c(rep(c("Hispanic", "Black", "Other"), 3)), Freq=c(round(pop.raceregion.all[1:3, 3] - pop.raceregion.pos[1:3, 3]), round(pop.raceregion.all[4:6, 3] - pop.raceregion.pos[4:6, 3]), round(pop.raceregion.all[7:9, 3] - pop.raceregion.pos[7:9, 3])))
    
#Race
    pop.hbo.all <- pop.raceregion.all %>% group_by(hbo) %>% summarise(Freq=sum(Freq))
    pop.hbo.pos <- pop.raceregion.pos %>% group_by(hbo) %>% summarise(Freq=sum(Freq))
    pop.hbo.neg <- pop.raceregion.neg %>% group_by(hbo) %>% summarise(Freq=sum(Freq))
         #Specify order of factors
        pop.hbo.neg$hbo <- factor(pop.hbo.neg$hbo, levels = c("Hispanic", "Black", "Other"))
        pop.hbo.neg <- pop.hbo.neg %>% arrange(hbo)

#Age
    #All MSM
    wa_acs_agebyregion$age_cat_alt <- ifelse(wa_acs_agebyregion$Age_group %in% c("males.40to44", "males.45to49"), "40-49", ifelse(wa_acs_agebyregion$Age_group %in% c("males.50to54", "males.55to59"), "50-59", ifelse(wa_acs_agebyregion$Age_group %in% "males.18to24", "18-24", ifelse(wa_acs_agebyregion$Age_group %in% "males.25to29", "25-29", ifelse(wa_acs_agebyregion$Age_group %in% "males.30to34", "30-34", ifelse(wa_acs_agebyregion$Age_group %in% "males.35to39", "35-39", NA))))))
    
    #Apply proportion MSM in each region to get age distribution among MSM
    wa_acs_agebyregion$numMSM <- ifelse(wa_acs_agebyregion$region %in% "Eastern", round(wa_acs_agebyregion$Frequency*propMSMbyregion$propmsm[propMSMbyregion$region %in% "Eastern WA"]), ifelse(wa_acs_agebyregion$region %in% "King County", round(wa_acs_agebyregion$Frequency*propMSMbyregion$propmsm[propMSMbyregion$region %in% "King County"]), ifelse(wa_acs_agebyregion$region %in% "Other Western", round(wa_acs_agebyregion$Frequency*propMSMbyregion$propmsm[propMSMbyregion$region %in% "Other Western WA"]), NA)))
    
    pop.age.all <- wa_acs_agebyregion %>% select(-Frequency) %>% group_by(age_cat_alt) %>% summarise(Freq = sum(numMSM))
    
    #HIV-positive only
    pop.age.pos <- plwha_age
    
    #HIV-negative only
    pop.age.neg <- cbind.data.frame(age_cat_alt = c("18-24", "25-29", "30-34", "35-39", "40-49", "50-59"), Freq = c(round(pop.age.all$Freq - pop.age.pos$Freq)))
    

#-----------------------------------------------------------------------------------
# Rake the survey sample using population totals for all MSM
#-----------------------------------------------------------------------------------
    sample_rake_neg_r <- rake(samplesvy_r, list(~hbo+region, ~age_cat_alt), list(pop.raceregion.neg, pop.age.neg))

```

```{r merge}

#-----------------------------------------------------------------------------------
# Merge ART-Net and WHPP datasets with the relevant variables ##
#-----------------------------------------------------------------------------------

    neg_wts <- cbind.data.frame("pid" = sample_rake_neg_r$variables$pid, "weight" = (1/sample_rake_neg_r$prob))
    neg <- merge(sample_nonmiss, neg_wts, by= "pid")
    neg$hiv <- 0
    neg$mrp_hivpos <- ifelse(neg$mrp_statuscat_now %in% "HIV-positive", 1, 
                                         ifelse(neg$mrp_statuscat_now %in% c("HIV-negative", "Unknown"), 0,
                                                NA))
    neg$mrp_type <- ifelse(neg$mrp_type_r %in% "Main", "Main", ifelse(neg$mrp_type_r %in% "Casual", "Pers", ifelse(neg$mrp_type_r %in% "One time", "Inst", NA)))
    setnames(neg, old = "mrp_ageinyears_approx", new = "mrp_ageinyrs")
    neg.rateinst <- neg %>% select(pid, rate_inst, degree_main, degreecat_cas, region, hbo, age, hiv, mrp_type_ongoing, mrp_type, mrp_ageinyrs, mrp_hivpos, weight)

    
    pos_wts <- cbind.data.frame("AMIS_ID" = artnet_pos_rake_w$variables$AMIS_ID, "weight" = (1/artnet_pos_rake_w$prob))
    pos <- merge(artnet_pos_w, pos_wts, by= "AMIS_ID")
    pos$hiv <- 1
    pos$region <- NA #Since ART-Net is a national sample, set the WA region variable to missing
    pos$mrp_type_ongoing <- ifelse(pos$mrp_type %in% "Main" & pos$mrp_ongoing %in% 1, "Main",
                                   ifelse(pos$mrp_type %in% "Pers" & pos$mrp_ongoing %in% 1, "Persistent",
                                          NA))
    pos$mrp_type_ongoing <- as.factor(pos$mrp_type_ongoing)
    pos$deg.pers_cat <- factor(pos$deg.pers_cat, levels = c(0, 1, 2), labels = c("None", "One", "Two or more"))
    setnames(pos, old = c("deg.main_cat", "deg.pers_cat", "AMIS_ID"), new = c("degree_main", "degreecat_cas", "pid"))
    pos.rateinst <- pos %>% select(pid, rate_inst, degree_main, degreecat_cas, region, hbo, age, hiv, mrp_type_ongoing, mrp_type, mrp_ageinyrs, mrp_hivpos, weight)

    inst.full.unweighted <- rbind.data.frame(pos.rateinst, neg.rateinst)
    inst.full <- svydesign(id=~1, data=inst.full.unweighted, weights = ~weight) # Note this doesn't get the variance correct, but it gets the sample composition
    
    rm(pos_wts, pos, pos.rateinst, neg_wts, neg, neg.rateinst, samplesvy_r)
  
#-----------------------------------------------------------------------------------
# Data manipulation
#-----------------------------------------------------------------------------------

# Change degree variables to factor and add labels
inst.full$variables$degree_main <- factor(inst.full$variables$degree_main, levels = c(0, 1), labels = c("No main", "Main"))
    
# Re-order race and region variables
inst.full$variables$hbo <- factor(inst.full$variables$hbo, levels = c("Hispanic", "Black", "Other"), labels = c("Hispanic", "Black", "Other"))
inst.full$variables$region <- factor(inst.full$variables$region, levels = c("King County", "Western WA", "Eastern WA"), labels = c("King County", "Western WA", "Eastern WA"))

# Define indicator of age 50+
inst.full$variables$age50plus <- cut(inst.full$variables$age, c(17, 49, 59), labels=c("18-49", "50-59")) 

#-----------------------------------------------------------------------------------
# Save
#-----------------------------------------------------------------------------------

save(inst.full, file = "Data/rate.inst.fullpop.Rdata")

```

Overall, the mean rate of instantaneous partnerships was `r round(svymean(~rate_inst, inst.full, na.rm=TRUE)[[1]], 4)` per day. Among men under 50, the mean was `r round(svymean(~rate_inst, inst.full[inst.full$variables$age50plus %in% "18-49"], na.rm=TRUE)[[1]], 4)` per day, and among men 50 and older, the mean was `r round(svymean(~rate_inst, inst.full[inst.full$variables$age50plus %in% "50-59"], na.rm=TRUE)[[1]], 4)` per day.

## Instantaneous partnerships by momentary degree
Based on exploratory analyses in section \@ref(explore_heterogeneity), we decided to stratify the rate of instantaneous partnerships by the joint distribution of main and persistent partnership status.
```{r rate_instXdeg}
means <- svyby(~rate_inst, ~degree_main + degreecat_cas, inst.full, svymean, na.rm=TRUE)
means$rate_inst <- round(means$rate_inst, 6)
meansXdegmatrix <- as.data.frame(matrix(as.vector(means$rate_inst), nrow=2, ncol=3, byrow=FALSE))
names(meansXdegmatrix) <- c("0 pers", "1 pers", "2+ pers")
row.names(meansXdegmatrix) <- c("0 main", "1 main")

kable(meansXdegmatrix, caption="Mean rate of instantaneous partnerships per day by momentary degree", digits=c(6, 6, 6)) %>% kable_styling(full_width=F, position="center") %>% column_spec(1, bold=T, color="black", width="2.5cm") %>% column_spec(2:4, width = "3cm")

#save means
save(meansXdegmatrix, file="Data/rate_inst_mdeg.Rdata")
```

## Mean rate of instantaneous partnerships by quartile
To capture heterogeneity in the rate of instantaneous partnerships by age, we decided to calculate the means within quartiles of the distribution for men aged 18 to 49 and for men aged 50 to 59 (section \@ref(decisions). The table below shows the mean rate of instantaneous partnerships within each quartile of the distribution by age group.

```{r rate_instXquart}
  #Apply the weights from inst.full to the unweighted dataframe to construct a new dataframe with the appropriate composition that can be manipulated and analyzed without using the 'survey' package commands. Need to do this b/c I can't divide the sample into even quartiles and take mean within each group using the survey package commands.) Note that it does not work to replicate each row according to the sample weights (i.e. `sample[rep(row.names(sample), sample$wts), ]`) b/c the weights are not integers, so it rounds down in deciding how many times to replicate.

# # Comment out so does not re-sample each time I run the file
#    #Resample from the original survey dataframe 20 times using the raked weights
#   qrtmeans_18to49 <- list()
#   qrtmeans_50to59 <- list()
# 
#   for(i in 1:20){
#       inst.full_rwt <- inst.full.unweighted %>% sample_n(1000000, replace=TRUE, weight=weight)
# 
#       #Age 18 to 49
#       inst.full_rwt_18to49 <- inst.full_rwt %>% filter(age %in% c(18:49))
#       inst.full_rwt_18to49$rate_inst <- sort(inst.full_rwt_18to49$rate_inst, na.last = TRUE)
#       qsize.18to49=floor(sum(!is.na(inst.full_rwt_18to49$rate_inst))/4)
#       qrtmeans_18to49_i <- mean(inst.full_rwt_18to49$rate_inst[1:qsize.18to49])
#       qrtmeans_18to49_i[2] <- mean(inst.full_rwt_18to49$rate_inst[(1*qsize.18to49+1):(2*qsize.18to49)])
#       qrtmeans_18to49_i[3] <- mean(inst.full_rwt_18to49$rate_inst[(2*qsize.18to49+1):(3*qsize.18to49)])
#       qrtmeans_18to49_i[4] <- mean(inst.full_rwt_18to49$rate_inst[(3*qsize.18to49+1):(sum(!is.na(inst.full_rwt_18to49$rate_inst)))])
# 
#       qrtmeans_18to49[[i]] <- qrtmeans_18to49_i
# 
#       #Age 50-59
#       inst.full_rwt_50to59 <- inst.full_rwt %>% filter(age %in% c(50:59))
#       inst.full_rwt_50to59$rate_inst <- sort(inst.full_rwt_50to59$rate_inst, na.last = TRUE)
#       qsize.50to59=floor(sum(!is.na(inst.full_rwt_50to59$rate_inst))/4)
#       qrtmeans_50to59_i <- mean(inst.full_rwt_50to59$rate_inst[1:qsize.50to59])
#       qrtmeans_50to59_i[2] <- mean(inst.full_rwt_50to59$rate_inst[(1*qsize.50to59+1):(2*qsize.50to59)])
#       qrtmeans_50to59_i[3] <- mean(inst.full_rwt_50to59$rate_inst[(2*qsize.50to59+1):(3*qsize.50to59)])
#       qrtmeans_50to59_i[4] <- mean(inst.full_rwt_50to59$rate_inst[(3*qsize.50to59+1):(sum(!is.na(inst.full_rwt_50to59$rate_inst)))])
# 
#       qrtmeans_50to59[[i]] <- qrtmeans_50to59_i
#   }
# 
#   #Take average of the 20 samples
#   avg.qrtmeans.18to49 <- mean(sapply(qrtmeans_18to49, `[[`, 1))
#   avg.qrtmeans.18to49[2] <- mean(sapply(qrtmeans_18to49, `[[`, 2))
#   avg.qrtmeans.18to49[3] <- mean(sapply(qrtmeans_18to49, `[[`, 3))
#   avg.qrtmeans.18to49[4] <- mean(sapply(qrtmeans_18to49, `[[`, 4))
# 
#   avg.qrtmeans.50to59 <- mean(sapply(qrtmeans_50to59, `[[`, 1))
#   avg.qrtmeans.50to59[2] <- mean(sapply(qrtmeans_50to59, `[[`, 2))
#   avg.qrtmeans.50to59[3] <- mean(sapply(qrtmeans_50to59, `[[`, 3))
#   avg.qrtmeans.50to59[4] <- mean(sapply(qrtmeans_50to59, `[[`, 4))
# 
# #Save means
#   save(avg.qrtmeans.18to49, file="Data/rate_inst_qrtmeans_18to49.Rdata")
#   save(avg.qrtmeans.50to59, file="Data/rate_inst_qrtmeans_50to59.Rdata")

  #Load means within quartiles
    load(file="Data/rate_inst_qrtmeans_18to49.Rdata")
    load(file="Data/rate_inst_qrtmeans_50to59.Rdata")

  #Combine into a kable
    meansXqrt <- cbind.data.frame("Age group" = c("18-49", "50-59"), "Q1"=c(avg.qrtmeans.18to49[1], avg.qrtmeans.50to59[1]), "Q2"=c(avg.qrtmeans.18to49[2], avg.qrtmeans.50to59[2]), "Q3"=c(avg.qrtmeans.18to49[3], avg.qrtmeans.50to59[3]), "Q4"=c(avg.qrtmeans.18to49[4], avg.qrtmeans.50to59[4]))

  kable(meansXqrt, col.names = c("Age group", "Q1", "Q2", "Q3", "Q4"), caption="Mean rate of instantaneous partnerships per day by quartile within age groups", digits=c(0, 6, 6, 6, 6)) %>% kable_styling(full_width=F, position="center") %>% column_spec(2:5, width = "2cm") %>% add_header_above(c(" ", "Mean rates"=4))
```

## Instantaneous partnerships by race/ethnicity
```{r rate_instXhbo}
means.hbo <- svyby(~rate_inst, ~hbo, inst.full, svymean, na.rm=TRUE)
meansXhbo <- cbind.data.frame("Race" = means.hbo$hbo, "Mean" = round(means.hbo$rate_inst, 6))

#Reorder race var to alphabetical order
meansXhbo$Race <- factor(meansXhbo$Race, levels = c("Black", "Hispanic", "Other"))
meansXhbo <- meansXhbo %>% arrange(Race)

#Make kable
kable(meansXhbo, caption="Mean rate of instantaneous partnerships per day by racial/ethnic group", digits=c(6)) %>% kable_styling(full_width=F, position="center") %>% column_spec(1:2, width = "4cm")

#save means
save(meansXhbo, file="Data/rate_inst_hbo.Rdata")
```

## Instantaneous partnerships by region
Since the data on HIV-positive men are from a national sample (ART-Net), we don't have data on the regional distribution within Washington of the rate of instantaneous partnerships among HIV-positives. As such, we will assume that the relative distribution of instantaneous partnerships among HIV-negative men in the WHPP sample is representative of the distribution in the full sample. We will estimate the proportion of instantaneous degree among HIV-negative men in the re-weighted sample that is in each region, and use this proportion to calculate the target statistics in the full network. 

First we will look at the rates of instantaneous partnerships by region among HIV-negative men.
```{r rate_instXregion}
means.region <- svyby(~rate_inst, ~region, inst.full, svymean, na.rm=TRUE)
meansXregion <- cbind.data.frame("Region" = means.region$region, "Mean" = round(means.region$rate_inst, 6))

#Reorder region var to alphabetical order
meansXregion$Region <- factor(meansXregion$Region, levels = c("Eastern WA", "King County", "Western WA"))
meansXregion <- meansXregion %>% arrange(Region)

#Make kable
kable(meansXregion, caption="Mean rate of instantaneous partnerships per day by region", digits=c(6)) %>% kable_styling(full_width=F, position="center") %>% column_spec(1:2, width = "4cm")

```

Next we will calculate the distribution of instantaneous degree by region.

```{r}
num.inst.EW <- meansXregion$Mean[1]*svytable(~region, inst.full, round=FALSE)[3]
num.inst.KC <- meansXregion$Mean[2]*svytable(~region, inst.full, round=FALSE)[1]
num.inst.OW <- meansXregion$Mean[3]*svytable(~region, inst.full, round=FALSE)[2]
num.inst.neg <- svymean(~rate_inst, inst.full[inst.full$variables$hiv %in% 0], na.rm=TRUE)[[1]]*svytable(~hiv, inst.full, round=FALSE)[1]

inst.dist.region <- cbind.data.frame(proportion = c(num.inst.EW/num.inst.neg, num.inst.KC/num.inst.neg, num.inst.OW/num.inst.neg))

kable(inst.dist.region, col.names=c("Proportion"),  digits = 4, caption="Distribution of instantaneous degree by region") %>% kable_styling(full_width=F, position="center") %>% column_spec(1:2, width = "4cm")

# Save
save(inst.dist.region, file="Data/rate_inst_region.Rdata")
```
