# Anal sex role {#sexrole}
```{r, echo=FALSE, include=FALSE}
####################################################################################
# Setup
####################################################################################
#-----------------------------------------------------------------------------------
# Load packages
#-----------------------------------------------------------------------------------

    library("tidyverse")
    library("ggplot2")
    library("survey")
    library("knitr")
    library("kableExtra")

#-----------------------------------------------------------------------------------
# Load data
#-----------------------------------------------------------------------------------
    # load(file="Data/InternetSurveySample.Rdata")
    # load(file="Data/rate.inst.fullpop.Rdata")
    # load(file="Data/degreedists.Rdata")
    # load(file="Data/race_mixing.Rdata")
    # load(file="/homes/dpwhite/win/project/MMP_WADOH/mmp_reweighted.Rdata")
    load(file = "Data/whpp_artnet.Rdata")
    load(file = "/homes/dpwhite/win/project/MMP_WADOH/whpp_mmp.Rdata")

# Set options
    opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE)
    options(knitr.table.format = "html") 
  
```
This section summarises the target statistics for anal sex role, operationalized as the proportion of nodes that are exclusively insertive, exclusively receptive, or versatile. We use data from the WHPP and MMP samples^[The proportions are similar using the WHPP data combined with ART-Net data for positives: 0.212 receptive, 0.144 insertive, 0.644 versatile.], reweighted to the population totals for Washington. In the WHPP survey, respondents were asked to characterize their role in anal sex with all of their male anal sex partners in the past 12 months, with options of: Always a bottom (receptive partner), Mostly a bottom (receptive partner), Equally a bottom (receptive partner) and a top (insertive partner), mostly a top (insertive partner), or always a top (insertive partner). Responses of mostly a bottom, equally a bottom and a top, and mostly a top were classified as versatile. In the MMP survey, sex role is determined from reports of receptive and insertive anal sex with each of the most recent 5 partners. Men who reported both receptive and insertive sex with their partners were classified as versatile. Based on the results of exploratory analyses with WHPP data (section \@ref(explore_heterogeneity)), we decided not to stratify sex role by any attributes.

```{r}
position <- as.data.frame(prop.table(svytable(~position_cat, whpp_mmp, round=FALSE)))

kable(position, col.names = c("", "Proportion"), digits=c(0, 3), align = c("l", "c"))  %>% column_spec(1, bold=T, color="black", width="4cm") %>% kable_styling(full_width=F, position="center")

sexrole.irv <- paste(round(prop.table(svytable(~position_cat, whpp_mmp, round=FALSE)),3)[[2]], round(prop.table(svytable(~position_cat, whpp_mmp, round=FALSE)),3)[[1]], round(prop.table(svytable(~position_cat, whpp_mmp, round=FALSE)),3)[[3]], sep=", ")
save(sexrole.irv, file="Data/sexrole.Rmd")
```