---
output:
  html_document:
    toc: true
    toc_float: true
---
# Network model diagnostics - balanced statistics with adjusted region mixing

## Load packages and model fits
```{r, warning=FALSE}
rm(list = ls())
suppressMessages(library("EpiModelHIV"))
library("latticeExtra")
library("knitr")
library("kableExtra")
library("here")


load(file = here("Model fits and simulations/Fit tests and debugging/est/fit.p.buildup.bal_region-adj.rda"))
#regional adjustment doesn't impact target stats for inst model, but does affect it in that it affects the deg.pers and deg.main terms
load(file = here("Model fits and simulations/Fit tests and debugging/est/fit.i.buildup.bal.rda")) 
load(file = here("Model fits and simulations/Fit tests and debugging/est/fit.m.buildup.bal_region-adj.rda"))

```

## Model terms and control settings
The control settings for these models are:
```{r, eval=FALSE}
# Main and persistent
set.control.ergm = control.ergm(MCMC.interval = 1e+5,
                                 MCMC.samplesize = 7500,
                                 MCMC.burnin = 1e+6,
                                 MPLE.max.dyad.types = 1e+7,
                                 init.method = "zeros",
                                 MCMLE.maxit = 400,
                                 parallel = np/2,
                                 parallel.type="PSOCK"))

# Instantaneous
set.control.ergm =control.ergm(MCMC.interval = 1e+5,
                                  MCMC.samplesize = 7500,
                                  MCMC.burnin = 1e+6,
                                  MPLE.max.dyad.types = 1e+7,
                                  MCMLE.maxit = 400,
                                  parallel = np/2, 
                                  parallel.type="PSOCK"))
```

## MCMC diagnostics

### Main, with 100% homophily on region
```{r, message=FALSE, echo=FALSE}
mcmc.diagnostics(est.m.buildup.bal[[7]]$fit)
```

### Persistent, with 80% homophily on region
```{r, message=FALSE, echo=FALSE}
mcmc.diagnostics(est.p.buildup.bal[[8]]$fit)
```

### Instantaneous, with 80% homophily on region
```{r, message=FALSE, echo=FALSE}
mcmc.diagnostics(est.i.buildup.bal[[8]]$fit)
```

## Summary of model fit

### Main, with 100% homophily on region
```{r, message=FALSE, echo=FALSE}
summary(est.m.buildup.bal[[7]])
```

### Persistent, with 80% homophily on region
```{r, message=FALSE, echo=FALSE}
summary(est.p.buildup.bal[[8]])
```

### Instantaneous, with 80% homophily on region
```{r, message=FALSE, echo=FALSE}
summary(est.i.buildup.bal[[8]])
```

## Network diagnostics

### Main, with 100% homophily on region
```{r}
(dx_main <- netdx(est.m.buildup.bal[[8]], nsims = 10, nsteps = 1000, ncores = 4, set.control.stergm = control.simulate.network(MCMC.burnin.min = 1e+5, MCMC.burnin.max = 1e+5)))
plot(dx_main, type="formation")
plot(dx_main, type="duration")
plot(dx_main, type="dissolution")
```

### Persistent, with 80% homophily on region
```{r}
(dx_pers <- netdx(est.p.buildup.bal[[8]], nsims = 10, nsteps = 1000, ncores = 4, set.control.stergm = control.simulate.network(MCMC.burnin.min = 1e+6, MCMC.burnin.max = 1e+6)))
plot(dx_pers, type="formation")
plot(dx_pers, type="duration")
plot(dx_pers, type="dissolution")
```

### Instantaneous, with 80% homophily on region
```{r}
(dx_inst <- netdx(est.i.buildup.bal[[8]], nsims = 10, nsteps = 1000, ncores = 4, set.control.ergm = control.simulate.ergm(MCMC.burnin = 1e+6, MCMC.interval = 1e+5)))
plot(dx_inst, type="formation")
plot(dx_inst, type="duration")
plot(dx_inst, type="dissolution")
```