---
output:
  html_document:
    toc: true
    toc_float: true
---
# Instantaneous network model diagnostics - balanced statistics
This file shows diagnostics for instantaneous network models fit using balanced racial/ethnic mixing matrices and adjusted degree terms. Here we test whether we can fit a model with only edges + nodefactor("riskg") to see if the risk group definitions are problematic independent of other terms in the model. We try fitting these using the original target statistics from the data, where the lowest groups have 0 instantaneous partnerships (model 1), and adjusting these to 0.0001 to give them a non-zero probability of partnership formation (model 2).

## Load packages and model fits
```{r, warning=FALSE}
rm(list = ls())
suppressMessages(library("EpiModelHIV"))
library("latticeExtra")
library("knitr")
library("kableExtra")
library("here")

load(file = here("Model fits and simulations/Fit tests and debugging/est/fit.i.testriskg.bal.rda"))

```

## Model terms and control settings
```{r, echo=FALSE}
targets <- cbind.data.frame("terms" = c(est.i.testriskg.bal[[2]]$target.stats.names, "nodematch.role.class.I", "nodematch.role.class.R"), "stats.1" = round(c(est.i.testriskg.bal[[1]]$target.stats, -Inf, -Inf),1), "stats.2" = round(c(est.i.testriskg.bal[[2]]$target.stats, -Inf, -Inf),1))

kable(targets, col.names = c("Terms", "Model 1", "Model 2"), caption="Model terms and target statistics") %>% kable_styling(full_width=F, position="center")
```

The control settings for these models are:
```{r, eval=FALSE}
set.control.ergm = control.ergm(MCMC.interval = 1e+5,
                                MCMC.samplesize = 7500,
                                MCMC.burnin = 1e+6,
                                MPLE.max.dyad.types = 1e+7,
                                MCMLE.maxit = 400,
                                parallel = np/2, 
                                parallel.type="PSOCK"))
```

## MCMC diagnostics

### Model 1
```{r, message=FALSE, echo=FALSE}
mcmc.diagnostics(est.i.testriskg.bal[[1]]$fit)
```

### Model 2
```{r, message=FALSE, echo=FALSE}
# mcmc.diagnostics(est.i.testriskg.bal[[2]]$fit)
```

## Summary of model fit

### Model 1
```{r}
summary(est.i.testriskg.bal[[1]])
```

### Model 2
```{r}
# summary(est.i.testriskg.bal[[2]])
```

## Network diagnostics

### Model 1
```{r}
(dx_main1 <- netdx(est.i.testriskg.bal[[1]], nsims = 10, nsteps = 1000, ncores = 4, set.control.ergm = control.simulate.ergm(MCMC.interval = 1e+5, MCMC.burnin = 1e+6)))
plot(dx_main1, type="formation")
plot(dx_main1, type="duration")
plot(dx_main1, type="dissolution")
```

### Model 2
```{r}
# (dx_main2 <- netdx(est.i.testriskg.bal[[2]], nsims = 10, nsteps = 1000, ncores = 4))
# plot(dx_main2, type="formation")
# plot(dx_main2, type="duration")
# plot(dx_main2, type="dissolution")
```

