---
output:
  html_document:
    toc: true
    toc_float: true
---
# Network model diagnostics - balanced statistics

## Load packages and model fits
```{r, warning=FALSE}
rm(list = ls())
suppressMessages(library("EpiModelHIV"))
library("latticeExtra")
library("knitr")
library("kableExtra")
library("here")

load(file = here("Model fits and simulations/Fit tests and debugging/est/est.m.bal.bdmaxout.rda"))

```

## Main model
This model uses balanced statistics for racial/ethnic mixing and race/ethnicity-specific degree, imposes the constraint on degree using the argument: `constraints = ~bd(maxout = 1),` and assumes 100% regional homophily.

### Model terms and control settings
```{r}
targets <- cbind.data.frame("terms" = c(fit.m$target.stats.names, "nodematch.role.class.I", "nodematch.role.class.R", "mix.region.EW.KC", "mix.region.EW.OW", "mix.region.KC.OW"), "stats" = round(c(fit.m$target.stats, rep(-Inf, 5)),1))

kable(targets, col.names = c("Terms and constraints", ""), caption="Model terms, constraints, and target statistics") %>% kable_styling(full_width=F, position="center")


```

```{r, eval=FALSE}
set.control.ergm = control.ergm(MCMC.interval = 1e+5,
                                 MCMC.samplesize = 7500,
                                 MCMC.burnin = 1e+6,
                                 MPLE.max.dyad.types = 1e+7,
                                 init.method = "zeros",
                                 MCMLE.maxit = 400,
                                 parallel = np/4, 
                                 parallel.type="PSOCK"))

```

### MCMC diagnostics
```{r, message=FALSE, echo=FALSE}
mcmc.diagnostics(fit.m$fit)
```

### Summary of model fit
```{r, message=FALSE, echo=FALSE}
summary(fit.m)
```

### Network diagnostics
```{r}
(dx_main <- netdx(fit.m, nsims = 10, nsteps = 1000, ncores = 4, set.control.stergm = control.simulate.network(MCMC.burnin.min = 1e+5, MCMC.burnin.max = 1e+5), set.control.ergm = control.simulate.ergm(MCMC.interval = 1e+5, MCMC.burnin = 1e+6)))
plot(dx_main, type="formation")
plot(dx_main, type="duration")
plot(dx_main, type="dissolution")
```
