---
output:
  html_document:
    toc: true
    toc_float: true
---
# Main network model diagnostics - balanced statistics
This file shows diagnostics for main network models fit using balanced racial/ethnic mixing matrices and degree terms as reported by egos. Here we test the impact of constraints by degree (max degree = 1) and mixing by role class (no receptive-receptive or insertive-insertive partnerships). The first model is a simple `edges + nodefactor(race) + nodematch(race)` model (corresponding to model 3 in dx_main_balanced_buildup) without constraints. We then add the constraint for degree in model 2, then the constraint for role class in model 3, then both constraints in model 4.

## Load packages and model fits
```{r, warning=FALSE}
rm(list = ls())
suppressMessages(library("EpiModelHIV"))
library("latticeExtra")
library("knitr")
library("kableExtra")
library("here")

load(file = here("Model fits and simulations/Fit tests and debugging/est/fit.m.testconstraints.bal.rda"))

```

## Model terms and control settings
```{r, echo=FALSE}
targets <- cbind.data.frame("terms" = c(est.m.testconstraints.bal[[4]]$target.stats.names, "degrange", "nodematch.role.class.I", "nodematch.role.class.R"), "stats.1" = round(c(est.m.testconstraints.bal[[1]]$target.stats, rep(NA,3)),1), "stats.2" = round(c(est.m.testconstraints.bal[[2]]$target.stats, rep(NA, 2)),1), "stats.3" = round(c(est.m.testconstraints.bal[[3]]$target.stats, NA, -Inf, -Inf),1), "stats.4" = round(c(est.m.testconstraints.bal[[4]]$target.stats, -Inf, -Inf),1))

kable(targets, col.names = c("Terms", "Model 1", "Model 2", "Model 3", "Model 4"), caption="Model terms and target statistics") %>% kable_styling(full_width=F, position="center")
```

The control settings for these models are:
```{r, eval=FALSE}
set.control.ergm = control.ergm(MCMC.interval = 1e+5,
                                MCMC.samplesize = 7500,
                                MCMC.burnin = 1e+6,
                                MPLE.max.dyad.types = 1e+7,
                                init.method = "zeros",
                                MCMLE.maxit = 400,
                                parallel = np/2, 
                                parallel.type="PSOCK"))
```

## MCMC diagnostics

### Model 1
```{r, message=FALSE, echo=FALSE}
mcmc.diagnostics(est.m.testconstraints.bal[[1]]$fit)
```

### Model 2
```{r, message=FALSE, echo=FALSE}
mcmc.diagnostics(est.m.testconstraints.bal[[2]]$fit)
```

### Model 3
```{r, message=FALSE, echo=FALSE}
mcmc.diagnostics(est.m.testconstraints.bal[[3]]$fit)
```

### Model 4
```{r, message=FALSE, echo=FALSE}
mcmc.diagnostics(est.m.testconstraints.bal[[4]]$fit)
```

## Summary of model fit

### Model 1
```{r}
summary(est.m.testconstraints.bal[[1]])
```

### Model 2
```{r}
summary(est.m.testconstraints.bal[[2]])
```

### Model 3
```{r}
summary(est.m.testconstraints.bal[[3]])
```

### Model 4
```{r}
summary(est.m.testconstraints.bal[[4]])
```

## Network diagnostics

### Model 1
```{r}
(dx_main1 <- netdx(est.m.testconstraints.bal[[1]], nsims = 10, nsteps = 1000, ncores = 4, nwstats.formula = est.m.testconstraints.bal[[4]]$formation))
plot(dx_main1, type="formation")
plot(dx_main1, type="duration")
plot(dx_main1, type="dissolution")
```

### Model 2
```{r}
(dx_main2 <- netdx(est.m.testconstraints.bal[[2]], nsims = 10, nsteps = 1000, ncores = 4, nwstats.formula = est.m.testconstraints.bal[[4]]$formation))
plot(dx_main2, type="formation")
plot(dx_main2, type="duration")
plot(dx_main2, type="dissolution")
```

### Model 3
```{r}
(dx_main3 <- netdx(est.m.testconstraints.bal[[3]], nsims = 10, nsteps = 1000, ncores = 4, nwstats.formula = est.m.testconstraints.bal[[4]]$formation))
plot(dx_main3, type="formation")
plot(dx_main3, type="duration")
plot(dx_main3, type="dissolution")
```

### Model 4
```{r}
(dx_main4 <- netdx(est.m.testconstraints.bal[[4]], nsims = 10, nsteps = 1000, ncores = 4, nwstats.formula = est.m.testconstraints.bal[[4]]$formation))
plot(dx_main4, type="formation")
plot(dx_main4, type="duration")
plot(dx_main4, type="dissolution")
```
