---
output:
  html_document:
    toc: true
    toc_float: true
---
# Main network model diagnostics - balanced statistics 
This file shows diagnostics for main network models fit using balanced racial/ethnic mixing matrices and degree terms adjusted to correspond to the balanced mixing matrices. In this file, we compare models with regional assortativity ranging from 60% to 100%.

## Load packages and model fits
```{r, warning=FALSE}
rm(list = ls())
suppressMessages(library("EpiModelHIV"))
library("latticeExtra")
library("knitr")
library("kableExtra")
library("here")

load(file = here("Model fits and simulations/Fit tests and debugging/est/fit.m.testregionmix.bal.rda"))

```

## Model terms and control settings

```{r, echo=FALSE}
targets <- cbind.data.frame("terms" = c(est.m.testregionmix.bal[[1]]$target.stats.names, "degrange", "nodematch.role.class.I", "nodematch.role.class.R", "mix.region.EW.KC", "mix.region.EW.OW", "mix.region.KC.OW"), "stats.1" = round(c(est.m.testregionmix.bal[[1]]$target.stats, -Inf, -Inf, rep(NA,3)),1), "stats.2" = round(c(est.m.testregionmix.bal[[2]]$target.stats, -Inf, -Inf, rep(NA,3)),1), "stats.3" = round(c(est.m.testregionmix.bal[[3]]$target.stats, -Inf, -Inf, rep(NA,3)),1), "stats.4" = round(c(est.m.testregionmix.bal[[4]]$target.stats, -Inf, -Inf, rep(NA,3)),1), "stats.5" = round(c(est.m.testregionmix.bal[[5]]$target.stats[1:11], NA, est.m.testregionmix.bal[[5]]$target.stats[12], -Inf, -Inf, -Inf, -Inf, -Inf),1))

kable(targets, col.names = c("Terms", "Model 1", "Model 2", "Model 3", "Model 4", "Model 5"), caption="Model terms and target statistics") %>% kable_styling(full_width=F, position="center")
```

The control settings for these models are:
```{r, eval=FALSE}
set.control.ergm = control.ergm(MCMC.interval = 1e+5,
                                MCMC.samplesize = 7500,
                                MCMC.burnin = 1e+6,
                                MPLE.max.dyad.types = 1e+7,
                                init.method = "zeros",
                                MCMLE.maxit = 400,
                                parallel = np/2, 
                                parallel.type="PSOCK"))
```

## MCMC diagnostics

### Model 1
```{r, message=FALSE, echo=FALSE}
mcmc.diagnostics(est.m.testregionmix.bal[[1]]$fit)
```

### Model 2
```{r, message=FALSE, echo=FALSE}
mcmc.diagnostics(est.m.testregionmix.bal[[2]]$fit)
```

### Model 3
```{r, message=FALSE, echo=FALSE}
mcmc.diagnostics(est.m.testregionmix.bal[[3]]$fit)
```

### Model 4
```{r, message=FALSE, echo=FALSE}
mcmc.diagnostics(est.m.testregionmix.bal[[4]]$fit)
```

### Model 5
```{r, message=FALSE, echo=FALSE}
mcmc.diagnostics(est.m.testregionmix.bal[[5]]$fit)
```

## Summary of model fit

### Model 1
```{r}
summary(est.m.testregionmix.bal[[1]])
```

### Model 2
```{r}
summary(est.m.testregionmix.bal[[2]])
```

### Model 3
```{r}
summary(est.m.testregionmix.bal[[3]])
```

### Model 4
```{r}
summary(est.m.testregionmix.bal[[4]])
```

### Model 5
```{r}
summary(est.m.testregionmix.bal[[5]])
```


## Network diagnostics

### Model 1
```{r}
(dx_main1 <- netdx(est.m.testregionmix.bal[[1]], nsims = 10, nsteps = 1000, ncores = 4, nwstats.formula = est.m.testregionmix.bal[[1]]$formation, set.control.stergm = control.simulate.network(MCMC.burnin.min = 1e+5, MCMC.burnin.max = 1e+5)))
plot(dx_main1, type="formation")
plot(dx_main1, type="duration")
plot(dx_main1, type="dissolution")
```

### Model 2
```{r}
(dx_main2 <- netdx(est.m.testregionmix.bal[[2]], nsims = 10, nsteps = 1000, ncores = 4, nwstats.formula = est.m.testregionmix.bal[[1]]$formation, set.control.stergm = control.simulate.network(MCMC.burnin.min = 1e+5, MCMC.burnin.max = 1e+5)))
plot(dx_main2, type="formation")
plot(dx_main2, type="duration")
plot(dx_main2, type="dissolution")
```

### Model 3
```{r}
(dx_main3 <- netdx(est.m.testregionmix.bal[[3]], nsims = 10, nsteps = 1000, ncores = 4, nwstats.formula = est.m.testregionmix.bal[[1]]$formation, set.control.stergm = control.simulate.network(MCMC.burnin.min = 1e+5, MCMC.burnin.max = 1e+5)))
plot(dx_main3, type="formation")
plot(dx_main3, type="duration")
plot(dx_main3, type="dissolution")
```

### Model 4
```{r}
(dx_main4 <- netdx(est.m.testregionmix.bal[[4]], nsims = 10, nsteps = 1000, ncores = 4, nwstats.formula = est.m.testregionmix.bal[[1]]$formation, set.control.stergm = control.simulate.network(MCMC.burnin.min = 1e+5, MCMC.burnin.max = 1e+5)))
                           
plot(dx_main4, type="formation")
plot(dx_main4, type="duration")
plot(dx_main4, type="dissolution")
```

### Model 5
```{r}
(dx_main5 <- netdx(est.m.testregionmix.bal[[5]], nsims = 10, nsteps = 1000, ncores = 4, set.control.stergm = control.simulate.network(MCMC.burnin.min = 1e+5, MCMC.burnin.max = 1e+5)))
plot(dx_main5, type="formation")
plot(dx_main5, type="duration")
plot(dx_main5, type="dissolution")
```
