---
output:
  html_document:
    toc: true
    toc_float: true
---
# Main network model diagnostics - unbalanced statistics
This file shows diagnostics for main network models fit using unbalanced racial/ethnic mixing matrices and degree terms as reported by egos. Here we try to identify which term added to a model with `nodefactor(race)` and `nodematch(race)` creates issues with MCMC diagnostics for race matching. This is motivated by observing, in the "dx_main_unbalanced_buildup.Rmd" file that the MCMC diagnostics for race matching are off when added to a model with `nodefactor(race)`, `nodefactor(region)`, and `nodefactor(deg.pers)`. We will see if we can get it to fit in the absence of these other `nodefactor` terms and then see how the fit changes with the addition of each alone.


## Load packages and model fits
```{r, warning=FALSE}
rm(list = ls())
suppressMessages(library("EpiModelHIV"))
library("latticeExtra")
library("knitr")
library("kableExtra")

load(file = "/homes/dpwhite/R/GitHub Repos/WHAMP/Model fits and simulations/Fit tests and debugging/est/fit.m.testracemix.unbal.rda")

```

## Model terms and control settings

```{r, echo=FALSE}
targets <- cbind.data.frame("terms" = c(est.m.testracemix.unbal[[4]]$target.stats.names, "degrange", "nodematch.role.class.I", "nodematch.role.class.R"), "stats.1" = round(c(est.m.testracemix.unbal[[1]]$target.stats[1], rep(NA,2), est.m.testracemix.unbal[[1]]$target.stats[2:3], rep(NA,2), est.m.testracemix.unbal[[1]]$target.stats[4:7], -Inf, -Inf),1), "stats.2" = round(c(est.m.testracemix.unbal[[2]]$target.stats[1:5], rep(NA,2), est.m.testracemix.unbal[[2]]$target.stats[6:9], -Inf, -Inf),1), "stats.3" = round(c(est.m.testracemix.unbal[[3]]$target.stats[1], rep(NA,2), est.m.testracemix.unbal[[3]]$target.stats[2:9], -Inf, -Inf),1), "stats.4" = round(c(est.m.testracemix.unbal[[4]]$target.stats, -Inf, -Inf),1))

kable(targets, col.names = c("Terms", "Model 1", "Model 2", "Model 3", "Model 4"), caption="Model terms and target statistics") %>% kable_styling(full_width=F, position="center")
```

The control settings for these models are:
```{r, eval=FALSE}
set.control.ergm = control.ergm(MCMC.interval = 1e+5,
                                MCMC.samplesize = 7500,
                                MCMC.burnin = 1e+6,
                                MPLE.max.dyad.types = 1e+7,
                                init.method = "zeros",
                                MCMLE.maxit = 400,
                                parallel = np/2, 
                                parallel.type="PSOCK"))
```

## MCMC diagnostics

### Model 1
```{r, message=FALSE, echo=FALSE}
mcmc.diagnostics(est.m.testracemix.unbal[[1]]$fit)
```

### Model 2
```{r, message=FALSE, echo=FALSE}
mcmc.diagnostics(est.m.testracemix.unbal[[2]]$fit)
```

### Model 3
```{r, message=FALSE, echo=FALSE}
mcmc.diagnostics(est.m.testracemix.unbal[[3]]$fit)
```

### Model 4
```{r, message=FALSE, echo=FALSE}
mcmc.diagnostics(est.m.testracemix.unbal[[4]]$fit)
```

## Summary of model fit

### Model 1
```{r}
summary(est.m.testracemix.unbal[[1]])
```

### Model 2
```{r}
summary(est.m.testracemix.unbal[[2]])
```

### Model 3
```{r}
summary(est.m.testracemix.unbal[[3]])
```

### Model 4
```{r}
summary(est.m.testracemix.unbal[[4]])
```

## Network diagnostics

### Model 1
```{r}
(dx_main1 <- netdx(est.m.testracemix.unbal[[1]], nsims = 10, nsteps = 1000, ncores = 4, nwstats.formula = est.m.testracemix.unbal[[4]]$formation))
plot(dx_main1, type="formation")
plot(dx_main1, type="duration")
plot(dx_main1, type="dissolution")
```

### Model 2
```{r}
(dx_main2 <- netdx(est.m.testracemix.unbal[[2]], nsims = 10, nsteps = 1000, ncores = 4, nwstats.formula = est.m.testracemix.unbal[[4]]$formation))
plot(dx_main2, type="formation")
plot(dx_main2, type="duration")
plot(dx_main2, type="dissolution")
```

### Model 3
```{r}
(dx_main3 <- netdx(est.m.testracemix.unbal[[3]], nsims = 10, nsteps = 1000, ncores = 4, nwstats.formula = est.m.testracemix.unbal[[4]]$formation))
plot(dx_main3, type="formation")
plot(dx_main3, type="duration")
plot(dx_main3, type="dissolution")
```

### Model 4
```{r}
(dx_main4 <- netdx(est.m.testracemix.unbal[[4]], nsims = 10, nsteps = 1000, ncores = 4, nwstats.formula = est.m.testracemix.unbal[[4]]$formation))
plot(dx_main4, type="formation")
plot(dx_main4, type="duration")
plot(dx_main4, type="dissolution")
```
