---
output:
  html_document:
    toc: true
    toc_float: true
---
# Main network model diagnostics - unbalanced statistics
This file shows diagnostics for main network models fit using unbalanced racial/ethnic mixing matrices and degree terms as reported by egos. In this file, we fit a series of nested models by adding one term at a time to examine changes to model estimates, MCMC diagnostics, and network diagnostics.

## Load packages and model fits
```{r, warning=FALSE}
rm(list = ls())
suppressMessages(library("EpiModelHIV"))
library("latticeExtra")
library("knitr")
library("kableExtra")

load(file = "/homes/dpwhite/R/GitHub Repos/WHAMP/Model fits and simulations/Fit tests and debugging/est/fit.m.buildup.unbal.rda")

```

## Model terms and control settings

```{r, echo=FALSE}
targets <- cbind.data.frame("terms" = c(est.m.buildup.unbal[[7]]$target.stats.names, "degrange", "nodematch.role.class.I", "nodematch.role.class.R", "mix.region.EW.KC", "mix.region.EW.OW", "mix.region.KC.OW", "nodematch.region"), "stats.1" = round(c(est.m.buildup.unbal[[1]]$target.stats[1], rep(NA,10), est.m.buildup.unbal[[1]]$target.stats[2], -Inf, -Inf, rep(NA,4)),1), "stats.2" = round(c(est.m.buildup.unbal[[2]]$target.stats[1], rep(NA,2), est.m.buildup.unbal[[2]]$target.stats[2:3], rep(NA,6), est.m.buildup.unbal[[2]]$target.stats[4], -Inf, -Inf, rep(NA,4)),1), "stats.3" = round(c(est.m.buildup.unbal[[3]]$target.stats[1], rep(NA,2), est.m.buildup.unbal[[3]]$target.stats[2:3], rep(NA,2), est.m.buildup.unbal[[3]]$target.stats[4:6], rep(NA,1), est.m.buildup.unbal[[3]]$target.stats[7], -Inf, -Inf, rep(NA,4)),1), "stats.4" = round(c(est.m.buildup.unbal[[4]]$target.stats[1:5], rep(NA,2), est.m.buildup.unbal[[4]]$target.stats[6:8], rep(NA,1), est.m.buildup.unbal[[4]]$target.stats[9], -Inf, -Inf, rep(NA,4)),1), "stats.5" = round(c(est.m.buildup.unbal[[5]]$target.stats[1:10], rep(NA,1), est.m.buildup.unbal[[5]]$target.stats[11], -Inf, -Inf, rep(NA,4)),1), "stats.6" = round(c(est.m.buildup.unbal[[6]]$target.stats, -Inf, -Inf, rep(NA,4)),1), "stats.7" = round(c(est.m.buildup.unbal[[7]]$target.stats, -Inf, -Inf, -Inf, -Inf, -Inf, rep(NA,1)),1), "stats.8" = round(c(est.m.buildup.unbal[[8]]$target.stats[c(1:11,13)], -Inf, -Inf, rep(NA,3), est.m.buildup.unbal[[8]]$target.stats[c(12)]),1))

kable(targets, col.names = c("Terms", "Model 1", "Model 2", "Model 3", "Model 4", "Model 5", "Model 6", "Model 7", "Model 8"), caption="Model terms and target statistics") %>% kable_styling(full_width=F, position="center")
```

The control settings for these models are:
```{r, eval=FALSE}
set.control.ergm = control.ergm(MCMC.interval = 1e+5,
                                MCMC.samplesize = 7500,
                                MCMC.burnin = 1e+6,
                                MPLE.max.dyad.types = 1e+7,
                                init.method = "zeros",
                                MCMLE.maxit = 400,
                                parallel = np/2, 
                                parallel.type="PSOCK"))
```

## MCMC diagnostics

### Model 1
```{r, message=FALSE, echo=FALSE}
mcmc.diagnostics(est.m.buildup.unbal[[1]]$fit)
```

### Model 2
```{r, message=FALSE, echo=FALSE}
mcmc.diagnostics(est.m.buildup.unbal[[2]]$fit)
```

### Model 3
```{r, message=FALSE, echo=FALSE}
mcmc.diagnostics(est.m.buildup.unbal[[3]]$fit)
```

### Model 4
```{r, message=FALSE, echo=FALSE}
mcmc.diagnostics(est.m.buildup.unbal[[4]]$fit)
```

### Model 5
```{r, message=FALSE, echo=FALSE}
mcmc.diagnostics(est.m.buildup.unbal[[5]]$fit)
```

### Model 6
```{r, message=FALSE, echo=FALSE}
mcmc.diagnostics(est.m.buildup.unbal[[6]]$fit)
```

### Model 7
```{r, message=FALSE, echo=FALSE}
mcmc.diagnostics(est.m.buildup.unbal[[7]]$fit)
```

### Model 8
```{r, message=FALSE, echo=FALSE}
mcmc.diagnostics(est.m.buildup.unbal[[8]]$fit)
```


## Summary of model fit

### Model 1
```{r}
summary(est.m.buildup.unbal[[1]])
```

### Model 2
```{r}
summary(est.m.buildup.unbal[[2]])
```

### Model 3
```{r}
summary(est.m.buildup.unbal[[3]])
```

### Model 4
```{r}
summary(est.m.buildup.unbal[[4]])
```

### Model 5
```{r}
summary(est.m.buildup.unbal[[5]])
```

### Model 6
```{r}
summary(est.m.buildup.unbal[[6]])
```

### Model 7
```{r}
summary(est.m.buildup.unbal[[7]])
```

### Model 8
```{r}
summary(est.m.buildup.unbal[[8]])
```


## Network diagnostics

### Model 1
```{r}
(dx_main1 <- netdx(est.m.buildup.unbal[[1]], nsims = 10, nsteps = 1000, ncores = 4, nwstats.formula = est.m.buildup.unbal[[8]]$formation))
plot(dx_main1, type="formation")
plot(dx_main1, type="duration")
plot(dx_main1, type="dissolution")
```

### Model 2
```{r}
(dx_main2 <- netdx(est.m.buildup.unbal[[2]], nsims = 10, nsteps = 1000, ncores = 4, nwstats.formula = est.m.buildup.unbal[[8]]$formation))
plot(dx_main2, type="formation")
plot(dx_main2, type="duration")
plot(dx_main2, type="dissolution")
```

### Model 3
```{r}
(dx_main3 <- netdx(est.m.buildup.unbal[[3]], nsims = 10, nsteps = 1000, ncores = 4, nwstats.formula = est.m.buildup.unbal[[8]]$formation))
plot(dx_main3, type="formation")
plot(dx_main3, type="duration")
plot(dx_main3, type="dissolution")
```

### Model 4
```{r}
(dx_main4 <- netdx(est.m.buildup.unbal[[4]], nsims = 10, nsteps = 1000, ncores = 4, nwstats.formula = est.m.buildup.unbal[[8]]$formation))
plot(dx_main4, type="formation")
plot(dx_main4, type="duration")
plot(dx_main4, type="dissolution")
```

### Model 5
```{r}
(dx_main5 <- netdx(est.m.buildup.unbal[[5]], nsims = 10, nsteps = 1000, ncores = 4, nwstats.formula = est.m.buildup.unbal[[8]]$formation))
plot(dx_main5, type="formation")
plot(dx_main5, type="duration")
plot(dx_main5, type="dissolution")
```

### Model 6
```{r}
(dx_main6 <- netdx(est.m.buildup.unbal[[6]], nsims = 10, nsteps = 1000, ncores = 4, nwstats.formula = est.m.buildup.unbal[[8]]$formation))
plot(dx_main6, type="formation")
plot(dx_main6, type="duration")
plot(dx_main6, type="dissolution")
```

### Model 7
```{r}
(dx_main7 <- netdx(est.m.buildup.unbal[[7]], nsims = 10, nsteps = 1000, ncores = 4))
plot(dx_main7, type="formation")
plot(dx_main7, type="duration")
plot(dx_main7, type="dissolution")
```

### Model 8
```{r}
(dx_main8 <- netdx(est.m.buildup.unbal[[7]], nsims = 10, nsteps = 1000, ncores = 4))
plot(dx_main8, type="formation")
plot(dx_main8, type="duration")
plot(dx_main8, type="dissolution")
```
