---
output:
  html_document:
    toc: true
    toc_float: true
---
# Persistent network model diagnostics - debugging fit issues
This file shows diagnostics for persistent network models fit using balanced racial/ethnic mixing matrices and degree terms adjusted to correspond to the balanced race/ethnicity mixing matrices. In this file, we test whether fit issues are due to constriants, edapprox, or MCMC control settings. 

## Load packages and model fits
```{r, warning=FALSE}
rm(list = ls())
suppressMessages(library("EpiModel"))
suppressMessages(library("EpiModelHIV"))
library("latticeExtra")
library("knitr")
library("kableExtra")
library("here")

load(file = here("Model fits and simulations/Fit tests and debugging/est/fit.p.edgesonly.rda"))

```

## 1. Edges only
This model has edges only and no constraints based on role class or to cap degree at 2. It also does not incorporate mortality into the disssolution coefficient. It uses the target statistic for edges and duration from our data, and it sets `edapprox=TRUE`. With this model, I got the error message about degeneracy with `init.method="zeros"` ("Number of edges in a simulated network exceeds that in the observed by a factor of more than 20"), so I set `init.method` to the NULL argument.
```{r, eval=FALSE}
nw <- network.initialize(10000,directed=FALSE)
time.step <- 7
fit.p1 <- netest(nw, 
                formation = ~edges, 
                target.stats = 2017.5,
                coef.diss = dissolution_coefs(dissolution = ~offset(edges), duration = 221 / time.step),
                edapprox = TRUE,
                set.control.ergm = control.ergm(MCMC.interval = 1e+5,
                                                 MCMC.samplesize = 7500,
                                                 MCMC.burnin = 1e+6,
                                                 MPLE.max.dyad.types = 1e+7,
                                                 MCMLE.maxit = 400,
                                                 parallel = np/2, 
                                                 parallel.type="PSOCK"))

```

### MCMC diagnostics
```{r}
mcmc.diagnostics(fit.p1$fit)
```

### Summary of model fit
```{r}
summary(fit.p1)
```

### Network diagnostics - MCMC burnin set to 1e+6
```{r}
(dx_pers1 <- netdx(fit.p1, nsims = 10, nsteps = 1000, ncores = 4, set.control.stergm = control.simulate.network(MCMC.burnin.min = 1e+6, MCMC.burnin.max = 1e+6)))
plot(dx_pers1, type="formation")
plot(dx_pers1, type="duration")
plot(dx_pers1, type="dissolution")
```

### Network diagnostics - MCMC burnin set to 1e+7
```{r}
(dx_pers1b <- netdx(fit.p1, nsims = 10, nsteps = 1000, ncores = 4, set.control.stergm = control.simulate.network(MCMC.burnin.min = 1e+7, MCMC.burnin.max = 1e+7)))
plot(dx_pers1b, type="formation")
plot(dx_pers1b, type="duration")
plot(dx_pers1b, type="dissolution")
```

## 2. Edges only but edapprox = FALSE
This model is the same as above but with edapprox = FALSE
```{r, eval=FALSE}
nw <- network.initialize(10000,directed=FALSE)
time.step <- 7
fit.p2 <- netest(nw, 
                formation = ~edges, 
                target.stats = 2017.5,
                coef.diss = dissolution_coefs(dissolution = ~offset(edges), duration = 221 / time.step),
                edapprox = FALSE,
                set.control.ergm = control.ergm(MCMC.interval = 1e+5,
                                                 MCMC.samplesize = 7500,
                                                 MCMC.burnin = 1e+6,
                                                 MPLE.max.dyad.types = 1e+7,
                                                 MCMLE.maxit = 400,
                                                 parallel = np/2, 
                                                 parallel.type="PSOCK"))

```

### MCMC diagnostics
```{r}
mcmc.diagnostics(fit.p2$fit)
```

### Summary of model fit
```{r}
summary(fit.p2)
```

### Network diagnostics - MCMC burnin set to 1e+7
```{r}
(dx_pers2b <- netdx(fit.p2, nsims = 10, nsteps = 1000, ncores = 4, set.control.stergm = control.simulate.network(MCMC.burnin.min = 1e+7, MCMC.burnin.max = 1e+7)))
plot(dx_pers2b, type="formation")
plot(dx_pers2b, type="duration")
plot(dx_pers2b, type="dissolution")
```

## 3. Edges only but duration = 500
This model is the same as above but with edapprox = FALSE
```{r, eval=FALSE}
nw <- network.initialize(10000,directed=FALSE)
time.step <- 7
fit.p3 <- netest(nw, 
                formation = ~edges, 
                target.stats = 2017.5,
                coef.diss = dissolution_coefs(dissolution = ~offset(edges), duration = 500 / time.step),
                edapprox = FALSE,
                set.control.ergm = control.ergm(MCMC.interval = 1e+5,
                                                 MCMC.samplesize = 7500,
                                                 MCMC.burnin = 1e+6,
                                                 MPLE.max.dyad.types = 1e+7,
                                                 MCMLE.maxit = 400,
                                                 parallel = np/2, 
                                                 parallel.type="PSOCK"))

```

### MCMC diagnostics
```{r}
mcmc.diagnostics(fit.p3$fit)
```

### Summary of model fit
```{r}
summary(fit.p3)
```

### Network diagnostics - MCMC burnin set to 1e+7
```{r}
(dx_pers3b <- netdx(fit.p3, nsims = 10, nsteps = 1000, ncores = 4, set.control.stergm = control.simulate.network(MCMC.burnin.min = 1e+7, MCMC.burnin.max = 1e+7)))
plot(dx_pers3b, type="formation")
plot(dx_pers3b, type="duration")
plot(dx_pers3b, type="dissolution")
```