---
output:
  html_document:
    toc: true
    toc_float: true
---
# Network model diagnostics - balanced statistics

## Load packages and model fits
```{r, warning=FALSE}
rm(list = ls())
suppressMessages(library("EpiModelHIV"))
library("latticeExtra")
library("knitr")
library("kableExtra")
library("here")

load(file = here("Model fits and simulations/Fit tests and debugging/est/est.p.bal.bdmaxout.rda"))
load(file = here("Model fits and simulations/Fit tests and debugging/est/est.p.bal.bdmaxout_longdur.rda"))

```

## Persistent model
This model uses balanced statistics for racial/ethnic mixing and race/ethnicity-specific degree, imposes the constraint on degree using the argument: `constraints = ~bd(maxout = 2),` and assumes 80% regional homophily.

### Model terms and control settings
Terms and constraints
```{r, echo = FALSE}
targets <- cbind.data.frame("terms" = c(fit.p$target.stats.names, "nodematch.role.class.I", "nodematch.role.class.R"), "stats" = round(c(fit.p$target.stats, rep(-Inf, 2)),1))

kable(targets, col.names = c("Terms and constraints", "Full model"), caption="Model terms, constraints, and target statistics") %>% kable_styling(full_width=F, position="center")

```

Control settings
```{r, eval=FALSE}
set.control.ergm = control.ergm(MCMC.interval = 1e+5,
                    MCMC.samplesize = 7500,
                    MCMC.burnin = 1e+6,
                    MPLE.max.dyad.types = 1e+7,
                    init.method = "zeros",
                    MCMLE.maxit = 400,
                    parallel = np/2,
                    parallel.type="PSOCK"))

```

### MCMC diagnostics
```{r, message=FALSE, echo=FALSE}
mcmc.diagnostics(fit.p$fit)
```

### Summary of model fit
```{r, message=FALSE, echo=FALSE}
summary(fit.p)
```

### Network diagnostics
```{r}
(dx_pers <- netdx(fit.p, nsims = 10, nsteps = 1000, ncores = 4, set.control.stergm = control.simulate.network(MCMC.burnin.min = 1e+5, MCMC.burnin.max = 1e+5), set.control.ergm = control.simulate.ergm(MCMC.interval = 1e+5, MCMC.burnin = 1e+6)))
plot(dx_pers, type="formation")
plot(dx_pers, type="duration")
plot(dx_pers, type="dissolution")
```

## Persistent model, longer duration
This model uses balanced statistics for racial/ethnic mixing and race/ethnicity-specific degree, imposes the constraint on degree using the argument: `constraints = ~bd(maxout = 2),` and assumes 80% regional homophily. In this model we specify a duration of 100 time steps to test whether fit issues are due to the duration being too short for edapprox.

### Model terms and control settings
Terms and constraints
```{r, echo = FALSE}
targets <- cbind.data.frame("terms" = c(fit.p2$target.stats.names, "nodematch.role.class.I", "nodematch.role.class.R"), "stats" = round(c(fit.p2$target.stats, rep(-Inf, 2)),1))

kable(targets, col.names = c("Terms and constraints", "Full model"), caption="Model terms, constraints, and target statistics") %>% kable_styling(full_width=F, position="center")

```
Control settings
```{r, eval=FALSE}
set.control.ergm = control.ergm(MCMC.interval = 1e+5,
                    MCMC.samplesize = 7500,
                    MCMC.burnin = 1e+6,
                    MPLE.max.dyad.types = 1e+7,
                    init.method = "zeros",
                    MCMLE.maxit = 400,
                    parallel = np/2,
                    parallel.type="PSOCK"))

```

### MCMC diagnostics
```{r, message=FALSE, echo=FALSE}
mcmc.diagnostics(fit.p2$fit)
```

### Summary of model fit
```{r, message=FALSE, echo=FALSE}
summary(fit.p2)
```

### Network diagnostics
```{r}
(dx_pers2 <- netdx(fit.p2, nsims = 10, nsteps = 1000, ncores = 4, set.control.stergm = control.simulate.network(MCMC.burnin.min = 1e+5, MCMC.burnin.max = 1e+5), set.control.ergm = control.simulate.ergm(MCMC.interval = 1e+5, MCMC.burnin = 1e+6)))
plot(dx_pers2, type="formation")
plot(dx_pers2, type="duration")
plot(dx_pers2, type="dissolution")
```

