---
output:
  html_document:
    toc: true
    toc_float: true
---
# Network model estimation and diagnostics - balanced
This file uses the balanced mixing matrices and degree distributions/rate of instantaneous partnerships adjusted to correspond to the balanced mixing matrices.

## Load packages and define options
```{r, warning=FALSE}
rm(list = ls())
suppressMessages(library("EpiModelHIV"))
```

## Calculate target statistics

```{r, message = FALSE}

# Time unit for simulation, relative to 1 day
time.unit <- 7

#Network size
num <- 10000

# Population size by race and region
    ##--ORIGINAL CODE - DELETE WHEN FINISH DE-BUGGING
    num.B <- 5000
    num.W <- 5000
  ## Vector with the proportion of Hispanic, black, and other race/ethnicity men in King County, other western WA, and eastern WA
  prop.race.region <- sumto1(c(0.0549, 0.0421, 0.4739, 0.0309, 0.0166, 0.2807, 0.0222, 0.0021, 0.0767))
  race.region <- apportion_lr(num, c("H.KC", "B.KC", "O.KC", "H.OW", "B.OW", "O.OW", "H.EW", "B.EW", "O.EW"),
                             prop.race.region)
  
  num.H.KC <- sum(race.region %in% "H.KC")
  num.B.KC <- sum(race.region %in% "B.KC")
  num.O.KC <- sum(race.region %in% "O.KC")
  num.H.OW <- sum(race.region %in% "H.OW")
  num.B.OW <- sum(race.region %in% "B.OW")
  num.O.OW <- sum(race.region %in% "O.OW")
  num.H.EW <- sum(race.region %in% "H.EW")
  num.B.EW <- sum(race.region %in% "B.EW")
  num.O.EW <- sum(race.region %in% "O.EW")
  
# Age structure (proportion in each age group 18-24, 25-29... 55-59)
agestr <- sumto1(c(0.1594, 0.1319, 0.1292, 0.1173, 0.1183, 0.1148, 0.1071, 0.122))
    
# mean/pers degree distributions matrices.
deg.mp <- matrix(sumto1(c(0.4108, 0.0735, 0.0672, 
                          0.3458, 0.0494, 0.0532)), byrow = TRUE, nrow = 2)
deg.mp.H <- matrix(sumto1(c(0.2366, 0.1575, 0.0391,
                            0.3413, 0.1759, 0.0496)), byrow = TRUE, nrow = 2)
deg.mp.B <- matrix(sumto1(c(0.4923, 0.0814, 0.0839, 
                            0.2307, 0.0395, 0.0723)), byrow = TRUE, nrow = 2)
deg.mp.O <- matrix(sumto1(c(0.4275, 0.062, 0.0696, 
                            0.3548, 0.0337, 0.0523)), byrow = TRUE, nrow = 2)
deg.mp.KC <- matrix(sumto1(c(0.3609, 0.0824, 0.0735, 
                             0.3792, 0.0464, 0.0577)), byrow = TRUE, nrow = 2)
deg.mp.OW <- matrix(sumto1(c(0.4885, 0.0688, 0.0517, 
                             0.289, 0.0502, 0.0518)), byrow = TRUE, nrow = 2)
deg.mp.EW <- matrix(sumto1(c(0.4186, 0.0621, 0.0806, 
                             0.364, 0.0401, 0.0346)), byrow = TRUE, nrow = 2)

# Instantaneous partner rates (Mean rate (degree) of inst partnerships per day by momentary main/pers degree)
  # (order: 0 main 0 pers, 0 main 1 pers, 0 main 2+ pers, 1 main 0 pers, 1 main 1 pers, 1 main 2+ pers)
mdeg.inst <- matrix(c(0.015734, 0.005987, 0.021057, 
                      0.007052, 0.009709, 0.032598), byrow = TRUE, nrow = 2) 

# Quintile distribution of overall instantaneous AI rates
qnts.18to49 <- c(0, 0.000525, 0.005024, 0.054838)
qnts.50to59 <- c(0, 0, 0.001551, 0.021283)

# Mean rate of instantaneous partnerships by race (black, Hispanic, other)
inst.bho <- c(0.0202, 0.012978, 0.012418)

# Proportion in same-race partnerships (main, pers, inst)
prop.hom.mpi.H <- c(0.4229, 0.1631, 0.1787)
prop.hom.mpi.B <- c(0.2939, 0.0701, 0.0853)
prop.hom.mpi.O <- c(0.8911, 0.7847, 0.7666)

# Mean age diffs (main, pers, inst)
sqrt.adiff.mpi <- c(0.539, 0.7619, 0.7741)

# Region mixing (main, pers, inst)
prop.hom.region.mpi <- c(1.0, 0.8, 0.8)

# Mean durations
durs.main <- 1020
durs.pers <- 192

# Age-sex-specific mortality rates
ages <- 18:59

asmr.B <- c(rep(0, 17),
            1-(1-c(rep(0.00159, 7),
                   rep(0.00225, 10),
                   rep(0.00348, 25)))^(1/(365/time.unit)), 1) #-- To make old code work with new age str, I added 20 to the last deaths vector

asmr.W <- c(rep(0, 17),
            1-(1-c(rep(0.00103, 7),
                   rep(0.00133, 10),
                   rep(0.00214, 25)))^(1/(365/time.unit)), 1) #-- To make old code work with new age str, I added 20 to the last deaths vector

asmr.H..wa <- c(rep(0, 17),
            1-(1-c(rep(0.00089, 2),
                   rep(0.00107, 5),
                   rep(0.00112, 5),
                   rep(0.00123, 5),
                   rep(0.00126, 5),
                   rep(0.00186, 5),
                   rep(0.00207, 5),
                   rep(0.00343, 5),
                   rep(0.00495, 5)))^(1/(365/time.unit)), 1)

asmr.B..wa <- c(rep(0, 17),
            1-(1-c(rep(0.00168, 2),
                   rep(0.00117, 5),
                   rep(0.00161, 5),
                   rep(0.00169, 5),
                   rep(0.00267, 5),
                   rep(0.00224, 5),
                   rep(0.00428, 5),
                   rep(0.00619, 5),
                   rep(0.01311, 5)))^(1/(365/time.unit)), 1)

asmr.O..wa <- c(rep(0, 17),
            1-(1-c(rep(0.00068, 2),
                   rep(0.00101, 5),
                   rep(0.00119, 5),
                   rep(0.00138, 5),
                   rep(0.00161, 5),
                   rep(0.00198, 5),
                   rep(0.00306, 5),
                   rep(0.00517, 5),
                   rep(0.00781, 5)))^(1/(365/time.unit)), 1)

# I, R, V role frequencies
role.prob <- c(0.15, 0.205, 0.645)


# Create meanstats
st <- calc_nwstats_msm_whamp(
  method = 1,
  time.unit = time.unit,
  num.B = num.B,
  num.W = num.W,
  num.H.KC = num.H.KC,
  num.B.KC = num.B.KC,
  num.O.KC = num.O.KC,
  num.H.OW = num.H.OW,
  num.B.OW = num.B.OW,
  num.O.OW = num.O.OW,
  num.H.EW = num.H.EW,
  num.B.EW = num.B.EW,
  num.O.EW = num.O.EW,
  agestr = agestr,
  deg.mp = deg.mp,
  deg.mp.H = deg.mp.H,
  deg.mp.B = deg.mp.B,
  deg.mp.O = deg.mp.O,
  deg.mp.KC = deg.mp.KC,
  deg.mp.OW = deg.mp.OW,
  deg.mp.EW = deg.mp.EW,
  mdeg.inst = mdeg.inst,
  qnts.18to49 = qnts.18to49,
  qnts.50to59 = qnts.50to59,
  inst.bho = inst.bho,
  prop.hom.mpi.H = prop.hom.mpi.H,
  prop.hom.mpi.B = prop.hom.mpi.B,
  prop.hom.mpi.O = prop.hom.mpi.O,
  sqrt.adiff.mpi = sqrt.adiff.mpi,
  prop.hom.region.mpi,
  diss.main = ~offset(edges),
  diss.pers = ~offset(edges),
  durs.main = durs.main,
  durs.pers = durs.pers,
  ages = ages,
  asmr.B <- asmr.B,
  asmr.W <- asmr.W,
  asmr.H..wa = asmr.H..wa,
  asmr.B..wa = asmr.B..wa,
  asmr.O..wa = asmr.O..wa,
  role.prob = role.prob)

save(st, file = "/homes/dpwhite/R/GitHub Repos/WHAMP/WHAMP scenarios/est/nwstats.whamp.balanced.rda")


```

## Fit models
```{r, message=FALSE}

#Load data
load("/homes/dpwhite/R/GitHub Repos/WHAMP/WHAMP scenarios/est/nwstats.whamp.balanced.rda")
  
# Fit models
  
  ## 1. Main Model -----------------------------------------------------------
   
  # Initialize network
  nw.main <- base_nw_msm_whamp(st)
  
  # Assign degree
  nw.main <- assign_degree_whamp(nw.main, deg.type = "pers", nwstats = st)
  
  # Formulas
  formation.m <- ~edges +
                  nodefactor("deg.pers") +
                  nodefactor("race..wa", base=3) + 
                  nodefactor("region", base=2) +
                  nodematch("race..wa", diff=TRUE) +
                  absdiff("sqrt.age") +
                  offset(nodematch("role.class", diff = TRUE, keep = 1:2)) +
                  offset(nodemix("region", base = c(1,3,6)))

    # Start clock to calculate runtime
    startclock_main <- proc.time()
    
    # Fit model
    fit.m <- netest(nw.main,
                    formation = formation.m,
                    target.stats = st$stats.m,
                    coef.form = c(-Inf, -Inf, -Inf, -Inf, -Inf),
                    coef.diss = st$coef.diss.m,
                    constraints = ~bd(maxout = 1),
                    set.control.ergm = control.ergm(MPLE.max.dyad.types = 1e10,
                                                    init.method = "zeros",
                                                    MCMLE.maxit = 250))

    # Fit time
    runtime_min_fit_main <- (proc.time()-startclock_main)['elapsed']/60
    
        
  ## 2. Casual Model ---------------------------------------------------------

    # Initialize network
    nw.pers <- nw.main

    # Assign degree
    nw.pers <- assign_degree_whamp(nw.pers, deg.type = "main", nwstats = st)
    
    # Formulas
    formation.p <- ~edges +
                    nodefactor("deg.main") +
                    concurrent +
                    nodematch("race..wa", diff=TRUE) +
                    nodematch("region", diff=FALSE) +
                    absdiff("sqrt.age") +
                    offset(nodematch("role.class", diff = TRUE, keep = 1:2))

        
    # Start clock to calculate runtime
    startclock_pers <- proc.time()
    
    # Fit model
    fit.p <- netest(nw.pers,
                    formation = formation.p,
                    target.stats = st$stats.p,
                    coef.form = c(-Inf, -Inf),
                    coef.diss = st$coef.diss.p,
                    constraints = ~bd(maxout = 2), 
                    edapprox = TRUE,
                    set.control.ergm = control.ergm(MPLE.max.dyad.types = 1e9,
                                                init.method = "zeros",
                                                MCMLE.maxit = 250))

    # Fit time
    runtime_min_fit_pers <- (proc.time()-startclock_pers)['elapsed']/60
    

  ## Fit inst model ----------------------------------------------------------

    # Initialize network
    nw.inst <- nw.main

    # Assign degree
    nw.inst <- set.vertex.attribute(nw.inst, "deg.main", nw.pers %v% "deg.main")
    nw.inst <- set.vertex.attribute(nw.inst, "deg.pers", nw.main %v% "deg.pers")
    table(nw.inst %v% "deg.main", nw.inst %v% "deg.pers")
    
    # Formulas
   formation.i <- ~edges +
                    nodefactor(c("deg.main", "deg.pers")) +
                    nodefactor("riskg") +
                    nodematch("race..wa", diff=TRUE) +
                    nodematch("region", diff=FALSE) +
                    absdiff("sqrt.age") +
                    offset(nodematch("role.class", diff = TRUE, keep = 1:2)) 
    
    # Start clock to calculate runtime
    startclock_inst <- proc.time()
    
    # Fit model
    fit.i <- netest(nw.inst,
                    formation = formation.i,
                    target.stats = st$stats.i,
                    coef.form = c(-Inf, -Inf),
                    coef.diss = dissolution_coefs(~offset(edges), 1),
                    set.control.ergm = control.ergm(MPLE.max.dyad.types = 1e9,
                                                    MCMLE.maxit = 250))
    
     # Fit time
    runtime_min_fit_inst <- (proc.time()-startclock_inst)['elapsed']/60
    
    est <- list(fit.m, fit.p, fit.i)

    save(est, file = "/homes/dpwhite/R/GitHub Repos/WHAMP/WHAMP scenarios/est/fit.whamp.balanced.rda")

```

## Fit times 
Main network: `r round(runtime_min_fit_main, 1)` minutes
Persistent: `r round(runtime_min_fit_pers, 1)` minutes
Instantaneous: `r round(runtime_min_fit_inst, 1)` minutes

## Suffificient statistics

### Main
```{r}
fit.m
```

### Persistent
```{r}
fit.p
```

### Instantaneous
```{r}
fit.i
```

## Summary of model fit

### Main
```{r}
summary(fit.m)
```

### Persistent
```{r}
summary(fit.p)
```

### Instantaneous
```{r}
summary(fit.i)
```

## MCMC diagnostics

### Main
```{r}
(dx_main <- netdx(est[[1]], nsims = 10, nsteps = 1000, ncores = 4))
plot(dx_main, type="formation")
plot(dx_main, type="duration")
plot(dx_main, type="dissolution")
```

### Persistent
```{r}
(dx_pers <- netdx(est[[2]], nsims = 10, nsteps = 1000, ncores = 4))
plot(dx_pers, type="formation")
plot(dx_pers, type="duration")
plot(dx_pers, type="dissolution")
```

### Instantaneous
```{r}
(dx_inst <- netdx(est[[3]], nsims = 10, nsteps = 1000, ncores = 4))
plot(dx_inst, type="formation")
```


