# Partnership duration {#duration}
```{r, echo=FALSE, include=FALSE}
####################################################################################
# Setup
####################################################################################
#-----------------------------------------------------------------------------------
# Load packages
#-----------------------------------------------------------------------------------

    library("tidyverse")
    library("ggplot2")
    library("survey")
    library("knitr")
    library("xtable")
    library("kableExtra")

#-----------------------------------------------------------------------------------
# Load data
#-----------------------------------------------------------------------------------
    load(file="Data/InternetSurveySample.Rdata")
    load(file="Data/InternetSurvey_reweighted_all.Rdata")
    load(file="Data/InternetSurvey_reweighted_neg.Rdata")

# Set options
    opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE)
    options(knitr.table.format = "html") 
  
#-----------------------------------------------------------------------------------
# Change degree_main variable to factor and add labels have character labels
#-----------------------------------------------------------------------------------
    sample_rake_all$variables$degree_main <- factor(sample_rake_all$variables$degree_main, levels = c(0, 1), labels = c("No main", "Main"))

```

This section summarises the data on the age of extant main and persistent ties and calculates the mean durations given by the observed medians based on an exponential distribution. For these analyses, we use the reweighted WHPP sample, reweighted to the population totals for all MSM since we do not have a separate data source from HIV-positive MSM from which to estimate durations.

## Main partnerships
This histogram below shows the distribution of main partnership ages in the re-weighted sample with an overlaid exponential distribution. The exponential distribution does not appear to be a great fit, but with current methods, assuming an exponential distribution is our best option (see [issue #29](https://github.com/statnet/WHAMP/issues/29)). Note that the data from the unweighted WHPP sample are a much closer fit to the exponential distribution.

```{r, fig.align="center", fig.width=6, fig.height=4}
#plot with exponential overlay
svyhist(~pship_age_main, sample_rake_all, probability = TRUE, breaks = 66, main = "Age of main partnerships - reweighted sample", xlab = "Partnership age in days")
median.main <- svyquantile(~pship_age_main, sample_rake_all, quantile=.5, na.rm=TRUE)
curve(dexp(x, rate = log(2)/median.main[1]), col = 2, lty=2, lwd=2, add=TRUE)

    # Original unweighted sample
    hist(sample$pship_age_main, probability=TRUE, breaks=66, main="Age of main partnerships - unweighted sample")
    curve(dexp(x, rate = log(2)/(median(sample$pship_age_main, na.rm=TRUE))), col = 2, lty = 2, lwd = 2, add = TRUE)
```

Assuming an exponential distribution, the mean duration of main partnerships given by the observed median duration of extant ties is shown in the table below.
```{r}
main.duration <- cbind.data.frame(statistic = c("Observed median age in days", "Calculated mean duration in days"), value = c(median.main, median.main/log(2)))

kable(main.duration, col.names=NULL, digits = 0) %>% kable_styling(full_width=F, position="center") %>% column_spec(1, bold=T, color="black", width="7cm") %>% column_spec(2, width = "2cm") 

```
## Persistent partnerships
The distribution of persistent partnership ages in the re-weighted sample are shown below with an overlaid exponential distribution. As with main partnerships, the exponential distribution does not appear to be a great fit to the re-weighted sample data, and it is also not a great fit to the original sample data.

```{r, fig.align="center", fig.width=6, fig.height=4}
#plot with exponential overlay
svyhist(~pship_age_pers, sample_rake_all, probability = TRUE, breaks = 66, main = "Age of persistent partnerships - reweighted sample", xlab = "Partnership age in days")
median.pers <- svyquantile(~pship_age_pers, sample_rake_all, quantile=.5, na.rm=TRUE)
curve(dexp(x, rate = log(2)/median.pers[1]), col = 2, lty=2, lwd=2, add=TRUE)

    # Original unweighted sample
    hist(sample$pship_age_pers, probability=TRUE, breaks=66, main="Age of persistent partnerships - unweighted sample")
    curve(dexp(x, rate = log(2)/(median(sample$pship_age_pers, na.rm=TRUE))), col = 2, lty = 2, lwd = 2, add = TRUE)
```

Assuming an exponential distribution, the mean duration of persistent partnerships given by the observed median duration of extant ties is shown in the table below.
```{r}
pers.duration <- cbind.data.frame(statistic = c("Observed median age in days", "Calculated mean duration in days"), value = c(median.pers, median.pers/log(2)))

kable(pers.duration, col.names=NULL, digits = 0) %>% kable_styling(full_width=F, position="center") %>% column_spec(1, bold=T, color="black", width="7cm") %>% column_spec(2, width = "2cm") 

```