### Exploring age mixing

```{r, echo=FALSE, include=FALSE}
####################################################################################
# Setup
####################################################################################
#-----------------------------------------------------------------------------------
# Load packages
#-----------------------------------------------------------------------------------

    library("tidyverse")
    library("knitr")
    library("data.table")
    library("lmtest")
    library("kableExtra")
    library("logbin")

#-----------------------------------------------------------------------------------
# Knitr options
#-----------------------------------------------------------------------------------
opts_chunk$set(echo=FALSE, message=FALSE, warning=TRUE, error=TRUE, fig.align = "center")
options(knitr.table.format = "html") 

#-----------------------------------------------------------------------------------
# Plot settings
#-----------------------------------------------------------------------------------
#save plot settings for white background and light grey lines and darkening the colors a bit
plot_background <- theme(panel.background = element_rect(fill="white", colour = "black")) + theme(panel.grid.major = element_line(colour = "grey90"))
darken_color <- scale_colour_hue(l=50)
theme_title <- theme(plot.title = element_text(hjust = 0.5, size=11, colour = "grey33")) 
        
#-----------------------------------------------------------------------------------
# Load data
#-----------------------------------------------------------------------------------

setwd("/homes/dpwhite/R/GitHub Repos/WHAMP/Parameter estimation")
load(file="Data/InternetSurveySample.Rdata")

#----------------------------------------------------------------------------------
# Define multiplot function
#_---------------------------------------------------------------------------------
        multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
            library(grid)
            
            # Make a list from the ... arguments and plotlist
            plots <- c(list(...), plotlist)
            
            numPlots = length(plots)
            
            # If layout is NULL, then use 'cols' to determine layout
            if (is.null(layout)) {
                # Make the panel
                # ncol: Number of columns of plots
                # nrow: Number of rows needed, calculated from # of cols
                layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                                 ncol = cols, nrow = ceiling(numPlots/cols))
            }
            
            if (numPlots==1) {
                print(plots[[1]])
                
            } else {
                # Set up the page
                grid.newpage()
                pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))
                
                # Make each plot, in the correct location
                for (i in 1:numPlots) {
                    # Get the i,j matrix positions of the regions that contain this subplot
                    matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))
                    
                    print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                                    layout.pos.col = matchidx$col))
                }
            }
        }

```

First we prepare the data and define age difference variables
```{r, echo=TRUE}
#Select ego and alter age variables
age_explore <- sample %>% filter(!is.na(mrp_ageinyears_approx)) %>% select(age, mrp_ageinyears_approx)
#Define a variable to indicate the older of the two partners' ages
age_explore$olderpartner <- apply(age_explore, 1, max)

#Define age differences
age_explore$agediff <- abs(age_explore$age - age_explore$mrp_ageinyears_approx)
age_explore$sqrt_agediff <- abs(sqrt(age_explore$age) - sqrt(age_explore$mrp_ageinyears_approx))
age_explore$cbrt_agediff <- abs(age_explore$age^(1/3) - age_explore$mrp_ageinyears_approx^(1/3))

#Define a variable to highlight specific age differences on the plot
age_explore$flagdiffs <- ifelse(age_explore$agediff %in% 6, "6 year diff", ifelse(age_explore$agediff %in% 15, "15 year diff", "other diff"))
```

List the first 20 rows to check that the variables were defined appropriately
```{r table, echo=TRUE}
age_explore[1:20,] %>% select(age, mrp_ageinyears_approx, agediff, sqrt_agediff, cbrt_agediff)
```

For the first 50 observations, plot the absolute value of the difference between the partners' ages in years, the absolute value of the difference between the square root of the partners' ages, and the absolute value of the difference between the cube root of the partners' ages on the same plot. The x-axis is the older of the two partner's ages.
```{r plots_1, echo=TRUE}
ggplot(age_explore[1:50,]) + geom_point(aes(x=olderpartner, y=agediff, color="a")) + geom_point(aes(x=olderpartner, y=sqrt_agediff, color="b")) + geom_point(aes(x=olderpartner, y=cbrt_agediff, color="c")) + scale_colour_manual(name = "Legend", values=c("a"="blue", "b"="green", "c"="red"), labels=c("Ages in years", "Square root of ages", "Cube root of ages")) + theme_title + plot_background + labs(x="Older partner's age", y="Age difference", title="Difference between ego and alter's ages")

```

Plot each difference separately. In these plots, 6- and 15-year age differences are highlighted to make it easier to track how taking the square and cube root of ages changes the relative position of points with the same absolute difference in age.
```{r plots_2, echo=TRUE}
p_ages <- ggplot(age_explore[1:50,]) + geom_point(aes(x=olderpartner, y=agediff, colour=flagdiffs), size=2) + theme_title + plot_background + labs(x="Older partner's age", title="Difference between ego and alter's ages")

p_sqrt <- ggplot(age_explore[1:50,]) + geom_point(aes(x=olderpartner, y=sqrt_agediff, colour=flagdiffs), size=2) + theme_title + plot_background + labs(x="Older partner's age", title="Difference between square root of ego and alter's ages")

p_cbrt <- ggplot(age_explore[1:50,]) + geom_point(aes(x=olderpartner, y=cbrt_agediff, colour=flagdiffs), size=2) + theme_title + plot_background + labs(x="Older partner's age", title="Difference between cube root of ego and alter's ages")

p_ages
p_sqrt
p_cbrt
```

__Interpretation__: It looks like taking the square root and cube root of ego and alter ages does make the magnitude of the same difference in age smaller if the partners involved in the dyad are older. But the trend across ages appears the same in all three plots... The plots below use data from the full sample (not just the first 50 observations) and stratify by partner type.

```{r, echo=FALSE}
  #Define a variable for partnership type that includes only ongoing main and persistent but all instantaneous partners
    sample$ptype_adiff <- ifelse(sample$mrp_type_ongoing %in% "Main", "Ongoing main", ifelse(sample$mrp_type_ongoing %in% "Persistent", "Ongoing persistent", ifelse(sample$mrp_type_r %in% "One time", "Instantaneous", NA)))
    sample$ptype_adiff <- factor(sample$ptype_adiff, levels = c("Ongoing main", "Ongoing persistent", "Instantaneous"))
    
    #Define a variable to indicate the absolute value of the difference in ages
    sample$agediff <- abs(sample$age - sample$mrp_ageinyears_approx)
    
    #Define a variable that is the older of the two partner's ages
    sample$olderpartner <- apply(sample[, c("age", "mrp_ageinyears_approx")], 1, max)

    #Define a variable for differnece in the cube root
    sample$cbrt_agediff <- abs(sample$age^(1/3) - sample$mrp_ageinyears_approx^(1/3))

```

```{r plots_3, echo=FALSE}
#Age mixing as the true age differences in the full sample, by partner type
    ggplot(sample[!is.na(sample$agediff) & !is.na(sample$ptype_adiff),], aes(x=olderpartner, y=agediff)) + geom_point() + geom_smooth(method="loess") + facet_grid(ptype_adiff ~.) + labs(x="Older partner's age", y="Age difference", title = "Age mixing as the absolute value of \n the difference between ego and alter ages") + theme_title + plot_background + theme_title

#Age mixing as the square root of age differences in the full sample, by partner type
    ggplot(sample[!is.na(sample$sqrt_agediff) & !is.na(sample$ptype_adiff),], aes(x=olderpartner, y=sqrt_agediff)) + geom_point() + geom_smooth(method="loess") + facet_grid(ptype_adiff ~.) + labs(x="Older partner's age", y="Difference in the sqrt of age", title = "Age mixing as the difference between the square root of ego and alter ages") + theme_title + plot_background
    
#Age mixing as the cube root of age differences in the full sample, by partner type
    ggplot(sample[!is.na(sample$cbrt_agediff) & !is.na(sample$ptype_adiff),], aes(x=olderpartner, y=cbrt_agediff)) + geom_point() + geom_smooth(method="loess") + facet_grid(ptype_adiff ~.) + labs(x="Older partner's age", y="Difference in the cube root of age", title = "Age mixing as the difference between the cube root of ego and alter ages") + theme_title + plot_background
   
```

