# Notes on excluding data from men whose partners are outside of the age range {#alter_age_boundary}
```{r setup, include=F}
####################################################################################
# Setup
####################################################################################
#-----------------------------------------------------------------------------------
# Load packages
#-----------------------------------------------------------------------------------

    library("tidyverse")
    library("knitr")
    library("data.table")
    library("kableExtra")

#-----------------------------------------------------------------------------------
# Knitr options
#-----------------------------------------------------------------------------------
opts_chunk$set(echo=FALSE, message=FALSE, warning=TRUE, error=TRUE, fig.align = "center")
options(knitr.table.format = "html") 

#-----------------------------------------------------------------------------------
# Plot settings
#-----------------------------------------------------------------------------------
#save plot settings for white background and light grey lines and darkening the colors a bit
plot_background <- theme(panel.background = element_rect(fill="white", colour = "black")) + theme(panel.grid.major = element_line(colour = "grey90"))
darken_color <- scale_colour_hue(l=50)
theme_title <- theme(plot.title = element_text(hjust = 0.5, size=11, colour = "grey33")) 
        
#-----------------------------------------------------------------------------------
# Load data
#-----------------------------------------------------------------------------------
setwd("/homes/dpwhite/R/GitHub Repos/WHAMP/Parameter estimation")
load(file="Data/InternetSurveySample_allages.Rdata")

# Restrict all ages dataset to age range and make other modifications. Don't use the "sample" dataset b/c that excludes men with a partner outside the age range for calculation of some parameters
    #Define sample age limit
        sample_incl.mrp.oor <- sample_allages %>%filter(age>17 & age<60)
        
    #Drop 18 observations with missing race/ethnicity -- to reweight the sample, can only use non-missing obs
        sample_incl.mrp.oor <- sample_incl.mrp.oor %>% filter(!is.na(hbo))
        
#-----------------------------------------------------------------------------------
# Define a variable that identifies men with mrp out of age range
#-----------------------------------------------------------------------------------

    sample_incl.mrp.oor$mrp_oor <- ifelse(sample_incl.mrp.oor$mrp_ageinyears_approx<18 | sample_incl.mrp.oor$mrp_ageinyears_approx >59, 1, ifelse(!is.na(sample_incl.mrp.oor$mrp_ageinyears_approx), 0, NA))

#----------------------------------------------------------------------------------
# Define multiplot function
#_---------------------------------------------------------------------------------
        multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
            library(grid)
            
            # Make a list from the ... arguments and plotlist
            plots <- c(list(...), plotlist)
            
            numPlots = length(plots)
            
            # If layout is NULL, then use 'cols' to determine layout
            if (is.null(layout)) {
                # Make the panel
                # ncol: Number of columns of plots
                # nrow: Number of rows needed, calculated from # of cols
                layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                                 ncol = cols, nrow = ceiling(numPlots/cols))
            }
            
            if (numPlots==1) {
                print(plots[[1]])
                
            } else {
                # Set up the page
                grid.newpage()
                pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))
                
                # Make each plot, in the correct location
                for (i in 1:numPlots) {
                    # Get the i,j matrix positions of the regions that contain this subplot
                    matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))
                    
                    print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                                    layout.pos.col = matchidx$col))
                }
            }
        }
```

This file looks at the characteristics of men whose most recent partner was outside of the modeled age range (<18 or >59) and whether these men differ in any meaningful way from other respondents. 

The table below shows the ages of most recent partners outside of the age range by the ages of the egos who reported them.
```{r dyadage_oor}
agecombo_oor <- sample_incl.mrp.oor %>% filter(mrp_oor %in% 1) %>% group_by(age, mrp_ageinyears_approx) %>% summarise(Freq = n()) %>% mutate(agediff = abs(age - mrp_ageinyears_approx))
kable(agecombo_oor, col.names=c("Ego age", "Alter age", "Frequency", "Age difference (abs value)"), caption = "Ego and alter age for alters out of modeled age range") %>% kable_styling(full_width=F, position="center")
```
Most men are within 6 years of these alters, but almost a quarter report an alter more than 10 years older than themselves. Partnerships reported with alters >59 tended to have larger age differences than partnerships reported with alters <18. Some of these may be data entry errors, but others could be legitimate. 

The table below shows the partnerships reported with alters out of the age range by partner type and whether the alter was <18 or >59. 
```{r}
# Define indicator of whether mrp is <18 or >59
    sample_incl.mrp.oor$mrp_oor_cat <- ifelse(sample_incl.mrp.oor$mrp_ageinyears_approx<18, "MRP <18", ifelse(sample_incl.mrp.oor$mrp_ageinyears_approx>59, "MRP >59", ifelse(!is.na(sample_incl.mrp.oor$mrp_ageinyears_approx), "MRP 18-59", NA)))

    num_oor <- sample_incl.mrp.oor %>% filter(!is.na(mrp_oor_cat) & mrp_oor %in% 1) %>% group_by(mrp_oor_cat, mrp_type_r, mrp_ongoing) %>% summarise(freq=n())
    num_oor.kbl <- cbind.data.frame(ptype = c("Main ongoing", "Main not ongoing", "Persistent ongoing", "Persistent not ongoing", "One-time", "Total"), lt18 = c(num_oor$freq[num_oor$mrp_oor_cat %in% "MRP <18" & num_oor$mrp_type_r %in% "Main" & num_oor$mrp_ongoing %in% 1], num_oor$freq[num_oor$mrp_oor_cat %in% "MRP <18" & num_oor$mrp_type_r %in% "Main" & num_oor$mrp_ongoing %in% 0], num_oor$freq[num_oor$mrp_oor_cat %in% "MRP <18" & num_oor$mrp_type_r %in% "Casual" & num_oor$mrp_ongoing %in% 1], 0, 0, sum(num_oor$freq[num_oor$mrp_oor_cat %in% "MRP <18"])), gt59 = c(num_oor$freq[num_oor$mrp_oor_cat %in% "MRP >59" & num_oor$mrp_type_r %in% "Main" & num_oor$mrp_ongoing %in% 1], 0, num_oor$freq[num_oor$mrp_oor_cat %in% "MRP >59" & num_oor$mrp_type_r %in% "Casual" & num_oor$mrp_ongoing %in% 1], 0, num_oor$freq[num_oor$mrp_oor_cat %in% "MRP >59" & num_oor$mrp_type_r %in% "One time"], sum(num_oor$freq[num_oor$mrp_oor_cat %in% "MRP >59"])))
    
    kable(num_oor.kbl, col.names = c("Partner type", "Partner <18", "Partner >59")) %>% row_spec(6, bold=T) %>% kable_styling(full_width=F, position="center")
    
```

Next we'll look to see whether men who reported partners outside of the age range differ in any important way from the rest of the sample. Because men whose partners are out of range are more likely to be close to the age cut-offs (Table \@ref(tab:dyadage_oor)), we will adjust for ego age in comparisons for other variables.

```{r, echo=TRUE}
# Race/ethnicity
table(sample_incl.mrp.oor$hbo, sample_incl.mrp.oor$mrp_oor)

# Define indicators
sample_incl.mrp.oor$H <- ifelse(sample_incl.mrp.oor$hbo %in% "Hispanic", 1, ifelse(!is.na(sample_incl.mrp.oor$hbo), 0, NA))
sample_incl.mrp.oor$B <- ifelse(sample_incl.mrp.oor$hbo %in% "Black", 1, ifelse(!is.na(sample_incl.mrp.oor$hbo), 0, NA))
sample_incl.mrp.oor$O <- ifelse(sample_incl.mrp.oor$hbo %in% "Other", 1, ifelse(!is.na(sample_incl.mrp.oor$hbo), 0, NA))

# Regression models
summary(glm(H ~ age_cat + mrp_oor, family=binomial(link="logit"), data=sample_incl.mrp.oor))
summary(glm(B ~ age_cat + mrp_oor, family=binomial(link="logit"), data=sample_incl.mrp.oor))
summary(glm(O ~ age_cat + mrp_oor, family=binomial(link="logit"), data=sample_incl.mrp.oor))

```

In light of the significant differences by race/ethnicity, we will also adjust for race/ethnicity in comparisons for other variables to look for differences independent of racial/ethnic differences.

```{r, echo=TRUE}
# Region
table(sample_incl.mrp.oor$region, sample_incl.mrp.oor$mrp_oor)
summary(glm(region ~ age_cat + hbo + mrp_oor, family=binomial(link="logit"), data=sample_incl.mrp.oor))


# Degree distribution
  ## Main partner
    table(sample_incl.mrp.oor$degree_main, sample_incl.mrp.oor$mrp_oor)
    summary(glm(degree_main ~ age_cat + hbo + mrp_oor, family=binomial(link="logit"), data=sample_incl.mrp.oor))

  ## Any persistent partner
    table(sample_incl.mrp.oor$anypers, sample_incl.mrp.oor$mrp_oor)
    summary(glm(anypers ~ age_cat + hbo + mrp_oor, family=binomial(link="logit"), data=sample_incl.mrp.oor))
    
  ## Two or more persistent partners
    table(sample_incl.mrp.oor$concurrent_pers, sample_incl.mrp.oor$mrp_oor)
    summary(glm(concurrent_pers ~ age_cat + hbo + mrp_oor, family=binomial(link="logit"), data=sample_incl.mrp.oor))
    
  ## Persistent partner concurrent with a main partner
    table(sample_incl.mrp.oor$concurrent_mainpers, sample_incl.mrp.oor$mrp_oor)
    summary(glm(concurrent_mainpers ~ age_cat + hbo + mrp_oor, family=binomial(link="logit"), data=sample_incl.mrp.oor))

# Rate of instantaneous partnerships
    sample_incl.mrp.oor %>% filter(!is.na(mrp_oor) & !is.na(rate_inst)) %>% group_by(mrp_oor) %>% summarise(n = n(), median = median(rate_inst, na.rm = TRUE), mean = mean(rate_inst, na.rm=TRUE))
    summary(lm(rate_inst ~ age_cat + hbo + mrp_oor, data=sample_incl.mrp.oor))

# Proportion never tested (of those >age 40)
    sample_incl.mrp.oor$nevertest <- 1-sample_incl.mrp.oor$evertest_r
    sample_incl.mrp.oor %>% filter(!is.na(mrp_oor) & age>40) %>% group_by(mrp_oor) %>% summarise(n = n(), never_tested = mean(nevertest, na.rm=TRUE))
    summary(glm(nevertest ~ age_cat + hbo + mrp_oor, family=binomial(link="logit"), data=sample_incl.mrp.oor, subset = age %in% c(40:59)))
    
# Intertest interval
    #Define dataframe excluding men who used PrEP in the past 12 months
    sample_incl.mrp.oor_p12noprep <- sample_incl.mrp.oor %>% filter((prep_use_r %in% c("Took PrEP in the past", "Never taken PrEP")) & !(monthsago_lastprep %in% c(0:12)))
    
    sample_incl.mrp.oor_p12noprep %>% filter(!is.na(mrp_oor) & !is.na(iti_int)) %>% group_by(mrp_oor) %>% summarise(median = median(iti_int, na.rm = TRUE), mean = mean(iti_int, na.rm=TRUE))
    summary(lm(iti_int ~ age_cat + hbo + mrp_oor, data=sample_incl.mrp.oor_p12noprep))

# Coital frequency
  ## Main partnerships
    sample_incl.mrp.oor %>% filter(!is.na(mrp_oor) & !is.na(airate_main)) %>% group_by(mrp_oor) %>% summarise(n = n(), median = median(airate_main, na.rm = TRUE), mean = mean(airate_main, na.rm=TRUE))
    summary(lm(airate_main ~ age_cat + hbo + mrp_oor, data=sample_incl.mrp.oor))
    
  ## Persistent partnerships
    sample_incl.mrp.oor %>% filter(!is.na(mrp_oor) & !is.na(airate_pers)) %>% group_by(mrp_oor) %>% summarise(n = n(), median = median(airate_pers, na.rm = TRUE), mean = mean(airate_pers, na.rm=TRUE))
    summary(lm(airate_pers ~ age_cat + hbo + mrp_oor, data=sample_incl.mrp.oor))
    
# Sex role
    #Define indicators
    sample_incl.mrp.oor$position_top <- ifelse(sample_incl.mrp.oor$position_cat=="Exclusively top", 1, ifelse(!is.na(sample_incl.mrp.oor$position_cat), 0, NA))
    sample_incl.mrp.oor$position_bottom <- ifelse(sample_incl.mrp.oor$position_cat=="Exclusively bottom", 1, ifelse(!is.na(sample_incl.mrp.oor$position_cat), 0, NA))
    sample_incl.mrp.oor$position_versatile <- ifelse(sample_incl.mrp.oor$position_cat=="Versatile", 1, ifelse(!is.na(sample_incl.mrp.oor$position_cat), 0, NA))
    
    table(sample_incl.mrp.oor$position_cat, sample_incl.mrp.oor$mrp_oor)
    summary(glm(position_top ~ age_cat + hbo + mrp_oor, family=binomial(link="logit"), data=sample_incl.mrp.oor))
    summary(glm(position_bottom ~ age_cat + hbo + mrp_oor, family=binomial(link="logit"), data=sample_incl.mrp.oor))
    summary(glm(position_versatile ~ age_cat + hbo + mrp_oor, family=binomial(link="logit"), data=sample_incl.mrp.oor))

# Condoms
    # Define sample_incl.mrp.oor for condom use analyses - exclude partners on PrEP and men who have taken PrEP in the past 12 months
    sample_incl.mrp.oor_p12noprep_noalterprep <- sample_incl.mrp.oor_p12noprep %>% filter(!(mrp_prep_r %in% 1))

  ## Main partners
     sample_incl.mrp.oor_p12noprep_noalterprep %>% filter(!is.na(mrp_oor) & !is.na(condoms_main)) %>% group_by(mrp_oor) %>% summarise(n = n(), mean = mean(condoms_main, na.rm=TRUE))
    summary(lm(condoms_main ~ age_cat + hbo + mrp_oor, data=sample_incl.mrp.oor_p12noprep_noalterprep))

  ## Persistent partners
     sample_incl.mrp.oor_p12noprep_noalterprep %>% filter(!is.na(mrp_oor) & !is.na(condoms_pers)) %>% group_by(mrp_oor) %>% summarise(n = n(), mean = mean(condoms_pers, na.rm=TRUE))
    summary(lm(condoms_pers ~ age_cat + hbo + mrp_oor, data=sample_incl.mrp.oor_p12noprep_noalterprep))
    
  ## Instantaneous partners
     sample_incl.mrp.oor_p12noprep_noalterprep %>% filter(!is.na(mrp_oor) & !is.na(condoms_inst)) %>% group_by(mrp_oor) %>% summarise(n = n(), mean = mean(condoms_inst, na.rm=TRUE))
    summary(glm(condoms_inst ~ age_cat + hbo + mrp_oor, family=binomial(link="logit"), data=sample_incl.mrp.oor_p12noprep_noalterprep))

# PrEP use
  ## PrEP recommended
    table(sample_incl.mrp.oor$prep_use_r[sample_incl.mrp.oor$prepelig_r %in% "Recommend"], sample_incl.mrp.oor$mrp_oor[sample_incl.mrp.oor$prepelig_r %in% "Recommend"])
    summary(glm(prep_use_curr ~ age_cat + hbo + mrp_oor, family=binomial(link="logit"), data=sample_incl.mrp.oor, subset = prepelig_r %in% "Recommend"))

  ## PrEP to be discussed
    table(sample_incl.mrp.oor$prep_use_r[sample_incl.mrp.oor$prepelig_r %in% "Discuss"], sample_incl.mrp.oor$mrp_oor[sample_incl.mrp.oor$prepelig_r %in% "Discuss"])
    summary(glm(prep_use_curr ~ age_cat + hbo + mrp_oor, family=binomial(link="logit"), data=sample_incl.mrp.oor, subset = prepelig_r %in% "Discuss"))

```

These analyses indicate that men whose partners are outside of the modeled age range differ from those who report partners in the age range in terms of race/ethnicity (a greater proportion are Hispanic and fewer are "other"), main partnership status (more likely to have a main partner), coital frequency in main partnerships (lower coital frequency), and sex role (more likely to be bottoms and less likely to be versatile). Some of these things (e.g. coital frequency) may just be reflective of the fact that these are dyads with younger or older partners.