# Assess mismatch between mean degrees by race/ethnicity from the balanced mixing matrices and from observed momentary degree distributions
As discussed in [issue #41](https://github.com/statnet/WHAMP/issues/41), our approach to estimating race-specific momentary degree distributions is as follows:  

  1. Obtain balanced mixing matrices from the data (this involves multiplying the observed row conditional proabilities by the observed mean degree for each racial/ethnic group),  
  2. Check for imbalances in the group-specific mean degree from the observed momentary degree distributions and the mean degree from the balanced mixing matrices.  
  3. If there are imbalances, make adjustments to the mixing matrix: Bump up the margins as needed by increasing/decreasing the values in each cell proportionately (if the mean degree was .5 and it needs to be 0.51, multiply all cells in the 1 main row by 0.51/0.50 and everything in the 0 main row by 0.50/0.51). For persistent degree, make adjustments in the 0 and 1 persistent columns and leave the 2 persistent partner column unchanged. 

This file looks to see how much mismatch there is between the mean degrees implied by the balanced mixing matrices and the observed mean degrees.

```{r, include=FALSE}
####################################################################################
# Setup
####################################################################################
#-----------------------------------------------------------------------------------
# Load packages
#-----------------------------------------------------------------------------------

    library("tidyverse")
    library("knitr")
    library("kableExtra")
    library("data.table")
    library("survey")

#-----------------------------------------------------------------------------------
# Knitr options
#-----------------------------------------------------------------------------------
opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE)
options(knitr.table.format = "html") 

#-----------------------------------------------------------------------------------
# Load data
#-----------------------------------------------------------------------------------
    load(file="/homes/dpwhite/R/GitHub Repos/WHAMP/Parameter estimation/Data/InternetSurveySample.Rdata")
    load(file="/homes/dpwhite/R/GitHub Repos/WHAMP/Parameter estimation/Data/InternetSurvey_reweighted_neg.Rdata")
    load(file="/homes/dpwhite/R/GitHub Repos/WHAMP/Parameter estimation/Data/InternetSurvey_reweighted_all.Rdata")
    load(file="/homes/dpwhite/R/GitHub Repos/WHAMP/Parameter estimation/Data/degreedists.Rdata")
        
#-----------------------------------------------------------------------------------
# Plot settings
#-----------------------------------------------------------------------------------
plot_background <- theme(panel.background = element_rect(fill="white", colour = "black")) +
            theme(panel.grid.major = element_line(colour = "grey90"))
theme_title <- theme(plot.title = element_text(hjust = 0.5, size=12)) 

```

## Main degree
The observed mean main degree among Hispanic, black, and other men are:
```{r}
(obs.degm = round(c("Hispanic" = degree$deg.mp.H[2,4], "Black" = degree$deg.mp.B[2,4], "Other" = degree$deg.mp.O[2,4]), 4))
```

From the balanced mixing matrices, we get the following mean main degrees:
```{r balanced_race_main}
#Conditional row probabilities
  racemix_main <- prop.table(svytable(~hbo + mrp_hbo, sample_rake_all[sample_rake_all$variables$mrp_type_ongoing %in% "Main"], round=FALSE),1)

  #Mean degree by race 
    meandegm.H <- degree$deg.mp.H[2,4]
    meandegm.B <- degree$deg.mp.B[2,4]
    meandegm.O <- degree$deg.mp.O[2,4]
    
  #N by race in reweighted sample (scaled back to the size of the original sample) -- scaling to the total N assumes that those with missing data on degree or who didn't provide the age of their most recent partner are msising at random
    nXrace <- svytable(~hbo, sample_rake_all, Ntotal=dim(sample)[1], round=FALSE)

  #Reweighted mixing matrix, accounting for mean degree
  racemix_main_rwt <- matrix(c(racemix_main[1,]*meandegm.H*nXrace[1], racemix_main[2,]*meandegm.B*nXrace[2], racemix_main[3,]*meandegm.O*nXrace[3]), byrow=TRUE, nrow=3)
  racemix_main_rwt <- as.data.frame(racemix_main_rwt, row.names=c("Hispanic", "Black", "Other"))
  names(racemix_main_rwt) <- c("Hispanic", "Black", "Other")
  
#Take average of off-diagonals to balance
  racemix_main_bal <- as.data.frame(matrix(c("HH"=racemix_main_rwt[1,1], "HB" = mean(c(racemix_main_rwt[1,2], racemix_main_rwt[2,1])), "HO" = mean(c(racemix_main_rwt[1,3], racemix_main_rwt[3,1])), "BH" = mean(c(racemix_main_rwt[1,2], racemix_main_rwt[2,1])), "BB" = racemix_main_rwt[2,2], "BO" = mean(c(racemix_main_rwt[2,3], racemix_main_rwt[3,2])), "OH" = mean(c(racemix_main_rwt[1,3], racemix_main_rwt[3,1])), "OB" = mean(c(racemix_main_rwt[2,3], racemix_main_rwt[3,2])), "OO" = racemix_main_rwt[3,3]), nrow=3, ncol=3, byrow=TRUE, dimnames=list(c("Hispanic", "Black", "Other"), c("Hispanic", "Black", "Other"))))

 #Implied mean degrees
  (bal.degm <- round(c(sum(racemix_main_bal[1,])/nXrace[1], sum(racemix_main_bal[2,])/nXrace[2], sum(racemix_main_bal[3,])/nXrace[3]),4))

```

## Persistent degree
The observed mean persistent degrees for Hispanic, black, and other men are:
```{r}
(obs.degp = round(c("Hispanic" = degree$deg.mp.H[3,2] + 2*degree$deg.mp.H[3,3], "Black" = degree$deg.mp.B[3,2] + 2*degree$deg.mp.B[3,3], "Other" = degree$deg.mp.B[3,2] + 2*degree$deg.mp.O[3,3]), 4))
```

From the balanced mixing matrices, we get the following mean persistent degrees:
```{r balanced_race_pers}
#Conditional row probabilities - using data from both ongoing persistent and most recent one-time partners
  racemix_pers <- prop.table(svytable(~hbo + mrp_hbo, sample_rake_all[sample_rake_all$variables$mrp_type_ongoing %in% "Persistent" | sample_rake_all$variables$mrp_type_r %in% "One time"], round=FALSE),1)

#Mean degree by race/ethnicity
    meandegp.H <- degree$deg.mp.H[3,2] + 2*degree$deg.mp.H[3,3]   
    meandegp.B <- degree$deg.mp.B[3,2] + 2*degree$deg.mp.B[3,3]
    meandegp.O <- degree$deg.mp.B[3,2] + 2*degree$deg.mp.O[3,3]

  #N by race in reweighted sample (scaled back to the size of the original sample)
  nXrace <- svytable(~hbo, sample_rake_all, Ntotal=dim(sample)[1], round=FALSE)

  #Reweighted mixing matrix, accounting for mean degree
  racemix_pers_rwt <- matrix(c(racemix_pers[1,]*meandegp.H*nXrace[1], racemix_pers[2,]*meandegp.B*nXrace[2], racemix_pers[3,]*meandegp.O*nXrace[3]), byrow=TRUE, nrow=3)
  racemix_pers_rwt <- as.data.frame(racemix_pers_rwt, row.names=c("Hispanic", "Black", "Other"))
  names(racemix_pers_rwt) <- c("Hispanic", "Black", "Other")
  
  #Take average of off-diagonals to balance
  racemix_pers_bal <- as.data.frame(matrix(c("HH"=racemix_pers_rwt[1,1], "HB" = mean(c(racemix_pers_rwt[1,2], racemix_pers_rwt[2,1])), "HO" = mean(c(racemix_pers_rwt[1,3], racemix_pers_rwt[3,1])), "BH" = mean(c(racemix_pers_rwt[1,2], racemix_pers_rwt[2,1])), "BB" = racemix_pers_rwt[2,2], "BO" = mean(c(racemix_pers_rwt[2,3], racemix_pers_rwt[3,2])), "OH" = mean(c(racemix_pers_rwt[1,3], racemix_pers_rwt[3,1])), "OB" = mean(c(racemix_pers_rwt[2,3], racemix_pers_rwt[3,2])), "OO" = racemix_pers_rwt[3,3]), nrow=3, ncol=3, byrow=TRUE, dimnames=list(c("Hispanic", "Black", "Other"), c("Hispanic", "Black", "Other"))))
  
 #Implied mean degrees
  (bal.degp <- round(c(sum(racemix_pers_bal[1,])/nXrace[1], sum(racemix_pers_bal[2,])/nXrace[2], sum(racemix_pers_bal[3,])/nXrace[3]), 4))

```

## Conclusion
For main partners, this doesn't look so bad, but for persistent partners, the mismatch is pretty big. If we look at the change from the unbalanced to balance mixing matrices, it is interesting that the mismatch arises from Hispanic men reporting fewer partnerships with Black and Other men than Black and Other men report with Hispanics. This pattern is consistent across partnership types. It could either be due to Hispanic men under-reporting all partnerships, Black and Other men misclassifying partners as Hispanic who aren't, or Hispanic men classifying men who aren't Hispanic as Hispanic (the latter seems unlikely). 

If we balance by taking the mean of the off-diagonal, we are bumping up the number of Hispanic-Black and Hispanic-Other partnerships, but leaving the number Hispanic-Hispanic unchanged, so we are decreasing the percent homophilous AND increasing the mean degree. One option for how to deal with this is to look at the overall percent increase in partnerships with black or other men when the matrix is balanced and increase the number of Hispanic-Hispanic partnerships proportionately. But this would result in an even greater increase in mean degree. Or, if we believe men are accurately reporting mean degree, we could calculate target statistics for mixing from the unbalanced matrix. This preserves the log-odds of within-race ties and preserves mean degree as reported by men in each racial/ethnic group.

__DECISION__: Try calculating degree and mixing target statistics two ways: 1) Take the approach we had been planning, where I balance the mixing matrix and adjust mean degree accordingly, with the limitation that this bumps down the percent homophilous for Hispanic and Black men and bumps it up for Other race men. 2) Take the approach where we use observed mean degree and the unbalanced mixing matrices. Try to fit the model both ways - it's possible it won't converge for the second approach if the expected number of mixed-race partnerships for each racial group are incompatible. Also run diagnoses to look at the patterns of mixing produced by the models.