# Regional variability {#explore_region}
```{r, include=FALSE}
####################################################################################
# Setup
####################################################################################
#-----------------------------------------------------------------------------------
# Load packages
#-----------------------------------------------------------------------------------

    library("tidyverse")
    library("knitr")
    library("data.table")
    library("lmtest")
    library("kableExtra")
    library("logbin")

#-----------------------------------------------------------------------------------
# Knitr options
#-----------------------------------------------------------------------------------
opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE)
options(knitr.table.format = "html") 

#-----------------------------------------------------------------------------------
# Plot settings
#-----------------------------------------------------------------------------------
#save plot settings for white background and light grey lines and darkening the colors a bit
plot_background <- theme(panel.background = element_rect(fill="white", colour = "black")) + theme(panel.grid.major = element_line(colour = "grey90"))
darken_color <- scale_colour_hue(l=50)
theme_title <- theme(plot.title = element_text(hjust = 0.5, size=12)) 
        
#-----------------------------------------------------------------------------------
# Load data
#-----------------------------------------------------------------------------------

load(file="Data/InternetSurveySample.Rdata")
load(file="Data/InternetSurveySample_allages.Rdata")

```


This section documents the results of regression analyses aimed at identifying parameters that vary by region after adjusting for age and race/ethnicity. P-values are to be used as a guide but not as the sole criteria determining which differences may be worth modeling. The purpose of this analysis is to determine which parameters need to be stratified on region to get the network to reproduce the data. It is not an analysis to determine from the data which parameters differ significantly by region in the population (since the sample is not probability-based, this would be difficult to conclude even if it were our goal). As such, corrections for multiple comparisons are not necessary, as these adjust the false discovery rate in analyses attempting to make inference about the population. We use likelihood ratio tests (package `lmtest`) to compare models with and without adjustment for region for joint significance testing.

## Degree distribution

To look for differences in the degree distribution, we will break it down to two binary indicators corresponding to whether men have one or more ongoing partner of any type and whether they have any concurrent partners. We use logistic regression to test the null hypothesis that region is not associated with the outcomes after adjusting for ego race and age. We first fit a model to test the main effects, then we will test the significance of interactions of race with region and age with region.

### One or more partners 
```{r somepartners, eval=TRUE}

  #Look at the number of observations by region that are non-missing for this outcome and for model predictors
  table(sample$region[!is.na(sample$race_eth_m) & !is.na(sample$somepartners)])

  #Main effects
  glm.somepartners_main <- glm(somepartners ~ age_cat + race_eth_m.reg + region.bKC, family=binomial(link="logit"), data=sample)
  glm.somepartners_nomain <- glm(somepartners ~ age_cat + race_eth_m.reg, family=binomial(link="logit"), data=sample)
  lrt.somepartners_main <- lrtest(glm.somepartners_main, glm.somepartners_nomain)
  lrt.somepartners_main
  
  #RaceXregion interaction
  glm.somepartners_raceint <- glm(somepartners ~ age_cat + race_eth_m.reg + region.bKC + race_eth_m.reg*region.bKC, family=binomial(link="logit"), data=sample)
  glm.somepartners_noraceint <- glm(somepartners ~ age_cat + race_eth_m.reg + region.bKC, family=binomial(link="logit"), data=sample)
  lrt.somepartners_raceint <- lrtest(glm.somepartners_raceint, glm.somepartners_noraceint)
  lrt.somepartners_raceint
  
  #RaceXage interaction
  glm.somepartners_ageint <- glm(somepartners ~ age_cat + race_eth_m.reg + region.bKC + age_cat*region.bKC, family=binomial(link="logit"), data=sample)
  glm.somepartners_noageint <- glm(somepartners ~ age_cat + race_eth_m.reg + region.bKC, family=binomial(link="logit"), data=sample)
  lrt.somepartners_ageint <- lrtest(glm.somepartners_ageint, glm.somepartners_noageint)
  lrt.somepartners_ageint
```


### Concurrency
```{r concurrency, eval=TRUE}

  #Look at the number of observations by region that are non-missing for this outcome and for model predictors
  table(sample$region[!is.na(sample$race_eth_m) & !is.na(sample$concurrent)])

  #Main effects
  glm.concurrent_main <- glm(concurrent ~ age_cat + race_eth_m.reg + region.bKC, family=binomial(link="logit"), data=sample)
  glm.concurrent_nomain <- glm(concurrent ~ age_cat + race_eth_m.reg, family=binomial(link="logit"), data=sample)
  lrt.concurrent_main <- lrtest(glm.concurrent_main, glm.concurrent_nomain)
  lrt.concurrent_main
  
  #RaceXregion interaction
  glm.concurrent_raceint <- glm(concurrent ~ age_cat + race_eth_m.reg + region.bKC + race_eth_m.reg*region.bKC, family=binomial(link="logit"), data=sample)
  glm.concurrent_noraceint <- glm(concurrent ~ age_cat + race_eth_m.reg + region.bKC, family=binomial(link="logit"), data=sample)
  lrt.concurrent_raceint <- lrtest(glm.concurrent_raceint, glm.concurrent_noraceint)
  lrt.concurrent_raceint
  
  #RaceXage interaction
  glm.concurrent_ageint <- glm(concurrent ~ age_cat + race_eth_m.reg + region.bKC + age_cat*region.bKC, family=binomial(link="logit"), data=sample)
  glm.concurrent_noageint <- glm(concurrent ~ age_cat + race_eth_m.reg + region.bKC, family=binomial(link="logit"), data=sample)
  lrt.concurrent_ageint <- lrtest(glm.concurrent_ageint, glm.concurrent_noageint)
  lrt.concurrent_ageint
```



## Rate of instantaneous partners
__Note__: This analysis does not control for men's momentary degree.

```{r rateinst, eval=TRUE}
  #Look at the number of observations by region that are non-missing for this outcome and for model predictors
  table(sample$region[!is.na(sample$race_eth_m) & !is.na(sample$rate_inst)])

  #Full model  
  lm.rateinst <- lm(rate_inst ~ age_cat + race_eth_m.reg + region.bKC + age_cat*region.bKC + race_eth_m.reg*region.bKC, data=sample[!is.na(sample$race_eth_m.reg), ])
  #Model without region
  lm.rateinst_noregion <- lm(rate_inst ~ age_cat + race_eth_m.reg, data=sample[!is.na(sample$race_eth_m.reg), ])

  lrt.rateinst <- lrtest(lm.rateinst, lm.rateinst_noregion)
  lrt.rateinst
```

The results of this analysis indicate that region is __`r ifelse(lrt.rateinst$'Pr(>Chisq)'[2]<siglevel, print("significantly"), print("not"))` associated__ with the rate of instantaneous partners after adjusting for age and race.

## Race/ethnicity mixing
To examine differences in mixing by race/ethnicity, we will look at the proportion of men reporting that their most recent partner was in the same racial/ethnic group (Hispanic, black, or other) as themselves. For main and persistent partner types, this analysis is restricted to most recent partners who are _ongoing_. __Note__: <span style="color:red">The outcome is based on ego reports of their partners race and, at this point, does not adjust for imbalances in reported partnering patterns.</span>
```{r samerace_define}

  #Set to missing if the respondent did not know his partner's race/ethnicity
  sample$mrp_race_eth_m_removedk <- sample$mrp_race_eth_m[!(sample$mrp_race_eth_m %in% "Dont know")]
  sample$mrp_race_eth_m_removedk <- factor(sample$mrp_race_eth_m_removedk)
  
  #Define indicator of respondent and partner being of the same race/ethnicity
  sample$samerace <- ifelse(sample$race_eth_m==sample$mrp_race_eth_m_removedk, 1,
                                   ifelse(!is.na(sample$race_eth_m) & !is.na(sample$mrp_race_eth_m_removedk), 0,
                                          NA))
```

### Main partners
```{r samerace_main, eval=TRUE}

  #Look at the number of observations by region that are non-missing for this outcome and for model predictors
  table(sample$region[!is.na(sample$race_eth_m) & !is.na(sample$samerace) & sample$mrp_type_ongoing %in% "Main"])

  #Full model  
  glm.samerace_main <- glm(samerace ~ age_cat + race_eth_m.reg + region.bKC + age_cat*region.bKC + race_eth_m.reg*region.bKC, family=binomial(link="logit"), data=sample[sample$mrp_type_ongoing %in% "Main", ])
  #Model without region
  glm.samerace_main_noregion <- glm(samerace ~ age_cat + race_eth_m.reg, family=binomial(link="logit"), data=sample[sample$mrp_type_ongoing %in% "Main", ])

  lrt.samerace_main <- lrtest(glm.samerace_main, glm.samerace_main_noregion)
  lrt.samerace_main
```

Region is __`r ifelse(lrt.samerace_main$'Pr(>Chisq)'[2]<siglevel, print("significantly"), print("not"))` associated__ with having a main partner of the same racial/ethnic group after adjusting for age and race.  

### Persistent partners
```{r samerace_pers, eval=TRUE}
  #Look at the number of observations by region that are non-missing for this outcome and for model predictors
  table(sample$region[!is.na(sample$race_eth_m) & !is.na(sample$samerace) & sample$mrp_type_ongoing %in% "Persistent"])

  #Full model  
  glm.samerace_pers <- glm(samerace ~ age_cat + race_eth_m.reg + region.bKC + age_cat*region.bKC + race_eth_m.reg*region.bKC, family=binomial(link="logit"), data=sample[sample$mrp_type_ongoing %in% "Persistent", ])
  #Model without region
  glm.samerace_pers_noregion <- glm(samerace ~ age_cat + race_eth_m.reg, family=binomial(link="logit"), data=sample[sample$mrp_type_ongoing %in% "Persistent", ])

  lrt.samerace_pers <- lrtest(glm.samerace_pers, glm.samerace_pers_noregion)
  lrt.samerace_pers
```

Region is __`r ifelse(lrt.samerace_pers$'Pr(>Chisq)'[2]<siglevel, print("significantly"), print("not"))` associated__ with having a persistent partner of the same racial/ethnic group after adjusting for age and race.

### Instantaneous partners
```{r samerace_inst, eval=TRUE}
  #Look at the number of observations by region that are non-missing for this outcome and for model predictors
  table(sample$region[!is.na(sample$race_eth_m) & !is.na(sample$samerace) & sample$mrp_type_r %in% "One time"])

  #Full model  
  glm.samerace_inst <- glm(samerace ~ age_cat + race_eth_m.reg + region.bKC + age_cat*region.bKC + race_eth_m.reg*region.bKC, family=binomial(link="logit"), data=sample[sample$mrp_type_r %in% "One time", ])
  #Model without region
  glm.samerace_inst_noregion <- glm(samerace ~ age_cat + race_eth_m.reg, family=binomial(link="logit"), data=sample[sample$mrp_type_r %in% "One time", ])

  lrt.samerace_inst <- lrtest(glm.samerace_inst, glm.samerace_inst_noregion)
  lrt.samerace_inst
```

Region is __`r ifelse(lrt.samerace_inst$'Pr(>Chisq)'[2]<siglevel, print("significantly"), print("not"))` associated__ with having an instantaneous partner of the same racial/ethnic group after adjusting for age and race.

## Age mixing
As with race/ethnicity, examination of age differences with main and persistent partners is restricted to most recent partners who are _ongoing_. For this analysis, <span style="color:red">we model age mixing using a linear model with the outcome being the absolute difference between the square root of the ego and alter's ages.</span> 

### Main partners
```{r agemix_main, eval=TRUE}
  #Look at the number of observations by region that are non-missing for this outcome and for model predictors
  table(sample$region[!is.na(sample$race_eth_m) & !is.na(sample$sqrt_agediff) & sample$mrp_type_ongoing %in% "Main"])

  #Full model  
  lm.agemix_main <- lm(sqrt_agediff ~ age_cat + race_eth_m.reg + region.bKC + age_cat*region.bKC + race_eth_m.reg*region.bKC, data=sample[sample$mrp_type_ongoing %in% "Main", ])
  #Model without region
  lm.agemix_main_noregion <- lm(sqrt_agediff ~ age_cat + race_eth_m.reg, data=sample[sample$mrp_type_ongoing %in% "Main", ])

  lrt.agemix_main <- lrtest(lm.agemix_main, lm.agemix_main_noregion)
  lrt.agemix_main
```

Region is __`r ifelse(lrt.agemix_main$'Pr(>Chisq)'[2]<siglevel, print("significantly"), print("not"))` associated__ with age mixing with main partners after adjusting for ego age and race.

### Persistent partners
```{r agemix_pers, eval=TRUE}
  #Look at the number of observations by region that are non-missing for this outcome and for model predictors
  table(sample$region[!is.na(sample$race_eth_m) & !is.na(sample$sqrt_agediff) & sample$mrp_type_ongoing %in% "Persistent"])

  #Full model  
  lm.agemix_pers <- lm(sqrt_agediff ~ age_cat + race_eth_m.reg + region.bKC + age_cat*region.bKC + race_eth_m.reg*region.bKC, data=sample[sample$mrp_type_ongoing %in% "Persistent", ])
  #Model without region
  lm.agemix_pers_noregion <- lm(sqrt_agediff ~ age_cat + race_eth_m.reg, data=sample[sample$mrp_type_ongoing %in% "Persistent", ])

  lrt.agemix_pers <- lrtest(lm.agemix_pers, lm.agemix_pers_noregion)
  lrt.agemix_pers
```

Region is __`r ifelse(lrt.agemix_pers$'Pr(>Chisq)'[2]<siglevel, print("significantly"), print("not"))` associated__ with age mixing with persistent partners after adjusting for ego age and race.

### Instantaneous partners
```{r agemix_inst, eval=TRUE}
  #Look at the number of observations by region that are non-missing for this outcome and for model predictors
  table(sample$region[!is.na(sample$race_eth_m) & !is.na(sample$sqrt_agediff) & sample$mrp_type_r %in% "One time"])

  #Full model  
  lm.agemix_inst <- lm(sqrt_agediff ~ age_cat + race_eth_m.reg + region.bKC + age_cat*region.bKC + race_eth_m.reg*region.bKC, data=sample[sample$mrp_type_r %in% "One time", ])
  #Model without region
  lm.agemix_inst_noregion <- lm(sqrt_agediff ~ age_cat + race_eth_m.reg, data=sample[sample$mrp_type_r %in% "One time", ])

  lrt.agemix_inst <- lrtest(lm.agemix_inst, lm.agemix_inst_noregion)
  lrt.agemix_inst
```

Region is __`r ifelse(lrt.agemix_inst$'Pr(>Chisq)'[2]<siglevel, print("significantly"), print("not"))` associated__ with age mixing with instantaneous partners after adjusting for ego age and race.

## Partnership age
Partnership age was modeled as a linear outcome.

### Main partners
```{r pshipage_main, eval=TRUE}
  #Look at the number of observations by region that are non-missing for this outcome and for model predictors
  table(sample$region[!is.na(sample$race_eth_m) & !is.na(sample$pship_age_main)])

  #Full model  
  lm.pshipage_main <- lm(pship_age_main ~ age_cat + race_eth_m.reg + region.bKC + age_cat*region.bKC + race_eth_m.reg*region.bKC, data=sample)
  #Model without region
  lm.pshipage_main_noregion <- lm(pship_age_main ~ age_cat + race_eth_m.reg, data=sample)

  lrt.pshipage_main <- lrtest(lm.pshipage_main, lm.pshipage_main_noregion)
  lrt.pshipage_main
```

Region is __`r ifelse(lrt.pshipage_main$'Pr(>Chisq)'[2]<siglevel, print("significantly"), print("not"))` associated__ with the age of main partnerships after adjusting for ego age and race.
                
### Persistent partners
```{r pshipage_pers, eval=TRUE}

  #Look at the number of observations by region that are non-missing for this outcome and for model predictors
  table(sample$region[!is.na(sample$race_eth_m) & !is.na(sample$pship_age_pers)])

  #Full model  
  lm.pshipage_pers <- lm(pship_age_pers ~ age_cat + race_eth_m.reg + region.bKC + age_cat*region.bKC + race_eth_m.reg*region.bKC, data=sample)
  #Model without region
  lm.pshipage_pers_noregion <- lm(pship_age_pers ~ age_cat + race_eth_m.reg, data=sample)

  lrt.pshipage_pers <- lrtest(lm.pshipage_pers, lm.pshipage_pers_noregion)
  lrt.pshipage_pers
```

Region is __`r ifelse(lrt.pshipage_pers$'Pr(>Chisq)'[2]<siglevel, print("significantly"), print("not"))` associated__ with the age of persistent partnerships after adjusting for ego age and race.

## Proportion never tested
The parameter indicating the proportion of men who never test is meant to indicate the proportion of men who will not be screened for HIV. In previous network models, this was defined as the proportion who never tested by age 40, since the model was capped at age 39. For this model, that may not be appropriate. In the graph below, it seems that if men don't test by ~age 45, they are unlikely to get tested. It's a bit tricky to interpret, however, because the number of respondents for some ages is small. <span style="color:red">But it may be more appropriate to define the proportion who don't test in a given age range and have men move in and out of the no testing group. For the current analysis, I simply modeled the probability that men had ever tested at their current age.</span>

```{r nevertest}
  #Construct graph to show ever testing by age
  evertested <- sample_allages %>%
              filter(!is.na(evertest_r) & !is.na(race_eth_m)) %>%
              group_by(age) %>%
              summarise(prop = mean(evertest_r, na.rm=TRUE))
  ggplot(evertested, aes(x=age, y=prop)) + geom_point(shape=16, size=3) + geom_smooth(method="loess") +
              plot_background + theme_title +
            labs(x="Age", y="Percent ever tested", title="Percent ever tested by age")        

  #Look at the number of observations by region that are non-missing for this outcome and for model predictors
  table(sample$region[!is.na(sample$race_eth_m) & !is.na(sample$evertest_r)])

  #Full model  
  glm.evertest <- glm(evertest_r ~ age_cat + race_eth_m.reg + region.bKC + age_cat*region.bKC + race_eth_m.reg*region.bKC, family=binomial(link="logit"), data=sample)
  #Model without region
  glm.evertest_noregion <- glm(evertest_r ~ age_cat + race_eth_m.reg, family=binomial(link="logit"), data=sample)

  lrt.evertest <- lrtest(glm.evertest, glm.evertest_noregion)
  lrt.evertest
```

Region is __`r ifelse(lrt.evertest$'Pr(>Chisq)'[2]<siglevel, print("significantly"), print("not"))` associated__ with the probability of having ever tested for HIV after adjusting for ego age and race.

## Intertest interval
The last test interval is estimated as the days since men reported their last HIV test, assuming men have a constant hazard of testing. This analysis is restricted to men who reported having ever tested.

```{r iti, eval=TRUE}

  #Look at the number of observations by region that are non-missing for this outcome and for model predictors
  table(sample$region[!is.na(sample$race_eth_m) & !is.na(sample$iti)])

  #Full model  
  lm.iti <- lm(iti ~ age_cat + race_eth_m.reg + region.bKC + age_cat*region.bKC + race_eth_m.reg*region.bKC, data=sample)
  #Model without region
  lm.iti_noregion <- lm(iti ~ age_cat + race_eth_m.reg, data=sample)

  lrt.iti <- lrtest(lm.iti, lm.iti_noregion)
  lrt.iti
```

Region is __`r ifelse(lrt.iti$'Pr(>Chisq)'[2]<siglevel, print("significantly"), print("not"))` associated__ with the intertest interval after adjusting for ego age and race.

## Coital frequency
Data on coital frequency are from all most recent partnerships, not just those that are ongoing. 

### Main partners
```{r coitalfreq_main}

 #Look at the number of observations by region that are non-missing for this outcome and for model predictors
  table(sample$region[!is.na(sample$race_eth_m) & !is.na(sample$airate_main)])

  #Full model  
  lm.airate_main <- lm(airate_main ~ age_cat + race_eth_m.reg + region.bKC + age_cat*region.bKC + race_eth_m.reg*region.bKC, data=sample)
  #Model without region
  lm.airate_main_noregion <- lm(airate_main ~ age_cat + race_eth_m.reg, data=sample)

  lrt.airate_main <- lrtest(lm.airate_main, lm.airate_main_noregion)
  lrt.airate_main
  
```

Region is __`r ifelse(lrt.airate_main$'Pr(>Chisq)'[2]<siglevel, print("significantly"), print("not"))` associated__ with coital frequency in main partnerships after adjusting for ego age and race.

### Persistent partners
```{r coitalfreq_pers}

 #Look at the number of observations by region that are non-missing for this outcome and for model predictors
  table(sample$region[!is.na(sample$race_eth_m) & !is.na(sample$airate_pers)])

  #Full model  
  lm.airate_pers <- lm(airate_pers ~ age_cat + race_eth_m.reg + region.bKC + age_cat*region.bKC + race_eth_m.reg*region.bKC, data=sample)
  #Model without region
  lm.airate_pers_noregion <- lm(airate_pers ~ age_cat + race_eth_m.reg, data=sample)

  lrt.airate_pers <- lrtest(lm.airate_pers, lm.airate_pers_noregion)
  lrt.airate_pers
  
```

Region is __`r ifelse(lrt.airate_pers$'Pr(>Chisq)'[2]<siglevel, print("significantly"), print("not"))` associated__ with coital frequency in persistent partnerships after adjusting for ego age and race.

## Sex role
Sex role is categorized as exclusively bottom, exclusively top, or versatile, based on men's reported role in anal sex over the past 12 months. Responses of "mostly a botom", "mostly a top", and "equally a bottom and a top" were categorized as versatile. <span style="color:red">For this analysis, a dichotomous indicator was constructed to measure whether men report any bottoming (bottoms and versatile men) or report exclusively topping.</span>

```{r sexrole}
  sample$position_top <- ifelse(sample$position_cat=="Exclusively top", 1, 
                                      ifelse(!is.na(sample$position_cat), 0, NA))
  sample$position_bottom <- ifelse(sample$position_cat=="Exclusively bottom", 1, 
                                      ifelse(!is.na(sample$position_cat), 0, NA))
  
  #Look at the number of observations by region that are non-missing for this outcome and for model predictors
  table(sample$region[!is.na(sample$race_eth_m) & !is.na(sample$position_top)])

  #Full model  
  glm.top <- glm(position_top ~ age_cat + race_eth_m.reg + region.bKC + age_cat*region.bKC + race_eth_m.reg*region.bKC, family=binomial(link="logit"), data=sample)
  #Model without region
  glm.top_noregion <- glm(position_top ~ age_cat + race_eth_m.reg, family=binomial(link="logit"), data=sample)

  lrt.top <- lrtest(glm.top, glm.top_noregion)
  lrt.top
  
```

Region is __`r ifelse(lrt.top$'Pr(>Chisq)'[2]<siglevel, print("significantly"), print("not"))` associated__ with being a top in anal sex after adjusting for ego age and race.

## Condom use
Data on condom use are restricted to dyads in which both the respondent and his partner were HIV-negative or of unknown status. This analysis includes data from all such partnerships, not just those that were ongoing. 

### Main partners
```{r condoms_main}

 #Look at the number of observations by region that are non-missing for this outcome and for model predictors
  table(sample$region[!is.na(sample$race_eth_m) & !is.na(sample$condoms_main)])

  #Full model  
  lm.condoms_main <- lm(condoms_main ~ age_cat + race_eth_m.reg + region.bKC + age_cat*region.bKC + race_eth_m.reg*region.bKC, data=sample)
  #Model without region
  lm.condoms_main_noregion <- lm(condoms_main ~ age_cat + race_eth_m.reg, data=sample)

  lrt.condoms_main <- lrtest(lm.condoms_main, lm.condoms_main_noregion)
  lrt.condoms_main
  
```

Region is __`r ifelse(lrt.condoms_main$'Pr(>Chisq)'[2]<siglevel, print("significantly"), print("not"))` associated__ with condom use in main partnerships after adjusting for ego age and race.

### Persistent partners
```{r condoms_pers}

 #Look at the number of observations by region that are non-missing for this outcome and for model predictors
  table(sample$region[!is.na(sample$race_eth_m) & !is.na(sample$condoms_pers)])

  #Full model  
  lm.condoms_pers <- lm(condoms_pers ~ age_cat + race_eth_m.reg + region.bKC + age_cat*region.bKC + race_eth_m.reg*region.bKC, data=sample)
  #Model without region
  lm.condoms_pers_noregion <- lm(condoms_pers ~ age_cat + race_eth_m.reg, data=sample)

  lrt.condoms_pers <- lrtest(lm.condoms_pers, lm.condoms_pers_noregion)
  lrt.condoms_pers
  
```

Region is __`r ifelse(lrt.condoms_pers$'Pr(>Chisq)'[2]<siglevel, print("significantly"), print("not"))` associated__ with condom use in persistent partnerships after adjusting for ego age and race.

### Instantaneous partners
```{r condoms_inst}

 #Look at the number of observations by region that are non-missing for this outcome and for model predictors
  table(sample$region[!is.na(sample$race_eth_m) & !is.na(sample$condoms_inst)])

  #Full model  
  glm.condoms_inst <- glm(condoms_inst ~ age_cat + race_eth_m.reg + region.bKC + age_cat*region.bKC + race_eth_m.reg*region.bKC, family=binomial(link="logit"), data=sample)
  #Model without region
  glm.condoms_inst_noregion <- glm(condoms_inst ~ age_cat + race_eth_m.reg, family=binomial(link="logit"), data=sample)

  lrt.condoms_inst <- lrtest(glm.condoms_inst, glm.condoms_inst_noregion)
  lrt.condoms_inst
  
```

Region is __`r ifelse(lrt.condoms_inst$'Pr(>Chisq)'[2]<siglevel, print("significantly"), print("not"))` associated__ with condom use in instantaneous partnerships after adjusting for ego age and race.

## PrEP use
To look at differences in PrEP use, the outcome is reported current use of PrEP _among those for whom PrEP is recommended_.
```{r prep}

 #Look at the number of observations by region that are non-missing for this outcome and for model predictors
  table(sample$region[!is.na(sample$race_eth_m) & !is.na(sample$prep_use_curr) & sample$prepelig_r %in% "Recommend"])

  #Full model  
  glm.prep <- glm(prep_use_curr ~ age_cat + race_eth_m.reg + region.bKC + age_cat*region.bKC + race_eth_m.reg*region.bKC, family=binomial(link="logit"), data=sample, subset=prepelig_r %in% "Recommend")
  #Model without region
  glm.prep_noregion <- glm(prep_use_curr ~ age_cat + race_eth_m.reg, family=binomial(link="logit"), data=sample, subset=prepelig_r %in% "Recommend")

  lrt.prep <- lrtest(glm.prep, glm.prep_noregion)
  lrt.prep
  
```

Region is __`r ifelse(lrt.prep$'Pr(>Chisq)'[2]<siglevel, print("significantly"), print("not"))` associated__ with PrEP use among those for whom it is recommeneded after adjusting for ego age and race.