# Test implications of balancing mixing matrices for degree
```{r, echo=FALSE, include=FALSE}
####################################################################################
# Setup
####################################################################################
#-----------------------------------------------------------------------------------
# Load packages
#-----------------------------------------------------------------------------------

    library("tidyverse")
    library("ggplot2")
    library("survey")
    library("knitr")
    library("xtable")
    library("kableExtra")

#-----------------------------------------------------------------------------------
# Load data
#-----------------------------------------------------------------------------------
    load(file="/homes/dpwhite/R/GitHub Repos/WHAMP/Parameter estimation/Data/InternetSurveySample.Rdata")
    load(file="/homes/dpwhite/R/GitHub Repos/WHAMP/Parameter estimation/Data/InternetSurvey_reweighted_all.Rdata")
    load(file="/homes/dpwhite/R/GitHub Repos/WHAMP/Parameter estimation/Data/InternetSurvey_reweighted_neg.Rdata")
    load(file="/homes/dpwhite/R/GitHub Repos/WHAMP/Parameter estimation/Data/degreedists.Rdata")
    load(file="/homes/dpwhite/R/GitHub Repos/WHAMP/Parameter estimation/Data/nodefactor_mp.Rdata")

# Set options
    opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE)
    options(knitr.table.format = "html") 
  
```
We calculate the mean degree by race/ethnicity from ego's reported counts of ongoing main and ongoing persistent partnerships, shown below.

```{r}
meandeg.main <- c(degree$deg.mp.H[2,4], degree$deg.mp.B[2,4], degree$deg.mp.O[2,4])
meandeg.pers <- c(sum(degree$deg.mp.H[3,2], 2*degree$deg.mp.H[3,3]), sum(degree$deg.mp.B[3,2], 2*degree$deg.mp.B[3,3]), sum(degree$deg.mp.O[3,2], 2*degree$deg.mp.O[3,3]))

meandegXrace <- cbind.data.frame("Race/ethnicity" = c("Hispanic", "Black", "Other"), "Main" = meandeg.main, "Pers" = meandeg.pers)

kable(meandegXrace, col.names=c("", "Main", "Persistent"), digits = c(4,4), caption="Mean main and persistent degree by race/ethnicity") %>% kable_styling(full_width=F, position="center")
```
However, to get target statistics for `nodefactor` terms and racial/ethnic mixing, we balance the mixing matrices. To do this, we obtain row percentages for mixing reported with the most recent partner, multiply these row percentages by mean degree, multiply this product by the target population size of each group, and then take the mean of the off-diagonal elements to balance. In the resulting balanced mixing matrices, the mean degree for each racial/ethnic group does not match the mean degree based on ego's reported number of ongoing partnerships, shown above.
```{r}
##MAIN PARTNERSHIPS
#Conditional row probabilities
  racemix_main <- prop.table(svytable(~hbo + mrp_hbo, sample_rake_all[sample_rake_all$variables$mrp_type_ongoing %in% "Main"], round=FALSE),1)

  #Mean degree by race 
    meandegm.H <- degree$deg.mp.H[2,4]
    meandegm.B <- degree$deg.mp.B[2,4]
    meandegm.O <- degree$deg.mp.O[2,4]
    
  #N by race in reweighted sample (scaled back to the size of the original sample) -- scaling to the total N assumes that those with missing data on degree or who didn't provide the age of their most recent partner are msising at random
    nXrace <- svytable(~hbo, sample_rake_all, Ntotal=dim(sample)[1], round=FALSE)

  #Reweighted mixing matrix, accounting for mean degree
  racemix_main_rwt <- matrix(c(racemix_main[1,]*meandegm.H*nXrace[1], racemix_main[2,]*meandegm.B*nXrace[2], racemix_main[3,]*meandegm.O*nXrace[3]), byrow=TRUE, nrow=3)
  racemix_main_rwt <- as.data.frame(racemix_main_rwt, row.names=c("Hispanic", "Black", "Other"))
  names(racemix_main_rwt) <- c("Hispanic", "Black", "Other")
  
  #Take average of off-diagonals to balance
  racemix_main_bal <- as.data.frame(matrix(c("HH"=racemix_main_rwt[1,1], "HB" = mean(c(racemix_main_rwt[1,2], racemix_main_rwt[2,1])), "HO" = mean(c(racemix_main_rwt[1,3], racemix_main_rwt[3,1])), "BH" = mean(c(racemix_main_rwt[1,2], racemix_main_rwt[2,1])), "BB" = racemix_main_rwt[2,2], "BO" = mean(c(racemix_main_rwt[2,3], racemix_main_rwt[3,2])), "OH" = mean(c(racemix_main_rwt[1,3], racemix_main_rwt[3,1])), "OB" = mean(c(racemix_main_rwt[2,3], racemix_main_rwt[3,2])), "OO" = racemix_main_rwt[3,3]), nrow=3, ncol=3, byrow=TRUE, dimnames=list(c("Hispanic", "Black", "Other"), c("Hispanic", "Black", "Other"))))

  # Caculate the implied mean degree by race/ethnicity
  meandegmXrace.bal <- c(sum(racemix_main_bal[1,])/nXrace[1], sum(racemix_main_bal[2,])/nXrace[2], sum(racemix_main_bal[3,])/nXrace[3])
  
## PERSISTENT PARTNERSHIPS
  #Conditional row probabilities - using data from both ongoing persistent and most recent one-time partners
  racemix_pers <- prop.table(svytable(~hbo + mrp_hbo, sample_rake_all[sample_rake_all$variables$mrp_type_ongoing %in% "Persistent" | sample_rake_all$variables$mrp_type_r %in% "One time"], round=FALSE),1)

#Mean degree by race/ethnicity
    meandegp.H <- degree$deg.mp.H[3,2] + 2*degree$deg.mp.H[3,3]   
    meandegp.B <- degree$deg.mp.B[3,2] + 2*degree$deg.mp.B[3,3]
    meandegp.O <- degree$deg.mp.O[3,2] + 2*degree$deg.mp.O[3,3]

  #Reweighted mixing matrix, accounting for mean degree
  racemix_pers_rwt <- matrix(c(racemix_pers[1,]*meandegp.H*nXrace[1], racemix_pers[2,]*meandegp.B*nXrace[2], racemix_pers[3,]*meandegp.O*nXrace[3]), byrow=TRUE, nrow=3)
  racemix_pers_rwt <- as.data.frame(racemix_pers_rwt, row.names=c("Hispanic", "Black", "Other"))
  names(racemix_pers_rwt) <- c("Hispanic", "Black", "Other")
  
  #Take average of off-diagonals to balance
  racemix_pers_bal <- as.data.frame(matrix(c("HH"=racemix_pers_rwt[1,1], "HB" = mean(c(racemix_pers_rwt[1,2], racemix_pers_rwt[2,1])), "HO" = mean(c(racemix_pers_rwt[1,3], racemix_pers_rwt[3,1])), "BH" = mean(c(racemix_pers_rwt[1,2], racemix_pers_rwt[2,1])), "BB" = racemix_pers_rwt[2,2], "BO" = mean(c(racemix_pers_rwt[2,3], racemix_pers_rwt[3,2])), "OH" = mean(c(racemix_pers_rwt[1,3], racemix_pers_rwt[3,1])), "OB" = mean(c(racemix_pers_rwt[2,3], racemix_pers_rwt[3,2])), "OO" = racemix_pers_rwt[3,3]), nrow=3, ncol=3, byrow=TRUE, dimnames=list(c("Hispanic", "Black", "Other"), c("Hispanic", "Black", "Other"))))

   # Caculate the implied mean degree by race/ethnicity
  meandegpXrace.bal <- c(sum(racemix_pers_bal[1,])/nXrace[1], sum(racemix_pers_bal[2,])/nXrace[2], sum(racemix_pers_bal[3,])/nXrace[3])
 
  meandegXrace.bal <- cbind.data.frame("Main" = meandegmXrace.bal, "Pers" = meandegpXrace.bal)

  
## KABLES  
  kable(racemix_main_bal, align=c("c", "c", "c"), digits=c(1, 1, 1), caption = "Balanced mixing matrix for main partnerships") %>% kable_styling(full_width=F, position="center") %>% column_spec(1, bold=T, color="black", width="2cm") %>% column_spec(2:4, width = "2cm")

  kable(racemix_pers_bal, align=c("c", "c", "c"), digits=c(1, 1, 1), caption = "Balanced mixing matrix for persistent partnerships") %>% kable_styling(full_width=F, position="center") %>% column_spec(1, bold=T, color="black", width="2cm") %>% column_spec(2:4, width = "2cm")
  
  kable(meandegXrace.bal, col.names=c("Main", "Persistent"), digits = c(4,4), caption="Mean main and persistent degree by race/ethnicity from the balanced matrices") %>% kable_styling(full_width=F, position="center")

```

The balanced mixing matrix is used for calculation of statistics for the proportion of partnerships that are homophilous on race/ethnicity and the target statistics for `nodefactor` on race/ethnicity. So we'll look at how much this issue matters for the implied network features.

We'll assume we have a newtork of size 10,000. Based on the overall degree distribution, we'd have `r round((degree$deg.mp[2,4]*10000)/2)` main and `r round((sum(degree$deg.mp[3,2], 2*degree$deg.mp[3,3])*10000)/2)` persistent edges in the network. The table below shows the number of times nodes of each race/ethnicity would appear in an edge, calculated based on the mean degrees by race/ethnicity.

```{r}
# Newtork size
n <- 10000

# Number in each racial/ethic group
nH <- n*prop.table(svytable(~hbo, sample_rake_all, round=FALSE))[1]
nB <- n*prop.table(svytable(~hbo, sample_rake_all, round=FALSE))[2]
nO <- n*prop.table(svytable(~hbo, sample_rake_all, round=FALSE))[3]

# Main and persistent edges
edges.m <- (degree$deg.mp[2,4]*n)/2
degree.m.H <- (degree$deg.mp.H[2,4]*nH)
degree.m.B <- (degree$deg.mp.B[2,4]*nB)
degree.m.O <- (degree$deg.mp.O[2,4]*nO)

edges.p <- (sum(degree$deg.mp[3,2], 2*degree$deg.mp[3,3])*n)/2
degree.p.H <- (sum(degree$deg.mp.H[3,2], 2*degree$deg.mp.H[3,3])*nH)
degree.p.B <- (sum(degree$deg.mp.B[3,2], 2*degree$deg.mp.B[3,3])*nB)
degree.p.O <- (sum(degree$deg.mp.o[3,2], 2*degree$deg.mp.O[3,3])*nO)

degree <- cbind.data.frame("Main" = as.vector(c(degree.m.H, degree.m.B, degree.m.O)), "Persistent" = as.vector(c(degree.p.H, degree.p.B, degree.p.O)))
rownames(degree) <- c("Hispanic", "Black", "Other")

 kable(degree, col.names=c("Main", "Persistent"), digits = c(0, 0), caption="Degree by race/ethnicity") %>% kable_styling(full_width=F, position="center")

```

Based on the balanced mixing matrix, the target statistics for `nodefactor("race")` in the main network would be as follows:

```{r}
nodefactor_mp$prop.inmainXrace*(2*edges.m)
```

