---
output:
  html_document:
    toc: true
    toc_float: true
---
# Network model diagnostics - balanced
This file shows diagnostics for models fit using balanced racial/ethnic mixing matrices and degree terms adjusted to correspond to the balanced mixing matrices.

## Load packages and model fits
```{r, warning=FALSE}
rm(list = ls())
suppressMessages(library("EpiModelHIV"))

load(file = "/homes/dpwhite/R/GitHub Repos/WHAMP/WHAMP scenarios/est/fit.bal.whamp.rda")

```

## Fit times 
Main network: `r round(runtime_min_fit_main, 1)` minutes
Persistent: `r round(runtime_min_fit_pers, 1)` minutes
Instantaneous: `r round(runtime_min_fit_inst, 1)` minutes

## MCMC diagnostics

### Main
```{r}
mcmc.diagnostics(est.bal[[1]])
```

### Persistent
```{r}
mcmc.diagnostics(est.bal[[2]])
```

### Instantaneous
```{r}
mcmc.diagnostics(est.bal[[3]])
```

## Suffificient statistics

### Main
```{r}
est.bal[[1]]
```

### Persistent
```{r}
est.bal[[2]]
```

### Instantaneous
```{r}
est.bal[[3]]
```

## Summary of model fit

### Main
```{r}
summary(est.bal[[1]])
```

### Persistent
```{r}
summary(est.bal[[2]])
```

### Instantaneous
```{r}
summary(est.bal[[3]])
```

## Network diagnostics

### Main
```{r}
(dx_main <- netdx(est.bal[[1]], nsims = 10, nsteps = 1000, ncores = 4))
plot(dx_main, type="formation")
plot(dx_main, type="duration")
plot(dx_main, type="dissolution")
```

### Persistent
```{r}
(dx_pers <- netdx(est.bal[[2]], nsims = 10, nsteps = 1000, ncores = 4))
plot(dx_pers, type="formation")
plot(dx_pers, type="duration")
plot(dx_pers, type="dissolution")
```

### Instantaneous
```{r}
(dx_inst <- netdx(est.bal[[3]], nsims = 10, nsteps = 1000, ncores = 4))
plot(dx_inst, type="formation")
```


