---
output:
  html_document:
    toc: true
    toc_float: true
---
# Network model estimation and diagnostics - balanced, nested models
This file uses the balanced mixing matrices and degree distributions/rate of instantaneous partnerships adjusted to correspond to the balanced mixing matrices. To understand the effect of adding specific terms, we build up the models term by term to see where the fit issues emerge.

## Load packages and define options
```{r, warning=FALSE}
rm(list = ls())
suppressMessages(library("EpiModelHIV"))
```

## Calculate target statistics
```{r, message = FALSE}

# Time unit for simulation, relative to 1 day
time.unit <- 7

#Network size
num <- 10000

# Population size by race and region
    ##--ORIGINAL CODE - DELETE WHEN FINISH DE-BUGGING
    num.B <- 5000
    num.W <- 5000
  ## Vector with the proportion of Hispanic, black, and other race/ethnicity men in King County, other western WA, and eastern WA
  prop.race.region <- sumto1(c(0.0549, 0.0421, 0.4739, 0.0309, 0.0166, 0.2807, 0.0222, 0.0021, 0.0767))
  race.region <- apportion_lr(num, c("H.KC", "B.KC", "O.KC", "H.OW", "B.OW", "O.OW", "H.EW", "B.EW", "O.EW"),
                             prop.race.region)
  
  num.H.KC <- sum(race.region %in% "H.KC")
  num.B.KC <- sum(race.region %in% "B.KC")
  num.O.KC <- sum(race.region %in% "O.KC")
  num.H.OW <- sum(race.region %in% "H.OW")
  num.B.OW <- sum(race.region %in% "B.OW")
  num.O.OW <- sum(race.region %in% "O.OW")
  num.H.EW <- sum(race.region %in% "H.EW")
  num.B.EW <- sum(race.region %in% "B.EW")
  num.O.EW <- sum(race.region %in% "O.EW")
  
# Age structure (proportion in each age group 18-24, 25-29... 55-59)
agestr <- sumto1(c(0.1594, 0.1319, 0.1292, 0.1173, 0.1183, 0.1148, 0.1071, 0.122))
    
# mean/pers degree distributions matrices.
deg.mp <- matrix(sumto1(c(0.4108, 0.0735, 0.0672, 
                          0.3458, 0.0494, 0.0532)), byrow = TRUE, nrow = 2)
deg.mp.H <- matrix(sumto1(c(0.2366, 0.1575, 0.0391,
                            0.3413, 0.1759, 0.0496)), byrow = TRUE, nrow = 2)
deg.mp.B <- matrix(sumto1(c(0.4923, 0.0814, 0.0839, 
                            0.2307, 0.0395, 0.0723)), byrow = TRUE, nrow = 2)
deg.mp.O <- matrix(sumto1(c(0.4275, 0.062, 0.0696, 
                            0.3548, 0.0337, 0.0523)), byrow = TRUE, nrow = 2)
deg.mp.KC <- matrix(sumto1(c(0.3609, 0.0824, 0.0735, 
                             0.3792, 0.0464, 0.0577)), byrow = TRUE, nrow = 2)
deg.mp.OW <- matrix(sumto1(c(0.4885, 0.0688, 0.0517, 
                             0.289, 0.0502, 0.0518)), byrow = TRUE, nrow = 2)
deg.mp.EW <- matrix(sumto1(c(0.4186, 0.0621, 0.0806, 
                             0.364, 0.0401, 0.0346)), byrow = TRUE, nrow = 2)

# Instantaneous partner rates (Mean rate (degree) of inst partnerships per day by momentary main/pers degree)
  # (order: 0 main 0 pers, 0 main 1 pers, 0 main 2+ pers, 1 main 0 pers, 1 main 1 pers, 1 main 2+ pers)
mdeg.inst <- matrix(c(0.015734, 0.005987, 0.021057, 
                      0.007052, 0.009709, 0.032598), byrow = TRUE, nrow = 2) 

# Quintile distribution of overall instantaneous AI rates
qnts.18to49 <- c(0.0001, 0.000525, 0.005024, 0.054838) #set to 0.0001 if 0 to give non-zero prob
qnts.50to59 <- c(0.0001, 0.0001, 0.001551, 0.021283)  #set to 0.0001 if 0 to give non-zero prob

# Mean rate of instantaneous partnerships by race (black, Hispanic, other)
inst.bho <- c(0.0202, 0.012978, 0.012418)

# Mean rate of instantaneous partnerships by region (EW, KC, OW)
inst.region <- c(0.011216, 0.014955, 0.01)

# Proportion in same-race partnerships (main, pers, inst)
prop.hom.mpi.H <- c(0.4229, 0.1631, 0.1787)
prop.hom.mpi.B <- c(0.2939, 0.0701, 0.0853)
prop.hom.mpi.O <- c(0.8911, 0.7847, 0.7666)

# Mean age diffs (main, pers, inst)
sqrt.adiff.mpi <- c(0.539, 0.7619, 0.7741)

# Region mixing (main, pers, inst)
prop.hom.region.mpi <- c(1.0, 0.8, 0.8)

# Mean durations
durs.main <- 1020
durs.pers <- 192

# Age-sex-specific mortality rates
ages <- 18:59

asmr.B <- c(rep(0, 17),
            1-(1-c(rep(0.00159, 7),
                   rep(0.00225, 10),
                   rep(0.00348, 25)))^(1/(365/time.unit)), 1) #-- To make old code work with new age str, I added 20 to the last deaths vector

asmr.W <- c(rep(0, 17),
            1-(1-c(rep(0.00103, 7),
                   rep(0.00133, 10),
                   rep(0.00214, 25)))^(1/(365/time.unit)), 1) #-- To make old code work with new age str, I added 20 to the last deaths vector

asmr.H..wa <- c(rep(0, 17),
            1-(1-c(rep(0.00089, 2),
                   rep(0.00107, 5),
                   rep(0.00112, 5),
                   rep(0.00123, 5),
                   rep(0.00126, 5),
                   rep(0.00186, 5),
                   rep(0.00207, 5),
                   rep(0.00343, 5),
                   rep(0.00495, 5)))^(1/(365/time.unit)), 1)

asmr.B..wa <- c(rep(0, 17),
            1-(1-c(rep(0.00168, 2),
                   rep(0.00117, 5),
                   rep(0.00161, 5),
                   rep(0.00169, 5),
                   rep(0.00267, 5),
                   rep(0.00224, 5),
                   rep(0.00428, 5),
                   rep(0.00619, 5),
                   rep(0.01311, 5)))^(1/(365/time.unit)), 1)

asmr.O..wa <- c(rep(0, 17),
            1-(1-c(rep(0.00068, 2),
                   rep(0.00101, 5),
                   rep(0.00119, 5),
                   rep(0.00138, 5),
                   rep(0.00161, 5),
                   rep(0.00198, 5),
                   rep(0.00306, 5),
                   rep(0.00517, 5),
                   rep(0.00781, 5)))^(1/(365/time.unit)), 1)

# I, R, V role frequencies
role.prob <- c(0.15, 0.205, 0.645)


# Create meanstats
st <- calc_nwstats_msm_whamp(
  method = 1,
  time.unit = time.unit,
  num.B = num.B,
  num.W = num.W,
  num.H.KC = num.H.KC,
  num.B.KC = num.B.KC,
  num.O.KC = num.O.KC,
  num.H.OW = num.H.OW,
  num.B.OW = num.B.OW,
  num.O.OW = num.O.OW,
  num.H.EW = num.H.EW,
  num.B.EW = num.B.EW,
  num.O.EW = num.O.EW,
  agestr = agestr,
  deg.mp = deg.mp,
  deg.mp.H = deg.mp.H,
  deg.mp.B = deg.mp.B,
  deg.mp.O = deg.mp.O,
  deg.mp.KC = deg.mp.KC,
  deg.mp.OW = deg.mp.OW,
  deg.mp.EW = deg.mp.EW,
  mdeg.inst = mdeg.inst,
  qnts.18to49 = qnts.18to49,
  qnts.50to59 = qnts.50to59,
  inst.bho = inst.bho,
  inst.region = inst.region,
  prop.hom.mpi.H = prop.hom.mpi.H,
  prop.hom.mpi.B = prop.hom.mpi.B,
  prop.hom.mpi.O = prop.hom.mpi.O,
  sqrt.adiff.mpi = sqrt.adiff.mpi,
  prop.hom.region.mpi,
  diss.main = ~offset(edges),
  diss.pers = ~offset(edges),
  durs.main = durs.main,
  durs.pers = durs.pers,
  ages = ages,
  asmr.B <- asmr.B,
  asmr.W <- asmr.W,
  asmr.H..wa = asmr.H..wa,
  asmr.B..wa = asmr.B..wa,
  asmr.O..wa = asmr.O..wa,
  role.prob = role.prob)

```

## Main partner network

### Fit models
```{r, message=FALSE}

  # Initialize network
  nw.main <- base_nw_msm_whamp(st)
  
  # Assign degree
  nw.main <- assign_degree_whamp(nw.main, deg.type = "pers", nwstats = st)

  # Formulas and fits
  
   ## 1. Edges + nodefactor terms -------------------------------------------
    formation.m1 <- ~edges +
                  nodefactor("deg.pers") +
                  nodefactor("race..wa", base=3) + 
                  nodefactor("region", base=2) +
                  offset(nodematch("role.class", diff = TRUE, keep = 1:2))

    fit.m1 <- netest(nw.main,
                    formation = formation.m1,
                    target.stats = st$stats.m[-(c(8:11))],
                    coef.form = c(-Inf, -Inf),
                    coef.diss = st$coef.diss.m,
                    constraints = ~bd(maxout = 1),
                    set.control.ergm = control.ergm(MPLE.max.dyad.types = 1e10,
                                                    init.method = "zeros",
                                                    MCMC.interval = 1e+6,
                                                    MCMLE.maxit = 250))

    ## 2. Edges + nodefactor terms + absdiff-------------------------------------------
    formation.m2 <- ~edges +
                  nodefactor("deg.pers") +
                  nodefactor("race..wa", base=3) + 
                  nodefactor("region", base=2) +
                  absdiff("sqrt.age") +
                  offset(nodematch("role.class", diff = TRUE, keep = 1:2))

    fit.m2 <- netest(nw.main,
                    formation = formation.m2,
                    target.stats = st$stats.m[-(c(8:10))],
                    coef.form = c(-Inf, -Inf),
                    coef.diss = st$coef.diss.m,
                    constraints = ~bd(maxout = 1),
                    set.control.ergm = control.ergm(MPLE.max.dyad.types = 1e10,
                                                    init.method = "zeros",
                                                    MCMC.interval = 1e+6,
                                                    MCMLE.maxit = 250))
    
    ## 3. Edges + nodefactor terms + absdiff + racematch--------------------------------------
    formation.m3 <- ~edges +
                  nodefactor("deg.pers") +
                  nodefactor("race..wa", base=3) + 
                  nodefactor("region", base=2) +
                  nodematch("race..wa", diff=TRUE) +
                  absdiff("sqrt.age") +
                  offset(nodematch("role.class", diff = TRUE, keep = 1:2))

    fit.m3 <- netest(nw.main,
                    formation = formation.m3,
                    target.stats = st$stats.m,
                    coef.form = c(-Inf, -Inf),
                    coef.diss = st$coef.diss.m,
                    constraints = ~bd(maxout = 1),
                    set.control.ergm = control.ergm(MPLE.max.dyad.types = 1e10,
                                                    init.method = "zeros",
                                                    MCMC.interval = 1e+6,
                                                    MCMLE.maxit = 250))
    ## 4. Edges + nodefactor terms + absdiff + racematch + offset for region matching-------
    formation.m4 <- ~edges +
                  nodefactor("deg.pers") +
                  nodefactor("race..wa", base=3) + 
                  nodefactor("region", base=2) +
                  nodematch("race..wa", diff=TRUE) +
                  absdiff("sqrt.age") +
                  offset(nodematch("role.class", diff = TRUE, keep = 1:2)) +
                  offset(nodemix("region", base = c(1,3,6)))


    fit.m4 <- netest(nw.main,
                    formation = formation.m4,
                    target.stats = st$stats.m,
                    coef.form = c(-Inf, -Inf, -Inf, -Inf, -Inf),
                    coef.diss = st$coef.diss.m,
                    constraints = ~bd(maxout = 1),
                    set.control.ergm = control.ergm(MPLE.max.dyad.types = 1e10,
                                                    init.method = "zeros",
                                                    MCMC.interval = 1e+6,
                                                    MCMLE.maxit = 250))
```
### MCMC diagnostics

```{r}
# Edges and nodefactor tersm
mcmc.diagnostics(fit.m1)
# Edges and nodefactor and absdiff
mcmc.diagnostics(fit.m2)
# Edges and nodefactor and absdiff and nodematch race
mcmc.diagnostics(fit.m3)
# Edges and nodefactor and absdiff and nodematch race and offset for nodematch region
mcmc.diagnostics(fit.m4)
```

### Suffificient statistics
```{r}
# Edges and nodefactor tersm
fit.m1
# Edges and nodefactor and absdiff
fit.m2
# Edges and nodefactor and absdiff and nodematch race
fit.m3
# Edges and nodefactor and absdiff and nodematch race and offset for nodematch region
fit.m4
```

### Summary of model fits
```{r}
# Edges and nodefactor tersm
summary(fit.m1)
# Edges and nodefactor and absdiff
summary(fit.m2)
# Edges and nodefactor and absdiff and nodematch race
summary(fit.m3)
# Edges and nodefactor and absdiff and nodematch race and offset for nodematch region
summary(fit.m4)

```

### Network diagnostics
```{r}
# Edges and nodefactor tersm
(dx_main1 <- netdx(fit.m1, nsims = 10, nsteps = 1000, ncores = 4))
plot(dx_main1, type="formation")
plot(dx_main1, type="duration")
plot(dx_main1, type="dissolution")

# Edges and nodefactor and absdiff
(dx_main2 <- netdx(fit.m2, nsims = 10, nsteps = 1000, ncores = 4))
plot(dx_main2, type="formation")
plot(dx_main2, type="duration")
plot(dx_main2, type="dissolution")

# Edges and nodefactor and absdiff and nodematch race
(dx_main3 <- netdx(fit.m3, nsims = 10, nsteps = 1000, ncores = 4))
plot(dx_main3, type="formation")
plot(dx_main3, type="duration")
plot(dx_main3, type="dissolution")

# Edges and nodefactor and absdiff and nodematch race and offset for nodematch region
(dx_main4 <- netdx(fit.m4, nsims = 10, nsteps = 1000, ncores = 4))
plot(dx_main4, type="formation")
plot(dx_main4, type="duration")
plot(dx_main4, type="dissolution")

```

## Persistent partner network

### Fit models
```{r, message=FALSE}
   # Initialize network
    nw.pers <- nw.main

    # Assign degree
    nw.pers <- assign_degree_whamp(nw.pers, deg.type = "main", nwstats = st)
    
    # Formulas and fits
    ## 1. Edges + nodefactor terms -------------------------------------------
    formation.p1 <- ~edges +
                    nodefactor("deg.main") +
                    nodefactor("race..wa", base=3) + 
                    nodefactor("region", base=2) +
                    offset(nodematch("role.class", diff = TRUE, keep = 1:2))
    
    fit.p1 <- netest(nw.pers,
                    formation = formation.p1,
                    target.stats = st$stats.p[1:6],
                    coef.form = c(-Inf, -Inf),
                    coef.diss = st$coef.diss.p,
                    constraints = ~bd(maxout = 2), 
                    edapprox = TRUE,
                    set.control.ergm = control.ergm(MPLE.max.dyad.types = 1e9,
                                                init.method = "zeros",
                                                MCMC.interval = 1e+6,
                                                MCMLE.maxit = 250))

    ## 2. Edges + nodefactor terms + nodematch race and absdiff---------------------
    formation.p2 <- ~edges +
                    nodefactor("deg.main") +
                    nodefactor("race..wa", base=3) + 
                    nodefactor("region", base=2) +
                    nodematch("race..wa", diff=TRUE) +
                    absdiff("sqrt.age") +
                    offset(nodematch("role.class", diff = TRUE, keep = 1:2))
    
      fit.p2 <- netest(nw.pers,
                    formation = formation.p2,
                    target.stats = st$stats.p[-c(7,11)],
                    coef.form = c(-Inf, -Inf),
                    coef.diss = st$coef.diss.p,
                    constraints = ~bd(maxout = 2), 
                    edapprox = TRUE,
                    set.control.ergm = control.ergm(MPLE.max.dyad.types = 1e9,
                                                init.method = "zeros",
                                                MCMC.interval = 1e+6,
                                                MCMLE.maxit = 250))
    
    ## 3. Edges + nodefactor terms + nodematch race and absdiff + concurrent------------------
        formation.p3 <- ~edges +
                    nodefactor("deg.main") +
                    nodefactor("race..wa", base=3) + 
                    nodefactor("region", base=2) +
                    concurrent +
                    nodematch("race..wa", diff=TRUE) +
                    absdiff("sqrt.age") +
                    offset(nodematch("role.class", diff = TRUE, keep = 1:2))
    
      fit.p3 <- netest(nw.pers,
                    formation = formation.p3,
                    target.stats = st$stats.p[-11],
                    coef.form = c(-Inf, -Inf),
                    coef.diss = st$coef.diss.p,
                    constraints = ~bd(maxout = 2), 
                    edapprox = TRUE,
                    set.control.ergm = control.ergm(MPLE.max.dyad.types = 1e9,
                                                init.method = "zeros",
                                                MCMC.interval = 1e+6,
                                                MCMLE.maxit = 250))
      
    ## 4. Edges + nodefactor terms + absdiff + race mixing + region match-----
      formation.p4 <- ~edges +
                    nodefactor("deg.main") +
                    nodematch("race..wa", diff=TRUE) +
                    nodematch("region", diff=FALSE) +
                    concurrent +
                    absdiff("sqrt.age") +
                    offset(nodematch("role.class", diff = TRUE, keep = 1:2))
    
      fit.p4 <- netest(nw.pers,
                    formation = formation.p4,
                    target.stats = st$stats.p,
                    coef.form = c(-Inf, -Inf),
                    coef.diss = st$coef.diss.p,
                    constraints = ~bd(maxout = 2), 
                    edapprox = TRUE,
                    set.control.ergm = control.ergm(MPLE.max.dyad.types = 1e9,
                                                init.method = "zeros",
                                                MCMC.interval = 1e+6,
                                                MCMLE.maxit = 250))
```

### MCMC diagnostics

```{r}
# Edges and nodefactor terms
mcmc.diagnostics(fit.p1)
# Edges, nodefactor, and race and age mixing
mcmc.diagnostics(fit.p2)
# Edges, nodefactor, race and age mixing, and concurrent
mcmc.diagnostics(fit.p3)
# Edges, nodefactor, race and age mixing, concurrent, and regional mixing
mcmc.diagnostics(fit.p4)
```

### Suffificient statistics
```{r}
# Edges and nodefactor terms
fit.p1
# Edges, nodefactor, and race and age mixing
fit.p2
# Edges, nodefactor, race and age mixing, and concurrent
fit.p3
# Edges, nodefactor, race and age mixing, concurrent, and regional mixing
fit.p4

```

### Summary of model fits
```{r}
# Edges and nodefactor terms
summary(fit.p1)
# Edges, nodefactor, and race and age mixing
summary(fit.p2)
# Edges, nodefactor, race and age mixing, and concurrent
summary(fit.p3)
# Edges, nodefactor, race and age mixing, concurrent, and regional mixing
summary(fit.p4)

```

### Network diagnostics
```{r}
# Edges and nodefactor tersm
(dx_pers1 <- netdx(fit.p1, nsims = 10, nsteps = 1000, ncores = 4))
plot(dx_pers1, type="formation")
plot(dx_pers1, type="duration")
plot(dx_pers1, type="dissolution")

# Edges and nodefactor and absdiff
(dx_pers2 <- netdx(fit.p2, nsims = 10, nsteps = 1000, ncores = 4))
plot(dx_pers2, type="formation")
plot(dx_pers2, type="duration")
plot(dx_pers2, type="dissolution")

# Edges and nodefactor and absdiff and nodematch race
(dx_pers3 <- netdx(fit.p3, nsims = 10, nsteps = 1000, ncores = 4))
plot(dx_pers3, type="formation")
plot(dx_pers3, type="duration")
plot(dx_pers3, type="dissolution")

# Edges and nodefactor and absdiff and nodematch race and offset for nodematch region
(dx_pers4 <- netdx(fit.p4, nsims = 10, nsteps = 1000, ncores = 4))
plot(dx_pers4, type="formation")
plot(dx_pers4, type="duration")
plot(dx_pers4, type="dissolution")

```

## Instantaneous partner network

### Fit models
```{r, message=FALSE}

   # Initialize network
    nw.inst <- nw.main

    # Assign degree
    nw.inst <- set.vertex.attribute(nw.inst, "deg.main", nw.pers %v% "deg.main")
    nw.inst <- set.vertex.attribute(nw.inst, "deg.pers", nw.main %v% "deg.pers")
    table(nw.inst %v% "deg.main", nw.inst %v% "deg.pers")
        
    # Formulas and fits
    ## 1. Edges + nodefactor degree, race, and region --------------------------------------
    formation.i1 <- ~edges +
                    nodefactor(c("deg.main", "deg.pers")) +
                    nodefactor("race..wa", base=3) + 
                    nodefactor("region", base=2) +
                    offset(nodematch("role.class", diff = TRUE, keep = 1:2)) 
    
    fit.i1 <- netest(nw.inst,
                    formation = formation.i1,
                    target.stats = st$stats.i[c(1:6, 14:17)],
                    coef.form = c(-Inf, -Inf),
                    coef.diss = dissolution_coefs(~offset(edges), 1),
                    set.control.ergm = control.ergm(MPLE.max.dyad.types = 1e9,
                                                    MCMC.interval = 1e+6,
                                                    MCMLE.maxit = 250))

    ## 2. Edges + nodefactor degree, race, and region + nodefactor risk group-----------------
      formation.i2 <- ~edges +
                    nodefactor(c("deg.main", "deg.pers")) +
                    nodefactor("riskg") +
                    nodefactor("race..wa", base=3) + 
                    nodefactor("region", base=2) +
                    offset(nodematch("role.class", diff = TRUE, keep = 1:2)) 
    
    fit.i2 <- netest(nw.inst,
                    formation = formation.i2,
                    target.stats = st$stats.i[1:17],
                    coef.form = c(-Inf, -Inf),
                    coef.diss = dissolution_coefs(~offset(edges), 1),
                    set.control.ergm = control.ergm(MPLE.max.dyad.types = 1e9,
                                                    MCMC.interval = 1e+6,
                                                    MCMLE.maxit = 250))
    
    ## 3. Edges + nodefactor degree, race, and region + nodefactor risk group + nodematch race and absdiff age------
      formation.i3 <- ~edges +
                    nodefactor(c("deg.main", "deg.pers")) +
                    nodefactor("riskg") +
                    nodefactor("race..wa", base=3) + 
                    nodefactor("region", base=2) +
                    nodematch("race..wa", diff=TRUE) +
                    absdiff("sqrt.age") +
                    offset(nodematch("role.class", diff = TRUE, keep = 1:2)) 
    
    fit.i3 <- netest(nw.inst,
                    formation = formation.i3,
                    target.stats = st$stats.i[-21],
                    coef.form = c(-Inf, -Inf),
                    coef.diss = dissolution_coefs(~offset(edges), 1),
                    set.control.ergm = control.ergm(MPLE.max.dyad.types = 1e9,
                                                    MCMC.interval = 1e+6,
                                                    MCMLE.maxit = 250))
      
    ## 4. Edges + nodefactor degree, race, and region + nodefactor risk group + nodematch race and absdiff age + nodematch region-----
      formation.i4 <- ~edges +
                    nodefactor(c("deg.main", "deg.pers")) +
                    nodefactor("riskg") +
                    nodefactor("race..wa", base=3) + 
                    nodefactor("region", base=2) +
                    nodematch("race..wa", diff=TRUE) +
                    nodematch("region", diff=FALSE) +
                    absdiff("sqrt.age") +
                    offset(nodematch("role.class", diff = TRUE, keep = 1:2)) 
    
    fit.i4 <- netest(nw.inst,
                    formation = formation.i4,
                    target.stats = st$stats.i,
                    coef.form = c(-Inf, -Inf),
                    coef.diss = dissolution_coefs(~offset(edges), 1),
                    set.control.ergm = control.ergm(MPLE.max.dyad.types = 1e9,
                                                    MCMC.interval = 1e+6,
                                                    MCMLE.maxit = 250))
```

### MCMC diagnostics

```{r}
# Edges and nodefactor terms
mcmc.diagnostics(fit.i1)
# Edges, nodefactor, and race and age mixing
mcmc.diagnostics(fit.i2)
# Edges, nodefactor, race and age mixing, and concurrent
mcmc.diagnostics(fit.i3)
# Edges, nodefactor, race and age mixing, concurrent, and regional mixing
mcmc.diagnostics(fit.i4)
```

### Suffificient statistics
```{r}
# Edges and nodefactor terms
fit.i1
# Edges, nodefactor, and race and age mixing
fit.i2
# Edges, nodefactor, race and age mixing, and concurrent
fit.i3
# Edges, nodefactor, race and age mixing, concurrent, and regional mixing
fit.i4

```

### Summary of model fits
```{r}
# Edges and nodefactor terms
summary(fit.i1)
# Edges, nodefactor, and race and age mixing
summary(fit.i2)
# Edges, nodefactor, race and age mixing, and concurrent
summary(fit.i3)
# Edges, nodefactor, race and age mixing, concurrent, and regional mixing
summary(fit.i4)

```

### Network diagnostics
```{r}
# Edges and nodefactor tersm
(dx_inst1 <- netdx(fit.i1, nsims = 10, nsteps = 1000, ncores = 4))
plot(dx_inst1, type="formation")
plot(dx_inst1, type="duration")
plot(dx_inst1, type="dissolution")

# Edges and nodefactor and absdiff
(dx_inst2 <- netdx(fit.i2, nsims = 10, nsteps = 1000, ncores = 4))
plot(dx_inst2, type="formation")
plot(dx_inst2, type="duration")
plot(dx_inst2, type="dissolution")

# Edges and nodefactor and absdiff and nodematch race
(dx_inst3 <- netdx(fit.i3, nsims = 10, nsteps = 1000, ncores = 4))
plot(dx_inst3, type="formation")
plot(dx_inst3, type="duration")
plot(dx_inst3, type="dissolution")

# Edges and nodefactor and absdiff and nodematch race and offset for nodematch region
(dx_inst4 <- netdx(fit.i4, nsims = 10, nsteps = 1000, ncores = 4))
plot(dx_inst4, type="formation")
plot(dx_inst4, type="duration")
plot(dx_inst4, type="dissolution")

```