# Test model fit

## Load packages and define options
```{r, warning=FALSE}
suppressMessages(library("EpiModelHIV"))
```

## Fit or load models
```{r, message=FALSE}
load <- TRUE
#load <- FALSE

if (load) {
  #Edit path to model fit object 
  load("/homes/dpwhite/R/GitHub Repos/WHAMP/WHAMP scenarios/est/fit.whamp.rda")
} else {
  #Load data
  load("/homes/dpwhite/R/GitHub Repos/WHAMP/WHAMP scenarios/est/nwstats.whamp.rda")
  
# Fit models
  
  ## 1. Main Model -----------------------------------------------------------
   
  # Initialize network
  nw.main <- base_nw_msm_whamp(st)
  
  # Assign degree
  nw.main <- assign_degree_whamp(nw.main, deg.type = "pers", nwstats = st)
  
  # Formulas
  formation.m <- ~edges +
                  nodefactor("deg.pers") +
                  nodefactor("race..wa", base=3) + 
                  nodefactor("region", base=2) +
                  nodematch("race..wa", diff=TRUE) +
                  absdiff("sqrt.age") +
                  offset(nodematch("role.class", diff = TRUE, keep = 1:2)) +
                  offset(nodemix("region", base = c(1,3,6)))

    # Start clock to calculate runtime
    startclock_main <- proc.time()
    
    # Fit model
    fit.m <- netest(nw.main,
                    formation = formation.m,
                    target.stats = st$stats.m,
                    coef.form = c(-Inf, -Inf, -Inf, -Inf, -Inf),
                    coef.diss = st$coef.diss.m,
                    constraints = ~bd(maxout = 1),
                    set.control.ergm = control.ergm(MPLE.max.dyad.types = 1e10,
                                                    init.method = "zeros",
                                                    MCMLE.maxit = 250))

    # Fit time
    runtime_min_fit_main <- (proc.time()-startclock_main)['elapsed']/60
    
        
  ## 2. Casual Model ---------------------------------------------------------

    # Initialize network
    nw.pers <- nw.main

    # Assign degree
    nw.pers <- assign_degree_whamp(nw.pers, deg.type = "main", nwstats = st)
    
    # Formulas
    formation.p <- ~edges +
                    nodefactor("deg.main") +
                    concurrent +
                    nodematch("race..wa", diff=TRUE) +
                    nodematch("region", diff=FALSE) +
                    absdiff("sqrt.age") +
                    offset(nodematch("role.class", diff = TRUE, keep = 1:2))

        
    # Start clock to calculate runtime
    startclock_pers <- proc.time()
    
    # Fit model
    fit.p <- netest(nw.pers,
                    formation = formation.p,
                    target.stats = st$stats.p,
                    coef.form = c(-Inf, -Inf),
                    coef.diss = st$coef.diss.p,
                    constraints = ~bd(maxout = 2), 
                    edapprox = TRUE,
                    set.control.ergm = control.ergm(MPLE.max.dyad.types = 1e9,
                                                init.method = "zeros",
                                                MCMLE.maxit = 250))

    # Fit time
    runtime_min_fit_pers <- (proc.time()-startclock_pers)['elapsed']/60
    

  ## Fit inst model ----------------------------------------------------------

    # Initialize network
    nw.inst <- nw.main

    # Assign degree
    nw.inst <- set.vertex.attribute(nw.inst, "deg.main", nw.pers %v% "deg.main")
    nw.inst <- set.vertex.attribute(nw.inst, "deg.pers", nw.main %v% "deg.pers")
    table(nw.inst %v% "deg.main", nw.inst %v% "deg.pers")
    
    # Formulas
   formation.i <- ~edges +
                    nodefactor(c("deg.main", "deg.pers")) +
                    nodefactor("riskg") +
                    nodematch("race..wa", diff=TRUE) +
                    nodematch("region", diff=FALSE) +
                    absdiff("sqrt.age") +
                    offset(nodematch("role.class", diff = TRUE, keep = 1:2)) 
    
    # Start clock to calculate runtime
    startclock_inst <- proc.time()
    
    # Fit model
    fit.i <- netest(nw.inst,
                    formation = formation.i,
                    target.stats = st$stats.i,
                    coef.form = c(-Inf, -Inf),
                    coef.diss = dissolution_coefs(~offset(edges), 1),
                    set.control.ergm = control.ergm(MPLE.max.dyad.types = 1e9,
                                                    MCMLE.maxit = 250))
    
     # Fit time
    runtime_min_fit_inst <- (proc.time()-startclock_inst)['elapsed']/60
    
    est <- list(fit.m, fit.p, fit.i)
}
```

## Fit times 
_(NA if loaded models that were fitted in the "02.estim.WHAMP.R" script)_

Main network: `r ifelse(load==FALSE,round(runtime_min_fit_main, 1),NA)` minutes
Persistent: `r ifelse(load==FALSE,round(runtime_min_fit_pers, 1),NA)` minutes
Instantaneous: `r ifelse(load==FALSE,round(runtime_min_fit_inst, 1),NA)` minutes

## Suffificient statistics

### Main
```{r}
if (load) {
  est[[1]]
} else {
fit.m
}
```

### Persistent
```{r}
if (load) {
  est[[2]]
} else {
fit.p
}
```

### Instantaneous
```{r}
if (load) {
  est[[3]]
} else {
fit.i
}
```

## Summary of model fit

### Main
```{r}
if (load) {
  summary(est[[1]])
} else {
summary(fit.m)
}
```

### Persistent
```{r}
if (load) {
  summary(est[[2]])
} else {
summary(fit.p)
}
```

### Instantaneous
```{r}
if (load) {
  summary(est[[3]])
} else {
summary(fit.i)
}
```

## MCMC diagnostics

### Main
```{r}
#Edit the nwstats.formula to reflect model formula and other stats want to evaluate
(dx_main <- netdx(est[[1]], nsims = 10, nsteps = 1000, ncores = 4))
plot(dx_main, type="formation")
plot(dx_main, type="duration")
plot(dx_main, type="dissolution")
```

### Persistent
```{r}
#Edit the nwstats.formula to reflect model formula and other stats want to evaluate
(dx_pers <- netdx(est[[2]], nsims = 10, nsteps = 1000, ncores = 4))
plot(dx_pers, type="formation")
plot(dx_pers, type="duration")
plot(dx_pers, type="dissolution")
```

### Instantaneous
```{r}
#Edit the nwstats.formula to reflect model formula and other stats want to evaluate
(dx_inst <- netdx(est[[3]], nsims = 10, nsteps = 1000, ncores = 4))
plot(dx_inst, type="formation")
```


